### 2024-01-06 written/paper.tex
added _written_ folder from previous paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12,
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Pricing Kernels and Risk Premia implied in Bitcoin Options},
  pdfauthor={Julian Winkel; Wolfgang K. Härdle},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin = 2.5cm]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{float}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{subfig}
\usepackage{caption}
\usepackage{eucal}
\floatplacement{figure}{H}

\title{Pricing Kernels and Risk Premia implied in Bitcoin Options}
\author{Julian Winkel\footnote{International Research Training Group 1792;
  Humboldt-Universität zu Berlin,
  \href{mailto:julian.winkel@hu-berlin.de}{\nolinkurl{julian.winkel@hu-berlin.de}}} \and Wolfgang K. Härdle\footnote{BRC Blockchain Research Center,
  Humboldt-Universität zu Berlin, Berlin, Germany; Sim Kee Boon
  Institute, Singapore Management University, Singapore; WISE Wang Yanan
  Institute for Studies in Economics, Xiamen University, Xiamen, China;
  Dept. Information Management and Finance, National Chiao Tung
  University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
  and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
  23020303 gratefully acknowledged,
  \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
\date{21 November 2022}

\begin{document}
\maketitle

\newcommand{\quantnet}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,}
\newcommand{\quantinar}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/quantinar_logo.png}}\,}

\definecolor{bittersweet}{rgb}{1.0, 0.44, 0.37} 
\definecolor{ao}{rgb}{0.0, 0.5, 0.0}
\definecolor{bananamania}{rgb}{0.98, 0.91, 0.71}
\definecolor{bluegray}{rgb}{0.4, 0.6, 0.8}

\pagenumbering{roman}

\begin{abstract}

\singlespacing 
Bitcoin Pricing Kernels (PK) are estimated using a novel data set from Deribit, the leading Bitcoin options exchange. The PKs, as the ratio between risk-neutral and physical density, dynamically reflect the change of investor preferences. Thus the PKs improve the understanding of investor expectations and risk premium in a new asset class. Bootstrap-based confidence bands are estimated in order to validate the results. Investors are heterogeneous in their risk profiles and preferences with respect to volatility and investment horizon. The empirical PKs turn out to be U-shaped for short-dated instruments and W-shaped for long-dated instruments. We find that investors are willing to pay a substantial risk premium to insure themselves against short-term price movements. The risk premium is smaller for longer-dated instruments and their traders are risk averse. The shape of the empirical PKs reveals the existence of a time-varying risk-premium. The similarity between the shape of empirical PKs for Bitcoin and other markets that represent aggregate wealth shows that Bitcoin is becoming an established asset class.

 \medskip
 \textbf{Keywords:} Bitcoin, Deribit, pricing kernel, risk aversion, speculation, hedging  \\
 \indent \textbf{JEL Classification:} C14, C50, G10  \\
 \bigskip

\end{abstract}

\pagenumbering{arabic}

\newpage

\section{Introduction}

The valuation of digital currencies has been a question that predated
its first representative, Bitcoin. Upon the creation of Bit Gold, Szabo
(2008) envisioned its value to arise from an interplay between the
benefits of the two entities which foremost represent value: cash and
metal. The argument put forward was that metal bears an inherent value
that is largely independent of trusted third parties. However, the
unwieldiness of metal incurs a relatively high transaction cost when
used as a means of exchange. (Unbacked) Cash, on the other hand, draws
its value largely from the trust in a third party's acceptance. The
combination of the two elements, coming in the form of a scarce digital
resource that is governed in a trustless system, has been passed on to
Bitcoin (BTC) and other Cryptocurrencies (CC).

Since the inception of BTC as proposed by Nakamoto (2009), various
arguments have been made on its valuation. Apart from the benefit of a
trustless system, the arguments typically include the production cost of
a block (Hayes 2019), the benefit of borderless transactions (Deng 2020;
Stellar Development Foundation 2022), the value of an inflation hedge
(Choi and Shin 2022), network effects (Chen and Vinogradov 2021; Gandal
and Halaburda 2016) or expectations about future price developments
(Blau 2017; Smaniotto and Neto 2022).

In addition to the former valuation approaches, we offer new insights by
means of the BTC derivatives market which has emerged over the course of
the last years. Since derivatives markets are particularly rich in
information, their evolution provides a unique opportunity to assess the
BTC market valuation through the application of proven econometric
techniques. Key information about preferences and forward looking
decisions are state price densities (SPD), that can be estimated from
option prices. SPDs yield risk-neutral probabilities, under which
investors price derivatives. They provide the key to pricing exotic or
illiquid options in an arbitrage-free manner (Aït-Sahalia and Lo 1998)
and offer insight into changing expectations about future developments.
In conjunction with the physical density (PD) of Bitcoin returns, the
resulting pricing kernels (PK) can be calculated. The shape and
evolution of PKs over time discloses investor expectations under
different market circumstances and gives insight into time varying
preferences. We present the first paper that is based on real Bitcoin
option data, inferring and disclosing investor preferences following
hypothesizing papers on bootstrap-based confidence bands for empirical
PKs (Härdle et al. 2014) and cryptocurrency option pricing under an SVCJ
model (Hou et al. 2020).

BTC derivatives markets can already be regarded as efficient information
processing mechanisms (Alexander et al. 2022). Among those markets,
\href{https://www.deribit.com/}{Deribit} is the leading crypto option
exchange as measured by open interest and trading volume. As of
2022-07-25, Deribit manages more than 90\% of the BTC option volume
which translates over a 30 day window into an average 24-hour trading
volume of over 331.8 million USD (Skew.com 2022). The competitors
LedgerX, OKEx, CME, bit.com and Binance are contributing respective
averages of 1.9, 15.7, 13.2, 1.5, 0.582 million USD.

A particularly interesting property of the BTC options market is its
decentralized nature. Trading on Deribit is largely dominated by
retailers. Despite an ongoing decline of retail market share in favor of
institutions (Coinbase 2022), who are cautious to invest in highly
volatile and unregulated assets, the options market on Deribit remains
driven by retailers: As of 2022-07-25, 86.65\% of the volume is
attributed to retail, whereas 9.16\% and 1.19\% are attributed to
investors and whales (Deribit 2022a). Deribit classifies market
participants according to their share of the circulating BTC supply.
According to Deribit's classification, a ``whale'' is an entity that
owns more than 1\% of the supply on Deribit, an ``investor'' owns
between 0.1\% and 1\% and a ``retailer'' owns less than 0.1\%.
Considering the retail share in trading volume in conjunction with
Deribit's dominating market share over the competition, we figure that
the Bitcoin price is mainly driven by retail. Analyzing a retail-driven
marketplace renders the study of digital currencies like BTC unique and
different from the well studied equity options markets, where retail
only has a minor influence (Bloomberg 2021).

Another interesting feature of the market under consideration is not
just the dominating presence of retailers, but their easy access to
leverage for speculation. Since Deribit is by design a margin-trading
platform, levers of up to 100 are available for longs. Easy access to
leverage could suggest the existence of the leverage effect if investors
were risk affine. However, we cannot confrm a leverage effect to be
present in the time frame under consideration.

All underlying code is available on \href{quantlet.com}{quantlet.com}
and a corresponding courselet is available on
\href{quantinar.com}{quantinar.com}.

\section{Pricing Kernels}

Assume a risky asset with a stochastic price process
\(\{S_t\}_{t \in \mathbb{N}}\) and a risk-free interest rate
\(\{r_t\}_{t \in \mathbb{N}}\) in a complete market. Following the
second Fundamental Theorem of Asset Pricing, a unique
martingale-equivalent measure \(Q\) exists in the described setting,
under which derivatives can be priced in an arbitrage-free manner (Huynh
et al. 2002; Pascucci and Agliardi 2011).

Let \(C_t\) be the price at time \(t\) of a contingent claim with payoff
\(\psi(\cdot)\) on the risky asset (underlying), which has a maturity at
\(T\) and a time-to-maturity \(\tau = T-t\). For simplicity assume a
constant interest rate \(r_t = r\). The price of any such contingent
claim can be expressed as the discounted value of expected future
payoffs, weighted with their respective probabilities of occurrence. The
expectation operator is conditional on the information set at \(t\)
under the equivalent martingale probability \(Q\)

\begin{equation}
C_t = e^{-r \tau} \mathbb{\sf{E}}^Q[\psi(S_T)] = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) f_t^Q(u) du
\end{equation}

Transforming the risk-neutral measure \(Q\) to the physical measure
\(P\) yields the PK by Itô's Lemma.

\begin{equation}
C_t = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) q(u) du = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) p(u) K(u) du
\end{equation}

where the PK \(K(\cdot)\) is defined as \(\frac{q(\cdot)}{p(\cdot)}\)
and for simplicity of notation we write \(q(\cdot)\) for
\(\frac{\partial Q}{\partial t}(\cdot)\) and drop the sequence \(r_t\).

The PK can therefore be approximated by the ratio between the
risk-neutral density and the physical density. This process is discussed
and executed in the following sections.

\section{Nonparametric Estimation of State Price Densities}

\subsection{Derivation}

As stated by Breeden and Litzenberger (1978), a SPD can be estimated via
the second derivative of the call price function
\(\psi(S_T) = \max(S_T - K, 0)\) with respect to the strike price \(K\).

\begin{equation}
\frac{\partial ^2 C_t}{\partial K^2}\bigg\rvert_{K = S_t} =  q(S_T)e^{-r \tau}
\end{equation}

A variety of call prices \(C\) with different strikes \(K\) is required
in order to calculate the complete SPD \(q\). The present value of a
call can be priced in implied volatility (IV). In conjunction with the
vector (time-to-maturity \(\tau\), strike \(K\), spot \(S\), interest
rate \(r\)), the market call price can be calculated.

IV is estimated as a function of time-to-maturity and moneyness in the
following section. Collapsing spot price \(S\) and strike \(K\) into a
single variable \(M = \frac{K}{S}\) reduces the effect of the curse of
dimensionality. Similarly, we collapse \(S\) and the interest rate \(r\)
into a Futures price.

\subsection{Local Polynomial Estimation of the IV Surface}

Assume that the implied volatilites have some noise added (Huynh et al.
2002; Rookley 1997).

\begin{equation}
\sigma (M, \tau) = g(M, \tau) + \sigma^{*}(M, \tau)  \varepsilon
\end{equation}

with a standardized error random variable \(\varepsilon\), moneyness
\(M\), \(\tau\) and \(\varepsilon\) independent and
\(\sigma^{*}(M, \tau)\) being the scaling of the error term given \(M\)
and \(\tau\). Suppose \(g\) is smooth, i.e.~it can be approximated using
Taylor's Theorem.

Taylor expansion of \(g\) in a neighborhood of \((M_0, \tau_0)\):
\begin{equation}
\begin{aligned}
g(M, \tau) = g(M_0, \tau_0) +
\frac{\partial g}{\partial M}(M-M_0) + 
\frac{1}{2} \frac{\partial^2 g}{\partial M^2}(M-M_0)^2 + \\
\frac{\partial g}{\partial \tau}(\tau - \tau_0) + 
\frac{1}{2} \frac{\partial^2 g}{\partial \tau^2}(\tau - \tau_0)^2 + \\ 
\frac{\partial^2 g}{\partial M \partial \tau}(M-M_0)(\tau - \tau_0)
\end{aligned}
\end{equation}

The functional relationship between the IV surface \(\sigma\) and \(M\)
and \(\tau\) can now be approximated using a Weighted Least Squares
Estimator (WLSE), minimizing the objective function

\begin{equation}
\operatorname{arg}\, \underset{\beta}{\operatorname{min}}{(\sigma - X\beta)^\top W (\sigma - X\beta)}
\end{equation}

where
\(W = \text{diag}(\mathcal{K}_{h_m, h_\tau}(M_j - M_0, \tau_j - \tau_0))\)
for a Gaussian kernel \(\mathcal{K}\) with bandwidths \(h_m\) and
\(h_\tau\). \(\sigma\) is the \(n \times 1\) vector of observed implied
volatilities, \(\beta\) is the vector of the local polynomial
coefficients.

\[
X = 
\begin{pmatrix}
1 & (M_1 - M_0) & (M_1 - M_0)^2 & (\tau_1 - \tau_0) & (\tau_1 - \tau_0)^2 & (M_1 - M_0) (\tau_1 - \tau_0) \\
\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \\
1 & (M_n - M_0) & (M_n - M_0)^2 & (\tau_n - \tau_0) & (\tau_n - \tau_0)^2 & (M_n - M_0) (\tau_n - \tau_0) \\
\end{pmatrix}
\]

The resulting WLSE is

\begin{equation}
\hat{\beta} = (X ^\top WX)^{-1}X ^\top W \sigma
\end{equation}

Following Härdle et al. (2014), a window of the last 500 daily returns
(based on \(\tau\)) is used to calculate a nonparametric Kernel Density
Estimator for the PD.\\
\href{https://quantinar.ro/course/103/statistics-of-financial-markets}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/quantinar_logo.png}}\,Chapter 24}

\section{Literature Review}

Breeden and Litzenberger (1978) derive SPDs using Arrow-Debreu prices
and Butterfly Spreads. Their paper was the cornerstone for the now
existing vast literature on estimation of SPDs. Without requiring a
parametric form for SPDs, Rookley (1997) who developed a nonparametric
estimation method. IV skews are estimated by decomposing the functional
relationship between IV, moneyness and time-to-maturity \(\tau\). In
this manner it is possible to derive the SPD at every point in a robust
way. Aı̈t-Sahalia et al. (2001) estimate PKs from S\&P500 options data
and the according return series in order to assess the efficiency of the
options market. Departures from SPD and PD are used to identify
inefficient pricing. They design a trading strategy, exploiting the
skewness and kurtosis of the densities. The strategy is shown to have a
high Sharpe Ratio. Grith et al. (2009) propose a systematic modeling
approach to study the evolution of PKs over time. With European DAX
data, a series of empirical PKs is estimated from 2003 until 2006. While
the risk-neutral density is inferred using Rookley's method, the PD is
estimated with a GARCH model. A common shape is identified and
deviations of the time varying EPKs are studied. The deviations between
individual PKs are described using a set of parameters for horizontal
and vertical shifts. The relationship between PKs and Arrow-Pratt
measure of Absolute Risk Aversion (ARA) give insight into investor's
risk aversion. In a related research, Härdle et al. (2014) derive
bootstrap-based confidence bands for nonparametrically estimated PKs.

Inverse Options, meaning options settled in kind of the underlying, are
dominant in the crypto world. Settlement of BTC options in terms of BTC
changes the payoff function of the option from \(\max(S_T - K; 0)\) to
\(\max(\frac{S_T - K}{S_T}; 0)\) and thus changes the contract's net
present value. Alexander and Imeraj (2021) adjust Black-Scholes prices
and hedge ratios to inverse options. However, it is argued that traders
are erroneously applying vanilla Black-Scholes valuation instead of the
corrected prices - perhaps because of being unaware of the concept. We
have decided to use with the standard, non-inverse Black Scholes pricing
for multiple reasons. Alexander and Imeraj (2021) argue that traders are
perhaps unaware of the difference. Since we are inferring investor
expectations, we figure that it is more appropriate to infer pricing
kernels under the same Black Scholes prices that the investors use.
Additionally, it is likely that many traders actually hedge their
overall Bitcoin exposure. This would negate the ``inverse'' part of the
option. Furthermore, reviewing the differences in pricing compared to
the adjusted prices, we find that the difference is small in the absence
of extreme moves in the underlying. This was not the case in the time
period under consideration.

Hou et al. (2020) price BTC options under an SVCJ model. Their results
emphasize the tail risk introduced by jumps in the underlying. Jumps in
particular introduce market incompleteness, but anonymity of
transactions may be relevant as well. Chen and Vinogradov (2021) derive
PKs and the impact of market incompleteness on risk premia. They state
that a key property of cryptocurrency valuation is the user's anonymity
(or pseudonymity), which is simultaneously the source of value and
incompleteness in the respective market. They argue that hedging an
anonymous transaction would require an identity disclosure. This
contradiction may introduce an effectively unhedgeable event.

\section{Deribit}

Deribit, a margin-trading platform for futures and options, has been
launched in June 2016 in the Netherlands and is currently incorporated
in Panama. As of time of the writing, Deribit is the largest BTC option
exchange (Skew.com 2022). For both types of derivatives, BTC and ETH are
the underlying as well as the currency in which settlement is conducted.
This allows to view them as inverse options.

\begin{center}
\begin{figure}
\includegraphics[width=0.9\textwidth]{/Users/julian/src/up/spd/plot/Skew_BTC_Open_Interest_cut.pdf}
\caption[Open Interest in BTC Options per Exchange.]%
{Open Interest in BTC Options per Exchange. Snapshot from \href{https://analytics.skew.com/dashboard/bitcoin-options}{skew.com} on 2022-01-16.  \color{bittersweet}{Deribit}, \color{ao}{LedgerX}, \color{bananamania}{CME}, \color{bluegray}{bit.com}. }
\label{fig: ivtest}
\end{figure}
\end{center}

\subsection{Bitcoin Option Contract Specifications}

Deribit offers cash-settled European-style options. The underlying is a
synthetic index, whose exact composition is described in the data
section. Settlement is first calculated in USD and then conducted in
kind of the underlying. E.g. a BTC call with a strike of \(10000\) and a
settlement value of \(12000\) at maturity will result in a cashflow of
\(2000\) USD, which is equivalent to \(\frac{1}{6}\) BTC (excluding
transaction cost). The settlement value is defined as the average of the
underlying BTC index for the last 30 minutes before settlement. Each
contract has a lot size of 1 BTC and is settled at 8am UTC on the
respective maturity date. Maturity dates have a daily, monthly,
quarterly and annual frequency. Deribit is the only derivatives exchange
to offer daily options. Instruments are trading 24/7 with a tick size of
0.0005 BTC. Due to the automatic usage of margin-trading, margin-based
liquidation of positions is possible. Initial margin and maintenance
margins are both zero for long positions. For short positions, initial
margin is required (Deribit 2022b). In case of liquidation, a penalty is
applied to the defaulting party, whose proceeds are paid into the
Deribit Insurance Fund (Deribit 2020a).

Trading and deliveries on Deribit are subject to fees (Deribit 2022c).
The applied fees generally vary depending on whether the order was a
liquidity maker or taker. However, for Bitcoin options they are equal.
Trading fees are 0.03\% of the underlying or 0.0003 BTC per options
contract. The fees constitute a maximum of 12.5\% of the contract's
value.

\section{Data}

\subsection{Data Structure}

The dataset consists of 8,444,664 order book snapshots, which have been
collected from Deribit in the time from 2021-04-01 until 2022-04-01. The
snapshots were captured via the Deribit API V2. The data base is
available on the
\href{https://blockchain-research-center.com}{Blockchain Research Center (BRC)}.
The full data set includes all parameters that the
\href{https://docs.deribit.com/#deribit-api-v2-1-1}{Deribit API V2}
returns at the time of collection under the methods

\begin{itemize}
\tightlist
\item
  \{\it public/get\_last\_trades\_by\_instrument\_and\_time\}
\item
  \{\it public/get\_order\_book\}
\end{itemize}

Most importantly the results include

\begin{itemize}
\tightlist
\item
  Timestamps
\item
  Greeks
\item
  Implied Volatility
\item
  Tick Direction
\item
  Order Type
\item
  Volume
\item
  Instrument Price
\item
  Strike
\item
  Spot
\end{itemize}

High-frequent order book changes and executed trades are captured for
options and futures whose underlying is BTC. Values of the underlying
synthetic BTC USD Index are also saved. The underlying is calculated as
an equally-weighted BTC/USD price of eleven major crypto exchanges,
namely Binance, Bitfinex, Bitstamp, Bittrex, Coinbase Pro, FTX, Gemini,
Huobi, Itbit, Kraken, LMAX Digital, OKEx. Individual feeds can be
excluded due to administrative decisions or in case if invalid data.
Remaining feeds are sorted, truncated around the median price and
weighted (Deribit 2020b).

\subsection{Data Integrity}

Data integrity plays a crucial role in crypto markets. Mark Carney, the
chair of the Financial Stability Board and head of the Bank of England,
warned that wash trading, pump and dumps and spoofing, known as outlawed
manipulation techniques in equity markets, are also present in crypto
and pose a risk to financial stability (Rodgers 2019). Wash trading is
used to increase trading volume and thus artificially increase demand. A
spoofer submits market non-bona fide price quotes in order to cause
artificial price volatility (Sar 2017). Pump \& Dump is a form of
securities fraud in which a group of traders rapidly and artificially
inflate a price in order to offload their previously acquired inventory.
Since Pump \& Dump schemes require low liquidity (in the underlying), we
can exclude this possibility for Bitcoin (La Morgia et al. 2020).

Aloosh and Li (2019) find evidence for exchange-driven inflated volume,
generated by wash trades, to market themselves under the guise of
liquidity. Cong et al. (2019) report that on average 70\% of volume on
decentralized exchanges is fake due to the use of wash trading.
According to Bitmex (2019), up to 95\% of trading volume on unregulated
exchanges is generated by wash trading. In order to ensure data
integrity, we exclusively use orderbooks instead of executed trades in
order to filter possible cases of wash trading.

To address the potential issue of spoofing, we adopt an approach related
to Tuccella et al. (2021). They attempt to identify spoofing on
cryptocurrency exchanges using a GRU model. Their predictors are a
function of the amount of cancelled orders relative to the cumulative
order size on each side of the order book. Since Bitcoin derivatives
order books do not have the same amount of depth as spot or futures
markets, we employ a stricter method and exclude all orders whose
lifetime does not exceed two seconds. We find that less than 5\% of
orders are filtered due to short order lifetime. We figure that
traditional spoofing techniques, based on the rapid submission and
cancellation of orders, are difficult to implement due to Deribit's rate
limits (Deribit 2023). Users with less than 1 million USD in
7-day-turnover can only post five matching engine requests. These
include request for a buy or sell order or a corresponding cancellation.
Although the limits for a market maker (who could be allowed to post 30
requests per second given a turnover of 25 million USD in 7 days) are
considerably higher, the market maker must still meet the quoting
requirements for a large range of instruments. This effectively
restricts the influence that single entities can have on certain
instruments via the rapid submission and cancellation of orders and
explains the rarity of such events in our dataset.

\subsection{Preprocessing}

Although market makers are obliged to quote most instruments for the
majority of the time, some may not be quoted at all or only be quoted at
the cost of a large spread (Deribit 2020c). For Far-Out-of-Money (FOTM)
contracts, when the minimum tick size exceeds the market IV, one can
observe bids for 0\% IV. Cases of quotes for 0\% IV and all duplicates
are excluded from the data set. Since the majority of option trading
volume concentrates on instruments with short or medium time-to-maturity
\(\tau\), we restrict \(\tau\) to be smaller or equal than one quarter
of a year. \(\tau\) is normalized on the span of a year. Instruments are
grouped according to their time-to-maturity, over a range of 0, 1, 2, 4,
8 weeks. We restrict moneyness \(M = \frac{K}{S}\) to the interval
\([0.7, 1.3]\) in order to exclude the influence of high-volatility
observations which could be unreliable (Grith et al. 2009).

Call options are exclusively used in order to estimate the IV surface in
Rookley's method. Put-Call-Parity ensures arbitrage-free call option
prices. However, we do not use Put-Call-Parity to increase our data
sample. Conversion of option prices via Put-Call-Parity could introduce
errors into our dataset due to market microstructure (MMN) noise. Our
high-frequent order book data is extracted via an API. Due to rate
limitations and a diverse amount of instruments, order book snapshots
cannot be taken simultaneously for all instruments. The data scraping
application successively iterates over all instruments and captures
changes in order books. While the resulting data base provides a clear
picture of order book data, it does not allow for a complete
reconstruction of all order books at all times. Without simultaneity,
volatility of the underlying and order competition within the spread
could change the prices of the corresponding instruments (required for
Put-Call-Parity) between the individual snapshots. A range of futures
may be available on Deribit, but only the perpetual futures contract is
actually liquid. The classic (non-perpetual) futures also price in the
settlement cost, which often causes them to trade in backwardation close
to maturity. But in spite of this, BTC options tend to be traded more
frequently when they are close to maturity. The combination of these
real-world limitations challenges the simple conversion via
Put-Call-Parity and could introduce errors into our dataset.
Furthermore, we do not see the necessity to use such a method as we have
sufficient call option data to compute the IV surface from which we
sample option prices.

\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Preprocessing}

\section{Volatility}

In accordance with Masset (2011) and Eraker (2021), the list of
well-established stylised facts on volatility in traditional markets
include horizontal dependence of volatility, leverage effect, the
volatility premium and extreme events. Horizontal dependence of
volatility describes the tendency of local volatility clusters and the
tendence to mean-reversion. Both properties can be observed in the 7 day
rolling volatility. Sudden spikes in realized volatility form clusters
and are often followed by similar drops. The leverage effect can be
measured as a negative correlation between returns and volatility.
Phases of negative returns coincide with high volatility and vice versa.
The Pearson correlation between the underlying and realized volatility
is -12.59\%. The Pearson correlation between the underlying and the bid
(ask) IV is -16.11\% (-13.05\%). Due to the low absolute values of
correlation, the existence of a leverage effect is unlikely. However,
the sign matches the direction of a leverage effect. Considering the
large share of retailers with easy access to leverage, the lack of
significance is a surprising result. It is well known that, in general,
the IV exceeds the unconditional annualized standard deviation. This is
displayed in Figure \ref{fig: iv_comparison}. The difference between the
implied and realized volatility is commonly referred to as volatility
premium. The mean 7 day rolling volatility is 70.96\%, whereas the mean
IV at the bid and ask are 85.28\% and 93.57\%. Spikes in realized
volatility rarely exceed the ask of the IV. Consequently, the volatility
premium is shown to be substantial throughout the regarded time period.
Fat-tail events are priced in due to the classic volatility skew. This
is depicted in Figure \ref{fig: emp_ivsmile}, the empirical volatility
skew.

Since the data are high frequency order book snapshots with substantial
bid-ask spreads, we must address the issue of Market Microstructure
Noise (MMN). A simple estimate of realized volatility would increase
with our sample due to order competition within the spread. We resolve
the issue of MMN in our calculation of realized volatility by taking the
arithmetic mean after aggregating the implied volatility of bids and
asks on a daily base. Therefore the frequency is matching the underlying
BTC index. The formula for annualized, realized volatility of price
\(p\) over a window of \(w\) days is

\begin{equation}
\sigma_w = \sqrt{\frac{1}{w}\sum_{t=1}^w{(\log{p_t} - \log{p_{t-1})}^2}} \sqrt{\frac{365}{w}}
\end{equation}

Annualization is based on 365 days since Bitcoin options are traded
continuously on Deribit.

The term structure itself is easier to assess when regarding ATM-options
in a series of dates (Figure 6). ATM-options are defined as those
options, whose moneyness falls in the interval \([0.9, 1.1]\). A typical
term structure of the Bitcoin options reveals a high level of implied
volatility for shorted-dated options. For options with a
time-to-maturity of three days or more, implied volatility drops sharply
compared to the initial level. Naturally, IV is increasing with
time-to-maturity.

\begin{center}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/iv_comparison_up.png}
\caption[Implied Volatiliy vs. Realized Volatility on Deribit]%
{Implied volatility vs. realized volatility. Realized volatility is annualized and regarded in a 7 day window.
IV is calculated as the average of observed orderbooks at the bid and ask. Described data filters apply. {\color{blue} Ask IV}, {\color{green} Bid IV}, {\color{red} 7 Day Rolling Volatility}.}
\label{fig: iv_comparison}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/src/vola.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Volatility}
\end{figure}
\end{center}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/vola_2021-05-23.png}
\caption[Empirical Volatility Surface]{Volatility Skew shown in the empirical Volatility Surface on 2021-05-23}
\label{fig: emp_ivsmile}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/vola_2021-09-08.png}
\caption[Empirical Volatility Surface 2]{Volatility Skew shown in a calmer period on 2021-09-08}
\label{fig: emp_ivsmile2}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/src/vola_plots.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,IV Smile}
\end{figure}
\end{centering}

\begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-010.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-020.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-030.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-040.08.png}

\end{minipage}
\begin{minipage}{0.5\textwidth}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-050.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-060.08.png}
    \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-070.08.png}
        \centering
    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-080.08.png}

\end{minipage}
    \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}

\label{ATM Term Structure}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}

\pagebreak
\newpage
\section{Empirical Pricing Kernels}

Instruments are grouped by time-to-maturity in order to summarize the
findings. All instruments with less than one week to maturity are
classified as having less than one, between one and two, between two and
three, between three and four and between five and eight weeks to
maturity. We typically observe U-shaped PKs for short-term maturities.
In a similar fashion to the oil market, investors perceive short-term
price changes in any direction as undesirable and prefer to hedge their
risk (Christoffersen et al. 2021). For short-dated instruemnts, option
writers are asking for substantial risk premia in order to reflect
unhedgeable risks, such as jumps in the underlying (Hou et al. 2020).

We find a differnet shape for longer-dated instruments. Typically, PKs
in traditional markets are monotonically decreasing. This results from
human risk aversion; investors are willing to insure themselves against
losses and have a preference for smooth consumption curves. However, PKs
outside of index options markets are not well studied (Cuesdeanu and
Jackwerth 2018). Grith et al. (2009) compartmentalize a pricing kernel
in two segments around a possible breakpoint. Testing an unrestricted
model against GMM estimates of the restricted one, they reject
monotonicity of the empirical PK in four out of five cases (performing a
D-test). The phenomenon of having a decreasing slope, although with
locally increasing sections in empirical PKs is called the pricing
kernel puzzle. We observe a similar behavior and extend the existing
literature on the pricing kernel puzzle to a new asset class.

Since the empirical PKs for short-dated instruments are U-shaped, we
figure that investors are willing to pay a high risk premium in order to
insure immediate price risks. With an increasing maturity of the
instrument, the shape of the empirical PK resembles a ``W'' or
``tilde''. This corresponds to a a lesser willingness to pay a risk
premium.\\
The dynamic of the empirical PKs also reveals the existence of a
time-varying risk premium in BTC markets. The observed PK shapes are
closely aligned with the results reported in Cuesdeanu and Jackwerth
(2018). However, their object of study are traditional markets, such as
major indices which are highly correlated with aggregate wealth. We
conclude that, due to the similarities of the empirical PKs, BTC is well
on its way to becoming an established asset class. It may prove to be
much rather a store of value than it is currently given credit for.

Apart from the discussion of results, deviations between PD and SPD can
be interpreted as trading opportunities. (Blaskowitz et al. 2004) design
and evaluate trading strategies based on deviations between PD and SPD.
Estimated PKs could be used by traders employing so-called Skewness or
Kurtosis trades. Nevertheless, traders must recognize the hidden cost of
employing such strategies in terms of substantial hedging cost, e.g.~in
the form of volatility and large spreads.

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=0.png}
\caption[Empirical Pricing Kernel - 0 Weeks to Expiration]{Pricing Kernels with less than one Week to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=1.png}
\caption[Empirical Pricing Kernel - 1 Week to Expiration]{Empirical Pricing Kernel - 1 Week to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=2.png}
\caption[Empirical Pricing Kernel - 2 Weeks to Expiration]{Empirical Pricing Kernel - 2 Weeks to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=3.png}
\caption[Empirical Pricing Kernel - 3 Weeks to Expiration]{Empirical Pricing Kernel - 3 Weeks to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=4.png}
\caption[Empirical Pricing Kernel - 4 Weeks to Expiration]{Empirical Pricing Kernel - 4 Weeks to Expiration}
\end{figure}
\end{centering}

\begin{centering}
\begin{figure}
\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=8.png}
\caption[Empirical Pricing Kernel - 5-8 Weeks to Expiration]{Empirical Pricing Kernel - 5-8 Weeks to Expiration}
\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
\end{figure}
\end{centering}

\pagebreak
\newpage

\section{Bootstrap-based Confidence Bands}

Having computed a large set of empirical PKs with varying maturities, it
should be ensured that the observed features are not mere artefacts. A
useful tool to assess the validity of our estimated PKs are
bootstrap-based confidence bands. Following the derivation of Härdle et
al. (2014), confidence bands at any confidence level can be derived via
the ``wild bootstrap method''. Figure
\ref{fig:Bootstrapped Confidence Bands - 2 Days} until Figure
\ref{fig:Bootstrapped Confidence Bands - 84 Days} are depicted
exemplarily for the whole set. Confidence bands are tighter around the
PKs when time to maturity increases. PKs are also flatter with growing
time to maturity.

The concept of bootstrapping PK can be introduced by linearization of
the PK. Stochastic deviation of the PK can be linearised into a
stochastic part, containing the estimator of the SPD and a deterministic
part containing the expectation of the physical density. Convergence of
both parts can be proven separately.

\[
\widehat{K}(x) = \frac{\widehat{q}(x)}{\widehat{p}(x)} 
\]

\[
\begin{aligned}
\underset{x \in E}{\operatorname{sup}} \lvert \widehat{K}(x) - K(x) \rvert = \underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}(x) - q(x)}{p(x)} - \frac{\widehat{p}(x) - p(x)}{p(x)} * \frac{q(x)}{p(x)} - \frac{\{\widehat{q}(x) - q(x)\} \{\widehat{p}(x) - p(x)\} }{p^2(x)} \rvert  \\
+ {\scriptstyle \mathcal{O}_p}[\operatorname{max}((n_p h_{n_p}/\log)^{-1/2} + h^2_{np},h_{n_q}^{-2} \{ n_q h_{n_q} / \log{n_q} \}^{-1/2} + h^2_{n_q})]
\end{aligned}
\]

Consider the leading term of \[
\underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}(x) - q(x)}{p(x)} \rvert
\]

Resample data from the smoothed bivariate distribution of strike and
moneyness (X,Y)

\[
{\widehat{f}(x,y)} = \frac{\widehat{\sigma_X}}{n_q h^2_{n_q}\widehat{\sigma_Y}} 
\Sigma_{i=1}^{n_q} K
\{ 
\frac{X_i - x}{h_{n_q}}, 
\frac{(Y_i - y)\widehat{\sigma_X}}{h_{n_q}\widehat{\sigma_Y}}
\}
\]

Using the resampled data, calculate the bootstrap analogue

\[
\underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}^*(x) - \widehat{q}(x)}{p(x)} \rvert
\]

where
\(\underset{x \in E}{\operatorname{sup}} \lvert\widehat{q}^*(x) - \widehat{q}(x) \rvert\)
converges to the Gumbel distribution at an unfortunately slow rate of
\(\frac{1}{\log n_q}\) (Hall 1991).

\begin{minipage}{.5\textwidth}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0055.pdf}
    \captionof{figure}{2 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 2 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0192.pdf}
    \captionof{figure}{7 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 7 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0384.pdf}
    \captionof{figure}{14 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 14 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0575.pdf}
    \captionof{figure}{21 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 21 Days}

\end{minipage}
\begin{minipage}{0.5\textwidth}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0767.pdf}
    \captionof{figure}{28 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 28 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.1534.pdf}
        \captionof{figure}{56 Days to Maturity.}
    \label{fig:Bootstrapped Confidence Bands - 56 Days}
    \centering
    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.2301.pdf}
        \captionof{figure}{84 Days to Maturity. \color{red}{Empirical Pricing Kernels} with \color{blue}{bootstrapped Confidence Bands} on 2021-12-31.}
    \href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
    \label{fig:Bootstrapped Confidence Bands - 84 Days}
\end{minipage}

\pagebreak
\newpage

\section{Conclusion}

Empirical PKs have been estimated using Rookley's Method on a dataset of
order book snapshots from Deribit, the leading BTC options market.
Bootstrap-based confidence bands have been estimated in order to
validate the results.

We assess the presence of well-established stylized facts of volatility
in the BTC market. We find horizontal dependence of volatility, meaning
that volatility tends to cluster and revert to the mean. The difference
between implied and realized volatility, commonly referred to as the
volatility premium, is substantial. Realized volatility rarely exceeds
the implied volatility. The IV term structure is found to be
traditional. Despite market participant's easy access to leverage, we
cannot confirm the existence of a leverage effect.

Our analysis extends the literature to a new asset class and contributes
to the pricing kernel puzzle. We are able to replicate empirical results
from the analysis of PKs in traditional markets, which are highly
correlated with aggregate wealth. Their similarity to PKs estimated from
BTC options indicates that BTC is becoming an established asset class.

Furthermore, our analysis sheds light on the BTC valuation and
risk-aversion of the retail traders. BTC option traders mostly consist
of retailers who are heterogeneous in their risk profile. The price of
short-dated instruments includes a high risk premium. Such instruments
reflect the anticipation of jumps in the underlying. These instruments
would be traded by either very risk-averse or risk-affine traders.
Long-dated instruments are employed as classic hedging instruments.
While a substantial risk premium is paid by traders in order to insure
themselves against falling prices, they are additionally (but to a
lesser degree) insuring themselves against sharply rising prices. Thus
investors are also hedging their risk of being priced out of a dynamic
market.

Several extensions of the presented research are available for the
future. Among those, we would find an extended dataset insightful, that
could support estimation of PKs and their evolution over a longer time
frame and possibly describe the convergence to the PKs of established
markets. It would also be interesting to analyze the evolution of PKs
around stress events in order to get further insights into investor risk
aversion, anticipation of such events and trading opportunities.

\section{References}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-aitsahalia01optionprice}{}%
Aı̈t-Sahalia, Y., Wang, Y., \& Yared, F. (2001). Do option markets
correctly price the probabilities of movement of the underlying asset?
\emph{Journal of Econometrics}, \emph{102}(1), 67--110.
\url{https://doi.org/https://doi.org/10.1016/S0304-4076(00)00091-9}

\leavevmode\hypertarget{ref-ait_sahalia_wang1998}{}%
Aït-Sahalia, Y., \& Lo, A. W. (1998). Nonparametric estimation of
state-price densities implicit in financial asset prices. \emph{The
Journal of Finance}, \emph{53}(2), 499--547.
\url{https://doi.org/https://doi.org/10.1111/0022-1082.215228}

\leavevmode\hypertarget{ref-alexander2022net}{}%
Alexander, C., Deng, J., Feng, J., \& Wan, H. (2022). Net buying
pressure and the information in bitcoin option trades. \emph{Journal of
Financial Markets}, 100764.

\leavevmode\hypertarget{ref-inverse_options}{}%
Alexander, C., \& Imeraj, A. (2021, July). Inverse options in a
black-scholes world.
\url{https://doi.org/https://doi.org/10.48550/arXiv.2107.12041}

\leavevmode\hypertarget{ref-aloosh}{}%
Aloosh, A., \& Li, J. (2019). Direct evidence of bitcoin wash trading.
\emph{Theory of Probability \& Its Applications, 5, 285-301}.
\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3362153}

\leavevmode\hypertarget{ref-bitmex}{}%
Bitmex. (2019). Presentation to the u.s. Securities and exchange
commission on wash trading.
\url{https://www.sec.gov/comments/sr-nysearca-2019-01/srnysearca201901-5164833-183434.pdf}.
Accessed 18 January 2022

\leavevmode\hypertarget{ref-blase}{}%
Blaskowitz, O., Härdle, W. K., \& Schmidt, P. (2004). Skewness and
kurtosis trades. In (pp. 1--14).
\url{https://doi.org/10.1007/978-0-8176-8180-7_1}

\leavevmode\hypertarget{ref-speculation}{}%
Blau, B. M. (2017). Price dynamics and speculative trading in bitcoin.
\emph{Research in International Business and Finance}, \emph{41},
493--499.
\url{https://doi.org/https://doi.org/10.1016/j.ribaf.2017.05.010}

\leavevmode\hypertarget{ref-bloomberg-retail-share}{}%
Bloomberg. (2021, November 17). Retail traders slide back below 20\% of
market's total volume.
\url{https://www.bloomberg.com/news/articles/2021-11-17/retail-traders-retreat-as-choppy-markets-challenge-easy-profits}.
Accessed 24 August 2021

\leavevmode\hypertarget{ref-breeden_litzenberger78}{}%
Breeden, D. T., \& Litzenberger, R. H. (1978). Prices of
state-contingent claims implicit in option prices. \emph{The Journal of
Business}, \emph{51}(4), 621--651.
\url{http://www.jstor.org/stable/2352653}

\leavevmode\hypertarget{ref-coins_with_benefits}{}%
Chen, C. Y., \& Vinogradov, D. (2021). Coins with benefits: On
existence, pricing kernel and risk premium of cryptocurrencies.
\emph{Available at SSRN 3959984}.
\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3864578}

\leavevmode\hypertarget{ref-choi}{}%
Choi, S., \& Shin, J. (2022). Bitcoin: An inflation hedge but not a safe
haven. \emph{Finance Research Letters}, \emph{46}, 102379.
\url{https://doi.org/https://doi.org/10.1016/j.frl.2021.102379}

\leavevmode\hypertarget{ref-oil_spd}{}%
Christoffersen, P., Jacobs, K., \& Pan, X. (. (2021). The State Price
Density Implied by Crude Oil Futures and Option Prices. \emph{The Review
of Financial Studies}, \emph{35}(2), 1064--1103.
\url{https://doi.org/10.1093/rfs/hhab011}

\leavevmode\hypertarget{ref-cryptonews_bitcoin_retail_share}{}%
Coinbase, S., Cryptonews. (2022). Institutions \& retail compete for
bitcoin - whose hands are stronger?
\url{https://cryptonews.com/exclusives/institutions-retail-compete-for-bitcoin-which-is-the-biggest-9695.htm}.
Accessed 22 March 2022

\leavevmode\hypertarget{ref-decentralized_wash_trading}{}%
Cong, L., Li, X., Tang, K., \& Yang, Y. (2019). Crypto wash trading.
\emph{SSRN Electronic Journal}.
\url{https://doi.org/10.2139/ssrn.3530220}

\leavevmode\hypertarget{ref-jackwerth_pk}{}%
Cuesdeanu, H., \& Jackwerth, J. C. (2018). The pricing kernel puzzle:
survey and outlook. \emph{Annals of Finance}, \emph{14}(3), 289--329.
\url{https://doi.org/10.1007/s10436-017-0317-9}

\leavevmode\hypertarget{ref-cross_border_payments}{}%
Deng, Q. (2020). Application analysis on blockchain technology in
cross-border payment. In.
\url{https://doi.org/10.2991/aebmr.k.200306.050}

\leavevmode\hypertarget{ref-deribit-insurance-fund}{}%
Deribit. (2020a). Deribit insurance fund.
\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021

\leavevmode\hypertarget{ref-synthetic-btc-index}{}%
Deribit. (2020b). Deribit btc-usd index.
\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021

\leavevmode\hypertarget{ref-market-maker-obligations}{}%
Deribit. (2020c). Deribit market maker obligations.
\url{https://www.deribit.com/pages/docs/options}. Accessed 2 January
2021

\leavevmode\hypertarget{ref-deribit_retail_piechart}{}%
Deribit. (2022a). Deribit volume share.
\url{https://www.deribit.com/statistics/BTC/market-data}. Accessed 25
July 2022

\leavevmode\hypertarget{ref-deribit_margin}{}%
Deribit. (2022b). Deribit margin requirements.
\url{https://legacy.deribit.com/pages/docs/options}. Accessed 2 May 2022

\leavevmode\hypertarget{ref-deribit_fees}{}%
Deribit. (2022c). Deribit margin requirements.
\url{https://www.deribit.com/kb/fees}. Accessed 2 May 2022

\leavevmode\hypertarget{ref-deribit-rate-limit}{}%
Deribit. (2023). Deribit rate limits.
\url{https://www.deribit.com/kb/deribit-rate-limits}. Accessed 16 April
2021

\leavevmode\hypertarget{ref-vola_premium}{}%
Eraker, B. (2021). The volatility premium. \emph{Quarterly Journal of
Finance (QJF)}, \emph{11}(03), 1--35.
\url{https://EconPapers.repec.org/RePEc:wsi:qjfxxx:v:11:y:2021:i:03:n:s2010139221500142}

\leavevmode\hypertarget{ref-networkeffect}{}%
Gandal, N., \& Halaburda, H. (2016). Can we predict the winner in a
market with network effects? Competition in cryptocurrency market.
\emph{Games}, \emph{7}(3). \url{https://doi.org/10.3390/g7030016}

\leavevmode\hypertarget{ref-Grith09sim}{}%
Grith, M., Härdle, W. K., \& Park, J. (2009). Shape invariant modelling
pricing kernels and risk aversion.
\url{https://doi.org/10.2139/ssrn.2894289}

\leavevmode\hypertarget{ref-hall_1991}{}%
Hall, P. (1991). Edgeworth expansions for nonparametric density
estimators, with applications. \emph{Statistics}, \emph{22}(2),
215--232. \url{https://doi.org/10.1080/02331889108802305}

\leavevmode\hypertarget{ref-hayes}{}%
Hayes, A. S. (2019). Bitcoin price and its marginal cost of production:
Support for a fundamental value. \emph{Applied Economics Letters},
\emph{26}(7), 554--560.
\url{https://doi.org/10.1080/13504851.2018.1488040}

\leavevmode\hypertarget{ref-w2yo}{}%
Härdle, W. K., Okhrin, Y., \& Wang, W. (2014). Uniform Confidence Bands
for Pricing Kernels. \emph{Journal of Financial Econometrics},
\emph{13}(2), 376--413. \url{https://doi.org/10.1093/jjfinec/nbu002}

\leavevmode\hypertarget{ref-pricing_cryptocurrency_options}{}%
Hou, A. J., Wang, W., Chen, C. Y. H., \& Härdle, W. K. (2020). Pricing
Cryptocurrency Options*. \emph{Journal of Financial Econometrics},
\emph{18}(2), 250--279. \url{https://doi.org/10.1093/jjfinec/nbaa006}

\leavevmode\hypertarget{ref-xfg_spd}{}%
Huynh, K., Kervella, P., \& Zheng, J. (2002). \emph{Estimating
state-price densities with nonparametric regression} (SFB 373 Discussion
Papers No. 2002,40). Humboldt University of Berlin, Interdisciplinary
Research Project 373: Quantification; Simulation of Economic Processes.
\url{https://EconPapers.repec.org/RePEc:zbw:sfb373:200240}

\leavevmode\hypertarget{ref-pumpndump}{}%
La Morgia, M., Mei, A., Sassi, F., \& Stefa, J. (2020). Pump and dumps
in the bitcoin era: Real time detection of cryptocurrency market
manipulations. In \emph{2020 29th international conference on computer
communications and networks (icccn)} (pp. 1--9).
\url{https://doi.org/10.1109/ICCCN49398.2020.9209660}

\leavevmode\hypertarget{ref-vola_stylized_facts}{}%
Masset, P. (2011). Volatility stylized facts. \emph{SSRN Electronic
Journal}. \url{https://doi.org/10.2139/ssrn.1804070}

\leavevmode\hypertarget{ref-satoshi2009}{}%
Nakamoto, S. (2009). Bitcoin: A peer-to-peer electronic cash system.
\url{http://www.bitcoin.org/bitcoin.pdf}

\leavevmode\hypertarget{ref-fundamental-theorem-of-asset-pricing}{}%
Pascucci, A., \& Agliardi, R. (2011). PDE and martingale methods in
option pricing. In (pp. 429--495).

\leavevmode\hypertarget{ref-rodgers2019}{}%
Rodgers, T. (2019, April 4). 95 percent of volume could be wash trading
as bitcoin price surges.
\url{https://www.forbes.com/sites/tomrodgers1/2019/04/04/99-of-volume-could-be-wash-trading-as-bitcoin-takes-back-5000/?sh=4640bcbc23d5}.
Accessed 15 April 2023

\leavevmode\hypertarget{ref-Rookley97}{}%
Rookley, C. (1997). Fully exploiting the information content of intra
day option quotes: Applications in option pricing and risk management.

\leavevmode\hypertarget{ref-sar2017}{}%
Sar, M. (2017). Dodd-frank and the spoofing prohibition in commodities
markets.

\leavevmode\hypertarget{ref-deriv_volume}{}%
Skew.com. (2022). Open interest for bitcoin options over time. Skew is a
leading crypto data analytics platform for institutional clients.
\url{https://analytics.skew.com/dashboard/bitcoin-options}. Accessed 25
July 2022

\leavevmode\hypertarget{ref-brazilian_speculation}{}%
Smaniotto, E. N., \& Neto, G. B. (2022). Speculative trading in bitcoin:
A brazilian market evidence. \emph{The Quarterly Review of Economics and
Finance}, \emph{85}, 47--54.
\url{https://doi.org/https://doi.org/10.1016/j.qref.2020.10.024}

\leavevmode\hypertarget{ref-cross_border_stellar}{}%
Stellar Development Foundation. (2022). 2022 research reveals high
awareness and growing cross-border use of cryptocurrency in four key
markets.
\url{https://www.prnewswire.com/news-releases/2022-research-reveals-high-awareness-and-growing-cross-border-use-of-cryptocurrency-in-four-key-markets-301512401.html}.
Accessed 22 July 2022

\leavevmode\hypertarget{ref-nickszabo}{}%
Szabo, N. (2008). Bit gold.
\url{https://unenumerated.blogspot.com/2005/12/bit-gold.html}. Accessed
28 July 2022

\leavevmode\hypertarget{ref-tuccella2021}{}%
Tuccella, J.-N., Nadler, P., \& Șerban, O. (2021). Protecting retail
investors from order book spoofing using a gru-based detection model.

\end{document}

### 2024-01-07 written/paper.tex
writing

@@
 \usepackage{lmodern}
+\usepackage[table,xcdraw]{xcolor}
 \usepackage{amssymb,amsmath}
@@
 \hypersetup{
-  pdftitle={Pricing Kernels and Risk Premia implied in Bitcoin Options},
+  pdftitle={Empirical Option Returns and the risk-free Rate in Crypto Asset Markets},
   pdfauthor={Julian Winkel; Wolfgang K. Härdle},
@@
   \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
-\date{21 November 2022}
+\date{7 January 2024}
 
@@
 \singlespacing 
-Bitcoin Pricing Kernels (PK) are estimated using a novel data set from Deribit, the leading Bitcoin options exchange.
-The PKs, as the ratio between risk-neutral and physical density, dynamically reflect the change of investor preferences.
-Thus the PKs improve the understanding of investor expectations and risk premium in a new asset class.
-Bootstrap-based confidence bands are estimated in order to validate the results.
-Investors are heterogeneous in their risk profiles and preferences with respect to volatility and investment horizon.
-The empirical PKs turn out to be U-shaped for short-dated instruments and W-shaped for long-dated instruments.
-We find that investors are willing to pay a substantial risk premium to insure themselves against short-term price movements.
-The risk premium is smaller for longer-dated instruments and their traders are risk averse.
-The shape of the empirical PKs reveals the existence of a time-varying risk-premium.
-The similarity between the shape of empirical PKs for Bitcoin and other markets that represent aggregate wealth shows that Bitcoin is becoming an established asset class.
+abstract
 
@@
 
-The valuation of digital currencies has been a question that predated
-its first representative, Bitcoin. Upon the creation of Bit Gold, Szabo
-(2008) envisioned its value to arise from an interplay between the
-benefits of the two entities which foremost represent value: cash and
-metal. The argument put forward was that metal bears an inherent value
-that is largely independent of trusted third parties. However, the
-unwieldiness of metal incurs a relatively high transaction cost when
-used as a means of exchange. (Unbacked) Cash, on the other hand, draws
-its value largely from the trust in a third party's acceptance. The
-combination of the two elements, coming in the form of a scarce digital
-resource that is governed in a trustless system, has been passed on to
-Bitcoin (BTC) and other Cryptocurrencies (CC).
-
-Since the inception of BTC as proposed by Nakamoto (2009), various
-arguments have been made on its valuation. Apart from the benefit of a
-trustless system, the arguments typically include the production cost of
-a block (Hayes 2019), the benefit of borderless transactions (Deng 2020;
-Stellar Development Foundation 2022), the value of an inflation hedge
-(Choi and Shin 2022), network effects (Chen and Vinogradov 2021; Gandal
-and Halaburda 2016) or expectations about future price developments
-(Blau 2017; Smaniotto and Neto 2022).
-
-In addition to the former valuation approaches, we offer new insights by
-means of the BTC derivatives market which has emerged over the course of
-the last years. Since derivatives markets are particularly rich in
-information, their evolution provides a unique opportunity to assess the
-BTC market valuation through the application of proven econometric
-techniques. Key information about preferences and forward looking
-decisions are state price densities (SPD), that can be estimated from
-option prices. SPDs yield risk-neutral probabilities, under which
-investors price derivatives. They provide the key to pricing exotic or
-illiquid options in an arbitrage-free manner (Aït-Sahalia and Lo 1998)
-and offer insight into changing expectations about future developments.
-In conjunction with the physical density (PD) of Bitcoin returns, the
-resulting pricing kernels (PK) can be calculated. The shape and
-evolution of PKs over time discloses investor expectations under
-different market circumstances and gives insight into time varying
-preferences. We present the first paper that is based on real Bitcoin
-option data, inferring and disclosing investor preferences following
-hypothesizing papers on bootstrap-based confidence bands for empirical
-PKs (Härdle et al. 2014) and cryptocurrency option pricing under an SVCJ
-model (Hou et al. 2020).
-
-BTC derivatives markets can already be regarded as efficient information
-processing mechanisms (Alexander et al. 2022). Among those markets,
-\href{https://www.deribit.com/}{Deribit} is the leading crypto option
-exchange as measured by open interest and trading volume. As of
-2022-07-25, Deribit manages more than 90\% of the BTC option volume
-which translates over a 30 day window into an average 24-hour trading
-volume of over 331.8 million USD (Skew.com 2022). The competitors
-LedgerX, OKEx, CME, bit.com and Binance are contributing respective
-averages of 1.9, 15.7, 13.2, 1.5, 0.582 million USD.
-
-A particularly interesting property of the BTC options market is its
-decentralized nature. Trading on Deribit is largely dominated by
-retailers. Despite an ongoing decline of retail market share in favor of
-institutions (Coinbase 2022), who are cautious to invest in highly
-volatile and unregulated assets, the options market on Deribit remains
-driven by retailers: As of 2022-07-25, 86.65\% of the volume is
-attributed to retail, whereas 9.16\% and 1.19\% are attributed to
-investors and whales (Deribit 2022a). Deribit classifies market
-participants according to their share of the circulating BTC supply.
-According to Deribit's classification, a ``whale'' is an entity that
-owns more than 1\% of the supply on Deribit, an ``investor'' owns
-between 0.1\% and 1\% and a ``retailer'' owns less than 0.1\%.
-Considering the retail share in trading volume in conjunction with
-Deribit's dominating market share over the competition, we figure that
-the Bitcoin price is mainly driven by retail. Analyzing a retail-driven
-marketplace renders the study of digital currencies like BTC unique and
-different from the well studied equity options markets, where retail
-only has a minor influence (Bloomberg 2021).
-
-Another interesting feature of the market under consideration is not
-just the dominating presence of retailers, but their easy access to
-leverage for speculation. Since Deribit is by design a margin-trading
-platform, levers of up to 100 are available for longs. Easy access to
-leverage could suggest the existence of the leverage effect if investors
-were risk affine. However, we cannot confrm a leverage effect to be
-present in the time frame under consideration.
+Another, so far rarely used pathway is the assessment of the risk-return characteristics of Bitcoin through the lens of the options written on it, which allow new model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
+
+This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option positions in the early 2000s.
+
+Bakshi and Shumway both found that expected call returns exceed those of the underlying and that expected put returns underperform the underlying.
+Both also found that the effect increases (decreases) with the strike.
+Bakshi found that zero-beta, at-the-money straddle positions produce average losses of approximately three percent per week and suggests that the reason may be a systematic volatility premium being priced in options.
+
+Following Shumway, the risk-return characteristics of options can be separated in two elements, a leverage effect and a curvature effect due to the sensitivity of option payoffs to higher moments of the underlying.
+First, the holder (buyer) of an option is subject to a leverage effect since exposure to the underlying can be obtained through the payment of a premium, which is small compared to the price of the underlying.
+If there is a leverage effect, then (long) call options should outperform their underlying and (long) put options should underperform their underlying.
+Furthermore, the effect should increase (decrease) with the strike price for calls (puts).
+This reasoning allows a simple test of existence and size of the leverage effect and thus conclusions about the level of speculation associated to Bitcoin valuation.
+
+(The second component, related to the sensitivity of options towards higher moments, implies that options are redundant assets...)
+
+If options were redundant assets, then apart of the leverage effect, delta-neutral option portfolios should earn the risk-free rate (no premium) on average.
+Until now, there is no risk-free rate available in the space of crypto assets.
+We establish a proxy or reference rate for a possible risk-free rate, which results from the perpetual futures written on Bitcoin and Ether.
+
+Use Deribit and Binance perpetual futures for this, equally weighted.
+
+(This proxy is clearly not risk-free due to counterparty risk, but we argue that a carry trade involving a short position on perpetual futures on multiple platforms in conjunction with a secured, on-chain underlying position reduces the platform-induced counterparty risk (which is the residual risk in the carry trade) as far as possible.) (This also leaves liquidity risk though!!)
 
@@
 
-\section{Pricing Kernels}
-
-Assume a risky asset with a stochastic price process
-\(\{S_t\}_{t \in \mathbb{N}}\) and a risk-free interest rate
-\(\{r_t\}_{t \in \mathbb{N}}\) in a complete market. Following the
-second Fundamental Theorem of Asset Pricing, a unique
-martingale-equivalent measure \(Q\) exists in the described setting,
-under which derivatives can be priced in an arbitrage-free manner (Huynh
-et al. 2002; Pascucci and Agliardi 2011).
-
-Let \(C_t\) be the price at time \(t\) of a contingent claim with payoff
-\(\psi(\cdot)\) on the risky asset (underlying), which has a maturity at
-\(T\) and a time-to-maturity \(\tau = T-t\). For simplicity assume a
-constant interest rate \(r_t = r\). The price of any such contingent
-claim can be expressed as the discounted value of expected future
-payoffs, weighted with their respective probabilities of occurrence. The
-expectation operator is conditional on the information set at \(t\)
-under the equivalent martingale probability \(Q\)
+\section{A Proxy for the risk-free Rate of Bitcoin and Ether}
+
+Evidently, there is no established risk-free rate in crypto (or digital asset) markets.
+In the absence of riskless bond, we refer to the next best thing as a proxy for the risk free rate, which is the replication of the market-implied yield through a position which only has liquidity risk and counterparty risk.
+To be fair, counterparty risk also exists for risk-free bonds.
+
+A large share of the trading volume in digital asset markets falls on the futures market.
+Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments (show both!).
+While it would be possible to use a yield from a long-short futures position (e.g.
+short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration.
+These are the perpetual futures, which are listed on some exchanges.
+
+As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
+Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
+
+BTC Futures
+
+Total Open Interest $1,405,918,350
+Total 24h Trade Volume $324,820,482
+
+ETH Futures
+Total Open Interest $466,932,584
+Total 24h Trade Volume $98,238,298
+
+\begin{table}[]
+\begin{tabular}{lll}
+\textbf{Instrument}            & \textbf{Aggregate Open Interest (USD)} & \textbf{24 Hour Aggregate Trade Volume (USD)} \\
+BTC Perpetual Futures & 19,343,021,437                & 50,339,886,015                       \\
+ETH Perpetual Futures & 14,945,055,482                & 18,097,004,167                       \\
+BTC Futures           & 1,405,918,350                 & 324,820,482                          \\
+ETH Futures           & 466,932,584                   & 98,238,298                          
+\end{tabular}
+\end{table}
+
+Source for liquidity: 
+https://www.coingecko.com/en/derivatives
+https://www.coingecko.com/en/derivatives/futures
+
+% Source: https://www.tablesgenerator.com/#
+% Please add the following required packages to your document preamble:
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+
+As of 2024-01-07
+
+Bitcoin Perpetuals with 
+Total Open Interest \$19,343,021,437
+Total 24h Trade Volume \$50,339,886,015
+
+\begin{table}[]
+\begin{tabular}{llrrrrrrr}
+\textbf{Exchange}    & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\# Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
+\# Binance (Futures) & BTCUSD\_PERP    & \$44,008.70                        & 44037.64 USD                             & +0.066\%                           & 0.01\%                              & 0.010\%                                   & \$808,036,100                              & \$973,585,131.72                        \\
+\# BingX (Futures)   & BTC-USDT        & \$44,042.40                        & 44046.6 USDT                             & +0.044\%                           & 0.01\%                              & 0.010\%                                   & \$909,897,901                              & \$1,867,895,422.35                      \\
+\# Bitget Futures    & BTCUSDT\_UMCBL  & \$44,049.08                        & 44033.85 USDT                            & +0.015\%                           & 0.01\%                              & 0.011\%                                   & \$1,790,553,246                            & \$5,701,072,691.79                      \\
+\# Bitmart Futures   & BTCUSDT         & \$44,015.47                        & 44003.79 USDT                            & +0.024\%                           & 0.01\%                              & 0.010\%                                   & \$641,006,203                              & \$2,917,088,729.74                      \\
+\# Bybit (Futures)   & BTCUSDT         & \$44,039.88                        & 44016.82 USDT                            & -0.003\%                           & 0.01\%                              & 0.010\%                                   & \$2,538,053,148                            & \$2,672,726,926.85                      \\
+\# Bybit (Futures)   & BTCUSD          & \$43,995.50                        & 44037.2 USD                              & +0.095\%                           & 0.01\%                              & 0.010\%                                   & \$652,512,486                              & \$283,394,472.00                        \\
+\# Deribit           & BTC-PERPETUAL   & \$44,020.00                        & 44028.17 USD                             & +0.019\%                           & 0.01\%                              & 0.004\%                                   & \$577,506,570                              & \$204,526,951.86                        \\
+\# OKX (Futures)     & BTC-USDT-SWAP   & \$44,014.07                        & 43989.3 USDT                             & -0.006\%                           & 0.01\%                              & -0.009\%                                  & \$984,130,801                              & \$2,648,725,568.71                      \\
+\# Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31
+\end{tabular}
+\end{table}
+
+Ether Perpetuals
+
+Total Open Interest \$14,945,055,482
+Total 24h Trade Volume \$18,097,004,167
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+
+\begin{table}[]
+\begin{tabular}{llrrrrrrr}
+\textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
+\# Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
+\# Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
+\# OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
+\# Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
+\# BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
+\# Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
+\# Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
+\# Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
+\# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30
+\end{tabular}
+\end{table}
+
+BTC Futures
+
+with
+
+Total Open Interest $1,405,918,350
+Total 24h Trade Volume $324,820,482
+
+\begin{table}[]
+\begin{tabular}{llrrrrrrr}
+\textbf{Exchange}                & \textbf{Symbol}    & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Expires in}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\# Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
+\# Binance (Futures)             & BTCUSD\_240628     & \$46,802.20                        & 44037.64 USD                             & -5.907\%                           & 0.02\%                              & 6 months                                & \$60,673,400                               & \$11,015,730.09                         \\
+\# Binance (Futures)             & BTCUSDT\_240329    & \$45,340.32                        & 44011.62 USDT                            & -2.883\%                           & 0.04\%                              & -                                       & \$38,608,233                               & \$13,341,161.63                         \\
+\# Binance (Futures)             & BTCUSDT\_240628    & \$46,588.03                        & 44011.62 USDT                            & -5.484\%                           & 0.02\%                              & -                                       & \$7,296,676                                & \$6,727,917.37                          \\
+\# BitMEX (Derivative)           & XBTH24             & \$45,170.00                        & 44016.02 USD                             & -2.555\%                           & 0.03\%                              & 3 months                                & \$23,123,300                               & \$2,586,155.50                          \\
+\# BitMEX (Derivative)           & XBTM24             & \$46,319.00                        & 44016.02 USD                             & -4.972\%                           & 0.15\%                              & 6 months                                & \$14,701,700                               & \$899,753.13                            \\
+\# BitMEX (Derivative)           & XBTF24             & \$44,599.50                        & 44016.02 USD                             & -1.308\%                           & 0.18\%                              & 19 days                                 & \$3,686,400                                & \$42,073.68                             \\
+\# BitMEX (Derivative)           & XBTU24             & \$47,680.00                        & 44016.02 USD                             & -7.685\%                           & 0.82\%                              & 9 months                                & \$874,700                                  & \$14,332.62                             \\
+\# BitMEX (Derivative)           & XBTG24             & \$45,034.50                        & 44016.02 USD                             & -2.262\%                           & 0.2\%                               & about 2 months                          & \$149,400                                  & \$502.57                                \\
+\# BitMEX (Derivative)           & XBTUSDTH24         & \$44,913.12                        & 43991.27 USDT                            & -2.003\%                           & 22.08\%                             & 3 months                                & \$67,027                                   & \$23,309.91                             \\
+\# BTSE (Futures)                & BTC-240329         & \$45,346.20                        & 45337.26 USD                             & -0.020\%                           & 0.15\%                              & 3 months                                & \$70,779,838                               & \$70,829.75                             \\
+\# BTSE (Futures)                & BTC-240628         & \$46,578.30                        & 46774.54 USD                             & +0.421\%                           & 0.2\%                               & 6 months                                & \$68,641,915                               & \$58,755.91                             \\
+\# Bybit (Futures)               & BTCUSDH24          & \$45,515.00                        & 44050.12 USD                             & -3.218\%                           & 0.01\%                              & 3 months                                & \$31,042,370                               & \$8,992,250.00                          \\
+\# Bybit (Futures)               & BTCUSDM24          & \$46,867.50                        & 44046.87 USD                             & -6.018\%                           & 0.01\%                              & 6 months                                & \$13,200,403                               & \$932,634.00                            \\
+\# Bybit (Futures)               & BTC-29MAR24        & \$45,288.92                        & 44042.99 USDC                            & -2.786\%                           & 0.07\%                              & 3 months                                & -                                          & \$1,650,409.10                          \\
+\# Bybit (Futures)               & BTC-28JUN24        & \$46,655.43                        & 44042.83 USDC                            & -5.633\%                           & 0.07\%                              & 6 months                                & -                                          & \$636,256.66                            \\
+\# Bybit (Futures)               & BTC-12JAN24        & \$44,205.30                        & 44042.83 USDC                            & -0.403\%                           & 0.02\%                              & 5 days                                  & -                                          & \$320,758.50                            \\
+\# Bybit (Futures)               & BTC-19JAN24        & \$44,341.25                        & 44042.83 USDC                            & -0.708\%                           & 0.03\%                              & 12 days                                 & -                                          & \$117,823.82                            \\
+\# Bybit (Futures)               & BTC-27SEP24        & \$47,694.06                        & 44042.99 USDC                            & -7.688\%                           & 0.08\%                              & 9 months                                & -                                          & \$66,406.59                             \\
+\# Bybit (Futures)               & BTC-26JAN24        & \$44,370.24                        & 44042.75 USDC                            & -0.773\%                           & 0.02\%                              & 19 days                                 & -                                          & \$47,245.15                             \\
+\# Bybit (Futures)               & BTC-23FEB24        & \$44,806.59                        & 44042.99 USDC                            & -1.739\%                           & 0.03\%                              & about 2 months                          & -                                          & \$8,650.36                              \\
+\# Crypto.com Exchange (Futures) & BTCUSD-240628      & \$46,384.20                        & 44003.38 USD                             & -5.133\%                           & 0.41\%                              & -                                       & \$24,557,224                               & \$15,659.31                             \\
+\# Crypto.com Exchange (Futures) & BTCUSD-240329      & \$45,024.60                        & 44003.38 USD                             & -2.268\%                           & 0.46\%                              & -                                       & \$1,118,289                                & \$17,244.42                             \\
+\# Crypto.com Exchange (Futures) & BTCUSD-240126      & \$44,215.10                        & 44003.38 USD                             & -0.479\%                           & 0.29\%                              & -                                       & \$9,701                                    & \$18,428.85                             \\
+\# Crypto.com Exchange (Futures) & BTCUSD-240223      & \$44,624.00                        & 44003.38 USD                             & -1.391\%                           & 0.43\%                              & -                                       & \$3,539                                    & \$14,931.19                             \\
+\# Deribit                       & BTC-29MAR24        & \$45,300.00                        & 44026.9 USD                              & -2.810\%                           & 0.02\%                              & 3 months                                & \$208,084,190                              & \$15,282,281.56                         \\
+\# Deribit                       & BTC-26JAN24        & \$44,475.00                        & 44026.9 USD                              & -1.008\%                           & 0.1\%                               & 19 days                                 & \$89,621,140                               & \$3,132,087.87                          \\
+\# Deribit                       & BTC-28JUN24        & \$46,577.50                        & 44026.9 USD                              & -5.476\%                           & 0.02\%                              & 6 months                                & \$79,314,230                               & \$7,916,251.72                          \\
+\# Deribit                       & BTC-27SEP24        & \$47,715.00                        & 44026.9 USD                              & -7.729\%                           & 0.09\%                              & 9 months                                & \$32,099,570                               & \$1,034,939.35                          \\
+\# Deribit                       & BTC-12JAN24        & \$44,110.00                        & 44026.9 USD                              & -0.188\%                           & 0.03\%                              & 5 days                                  & \$25,884,930                               & \$7,230,738.10                          \\
+\# Deribit                       & BTC-23FEB24        & \$44,767.50                        & 44026.9 USD                              & -1.654\%                           & 0.03\%                              & about 2 months                          & \$22,571,940                               & \$744,850.73                            \\
+\# Deribit                       & BTC-27DEC24        & \$49,247.50                        & 44026.9 USD                              & -10.601\%                          & 0.13\%                              & 12 months                               & \$11,398,600                               & \$600,503.46                            \\
+\# Deribit                       & BTC-19JAN24        & \$44,222.50                        & 44026.9 USD                              & -0.442\%                           & 0.04\%                              & 12 days                                 & \$5,538,440                                & \$2,799,269.71                          \\
+\# HTX Futures                   & BTC\_CQ            & \$45,297.68                        & 44023.11 USD                             & -2.814\%                           & 0.38\%                              & 3 months                                & \$1,002,200                                & \$1,602,716.03                          \\
+\# HTX Futures                   & BTC\_CW            & \$44,095.65                        & 44030.71 USD                             & -0.147\%                           & 0.45\%                              & 4 days                                  & \$47,100                                   & \$1,011,419.90                          \\
+\# HTX Futures                   & BTC\_NW            & \$44,211.45                        & 44023.11 USD                             & -0.426\%                           & 0.4\%                               & 11 days                                 & \$9,000                                    & \$967,082.71                            \\
+\# Kraken (Futures)              & FI\_XBTUSD\_240329 & \$45,520.50                        & 44013.38 USD                             & -3.311\%                           & 0.08\%                              & 3 months                                & \$6,608,999                                & \$112,442.00                            \\
+\# Kraken (Futures)              & FI\_XBTUSD\_240628 & \$46,571.50                        & 44013.38 USD                             & -5.493\%                           & 0.24\%                              & 6 months                                & \$1,929,982                                & \$275,529.00                            \\
+\# Kraken (Futures)              & FI\_XBTUSD\_240126 & \$44,191.50                        & 44013.38 USD                             & -0.403\%                           & 0.4\%                               & 19 days                                 & \$300,856                                  & \$3.00                                  \\
+\# Kraken (Futures)              & FF\_XBTUSD\_240329 & \$45,284.00                        & 44013.38 USD                             & -2.806\%                           & 0.11\%                              & 3 months                                & \$87                                       & \$22.68                                 \\
+\# Kraken (Futures)              & FF\_XBTUSD\_240126 & \$44,307.00                        & 44013.38 USD                             & -0.663\%                           & 0.08\%                              & 19 days                                 & \$32                                       & \$4.61                                  \\
+\# KuCoin Futures                & XBTMH24            & \$45,444.00                        & 44072.8 USD                              & -3.017\%                           & 0.19\%                              & 3 months                                & \$11,251,580                               & \$86,193.00                             \\
+\# OKX (Futures)                 & BTC-USD-240329     & \$45,322.90                        & 44016.1 USD                              & -2.883\%                           & 0.01\%                              & 3 months                                & \$175,555,100                              & \$42,597,534.31                         \\
+\# OKX (Futures)                 & BTC-USD-240628     & \$46,744.90                        & 44016.1 USD                              & -5.838\%                           & 0.03\%                              & 6 months                                & \$67,199,400                               & \$13,281,039.45                         \\
+\# OKX (Futures)                 & BTC-USDT-240329    & \$45,345.34                        & 43989.3 USDT                             & -2.942\%                           & 0.02\%                              & 3 months                                & \$54,809,841                               & \$32,494,014.76                         \\
+\# OKX (Futures)                 & BTC-USDT-240628    & \$46,824.58                        & 43989.3 USDT                             & -6.008\%                           & 0.02\%                              & 6 months                                & \$49,096,426                               & \$8,216,309.33                          \\
+\# OKX (Futures)                 & BTC-USD-240126     & \$44,235.20                        & 44016.1 USD                              & -0.495\%                           & 0.04\%                              & 19 days                                 & \$20,945,300                               & \$1,424,116.88                          \\
+\# OKX (Futures)                 & BTC-USD-240112     & \$44,085.20                        & 44016.1 USD                              & -0.157\%                           & 0.01\%                              & 5 days                                  & \$15,394,800                               & \$11,575,786.01                         \\
+\# OKX (Futures)                 & BTC-USDT-240126    & \$44,284.50                        & 43989.3 USDT                             & -0.617\%                           & 0.06\%                              & 19 days                                 & \$8,573,427                                & \$1,552,614.65                          \\
+\# OKX (Futures)                 & BTC-USD-240223     & \$44,719.10                        & 44016.1 USD                              & -1.572\%                           & 0.04\%                              & about 2 months                          & \$8,046,700                                & \$3,603,630.54                          \\
+\# OKX (Futures)                 & BTC-USD-240119     & \$44,198.90                        & 44016.1 USD                              & -0.414\%                           & 0.01\%                              & 12 days                                 & \$4,957,200                                & \$6,247,231.64                          \\
+\# OKX (Futures)                 & BTC-USDT-240112    & \$44,080.50                        & 43989.3 USDT                             & -0.157\%                           & 0.03\%                              & 5 days                                  & \$3,560,036                                & \$12,798,332.26                         \\
+\# OKX (Futures)                 & BTC-USDT-240223    & \$44,781.65                        & 43989.3 USDT                             & -1.720\%                           & 0.08\%                              & about 2 months                          & \$2,960,896                                & \$711,132.65                            \\
+\# OKX (Futures)                 & BTC-USDT-240119    & \$44,192.36                        & 43989.3 USDT                             & -0.409\%                           & 0.04\%                              & 12 days                                 & \$975,364                                  & \$4,235,395.39                          \\
+\# OKX (Futures)                 & BTC-USDC-240628    & \$46,788.02                        & 44015.4 USDC                             & -5.958\%                           & 0.39\%                              & 6 months                                & -                                          & \$17,320.92                             \\
+\# OKX (Futures)                 & BTC-USDC-240119    & \$44,137.13                        & 44020.7 USDC                             & -0.298\%                           & 0.1\%                               & 12 days                                 & -                                          & \$6,285.13                              \\
+\# OKX (Futures)                 & BTC-USDC-240329    & \$45,832.15                        & 44020.7 USDC                             & -3.985\%                           & 0.31\%                              & 3 months                                & -                                          & \$1,874.53                              \\
+\# OKX (Futures)                 & BTC-USDC-240112    & \$44,107.04                        & 44015.4 USDC                             & -0.242\%                           & 0.13\%                              & 5 days                                  & -                                          & \$9,765.30                              \\
+\# XT.COM (Derivatives)          & BTC\_USD\_240329   & \$45,380.70                        & -                                        & -3.586\%                           & 0.01\%                              & 3 months                                & -                                          & \$33,113,000.00                         \\
+\# XT.COM (Derivatives)          & BTC\_USD\_240628   & \$46,797.20                        & -                                        & -                                  & 0.01\%                              & 6 months                                & -                                          & \$31,000,200.00                         \\
+\# XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & -                                  & 0.06\%                              & 3 months                                & -                                          & \$20,870,477.00
+\end{tabular}
+\end{table}
+
+ETH Futures
+
+with 
+Total Open Interest $466,932,584
+Total 24h Trade Volume $98,238,298
+
+\begin{table}[]
+\begin{tabular}{llrrrrrrr}
+\textbf{Exchange}                & \textbf{Symbol}    & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Expires in}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\# Binance (Futures)             & ETHUSD\_240329     & \$2,300.60                         & 2228.81 USD                              & -3.121\%                           & 0.01\%                              & 3 months                                & \$72,215,240                               & \$16,326,927.83                         \\
+\# Binance (Futures)             & ETHUSD\_240628     & \$2,368.79                         & 2229.03 USD                              & -5.900\%                           & 0.02\%                              & 6 months                                & \$11,183,360                               & \$4,224,925.26                          \\
+\# Binance (Futures)             & ETHUSDT\_240329    & \$2,300.46                         & 2227.81 USDT                             & -3.110\%                           & 0.02\%                              & -                                       & \$35,040                                   & \$6,902,127.72                          \\
+\# Binance (Futures)             & ETHUSDT\_240628    & \$2,360.43                         & 2227.81 USDT                             & -5.572\%                           & 0.03\%                              & -                                       & \$4,604                                    & \$4,303,853.27                          \\
+\# BitMEX (Derivative)           & ETHUSDH24          & \$2,452.60                         & 2228.01 USD                              & -9.157\%                           & 0.02\%                              & 3 months                                & \$4,341,286                                & \$537,210.05                            \\
+\# BitMEX (Derivative)           & ETHH24             & \$2,217.23                         & 0.05 XBT                                 & +0.457\%                           & 0.37\%                              & 3 months                                & \$1,575,478                                & \$69,244.08                             \\
+\# BTSE (Futures)                & ETH-240628         & \$2,350.05                         & 2367.26 USD                              & +0.732\%                           & 0.75\%                              & 6 months                                & \$2,517,764                                & \$49,845.75                             \\
+\# BTSE (Futures)                & ETH-240329         & \$2,297.48                         & 2298.78 USD                              & +0.057\%                           & 0.23\%                              & 3 months                                & \$2,081,180                                & \$49,130.96                             \\
+\# Bybit (Futures)               & ETHUSDM24          & \$2,357.45                         & 2229.63 USD                              & -5.422\%                           & 0.05\%                              & 6 months                                & -                                          & \$448,716.00                            \\
+\# Bybit (Futures)               & ETHUSDH24          & \$2,287.90                         & 2229.53 USD                              & -2.551\%                           & 0.06\%                              & 3 months                                & -                                          & \$294,007.00                            \\
+\# Bybit (Futures)               & ETH-26JAN24        & \$2,243.65                         & 2229.46 USDC                             & -0.668\%                           & 0.05\%                              & 19 days                                 & -                                          & \$286,245.77                            \\
+\# Bybit (Futures)               & ETH-12JAN24        & \$2,231.66                         & 2229.51 USDC                             & -0.132\%                           & 0.03\%                              & 5 days                                  & -                                          & \$99,683.25                             \\
+\# Bybit (Futures)               & ETH-28JUN24        & \$2,368.66                         & 2229.46 USDC                             & -5.910\%                           & 0.1\%                               & 6 months                                & -                                          & \$97,357.35                             \\
+\# Bybit (Futures)               & ETH-19JAN24        & \$2,238.21                         & 2229.51 USDC                             & -0.424\%                           & 0.06\%                              & 12 days                                 & -                                          & \$92,957.40                             \\
+\# Bybit (Futures)               & ETH-23FEB24        & \$2,274.64                         & 2229.51 USDC                             & -2.019\%                           & 0.03\%                              & about 2 months                          & -                                          & \$68,610.65                             \\
+\# Bybit (Futures)               & ETH-29MAR24        & \$2,297.48                         & 2229.51 USDC                             & -2.993\%                           & 0.03\%                              & 3 months                                & -                                          & \$36,926.81                             \\
+\# Bybit (Futures)               & ETH-27SEP24        & \$2,420.24                         & 2229.46 USDC                             & -7.915\%                           & 0.12\%                              & 9 months                                & -                                          & \$30,008.99                             \\
+\# Crypto.com Exchange (Futures) & ETHUSD-240628      & \$2,347.68                         & 2224.96 USD                              & -5.227\%                           & 0.24\%                              & -                                       & \$24,573,170                               & \$822.63                                \\
+\# Crypto.com Exchange (Futures) & ETHUSD-240126      & \$2,234.13                         & 2224.96 USD                              & -0.410\%                           & 0.14\%                              & -                                       & \$79,732                                   & \$742.18                                \\
+\# Crypto.com Exchange (Futures) & ETHUSD-240329      & \$2,286.18                         & 2224.96 USD                              & -2.678\%                           & 0.29\%                              & -                                       & \$58,845                                   & \$895.27                                \\
+\# Crypto.com Exchange (Futures) & ETHUSD-240223      & \$2,249.95                         & 2224.92 USD                              & -1.112\%                           & 0.17\%                              & -                                       & \$27,557                                   & \$1,247.37                              \\
+\# Deribit                       & ETH-29MAR24        & \$2,296.00                         & 2228.59 USD                              & -2.936\%                           & 0.02\%                              & 3 months                                & \$88,364,731                               & \$2,438,537.07                          \\
+\# Deribit                       & ETH-28JUN24        & \$2,363.75                         & 2228.59 USD                              & -5.718\%                           & 0.01\%                              & 6 months                                & \$35,776,949                               & \$1,152,627.40                          \\
+\# Deribit                       & ETH-26JAN24        & \$2,247.75                         & 2228.59 USD                              & -0.852\%                           & 0.02\%                              & 19 days                                 & \$34,172,788                               & \$2,694,255.34                          \\
+\# Deribit                       & ETH-27SEP24        & \$2,414.50                         & 2228.59 USD                              & -7.700\%                           & 0.02\%                              & 9 months                                & \$22,332,082                               & \$781,745.26                            \\
+\# Deribit                       & ETH-12JAN24        & \$2,232.25                         & 2228.59 USD                              & -0.164\%                           & 0.01\%                              & 5 days                                  & \$10,281,174                               & \$1,626,945.44                          \\
+\# Deribit                       & ETH-23FEB24        & \$2,273.25                         & 2228.59 USD                              & -1.965\%                           & 0.08\%                              & about 2 months                          & \$10,187,446                               & \$484,690.68                            \\
+\# Deribit                       & ETH-27DEC24        & \$2,463.00                         & 2228.59 USD                              & -9.517\%                           & 0.21\%                              & 12 months                               & \$6,513,788                                & \$630,519.38                            \\
+\# Deribit                       & ETH-19JAN24        & \$2,235.50                         & 2228.59 USD                              & -0.309\%                           & 0.03\%                              & 12 days                                 & \$1,564,812                                & \$1,319,273.13                          \\
+\# HTX Futures                   & ETH\_CQ            & \$2,298.00                         & 2228.66 USD                              & -3.018\%                           & 0.01\%                              & 3 months                                & \$1,130,370                                & \$562,732.95                            \\
+\# HTX Futures                   & ETH\_CW            & \$2,233.11                         & 2228.54 USD                              & -0.205\%                           & 0.01\%                              & 4 days                                  & \$49,870                                   & \$481,669.51                            \\
+\# HTX Futures                   & ETH\_NW            & \$2,242.45                         & 2228.66 USD                              & -0.615\%                           & 0.35\%                              & 11 days                                 & \$31,200                                   & \$302,572.28                            \\
+\# Kraken (Futures)              & FI\_ETHUSD\_240329 & \$2,300.00                         & 2228 USD                                 & -3.130\%                           & 0.11\%                              & 3 months                                & \$4,415,821                                & \$29,062.00                             \\
+\# Kraken (Futures)              & FI\_ETHUSD\_240628 & \$2,366.30                         & 2228 USD                                 & -5.845\%                           & 0.25\%                              & 6 months                                & \$3,541,749                                & \$40,752.00                             \\
+\# Kraken (Futures)              & FF\_ETHUSD\_240329 & \$2,314.00                         & 2228 USD                                 & -3.717\%                           & 0.13\%                              & 3 months                                & \$1,584                                    & \$0.45                                  \\
+\# Kraken (Futures)              & FF\_ETHUSD\_240126 & \$2,254.90                         & 2228 USD                                 & -1.193\%                           & 0.09\%                              & 19 days                                 & \$299                                      & \$36.69                                 \\
+\# Kraken (Futures)              & FI\_ETHUSD\_240126 & \$2,254.15                         & 2228 USD                                 & -1.160\%                           & 0.24\%                              & 19 days                                 & \$48,594                                   & \$10,184.00                             \\
+\# OKX (Futures)                 & ETH-USD-240329     & \$2,296.78                         & 2228.71 USD                              & -2.964\%                           & 0.01\%                              & 3 months                                & \$61,638,000                               & \$13,362,284.32                         \\
+\# OKX (Futures)                 & ETH-USD-240628     & \$2,370.47                         & 2228.67 USD                              & -5.982\%                           & 0.03\%                              & 6 months                                & \$29,831,250                               & \$8,793,848.00                          \\
+\# OKX (Futures)                 & ETH-USDT-240329    & \$2,296.43                         & 2226.75 USDT                             & -2.985\%                           & 0.02\%                              & 3 months                                & \$20,412,503                               & \$5,701,567.75                          \\
+\# OKX (Futures)                 & ETH-USD-240112     & \$2,231.34                         & 2228.71 USD                              & -0.118\%                           & 0.01\%                              & 5 days                                  & \$7,456,500                                & \$8,340,344.15                          \\
+\# OKX (Futures)                 & ETH-USDT-240628    & \$2,366.59                         & 2227.15 USDT                             & -5.845\%                           & 0.02\%                              & 6 months                                & \$3,885,976                                & \$3,157,980.17                          \\
+\# OKX (Futures)                 & ETH-USD-240119     & \$2,233.42                         & 2228.71 USD                              & -0.211\%                           & 0.03\%                              & 12 days                                 & \$3,212,320                                & \$3,467,988.47                          \\
+\# OKX (Futures)                 & ETH-USDT-240112    & \$2,229.86                         & 2226.75 USDT                             & -0.089\%                           & 0.01\%                              & 5 days                                  & \$2,298,019                                & \$3,571,348.57                          \\
+\# OKX (Futures)                 & ETH-USDT-240119    & \$2,235.50                         & 2226.75 USDT                             & -0.341\%                           & 0.01\%                              & 12 days                                 & \$690,474                                  & \$2,364,707.49                          \\
+\# OKX (Futures)                 & ETH-USDC-240329    & \$2,296.52                         & 2227.93 USDC                             & -3.020\%                           & 0.38\%                              & 3 months                                & -                                          & \$55,373.71                             \\
+\# OKX (Futures)                 & ETH-USDC-240112    & \$2,251.63                         & 2227.89 USDC                             & -1.088\%                           & 0.09\%                              & 5 days                                  & -                                          & \$5,770.92                              \\
+\# OKX (Futures)                 & ETH-USDC-240119    & \$2,251.87                         & 2227.93 USDC                             & -1.037\%                           & 0.14\%                              & 12 days                                 & -                                          & \$9.01                                  \\
+\# XT.COM (Derivatives)          & ETH\_USD\_240628   & \$2,368.07                         & -                                        & -                                  & 0.04\%                              & 6 months                                & -                                          & \$2,929,170.00                          \\
+\# XT.COM (Derivatives)          & ETH\_USD\_240329   & \$2,299.63                         & -                                        & -2.350\%                           & 0.01\%                              & 3 months                                & -                                          & \$2,698,030.00                          \\
+\# XT.COM (Derivatives)          & ETH\_USDT\_240329  & \$2,301.93                         & -                                        & -                                  & 0.03\%                              & 3 months                                & -                                          & \$124,645.12                            \\
+\# OKX (Futures)                 & BTC-USDT-240112    & \$44,080.50                        & -0.157\%                                 & 0.03\%                             & 5 days                              & \$3,560,036                             & \$12,798,332.26                            & \multicolumn{1}{l}{}                    \\
+\# OKX (Futures)                 & BTC-USDT-240223    & \$44,781.65                        & -1.720\%                                 & 0.08\%                             & about 2 months                      & \$2,960,896                             & \$711,132.65                               & \multicolumn{1}{l}{}                    \\
+\# OKX (Futures)                 & BTC-USDT-240119    & \$44,192.36                        & -0.409\%                                 & 0.04\%                             & 12 days                             & \$975,364                               & \$4,235,395.39                             & \multicolumn{1}{l}{}                    \\
+\# OKX (Futures)                 & BTC-USDC-240628    & \$46,788.02                        & -5.958\%                                 & 0.39\%                             & 6 months                            & -                                       & \$17,320.92                                & \multicolumn{1}{l}{}                    \\
+\# OKX (Futures)                 & BTC-USDC-240119    & \$44,137.13                        & -0.298\%                                 & 0.1\%                              & 12 days                             & -                                       & \$6,285.13                                 & \multicolumn{1}{l}{}                    \\
+\# OKX (Futures)                 & BTC-USDC-240329    & \$45,832.15                        & -3.985\%                                 & 0.31\%                             & 3 months                            & -                                       & \$1,874.53                                 & \multicolumn{1}{l}{}                    \\
+\# OKX (Futures)                 & BTC-USDC-240112    & \$44,107.04                        & -0.242\%                                 & 0.13\%                             & 5 days                              & -                                       & \$9,765.30                                 & \multicolumn{1}{l}{}                    \\
+\# XT.COM (Derivatives)          & BTC\_USD\_240329   & \$45,380.70                        & -3.586\%                                 & 0.01\%                             & 3 months                            & -                                       & \$33,113,000.00                            & \multicolumn{1}{l}{}                    \\
+\# XT.COM (Derivatives)          & BTC\_USD\_240628   & \$46,797.20                        & -                                        & 0.01\%                             & 6 months                            & -                                       & \$31,000,200.00                            & \multicolumn{1}{l}{}                    \\
+\# XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & 0.06\%                             & 3 months                            & -                                       & \$20,870,477.00                            & \multicolumn{1}{l}{}
+\end{tabular}
+\end{table}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+
+Crypto exchanges often provide a so-called perpetual future, which is a synthetic (typically cash-settled instrument) whose return is tied to the underlying via a funding rate.
+Most exchanges (quote here) provide perpetual futures for Bitcoin and Ethereum.
+The price of each perpetual future is linked to the underlying by adjusting a variable interest rate, called the funding rate, that fluctuates depending on the deviation between the price of the perpetual future and the underlying.
+The funding rate increases the cost of holding positions against the deviation, meaning that if the price of the perpetual future is higher than the underlying, the funding rate is positive which causes the market participants who are long to pay the short side in a contractually predefined frequency.
+Broadly said, the more extreme the deviation, the higher the funding rate and thus the higher the incentive to trade against the deviation and thus converge the price of the perpetual future towards its underlying.
+The risk-free rate is approximated using the simplest and most liquid way of realising the funding rate, a carry trade.
+In such a trade, the trader shorts (longs) the perpetual future if the funding rate is positive (negative) and simulateously buys (sells) the underlying such that the market delta of the combined position is zero.
+
+The funding rate on \href{https://www.deribit.com/kb/deribit-linear-perpetual}{Deribit} is calculated as follows:
+
+Deribit perpetual contracts are a derivative product similar to a future, however, they do not have an expiry date.
+The perpetual contract features funding payments.
+These payments have been introduced to keep the perpetual contract price as close as possible to the underlying crypto price - the relevant Deribit Index.
+If the perpetual contract trades at a higher price than the index, traders that have long positions need to make funding payments to the traders that have short positions.
+This will make the product less attractive to the long position holders and more attractive to the short position holders.
+This subsequently will cause a perpetual price to trade in line with the price of the index.
+If the perpetual trades at a price lower than the index, the short position holders will have to pay the long position holders instead.
+
+The Deribit perpetual contract features a continuous measurement of the difference between the mark price of the contract and the relevant Deribit Index.
+The percentage difference between these two price levels is the basis for the 8-hourly funding rate that is applied to all outstanding perpetual contracts.
+
+Funding payments are calculated every millisecond.
+The funding payments will be added to or subtracted from the realized PNL, which is also part of the available trading balance.
+At each daily settlement, the realized PNL will be moved to or from the cash balance, from which withdrawals can be made.
+
+The total funding paid will show up in the transaction log in the "funding" column.
+This column shows the funding amount that is applied to the trader's entire net position in the period between the relevant trade and the trade before that.
+Put differently: the trader can see the funding paid or received on the position between position changes.
+
+Funding Rate
+When the funding rate is positive, long position holders pay funding to the short position holders; when the funding rate is negative, short position holders pay funding to the long position holders.
+The funding rate is expressed as an 8-hour interest rate, and is calculated at any given time as follows:
+
+Premium Rate
+Premium Rate = ((Mark Price - Deribit Index) / Deribit Index) * 100%
+
+Funding Rate
+Sequentially, the funding rate is derived from the premium rate by applying a damper.
+
+If the premium rate is within -0.025\% and 0.025\% range, the actual funding rate will be reduced to 0.00\%.
+If the premium rate is lower than -0.025\%, then the actual funding rate will be the premium rate + 0.025\%.
+If the premium rate is higher than 0.025\%, then the actual funding rate will be the premium rate - 0.025\%.
+Additionally, the funding rate is capped at +/ - 5\% for all linear USDC perpetuals.
+Funding Rate = Maximum (0.025\%, Premium Rate) + Minimum (-0.025\%, Premium Rate)
+
+Time Fraction
+Time Fraction = Funding Rate Time Period / 8 hours
+
+The actual funding payment is calculated by multiplying the funding rate by the position size and the time fraction.
+
+Funding Payment = Funding Rate * Position Size * Time Fraction
+
+In reality, the spread of the Deribit Index and the mark price changes continuously, and all changes are taken into account.
+Therefore, the examples above are extreme simplifications of the actual calculations.
+The funding paid or received is continuously added to the realized PNL and is moved to or from the cash balance at the daily settlement, at 08:00 UTC.
+
+Fees on Funding
+Deribit does not charge any fees on funding.
+All the funding payments are transferred between the holders of the perpetual contracts.
+This makes the funding a zero-sum game, where longs receive all funding from shorts, or shorts receive all funding from longs.
+
+Mark Price
+It is essential to understand how the mark price is calculated. We start by determining the "Fair Price". The fair price is calculated as the average of the fair impact bid and the fair impact ask.
+
+Fair Impact Bid Price is an average price at which 100,000 USDC worth of contracts can be bought.
+
+Fair Impact Ask Price is an average price at which 100,000 USDC worth of contracts can be sold.
+
+Fair Price can never be higher than 0.1 % of best ask or lower than best bid
+
+Fair Price = (Fair Impact Bid + Fair Impact Ask) / 2
+The mark price is derived using both the Deribit Index and the fair price, by adding to the Deribit Index the 30 second exponential moving average (EMA) of the Fair Price - Deribit Index.
+
+Mark Price = Deribit Index + 30 second EMA (Fair Price - Deribit Index)
+We implement a safety setting on our mark price to not deviate by more than a certain percentage of Index.
+This is to prevent manipulation or to curb the impact of panic trading.
+When a deviation from index is genuine, then we would increase the possible deviation.
+
+Trading outside of this bandwidth is still allowed.
+
+The 30 second EMA is recalculated every second, so in total, there are 30 time periods in which the measurement of the latest second has a weight of 2 / (30 + 1) = 0.0645 or (6.45%).
+
+Allowed Trading Bandwidth
+Two parameters act as a boundary to the allowed trading range:
+
+Perpetual trades are limited by Deribit Index + 1 minute EMA (Fair Price - Index) +/- 1.5%, and a fixed bandwidth of the Deribit Index of +/- 7.5%.
+
+If the market circumstances require so, bandwidth parameters can be adjusted at the sole discretion of Deribit.
+
+Insert Plot Funding Rate!!
 
@@
 
-Transforming the risk-neutral measure \(Q\) to the physical measure
-\(P\) yields the PK by Itô's Lemma.
-
-\begin{equation}
-C_t = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) q(u) du = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) p(u) K(u) du
-\end{equation}
-
 where the PK \(K(\cdot)\) is defined as \(\frac{q(\cdot)}{p(\cdot)}\)
@@
 
-The PK can therefore be approximated by the ratio between the
-risk-neutral density and the physical density. This process is discussed
-and executed in the following sections.
-
 \section{Nonparametric Estimation of State Price Densities}
@@
 \subsection{Derivation}
-
-As stated by Breeden and Litzenberger (1978), a SPD can be estimated via
-the second derivative of the call price function
-\(\psi(S_T) = \max(S_T - K, 0)\) with respect to the strike price \(K\).
-
-\begin{equation}
-\frac{\partial ^2 C_t}{\partial K^2}\bigg\rvert_{K = S_t} =  q(S_T)e^{-r \tau}
-\end{equation}
-
-A variety of call prices \(C\) with different strikes \(K\) is required
-in order to calculate the complete SPD \(q\). The present value of a
-call can be priced in implied volatility (IV). In conjunction with the
-vector (time-to-maturity \(\tau\), strike \(K\), spot \(S\), interest
-rate \(r\)), the market call price can be calculated.
-
-IV is estimated as a function of time-to-maturity and moneyness in the
-following section. Collapsing spot price \(S\) and strike \(K\) into a
-single variable \(M = \frac{K}{S}\) reduces the effect of the curse of
-dimensionality. Similarly, we collapse \(S\) and the interest rate \(r\)
-into a Futures price.
 

### 2024-01-07 written/paper.tex
writing

@@
 
-Insert Plot Funding Rate!!
+funding_btc_vs_eth_annualized_zoom.png
+funding_btc_vs_eth_zoom.png
+funding_btc_vs_eth_annualized.png
+funding_btc_vs_eth.png
+
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized.png}
+    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized_zoom.png}
+
+     \captionof{figure}{(Zoomed) Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth.png}
+    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_zoom.png}
+    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\pagebreak
+\newpage
 

### 2024-01-12 written/paper.tex
first compressed table

@@
 
-\begin{table}[]
-\begin{tabular}{llrrrrrrr}
+\begin{table}[ht]
+\centering
+\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
+\hline
 \textbf{Exchange}    & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\hline
+\hline
 \# Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
@@
 \# Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 
-\begin{table}[]
+\begin{table}[ht]
 \begin{tabular}{llrrrrrrr}
+\hline
 \textbf{Exchange}         & \textbf{Symbol} & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Funding Rate}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\hline
+\hline
 \# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
@@
 
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{Performance - Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{Performance - Vanilla - Fees}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{Performance - Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{Performance - Crash Resistant - Fees}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\pagebreak
+\newpage
+
+NOTE: 
+USE THE TRADED VOLUME * INSTRUMENT PRICE TO FIND THE AMOUNT OF VALUE LOST DUE TO THE VOLA PREMIUM
+
 \begin{equation}

### 2024-01-13 compare.py
t test

@@ -1,0 +1,68 @@
+# Compare Performance of analyzeZeroBetaStraddles
+
+import pandas as pd
+import numpy as np
+from pathlib import Path
+import matplotlib.pyplot as plt
+import pdb
+from scipy import stats 
+from scipy.stats import ttest_1samp
+import time
+
+p1 = 'out/vanilla/fees/performance_overview.csv'
+p2 = 'out/vanilla/no_fees/performance_overview.csv'
+
+vanilla_fee = pd.read_csv(p1)
+vanilla_no_fee = pd.read_csv(p2)
+
+# InterestRates start on this date
+#print('Restricting date!')
+#vanilla_fee['date'] = pd.to_datetime(vanilla_fee['day'])
+#dat = vanilla_fee.loc[vanilla_fee['day'] >= '2019-05-01']
+#pdb.set_trace()
+
+for df in [vanilla_fee, vanilla_no_fee]:
+    df.replace([np.inf, -np.inf], np.nan, inplace=True)
+    df.dropna(subset=["combined_payoff_daily", "combined_ret_daily"], how="all", inplace=True)
+
+vanilla_fee[['combined_payoff']].describe()
+vanilla_no_fee[['combined_payoff']].describe()
+
+# Test significance
+out_path = 'out/vanilla/fees/density'
+Path(out_path).mkdir(parents=True, exist_ok=True)
+pdct = {}
+df = vanilla_no_fee.copy(deep = True)
+for mn in df['moneyness'].sort_values().unique():
+
+    fig = plt.figure(figsize = (20, 14))
+    higher = mn + 0.05
+    sub = df.loc[(df['moneyness'] <= higher) & (df['moneyness'] >= mn)]
+    sub['combined_ret_daily'].plot.kde()
+    plt.title('n = ' + str(sub.shape[0]))
+    plt.savefig(out_path + '/moneyness>=' + str(mn) + '&moneyness<=' + str(higher) + '.png')
+    t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
+    print(sub.describe())
+    print('Moneyness Level: ', mn)
+    print("T-statistic value: ", t_stat)
+    print("P-Value: ", p_value)
+    pdct[mn] = p_value
+    #time.sleep(3)
+
+print(pdct)
+
+# Cool! 
[…]

### 2024-01-14 compare.py
ttest ready

@@ -2,18 +2,66 @@
 
 import pandas as pd
 import numpy as np
-from pathlib import Path
+
 import matplotlib.pyplot as plt
 import pdb
+import time
+import csv
 from scipy import stats 
 from scipy.stats import ttest_1samp
-import time
+from pathlib import Path
 
-p1 = 'out/vanilla/fees/performance_overview.csv'
-p2 = 'out/vanilla/no_fees/performance_overview.csv'
+def ttest(dat, out_path):
+    """
+    Groups returns by levels of moneyness (in steps of 0.05)
+    performs kernel density estimation
+    performs a left-sided t-test on a population mean of 0
+    """
+
+    Path(out_path).mkdir(parents=True, exist_ok=True)
+    pdct = {}
+    df = dat.copy(deep = True)
+    for mn in df['moneyness'].sort_values().unique():
+
+        fig = plt.figure(figsize = (20, 14))
+        higher = round(mn + 0.05, 2)
+        sub = df.loc[(df['moneyness'] <= higher) & (df['moneyness'] >= mn)]
+        sub['combined_ret_daily'].plot.kde()
+        plt.title('n = ' + str(sub.shape[0]))
+        plt.xlim((-1, 1))
+        plt.savefig(out_path + '/moneyness>=' + str(mn) + '&moneyness<=' + str(higher) + '.png')
+        t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
+        print(sub.describe())
+        print('Moneyness Level: ', mn)
+        print("T-statistic value: ", t_stat)
+        print("P-Value: ", p_value)
+        pdct[mn] = p_value
+        #time.sleep(3)
+
+    print(pdct)
+
+    # Cool! 
+    sub = df.loc[(df['moneyness'] >= 0.95) & (df['moneyness'] <= 1.05)]
+    t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
+
+    with open(out_path + '/t-tests.csv', 'w') as f:  # You will need 'wb' mode in Python 2.x
+        w = csv.DictWriter(f, pdct.keys())
[…]

### 2024-01-14 written/paper.tex
second compressed table
third compressed table
added pvalue table

@@
 
-\title{Pricing Kernels and Risk Premia implied in Bitcoin Options}
+\title{Expected Option Returns and the risk-free Rate in Crypto Asset Markets}
 \author{Julian Winkel\footnote{International Research Training Group 1792;
@@
 \section{Introduction}
+Despite the ongoing attention that crypto assets receive and despite their ongoing integration into traditional markets, whereas the last example would be the SEC's approval of a range of Bitcoin Spot ETFs, fundamental questions about crypto asset markets remain unclear:
+How efficient are crypto asset markets relative to established, traditional markets such as equities? 
+Does a risk-free rate exist and if yes, how does it relate to the risk-free rate in established markets?
+Are derivatives, written on crypto assets, fairly priced or at least fairly priced relative to other derivatives?
+What do we know about the risk-return characteristics of crypto assets?
+We assess these fundamental questions and find that the methods required to conduct our analysis have been out in the open for long; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s.
+The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway and Bakshi et al in XZY year.
+
+We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
+We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness.
+We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., severe overpricings of at-the-money options.
+The effect holds after compensating for market crash insurance and transaction cost.
+We assess the deadeweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.
+
+Evidence for leverage effect?
+
+We constructs and evaluate the empirical performance of option portfolios, written on crypto assets such as Bitcoin and Ether, to allow model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
+
+What evidence or contradictions can we find?
+The precise and bespoke tailoring of risk-return characteristics through the use of options allows promising insights into the risk-return characteristics of crypto assets, such as Bitcoin and Ether.
+
+From our point of view, the primary question leading such research is the question of market efficiency.
+
+Due to the youth of the crypto asset option markets, the primary question foregoing such research is that of the efficiency of named market.
+Do the laws that govern equity option markets also apply to crypto asset option markets?
+Can we find empirical evidence or contradictions?
+
+- Is there a risk-free rate in crypto markets?
+- How efficient is the crypto (option) market compared to equity option markets?
 
@@
 
-This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option positions in the early 2000s.
+This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option portfolios in the early 2000s.
 
@@
 
+\section{Literature Review}
+
+\section{Methodology}
+
+\section{Data}
+
+We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
+The exchange started operations in July 2017. 
+Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates since (approx.) July 2019.
+
+- table of amount of transactions per group
+- plot: amount of transactions over time per group (crypto)
+
 \section{A Proxy for the risk-free Rate of Bitcoin and Ether}
@@
 As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
-Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
+Open Interest for Ether Perpetual Futurews contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
 
@@
 \begin{table}[ht]
-\begin{tabular}{llrrrrrrr}
+\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
 \hline
@@
 \# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 
-\begin{table}[]
-\begin{tabular}{llrrrrrrr}
+\begin{table}[ht]
+\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
+\hline
 \textbf{Exchange}                & \textbf{Symbol}    & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Expires in}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\hline
+\hline
 \# Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
@@
 \# XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & -                                  & 0.06\%                              & 3 months                                & -                                          & \$20,870,477.00
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 
-\begin{table}[]
-\begin{tabular}{llrrrrrrr}
+\begin{table}[ht]
+\resizebox{\textwidth}{!}{\begin{tabular}{llrrrrrrr}
+\hline
 \textbf{Exchange}                & \textbf{Symbol}    & \multicolumn{1}{l}{\textbf{Price}} & \multicolumn{1}{l}{\textbf{Index Price}} & \multicolumn{1}{l}{\textbf{Basis}} & \multicolumn{1}{l}{\textbf{Spread}} & \multicolumn{1}{l}{\textbf{Expires in}} & \multicolumn{1}{l}{\textbf{Open Interest}} & \multicolumn{1}{l}{\textbf{24h Volume}} \\
+\hline
+\hline
 \# Binance (Futures)             & ETHUSD\_240329     & \$2,300.60                         & 2228.81 USD                              & -3.121\%                           & 0.01\%                              & 3 months                                & \$72,215,240                               & \$16,326,927.83                         \\
@@
 \# XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & 0.06\%                             & 3 months                            & -                                       & \$20,870,477.00                            & \multicolumn{1}{l}{}
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 
+Solve for interest rates from
+
+\begin{equation}
+F_t = e^{r \tau} S_t
+\end{equation}
+
 funding_btc_vs_eth_annualized_zoom.png
@@
 \href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+We conduct a left-sided t-test to test for a population mean of zero. Values are rounded to 4 digits.
+
+\begin{table}[]
+\begin{tabular}{lllll}
+     & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\
+0.7  & 0.6088         & 0.5854          & 0.5845                 & 0.6078                  \\
+0.71 & 0.7993         & 0.7769          & 0.7762                 & 0.7987                  \\
+0.72 & 0.9943         & 0.9925          & 0.9925                 & 0.9943                  \\
+0.73 & 0.9348         & 0.9222          & 0.9222                 & 0.9348                  \\
+0.74 & 0.9997         & 0.9996          & 0.9996                 & 0.9997                  \\
+0.75 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.76 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.77 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.78 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.79 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.8  & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.81 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.82 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.83 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.84 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.85 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.86 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.87 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.88 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.89 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.9  & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.91 & 1.0            & 0.9998          & 0.9998                 & 1.0                     \\
+0.92 & 1.0            & 0.9968          & 0.9968                 & 1.0                     \\
+0.93 & 0.9984         & 0.9437          & 0.9437                 & 0.9984                  \\
+0.94 & 0.9669         & 0.6277          & 0.6277                 & 0.9669                  \\
+0.95 & 0.8817         & 0.3093          & 0.3093                 & 0.8817                  \\
+0.96 & 0.3229         & 0.0129          & 0.0129                 & 0.3229                  \\
+0.97 & 0.2143         & 0.0047          & 0.0047                 & 0.2143                  \\
+0.98 & 0.0082         & 0.0             & 0.0                    & 0.0082                  \\
+0.99 & 0.0002         & 0.0             & 0.0                    & 0.0002                  \\
+1.0  & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.01 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.02 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.03 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.04 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.05 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.06 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.07 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.08 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.09 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.1  & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.11 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.12 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.13 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.14 & 0.0172         & 0.0106          & 0.0106                 & 0.0172                  \\
+1.15 & 0.0484         & 0.0347          & 0.0347                 & 0.0484                  \\
+1.16 & 0.0563         & 0.0421          & 0.0421                 & 0.0564                  \\
+1.17 & 0.1889         & 0.1588          & 0.1587                 & 0.1887                  \\
+1.18 & 0.8503         & 0.8119          & 0.8115                 & 0.8499                  \\
+1.19 & 0.9906         & 0.9861          & 0.9859                 & 0.9905                  \\
+1.2  & 0.8888         & 0.8593          & 0.8562                 & 0.8862                  \\
+1.21 & 0.9796         & 0.9713          & 0.9701                 & 0.9787                  \\
+1.22 & 0.986          & 0.9805          & 0.9793                 & 0.985                   \\
+1.23 & 0.9627         & 0.951           & 0.9464                 & 0.959                   \\
+1.24 & 0.9969         & 0.9954          & 0.9945                 & 0.9962                  \\
+1.25 & 0.9976         & 0.9966          & 0.9957                 & 0.9969                  \\
+1.26 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+1.27 & 0.9999         & 0.9999          & 0.9998                 & 0.9999                  \\
+1.28 & 0.9996         & 0.9995          & 0.9993                 & 0.9995                  \\
+1.29 & 0.9939         & 0.9932          & 0.9919                 & 0.9927                  \\
+1.3  & 0.9436         & 0.9403          & 0.9334                 & 0.937                  
+\end{tabular}
+\end{table}
 

### 2024-01-19 written/paper.tex
minor written

@@
 
-\title{Expected Option Returns and the risk-free Rate in Crypto Asset Markets}
+\title{Empirical Option Returns and the risk-free Rate in Crypto Asset Markets}
 \author{Julian Winkel\footnote{International Research Training Group 1792;
@@
 The effect holds after compensating for market crash insurance and transaction cost.
-We assess the deadeweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.
-
-Evidence for leverage effect?
+We assess the deadweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.
 
@@
 \section{Methodology}
+
+- scrape 8h funding rate continuously and use as market-interest rate
+
+- scrape all BTC, ETH transactions from Deribit 
+- load data, clean
+- center on settlement date for each day (10am UTC)
+- for each option, find the pendant via put-call-parity
+- calculate the beta of each put, call
+- build zero-beta straddles by finding weights such that the sum of weights is zero
+- assess empirical, daily returns of the straddle
+- build boxplots over levels of moneyness
+- KDE --> t-distribution
+- perform t-test for population mean of 0
 
@@
 
+\section{Results}
+
+We find the returns of the zero-beta-straddles to be t-distributed and conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
+The null hypothesis is not rejected for all models, vanilla and crash-resistant, for ITM and OTM options.
+Conversely, the null hypothesis is firmly rejected on a high significance level for ATM options.
+Therefore, we accept the alternative hypothesis of an underperformance for ATM options.
+Consequently, we find a similar result to Shumway and Bakshi - that is the existence of a premium for ATM contracts.
+We figure the premium to be a volatility premium since a straddle's payoff depends on the relationship of Implied Volatility to Realized Volatility. 
+Unsurprisingly, the size of the premium in crypto markets is higher than the counterpart in equity markets - we figure that the reason is the higher risk in crypto markets, particularly via volatility and counterparty risk.
+Furthermore, there are mostly retailers present in the crypto option market.
+Some professional liquidity providers exist, but they remain few and therefore another reason for the premium's size could be illiquidity.
+
+- the premium is larger when tau is small.
+
 \begin{minipage}{\textwidth}
@@
 
-\begin{table}[]
-\begin{tabular}{lllll}
-     & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\
+\section{Conclusion}
+
+Further research: 
+- Evidence for leverage effect
+
+%\begin{minipage}{\textwidth}
+%    \centering
+  %  \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
+    %\captionof{figure}{Performance - Vanilla - No Fees}
+    %\centering
+    %\includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
+     %\captionof{figure}{Performance - Vanilla - Fees}
+
+%\end{minipage}
+%\begin{minipage}{\textwidth}
+%    \centering
+%    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
+%    \captionof{figure}{Performance - Crash Resistant - No Fees}
+ %   \centering
+ %   \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
+ %    \captionof{figure}{Performance - Crash Resistant - Fees}
+
+%\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+%\label{ATM Term Structure}
+%\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\begin{table}[ht]
+\hline
+\resizebox{\textwidth}{!}{\begin{tabular}{lllll}
+  Moneyness    & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\
+\hline
+\hline
 0.7  & 0.6088         & 0.5854          & 0.5845                 & 0.6078                  \\
@@
 1.3  & 0.9436         & 0.9403          & 0.9334                 & 0.937                  
-\end{tabular}
+\end{tabular}}
 \end{table}
@@
 USE THE TRADED VOLUME * INSTRUMENT PRICE TO FIND THE AMOUNT OF VALUE LOST DUE TO THE VOLA PREMIUM
-
-\begin{equation}
-C_t = e^{-r \tau} \mathbb{\sf{E}}^Q[\psi(S_T)] = e^{-r, \tau}  \int_{-\infty}^\infty \psi(u) f_t^Q(u) du
-\end{equation}
-
-where the PK \(K(\cdot)\) is defined as \(\frac{q(\cdot)}{p(\cdot)}\)
-and for simplicity of notation we write \(q(\cdot)\) for
-\(\frac{\partial Q}{\partial t}(\cdot)\) and drop the sequence \(r_t\).
-
-\section{Nonparametric Estimation of State Price Densities}
-
-\subsection{Derivation}
-
-\subsection{Local Polynomial Estimation of the IV Surface}
-
-Assume that the implied volatilites have some noise added (Huynh et al.
-2002; Rookley 1997).
-
-\begin{equation}
-\sigma (M, \tau) = g(M, \tau) + \sigma^{*}(M, \tau)  \varepsilon
-\end{equation}
-
-with a standardized error random variable \(\varepsilon\), moneyness
-\(M\), \(\tau\) and \(\varepsilon\) independent and
-\(\sigma^{*}(M, \tau)\) being the scaling of the error term given \(M\)
-and \(\tau\). Suppose \(g\) is smooth, i.e.~it can be approximated using
-Taylor's Theorem.
-
-Taylor expansion of \(g\) in a neighborhood of \((M_0, \tau_0)\):
-\begin{equation}
-\begin{aligned}
-g(M, \tau) = g(M_0, \tau_0) +
-\frac{\partial g}{\partial M}(M-M_0) + 
-\frac{1}{2} \frac{\partial^2 g}{\partial M^2}(M-M_0)^2 + \\
-\frac{\partial g}{\partial \tau}(\tau - \tau_0) + 
-\frac{1}{2} \frac{\partial^2 g}{\partial \tau^2}(\tau - \tau_0)^2 + \\ 
-\frac{\partial^2 g}{\partial M \partial \tau}(M-M_0)(\tau - \tau_0)
-\end{aligned}
-\end{equation}
-
-The functional relationship between the IV surface \(\sigma\) and \(M\)
-and \(\tau\) can now be approximated using a Weighted Least Squares
-Estimator (WLSE), minimizing the objective function
-
-\begin{equation}
-\operatorname{arg}\, \underset{\beta}{\operatorname{min}}{(\sigma - X\beta)^\top W (\sigma - X\beta)}
-\end{equation}
-
-where
-\(W = \text{diag}(\mathcal{K}_{h_m, h_\tau}(M_j - M_0, \tau_j - \tau_0))\)
-for a Gaussian kernel \(\mathcal{K}\) with bandwidths \(h_m\) and
-\(h_\tau\). \(\sigma\) is the \(n \times 1\) vector of observed implied
-volatilities, \(\beta\) is the vector of the local polynomial
-coefficients.
-
-\[
-X = 
-\begin{pmatrix}
-1 & (M_1 - M_0) & (M_1 - M_0)^2 & (\tau_1 - \tau_0) & (\tau_1 - \tau_0)^2 & (M_1 - M_0) (\tau_1 - \tau_0) \\
-\vdots & \vdots & \vdots & \vdots & \vdots & \vdots & \\
-1 & (M_n - M_0) & (M_n - M_0)^2 & (\tau_n - \tau_0) & (\tau_n - \tau_0)^2 & (M_n - M_0) (\tau_n - \tau_0) \\
-\end{pmatrix}
-\]
-
-The resulting WLSE is
-
-\begin{equation}
-\hat{\beta} = (X ^\top WX)^{-1}X ^\top W \sigma
-\end{equation}
-
-Following Härdle et al. (2014), a window of the last 500 daily returns
-(based on \(\tau\)) is used to calculate a nonparametric Kernel Density
-Estimator for the PD.\\
-\href{https://quantinar.ro/course/103/statistics-of-financial-markets}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/quantinar_logo.png}}\,Chapter 24}
-
-\section{Literature Review}
-
-Breeden and Litzenberger (1978) derive SPDs using Arrow-Debreu prices
-and Butterfly Spreads. Their paper was the cornerstone for the now
-existing vast literature on estimation of SPDs. Without requiring a
-parametric form for SPDs, Rookley (1997) who developed a nonparametric
-estimation method. IV skews are estimated by decomposing the functional
-relationship between IV, moneyness and time-to-maturity \(\tau\). In
-this manner it is possible to derive the SPD at every point in a robust
-way. Aı̈t-Sahalia et al. (2001) estimate PKs from S\&P500 options data
-and the according return series in order to assess the efficiency of the
-options market. Departures from SPD and PD are used to identify
-inefficient pricing. They design a trading strategy, exploiting the
-skewness and kurtosis of the densities. The strategy is shown to have a
-high Sharpe Ratio. Grith et al. (2009) propose a systematic modeling
-approach to study the evolution of PKs over time. With European DAX
-data, a series of empirical PKs is estimated from 2003 until 2006. While
-the risk-neutral density is inferred using Rookley's method, the PD is
-estimated with a GARCH model. A common shape is identified and
-deviations of the time varying EPKs are studied. The deviations between
-individual PKs are described using a set of parameters for horizontal
-and vertical shifts. The relationship between PKs and Arrow-Pratt
-measure of Absolute Risk Aversion (ARA) give insight into investor's
-risk aversion. In a related research, Härdle et al. (2014) derive
-bootstrap-based confidence bands for nonparametrically estimated PKs.
-
-Inverse Options, meaning options settled in kind of the underlying, are
-dominant in the crypto world. Settlement of BTC options in terms of BTC
-changes the payoff function of the option from \(\max(S_T - K; 0)\) to
-\(\max(\frac{S_T - K}{S_T}; 0)\) and thus changes the contract's net
-present value. Alexander and Imeraj (2021) adjust Black-Scholes prices
-and hedge ratios to inverse options. However, it is argued that traders
-are erroneously applying vanilla Black-Scholes valuation instead of the
-corrected prices - perhaps because of being unaware of the concept. We
-have decided to use with the standard, non-inverse Black Scholes pricing
-for multiple reasons. Alexander and Imeraj (2021) argue that traders are
-perhaps unaware of the difference. Since we are inferring investor
-expectations, we figure that it is more appropriate to infer pricing
-kernels under the same Black Scholes prices that the investors use.
-Additionally, it is likely that many traders actually hedge their
-overall Bitcoin exposure. This would negate the ``inverse'' part of the
-option. Furthermore, reviewing the differences in pricing compared to
-the adjusted prices, we find that the difference is small in the absence
-of extreme moves in the underlying. This was not the case in the time
-period under consideration.
-
-Hou et al. (2020) price BTC options under an SVCJ model. Their results
-emphasize the tail risk introduced by jumps in the underlying. Jumps in
-particular introduce market incompleteness, but anonymity of
-transactions may be relevant as well. Chen and Vinogradov (2021) derive
-PKs and the impact of market incompleteness on risk premia. They state
-that a key property of cryptocurrency valuation is the user's anonymity
-(or pseudonymity), which is simultaneously the source of value and
-incompleteness in the respective market. They argue that hedging an
-anonymous transaction would require an identity disclosure. This
-contradiction may introduce an effectively unhedgeable event.
 
@@
 
-\section{Volatility}
-
-In accordance with Masset (2011) and Eraker (2021), the list of
-well-established stylised facts on volatility in traditional markets
-include horizontal dependence of volatility, leverage effect, the
-volatility premium and extreme events. Horizontal dependence of
-volatility describes the tendency of local volatility clusters and the
-tendence to mean-reversion. Both properties can be observed in the 7 day
-rolling volatility. Sudden spikes in realized volatility form clusters
-and are often followed by similar drops. The leverage effect can be
-measured as a negative correlation between returns and volatility.
-Phases of negative returns coincide with high volatility and vice versa.
-The Pearson correlation between the underlying and realized volatility
-is -12.59\%. The Pearson correlation between the underlying and the bid
-(ask) IV is -16.11\% (-13.05\%). Due to the low absolute values of
-correlation, the existence of a leverage effect is unlikely. However,
-the sign matches the direction of a leverage effect. Considering the
-large share of retailers with easy access to leverage, the lack of
-significance is a surprising result. It is well known that, in general,
-the IV exceeds the unconditional annualized standard deviation. This is
-displayed in Figure \ref{fig: iv_comparison}. The difference between the
-implied and realized volatility is commonly referred to as volatility
-premium. The mean 7 day rolling volatility is 70.96\%, whereas the mean
-IV at the bid and ask are 85.28\% and 93.57\%. Spikes in realized
-volatility rarely exceed the ask of the IV. Consequently, the volatility
-premium is shown to be substantial throughout the regarded time period.
-Fat-tail events are priced in due to the classic volatility skew. This
-is depicted in Figure \ref{fig: emp_ivsmile}, the empirical volatility
-skew.
-
-Since the data are high frequency order book snapshots with substantial
-bid-ask spreads, we must address the issue of Market Microstructure
-Noise (MMN). A simple estimate of realized volatility would increase
-with our sample due to order competition within the spread. We resolve
-the issue of MMN in our calculation of realized volatility by taking the
-arithmetic mean after aggregating the implied volatility of bids and
-asks on a daily base. Therefore the frequency is matching the underlying
-BTC index. The formula for annualized, realized volatility of price
-\(p\) over a window of \(w\) days is
-
-\begin{equation}
-\sigma_w = \sqrt{\frac{1}{w}\sum_{t=1}^w{(\log{p_t} - \log{p_{t-1})}^2}} \sqrt{\frac{365}{w}}
-\end{equation}
-
-Annualization is based on 365 days since Bitcoin options are traded
-continuously on Deribit.
-
-The term structure itself is easier to assess when regarding ATM-options
-in a series of dates (Figure 6). ATM-options are defined as those
-options, whose moneyness falls in the interval \([0.9, 1.1]\). A typical
-term structure of the Bitcoin options reveals a high level of implied
-volatility for shorted-dated options. For options with a
-time-to-maturity of three days or more, implied volatility drops sharply
-compared to the initial level. Naturally, IV is increasing with
-time-to-maturity.
-
-\begin{center}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/iv_comparison_up.png}
-\caption[Implied Volatiliy vs. Realized Volatility on Deribit]%
-{Implied volatility vs. realized volatility. Realized volatility is annualized and regarded in a 7 day window.
-IV is calculated as the average of observed orderbooks at the bid and ask. Described data filters apply. {\color{blue} Ask IV}, {\color{green} Bid IV}, {\color{red} 7 Day Rolling Volatility}.}
-\label{fig: iv_comparison}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/src/vola.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Volatility}
-\end{figure}
-\end{center}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/vola_2021-05-23.png}
-\caption[Empirical Volatility Surface]{Volatility Skew shown in the empirical Volatility Surface on 2021-05-23}
-\label{fig: emp_ivsmile}
-\end{figure}
-\end{centering}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/vola_2021-09-08.png}
-\caption[Empirical Volatility Surface 2]{Volatility Skew shown in a calmer period on 2021-09-08}
-\label{fig: emp_ivsmile2}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/src/vola_plots.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,IV Smile}
-\end{figure}
-\end{centering}
-
-\begin{minipage}{.5\textwidth}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-010.08.png}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-020.08.png}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-030.08.png}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-040.08.png}
-
-\end{minipage}
-\begin{minipage}{0.5\textwidth}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-050.08.png}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-060.08.png}
-    \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-070.08.png}
-        \centering
-    \includegraphics[width=2.8in]{/Users/julian/src/up/spd/plot/term_structure_atm_options_on_-2022-01-080.08.png}
-
-\end{minipage}
-    \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
-
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-
-\pagebreak
-\newpage
-\section{Empirical Pricing Kernels}
-
-Instruments are grouped by time-to-maturity in order to summarize the
-findings. All instruments with less than one week to maturity are
-classified as having less than one, between one and two, between two and
-three, between three and four and between five and eight weeks to
-maturity. We typically observe U-shaped PKs for short-term maturities.
-In a similar fashion to the oil market, investors perceive short-term
-price changes in any direction as undesirable and prefer to hedge their
-risk (Christoffersen et al. 2021). For short-dated instruemnts, option
-writers are asking for substantial risk premia in order to reflect
-unhedgeable risks, such as jumps in the underlying (Hou et al. 2020).
-
-We find a differnet shape for longer-dated instruments. Typically, PKs
-in traditional markets are monotonically decreasing. This results from
-human risk aversion; investors are willing to insure themselves against
-losses and have a preference for smooth consumption curves. However, PKs
-outside of index options markets are not well studied (Cuesdeanu and
-Jackwerth 2018). Grith et al. (2009) compartmentalize a pricing kernel
-in two segments around a possible breakpoint. Testing an unrestricted
-model against GMM estimates of the restricted one, they reject
-monotonicity of the empirical PK in four out of five cases (performing a
-D-test). The phenomenon of having a decreasing slope, although with
-locally increasing sections in empirical PKs is called the pricing
-kernel puzzle. We observe a similar behavior and extend the existing
-literature on the pricing kernel puzzle to a new asset class.
-
-Since the empirical PKs for short-dated instruments are U-shaped, we
-figure that investors are willing to pay a high risk premium in order to
-insure immediate price risks. With an increasing maturity of the
-instrument, the shape of the empirical PK resembles a ``W'' or
-``tilde''. This corresponds to a a lesser willingness to pay a risk
-premium.\\
-The dynamic of the empirical PKs also reveals the existence of a
-time-varying risk premium in BTC markets. The observed PK shapes are
-closely aligned with the results reported in Cuesdeanu and Jackwerth
-(2018). However, their object of study are traditional markets, such as
-major indices which are highly correlated with aggregate wealth. We
-conclude that, due to the similarities of the empirical PKs, BTC is well
-on its way to becoming an established asset class. It may prove to be
-much rather a store of value than it is currently given credit for.
-
-Apart from the discussion of results, deviations between PD and SPD can
-be interpreted as trading opportunities. (Blaskowitz et al. 2004) design
-and evaluate trading strategies based on deviations between PD and SPD.
-Estimated PKs could be used by traders employing so-called Skewness or
-Kurtosis trades. Nevertheless, traders must recognize the hidden cost of
-employing such strategies in terms of substantial hedging cost, e.g.~in
-the form of volatility and large spreads.
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=0.png}
-\caption[Empirical Pricing Kernel - 0 Weeks to Expiration]{Pricing Kernels with less than one Week to Expiration}
-\end{figure}
-\end{centering}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=1.png}
-\caption[Empirical Pricing Kernel - 1 Week to Expiration]{Empirical Pricing Kernel - 1 Week to Expiration}
-\end{figure}
-\end{centering}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=2.png}
-\caption[Empirical Pricing Kernel - 2 Weeks to Expiration]{Empirical Pricing Kernel - 2 Weeks to Expiration}
-\end{figure}
-\end{centering}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=3.png}
-\caption[Empirical Pricing Kernel - 3 Weeks to Expiration]{Empirical Pricing Kernel - 3 Weeks to Expiration}
-\end{figure}
-\end{centering}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=4.png}
-\caption[Empirical Pricing Kernel - 4 Weeks to Expiration]{Empirical Pricing Kernel - 4 Weeks to Expiration}
-\end{figure}
-\end{centering}
-
-\begin{centering}
-\begin{figure}
-\includegraphics[width=1\textwidth]{/Users/julian/src/up/spd/plot/Pricing Kernel_over_time_nweeks=8.png}
-\caption[Empirical Pricing Kernel - 5-8 Weeks to Expiration]{Empirical Pricing Kernel - 5-8 Weeks to Expiration}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-\end{figure}
-\end{centering}
-
-\pagebreak
-\newpage
-
-\section{Bootstrap-based Confidence Bands}
-
-Having computed a large set of empirical PKs with varying maturities, it
-should be ensured that the observed features are not mere artefacts. A
-useful tool to assess the validity of our estimated PKs are
-bootstrap-based confidence bands. Following the derivation of Härdle et
-al. (2014), confidence bands at any confidence level can be derived via
-the ``wild bootstrap method''. Figure
-\ref{fig:Bootstrapped Confidence Bands - 2 Days} until Figure
-\ref{fig:Bootstrapped Confidence Bands - 84 Days} are depicted
-exemplarily for the whole set. Confidence bands are tighter around the
-PKs when time to maturity increases. PKs are also flatter with growing
-time to maturity.
-
-The concept of bootstrapping PK can be introduced by linearization of
-the PK. Stochastic deviation of the PK can be linearised into a
-stochastic part, containing the estimator of the SPD and a deterministic
-part containing the expectation of the physical density. Convergence of
-both parts can be proven separately.
-
-\[
-\widehat{K}(x) = \frac{\widehat{q}(x)}{\widehat{p}(x)} 
-\]
-
-\[
-\begin{aligned}
-\underset{x \in E}{\operatorname{sup}} \lvert \widehat{K}(x) - K(x) \rvert = \underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}(x) - q(x)}{p(x)} - \frac{\widehat{p}(x) - p(x)}{p(x)} * \frac{q(x)}{p(x)} - \frac{\{\widehat{q}(x) - q(x)\} \{\widehat{p}(x) - p(x)\} }{p^2(x)} \rvert  \\
-+ {\scriptstyle \mathcal{O}_p}[\operatorname{max}((n_p h_{n_p}/\log)^{-1/2} + h^2_{np},h_{n_q}^{-2} \{ n_q h_{n_q} / \log{n_q} \}^{-1/2} + h^2_{n_q})]
-\end{aligned}
-\]
-
-Consider the leading term of \[
-\underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}(x) - q(x)}{p(x)} \rvert
-\]
-
-Resample data from the smoothed bivariate distribution of strike and
-moneyness (X,Y)
-
-\[
-{\widehat{f}(x,y)} = \frac{\widehat{\sigma_X}}{n_q h^2_{n_q}\widehat{\sigma_Y}} 
-\Sigma_{i=1}^{n_q} K
-\{ 
-\frac{X_i - x}{h_{n_q}}, 
-\frac{(Y_i - y)\widehat{\sigma_X}}{h_{n_q}\widehat{\sigma_Y}}
-\}
-\]
-
-Using the resampled data, calculate the bootstrap analogue
-
-\[
-\underset{x \in E}{\operatorname{sup}} \lvert \frac{\widehat{q}^*(x) - \widehat{q}(x)}{p(x)} \rvert
-\]
-
-where
-\(\underset{x \in E}{\operatorname{sup}} \lvert\widehat{q}^*(x) - \widehat{q}(x) \rvert\)
-converges to the Gumbel distribution at an unfortunately slow rate of
-\(\frac{1}{\log n_q}\) (Hall 1991).
-
-\begin{minipage}{.5\textwidth}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0055.pdf}
-    \captionof{figure}{2 Days to Maturity.}
-    \label{fig:Bootstrapped Confidence Bands - 2 Days}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0192.pdf}
-    \captionof{figure}{7 Days to Maturity.}
-    \label{fig:Bootstrapped Confidence Bands - 7 Days}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0384.pdf}
-    \captionof{figure}{14 Days to Maturity.}
-    \label{fig:Bootstrapped Confidence Bands - 14 Days}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0575.pdf}
-    \captionof{figure}{21 Days to Maturity.}
-    \label{fig:Bootstrapped Confidence Bands - 21 Days}
-
-\end{minipage}
-\begin{minipage}{0.5\textwidth}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.0767.pdf}
-    \captionof{figure}{28 Days to Maturity.}
-    \label{fig:Bootstrapped Confidence Bands - 28 Days}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.1534.pdf}
-        \captionof{figure}{56 Days to Maturity.}
-    \label{fig:Bootstrapped Confidence Bands - 56 Days}
-    \centering
-    \includegraphics[width=3.0in]{/Users/julian/src/up/spd/plot/EPK_2021-12-31_0.2301.pdf}
-        \captionof{figure}{84 Days to Maturity. \color{red}{Empirical Pricing Kernels} with \color{blue}{bootstrapped Confidence Bands} on 2021-12-31.}
-    \href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-    \label{fig:Bootstrapped Confidence Bands - 84 Days}
-\end{minipage}
-
-\pagebreak
-\newpage
-
-\section{Conclusion}
-
-Empirical PKs have been estimated using Rookley's Method on a dataset of
-order book snapshots from Deribit, the leading BTC options market.
-Bootstrap-based confidence bands have been estimated in order to
-validate the results.
-
-We assess the presence of well-established stylized facts of volatility
-in the BTC market. We find horizontal dependence of volatility, meaning
-that volatility tends to cluster and revert to the mean. The difference
-between implied and realized volatility, commonly referred to as the
-volatility premium, is substantial. Realized volatility rarely exceeds
-the implied volatility. The IV term structure is found to be
-traditional. Despite market participant's easy access to leverage, we
-cannot confirm the existence of a leverage effect.
-
-Our analysis extends the literature to a new asset class and contributes
-to the pricing kernel puzzle. We are able to replicate empirical results
-from the analysis of PKs in traditional markets, which are highly
-correlated with aggregate wealth. Their similarity to PKs estimated from
-BTC options indicates that BTC is becoming an established asset class.
-
-Furthermore, our analysis sheds light on the BTC valuation and
-risk-aversion of the retail traders. BTC option traders mostly consist
-of retailers who are heterogeneous in their risk profile. The price of
-short-dated instruments includes a high risk premium. Such instruments
-reflect the anticipation of jumps in the underlying. These instruments
-would be traded by either very risk-averse or risk-affine traders.
-Long-dated instruments are employed as classic hedging instruments.
-While a substantial risk premium is paid by traders in order to insure
-themselves against falling prices, they are additionally (but to a
-lesser degree) insuring themselves against sharply rising prices. Thus
-investors are also hedging their risk of being priced out of a dynamic
-market.
-
-Several extensions of the presented research are available for the
-future. Among those, we would find an extended dataset insightful, that
-could support estimation of PKs and their evolution over a longer time
-frame and possibly describe the convergence to the PKs of established
-markets. It would also be interesting to analyze the evolution of PKs
-around stress events in order to get further insights into investor risk
-aversion, anticipation of such events and trading opportunities.
-
 \section{References}

### 2024-01-21 written/paper.tex
minor

@@
  \medskip
- \textbf{Keywords:} Bitcoin, Deribit, pricing kernel, risk aversion, speculation, hedging  \\
+ \textbf{Keywords:} Bitcoin, Ether, Deribit, risk, risk premium, volatility premium, option, hedging  \\
  \indent \textbf{JEL Classification:} C14, C50, G10  \\
@@
 \section{Introduction}
-Despite the ongoing attention that crypto assets receive and despite their ongoing integration into traditional markets, whereas the last example would be the SEC's approval of a range of Bitcoin Spot ETFs, fundamental questions about crypto asset markets remain unclear:
+Despite the ongoing integration into established markets (whereas the last example would be the SEC's approval of a range of Bitcoin Spot ETFs), fundamental questions about crypto asset markets remain unclear:
 How efficient are crypto asset markets relative to established, traditional markets such as equities? 
@@
 Are derivatives, written on crypto assets, fairly priced or at least fairly priced relative to other derivatives?
-What do we know about the risk-return characteristics of crypto assets?
-We assess these fundamental questions and find that the methods required to conduct our analysis have been out in the open for long; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s.
+We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s.
 The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway and Bakshi et al in XZY year.
@@
 We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness.
-We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., severe overpricings of at-the-money options.
+We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., high premia.of at-the-money options.
 The effect holds after compensating for market crash insurance and transaction cost.
-We assess the deadweight loss due to overpricings and propose a simple trading strategy that exploits this partciular inefficiency.
+We assess the deadweight loss due to observed risk premia and propose a simple trading strategy that exploits this particular inefficiency.
 
 We constructs and evaluate the empirical performance of option portfolios, written on crypto assets such as Bitcoin and Ether, to allow model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
-
-What evidence or contradictions can we find?
-The precise and bespoke tailoring of risk-return characteristics through the use of options allows promising insights into the risk-return characteristics of crypto assets, such as Bitcoin and Ether.
-
-From our point of view, the primary question leading such research is the question of market efficiency.
-
-Due to the youth of the crypto asset option markets, the primary question foregoing such research is that of the efficiency of named market.
-Do the laws that govern equity option markets also apply to crypto asset option markets?
-Can we find empirical evidence or contradictions?
-
-- Is there a risk-free rate in crypto markets?
-- How efficient is the crypto (option) market compared to equity option markets?
 
@@
 \href{quantinar.com}{quantinar.com}.
-
-\section{Literature Review}
 
@@
 
+In accordance with Shumway, we follow the argument that any beta-neutral portfolio should yield the risk-free rate.
+We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so, that the sum of option betas yields zero.
+The underlying data are executed transactions.
+All option greeks remain constant except time-to-maturity.
+Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time.
+All options are bought and held until settlement at 10am UTC.
+To match always a call and a put with an equal strike price for a straddle, we use Put-Call-Parity to ensure the existence of each straddle.
+The empirical performance of the resulting zero-beta straddles is assessed on a daily base.
+
 \section{Data}
@@
 \section{A Proxy for the risk-free Rate of Bitcoin and Ether}
+
+Another possibility: Staking
 
@@
 
+- report average returns for options grouped per strike (and overall)
+
 \begin{minipage}{\textwidth}

### 2024-01-23 written/paper.tex
writing methodology section. some prints for ana.

@@
 We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
-We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for particular levels of moneyness.
+We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for at-the-money instruments.
 We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., high premia.of at-the-money options.
@@
 
-In accordance with Shumway, we follow the argument that any beta-neutral portfolio should yield the risk-free rate.
-We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so, that the sum of option betas yields zero.
+We follow the argument that any beta-neutral portfolio should yield the risk-free rate.
+We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
+The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
+The weight $\theta$ is found by solving Equation 2 through Equation 3.
+The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4.
 The underlying data are executed transactions.
@@
 All options are bought and held until settlement at 10am UTC.
-To match always a call and a put with an equal strike price for a straddle, we use Put-Call-Parity to ensure the existence of each straddle.
+We match our universe of straddles as follows:
+Per definition, a straddle exists of a call and a put with similar strike and maturity.
+We construct the set of empirical straddles by iterating over our list of executed calls and puts.
+For each call (put), we use Put-Call-Parity to complete the straddle.
 The empirical performance of the resulting zero-beta straddles is assessed on a daily base.
+We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
+For each level of moneyness m, we construct an interval $[m, m + 0.05]$.
+We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
+We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
+
+- Formulas for the weights!
+
+Straddle Return $r_v$￼, Share of Straddle’s value in Call Options ￼$\theta$,
+Call and Put market Beta ￼$\beta_c$, $\beta_p$.
+
+\begin{equation}
+r_v = \theta r_c + (1-\theta)r_p
+\end{equation}
+
+\begin{equation}
+\theta \beta_c + (1-\theta)\beta_p = 0\\
+\end{equation}
+
+\begin{equation}
+\theta = \frac{-\beta_p}{\beta_c - \beta_p}\\
+\end{equation}
+
+\begin{equation}
+\beta_c = \frac{s}{C} \Delta \beta_s\\
+\end{equation}
+
+We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events.
+Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
+Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
+Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
+Maybe make a summary of the relationship between ATM and 20\% OTM premium.
+
+The performance of the vanilla and crash-resistant straddles is evaluated with and without fees.
+Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs.
+The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
+Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
+Consequently, the trading fee for one option spread would be the lesser of 0.0003 Bitcoin or 12.5\% of the more expensive option price.
+All fees are converted into USD based on the BTC/USDT exchange rate around settlement time.
 
@@
 - plot: amount of transactions over time per group (crypto)
+
+We impose a maximum IV of 2.5
 
@@
 
+The actual annualized returns of such a carry trade would be
+
+Table:
+
+Year, Currency, Exchange, Annual Return
+
 funding_btc_vs_eth_annualized_zoom.png
@@
 We conduct a left-sided t-test to test for a population mean of zero. Values are rounded to 4 digits.
+
+Compare to weekly 0.5\% loss observed in equity options.
 

### 2024-01-23 analyzeZeroBetaStraddles.py

@@ -74,7 +74,7 @@ def get_synthetic_options(existing_options, fotm, move_strike_call = 1.2, move_s
     return missing_options
 
 
-def portfolio_calculations(pf_df, weight, long):
+def portfolio_calculations(pf_df, weight, is_long):
     """
     pf_df: call_df, put_df
     weight from straddle_weight
@@ -85,7 +85,7 @@ def portfolio_calculations(pf_df, weight, long):
     pf_df['weight'] = weight
     
     pf_df['cost_base'] = pf_df['weight'] * (pf_df['instrument_price'])
-    if long:
+    if is_long:
         pf_df['payoff'] = pf_df['instrument_price_on_expiration'] - pf_df['instrument_price'] 
         pf_df['direction'] = 'long'
     else:
@@ -263,12 +263,14 @@ def analyze_portfolio(dat, week, iv_var_name, center_on_expiration_price, first_
             # Restrict max Payoff with the FOTM Strike (e.g. 2000)
             # Consider Cost of FOTM Option
 
-            call_df = portfolio_calculations(call_df, call_weight, False)            
-            put_df = portfolio_calculations(put_df, put_weight, False)
+            # Change to accept parent parameter of is_long
+            not_long = not long
 
-            fotm_call_df = portfolio_calculations(fotm_call, call_weight, True)
-            fotm_put_df = portfolio_calculations(fotm_put, put_weight, True)
+            call_df = portfolio_calculations(call_df, call_weight, long)            
+            put_df = portfolio_calculations(put_df, put_weight, long)
 
+            fotm_call_df = portfolio_calculations(fotm_call, call_weight, not_long)
+            fotm_put_df = portfolio_calculations(fotm_put, put_weight, not_long)
             
             cols = ['instrument_name', 'index_change_rel', 'spot', 'strike', 'moneyness', 'tau', 'instrument_price', 'instrument_price_on_expiration', 'direction', 'beta', 'cost_base','payoff', 'weight', 'weighted_payoff', 'ret', 'weighted_ret']
             call_sub = call_df[cols]
@@ -281,6 +283,7 @@ def analyze_portfolio(dat, week, iv_var_name, center_on_expiration_price, first_
                 n_options = 2
                 btc_fee_per_option = 0.0003
                 fees_abs = n_options * btc_fee_per_option * index_price
+                print("make sure that fees are max 12.5% of option price!")
             else:
                 fees_abs = 0
[…]

### 2024-02-11 written/paper.tex
writing

@@
 The exchange started operations in July 2017. 
-Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates since (approx.) July 2019.
+Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates for the perpetual future of Bitcoin and Ether since (approx.) July 2019.
+
+Two conditions are imposed on the option data:
+1) The maximum IV is 2.5 and the minimum IV is 0.1.
+2) In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
+3) Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
+4) We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
+
+The purpose of the first restriction is to impose a fair bound to the options that is independent of liquidity levels.
+For illiquid options, occurrences of bid prices at 0\% IV and ask prices of 500\% may occur.
+The purpose the second restriction of unique usage is to prevent a bias due to the possible more frequent trading of certain options.
+Generally, we observe that instruments with short maturity are traded more frequently.
+Yet, this could also be understood as cheaper instruments trading more frequently since (Black-Scholes) option prices increase with time-to-maturity.
+
+Bitcoin only:
+We drop 0.9\% of observations due to restriction 1)
+We drop 17\% of observations due to restriction 3)
+Overall, we have 5,028,945 observations. Post filtering, 4,150,778 observations remain in the set.
+
+Ethereum: 
+?!
+Todo
+
+Regarding data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
+Indeed, using actual transaction data instead of orderbook data removes the threat of wash trading (etc) to our data.
+The most likely negative factor that could affect our data quality is wash trading.
+We assess the risk of wash trading as follows:
+
+"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." (from: https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf)
+
+We asses the risk of wash trading contaminating our data set as low.
+The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
+At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot 12 USD.
+Such fees, even without consideration of spreads, make wash trading from a trader's perspective entirely infeasible.
 
@@
 
-We impose a maximum IV of 2.5
-
 \section{A Proxy for the risk-free Rate of Bitcoin and Ether}
@@
 Evidently, there is no established risk-free rate in crypto (or digital asset) markets.
-In the absence of riskless bond, we refer to the next best thing as a proxy for the risk free rate, which is the replication of the market-implied yield through a position which only has liquidity risk and counterparty risk.
-To be fair, counterparty risk also exists for risk-free bonds.
-
+In the absence of riskless bond, we construct as a proxy for the risk free rate, which is the replication of the market-implied yield through a position which only has liquidity risk and counterparty risk.
 A large share of the trading volume in digital asset markets falls on the futures market.
-Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments (show both!).
+Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments.
 While it would be possible to use a yield from a long-short futures position (e.g.
 short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration.
-These are the perpetual futures, which are listed on some exchanges.
 
 As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
-Open Interest for Ether Perpetual Futurews contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
+Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
 
@@
 Crypto exchanges often provide a so-called perpetual future, which is a synthetic (typically cash-settled instrument) whose return is tied to the underlying via a funding rate.
-Most exchanges (quote here) provide perpetual futures for Bitcoin and Ethereum.
+Most exchanges (quote here) provide perpetual futures for Bitcoin and Ether.
 The price of each perpetual future is linked to the underlying by adjusting a variable interest rate, called the funding rate, that fluctuates depending on the deviation between the price of the perpetual future and the underlying.
-The funding rate increases the cost of holding positions against the deviation, meaning that if the price of the perpetual future is higher than the underlying, the funding rate is positive which causes the market participants who are long to pay the short side in a contractually predefined frequency.
+The funding rate increases the cost of holding positions against the deviation, meaning that if the price of the perpetual future is higher than the underlying, the funding rate is positive which causes the market participants who are long to pay the short side in a predefined frequency.
 Broadly said, the more extreme the deviation, the higher the funding rate and thus the higher the incentive to trade against the deviation and thus converge the price of the perpetual future towards its underlying.
@@
 
-Deribit perpetual contracts are a derivative product similar to a future, however, they do not have an expiry date.
-The perpetual contract features funding payments.
-These payments have been introduced to keep the perpetual contract price as close as possible to the underlying crypto price - the relevant Deribit Index.
-If the perpetual contract trades at a higher price than the index, traders that have long positions need to make funding payments to the traders that have short positions.
-This will make the product less attractive to the long position holders and more attractive to the short position holders.
-This subsequently will cause a perpetual price to trade in line with the price of the index.
-If the perpetual trades at a price lower than the index, the short position holders will have to pay the long position holders instead.
-
-The Deribit perpetual contract features a continuous measurement of the difference between the mark price of the contract and the relevant Deribit Index.
-The percentage difference between these two price levels is the basis for the 8-hourly funding rate that is applied to all outstanding perpetual contracts.
-
-Funding payments are calculated every millisecond.
-The funding payments will be added to or subtracted from the realized PNL, which is also part of the available trading balance.
-At each daily settlement, the realized PNL will be moved to or from the cash balance, from which withdrawals can be made.
-
-The total funding paid will show up in the transaction log in the "funding" column.
-This column shows the funding amount that is applied to the trader's entire net position in the period between the relevant trade and the trade before that.
-Put differently: the trader can see the funding paid or received on the position between position changes.
-
-Funding Rate
-When the funding rate is positive, long position holders pay funding to the short position holders; when the funding rate is negative, short position holders pay funding to the long position holders.
-The funding rate is expressed as an 8-hour interest rate, and is calculated at any given time as follows:
-
-Premium Rate
-Premium Rate = ((Mark Price - Deribit Index) / Deribit Index) * 100%
-
-Funding Rate
-Sequentially, the funding rate is derived from the premium rate by applying a damper.
-
-If the premium rate is within -0.025\% and 0.025\% range, the actual funding rate will be reduced to 0.00\%.
-If the premium rate is lower than -0.025\%, then the actual funding rate will be the premium rate + 0.025\%.
-If the premium rate is higher than 0.025\%, then the actual funding rate will be the premium rate - 0.025\%.
-Additionally, the funding rate is capped at +/ - 5\% for all linear USDC perpetuals.
-Funding Rate = Maximum (0.025\%, Premium Rate) + Minimum (-0.025\%, Premium Rate)
-
-Time Fraction
-Time Fraction = Funding Rate Time Period / 8 hours
-
-The actual funding payment is calculated by multiplying the funding rate by the position size and the time fraction.
-
-Funding Payment = Funding Rate * Position Size * Time Fraction
-
-In reality, the spread of the Deribit Index and the mark price changes continuously, and all changes are taken into account.
-Therefore, the examples above are extreme simplifications of the actual calculations.
-The funding paid or received is continuously added to the realized PNL and is moved to or from the cash balance at the daily settlement, at 08:00 UTC.
-
-Fees on Funding
-Deribit does not charge any fees on funding.
-All the funding payments are transferred between the holders of the perpetual contracts.
-This makes the funding a zero-sum game, where longs receive all funding from shorts, or shorts receive all funding from longs.
-
+Instruments, such as inverse options, futures and perpetual futures, have a Mark Price $M$.
+The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth (quote:
+Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system.
+Usually, this is the average of the best bid and best ask price.
+However, for risk management purposes, there is price bandwidth in place.
+).
+The Deribit Index $D$, which is a Lasperes Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.
+
+\begin{equation}
+P = \frac{M - D}{D}
+\end{equation}
+
+The Funding Rate results as an 8-hour interest rate from the interval in which the Premium Rate falls.
+
+\begin{equation}
+F = \max{0.025\%, P} + \min{-0.025\%, P}
+\end{equation}
+
+The actual funding payment results $f$ from the product of the Funding Rate, Position Size and Holding Time. It is continuously added to the PnL account and settled daily at 8:00 UTC.
+
+@Todo: Summarize!
 Mark Price
 It is essential to understand how the mark price is calculated. We start by determining the "Fair Price". The fair price is calculated as the average of the fair impact bid and the fair impact ask.
-
-Fair Impact Bid Price is an average price at which 100,000 USDC worth of contracts can be bought.
-
+Fair Impact Bid Price is an average price at which 100,000 USDC worth of contracts can be bought.=
 Fair Impact Ask Price is an average price at which 100,000 USDC worth of contracts can be sold.
-
-Fair Price can never be higher than 0.1 % of best ask or lower than best bid
-
+Fair Price can never be higher than 0.1\% of best ask or lower than best bid
 Fair Price = (Fair Impact Bid + Fair Impact Ask) / 2
@@
 
-Trading outside of this bandwidth is still allowed.
-
-The 30 second EMA is recalculated every second, so in total, there are 30 time periods in which the measurement of the latest second has a weight of 2 / (30 + 1) = 0.0645 or (6.45%).
-
-Allowed Trading Bandwidth
-Two parameters act as a boundary to the allowed trading range:
-
-Perpetual trades are limited by Deribit Index + 1 minute EMA (Fair Price - Index) +/- 1.5%, and a fixed bandwidth of the Deribit Index of +/- 7.5%.
-
-If the market circumstances require so, bandwidth parameters can be adjusted at the sole discretion of Deribit.
-
-Solve for interest rates from
+Solve for interest rates from Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$.
 
@@
 
-The actual annualized returns of such a carry trade would be
+The actual annualized returns of such a carry trade are summarized in the table below.
 
@@
 
+%Deribit perpetual contracts are a derivative product similar to a future, however, they do not have an expiry date.
+The perpetual contract features funding payments.
+These payments have been introduced to keep the perpetual contract price as close as possible to the underlying crypto price - the relevant Deribit Index.
+If the perpetual contract trades at a higher price than the index, traders that have long positions need to make funding payments to the traders that have short positions.
+This will make the product less attractive to the long position holders and more attractive to the short position holders.
+This subsequently will cause a perpetual price to trade in line with the price of the index.
+If the perpetual trades at a price lower than the index, the short position holders will have to pay the long position holders instead.
+%
+%The Deribit perpetual contract features a continuous measurement of the difference between the mark price of the contract and the relevant Deribit Index.
+The percentage difference between these two price levels is the basis for the 8-hourly funding rate that is applied to all outstanding perpetual contracts.
+%
+%Funding payments are calculated every millisecond.
+The funding payments will be added to or subtracted from the realized PNL, which is also part of the available trading balance.
+At each daily settlement, the realized PNL will be moved to or from the cash balance, from which withdrawals can be made.
+%
+%The total funding paid will show up in the transaction log in the "funding" column.
+This column shows the funding amount that is applied to the trader's entire net position in the period between the relevant trade and the trade before that.
+Put differently: the trader can see the funding paid or received on the position between position changes.
+%
+%Funding Rate
+%When the funding rate is positive, long position holders pay funding to the short position holders; when the funding rate is negative, short position holders pay funding to the long position holders.
+The funding rate is expressed as an 8-hour interest rate, and is calculated at any given time as follows:
+%
+%Premium Rate
+%Premium Rate = ((Mark Price - Deribit Index) / Deribit Index) * 100%
+%
+%Funding Rate
+%Sequentially, the funding rate is derived from the premium rate by applying a damper.
+%
+%If the premium rate is within -0.025\% and 0.025\% range, the actual funding rate will be reduced to 0.00\%.
+%If the premium rate is lower than -0.025\%, then the actual funding rate will be the premium rate + 0.025\%.
+%If the premium rate is higher than 0.025\%, then the actual funding rate will be the premium rate - 0.025\%.
+%Additionally, the funding rate is capped at +/ - 5\% for all linear USDC perpetuals.
+%Funding Rate = Maximum (0.025\%, Premium Rate) + Minimum (-0.025\%, Premium Rate)
+%
+%Time Fraction
+%Time Fraction = Funding Rate Time Period / 8 hours
+%
+%The actual funding payment is calculated by multiplying the funding rate by the position size and the time fraction.
+%
+%Funding Payment = Funding Rate * Position Size * Time Fraction
+%
+%In reality, the spread of the Deribit Index and the mark price changes continuously, and all changes are taken into account.
+Therefore, the examples above are extreme simplifications of the actual calculations.
+The funding paid or received is continuously added to the realized PNL and is moved to or from the cash balance at the daily settlement, at 08:00 UTC.
+
 \section{References}

### 2024-02-11 compare.py
t tests finished

@@ -41,8 +41,13 @@ def ttest(dat, out_path):
     print(pdct)
 
     # Cool! 
+    fig = plt.figure(figsize = (20, 14))
     sub = df.loc[(df['moneyness'] >= 0.95) & (df['moneyness'] <= 1.05)]
     t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
+    sub['combined_ret_daily'].plot.kde()
+    plt.title('n = ' + str(sub.shape[0]))
+    plt.xlim((-1, 1))
+    plt.savefig(out_path + '/moneyness_between_95_and_105' + '.png')
 
     with open(out_path + '/t-tests.csv', 'w') as f:  # You will need 'wb' mode in Python 2.x
         w = csv.DictWriter(f, pdct.keys())
@@ -83,7 +88,7 @@ p3_values = ttest(crash_resistant_fee, out_path = 'out/crash_resistant/fees/dens
 p4_values = ttest(crash_resistant_no_fee, out_path = 'out/crash_resistant/no_fees/density')
 
 pv = pd.DataFrame({'Vanilla ex Fee': p1_values, 'Vanilla cum Fee': p2_values, 'Crash Resistant ex Fee': p3_values, 'Crash Resistant cum Fee': p4_values})
-pv.to_csv('out/pvalues.csv')
+pv.round(4).to_csv('out/pvalues.csv')
 
 pdb.set_trace()
 vanilla_fee.loc[vanilla_fee['days_to_maturity'] <= 20].groupby('days_to_maturity')['combined_payoff'].describe()
@@ -92,5 +97,3 @@ vanilla_no_fee.loc[vanilla_fee['days_to_maturity'] <= 20].groupby('days_to_matur
 vanilla_fee.loc[vanilla_fee['days_to_maturity'] <= 20].groupby('days_to_maturity')['combined_ret'].describe()
 vanilla_no_fee.loc[vanilla_fee['days_to_maturity'] <= 20].groupby('days_to_maturity')['combined_ret'].describe()
 
-# Get average option returns etc. 
-# average index returns

### 2024-02-13 written/paper.tex
added eth plots

@@
 
-\section{Methodology}
-
-- scrape 8h funding rate continuously and use as market-interest rate
-
-- scrape all BTC, ETH transactions from Deribit 
-- load data, clean
-- center on settlement date for each day (10am UTC)
-- for each option, find the pendant via put-call-parity
-- calculate the beta of each put, call
-- build zero-beta straddles by finding weights such that the sum of weights is zero
-- assess empirical, daily returns of the straddle
-- build boxplots over levels of moneyness
-- KDE --> t-distribution
-- perform t-test for population mean of 0
-
-We follow the argument that any beta-neutral portfolio should yield the risk-free rate.
-We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
-The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
-The weight $\theta$ is found by solving Equation 2 through Equation 3.
-The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4.
-The underlying data are executed transactions.
-All option greeks remain constant except time-to-maturity.
-Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time.
-All options are bought and held until settlement at 10am UTC.
-We match our universe of straddles as follows:
-Per definition, a straddle exists of a call and a put with similar strike and maturity.
-We construct the set of empirical straddles by iterating over our list of executed calls and puts.
-For each call (put), we use Put-Call-Parity to complete the straddle.
-The empirical performance of the resulting zero-beta straddles is assessed on a daily base.
-We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
-For each level of moneyness m, we construct an interval $[m, m + 0.05]$.
-We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
-We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
-
-- Formulas for the weights!
-
-Straddle Return $r_v$￼, Share of Straddle’s value in Call Options ￼$\theta$,
-Call and Put market Beta ￼$\beta_c$, $\beta_p$.
-
-\begin{equation}
-r_v = \theta r_c + (1-\theta)r_p
-\end{equation}
-
-\begin{equation}
-\theta \beta_c + (1-\theta)\beta_p = 0\\
-\end{equation}
-
-\begin{equation}
-\theta = \frac{-\beta_p}{\beta_c - \beta_p}\\
-\end{equation}
-
-\begin{equation}
-\beta_c = \frac{s}{C} \Delta \beta_s\\
-\end{equation}
-
-We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events.
-Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
-Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
-Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
-Maybe make a summary of the relationship between ATM and 20\% OTM premium.
-
-The performance of the vanilla and crash-resistant straddles is evaluated with and without fees.
-Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs.
-The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
-Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
-Consequently, the trading fee for one option spread would be the lesser of 0.0003 Bitcoin or 12.5\% of the more expensive option price.
-All fees are converted into USD based on the BTC/USDT exchange rate around settlement time.
-
-\section{Data}
-
-We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
-The exchange started operations in July 2017. 
-Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates for the perpetual future of Bitcoin and Ether since (approx.) July 2019.
-
-Two conditions are imposed on the option data:
-1) The maximum IV is 2.5 and the minimum IV is 0.1.
-2) In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
-3) Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
-4) We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
-
-The purpose of the first restriction is to impose a fair bound to the options that is independent of liquidity levels.
-For illiquid options, occurrences of bid prices at 0\% IV and ask prices of 500\% may occur.
-The purpose the second restriction of unique usage is to prevent a bias due to the possible more frequent trading of certain options.
-Generally, we observe that instruments with short maturity are traded more frequently.
-Yet, this could also be understood as cheaper instruments trading more frequently since (Black-Scholes) option prices increase with time-to-maturity.
-
-Bitcoin only:
-We drop 0.9\% of observations due to restriction 1)
-We drop 17\% of observations due to restriction 3)
-Overall, we have 5,028,945 observations. Post filtering, 4,150,778 observations remain in the set.
-
-Ethereum: 
-?!
-Todo
-
-Regarding data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
-Indeed, using actual transaction data instead of orderbook data removes the threat of wash trading (etc) to our data.
-The most likely negative factor that could affect our data quality is wash trading.
-We assess the risk of wash trading as follows:
-
-"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." (from: https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf)
-
-We asses the risk of wash trading contaminating our data set as low.
-The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
-At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot 12 USD.
-Such fees, even without consideration of spreads, make wash trading from a trader's perspective entirely infeasible.
-
-- table of amount of transactions per group
-- plot: amount of transactions over time per group (crypto)
-
 \section{A Proxy for the risk-free Rate of Bitcoin and Ether}
@@
 ).
-The Deribit Index $D$, which is a Lasperes Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.
+The Deribit Index $D$, which is an equally weighted Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.
 
@@
 funding_btc_vs_eth.png
+
+\section{Methodology}
+
+We follow the argument that any beta-neutral portfolio should yield the risk-free rate.
+We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
+The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
+The weight $\theta$ is found by solving Equation 2 through Equation 3.
+The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4.
+The underlying data are executed transactions.
+All option greeks remain constant except time-to-maturity.
+Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time.
+All options are bought and held until settlement at 10am UTC.
+We match our universe of straddles as follows:
+Per definition, a straddle exists of a call and a put with similar strike and maturity.
+We construct the set of empirical straddles by iterating over our list of executed calls and puts.
+For each call (put), we use Put-Call-Parity to complete the straddle.
+The empirical performance of the resulting zero-beta straddles is assessed on a daily base.
+We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
+For each level of moneyness m, we construct an interval $[m, m + 0.05]$.
+We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
+We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
+
+Straddle Return $r_v$￼, Share of Straddle’s value in Call Options ￼$\theta$, Call and Put market Beta ￼$\beta_c$, $\beta_p$.
+
+\begin{equation}
+r_v = \theta r_c + (1-\theta)r_p
+\end{equation}
+
+\begin{equation}
+\theta \beta_c + (1-\theta)\beta_p = 0\\
+\end{equation}
+
+\begin{equation}
+\theta = \frac{-\beta_p}{\beta_c - \beta_p}\\
+\end{equation}
+
+\begin{equation}
+\beta_c = \frac{s}{C} \Delta \beta_s\\
+\end{equation}
+
+We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events.
+Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
+Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
+Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
+Maybe make a summary of the relationship between ATM and 20\% OTM premium.
+
+The performance of the vanilla and crash-resistant straddles is evaluated with and without fees.
+Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs.
+The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
+Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
+Consequently, the trading fee for one option spread would be the lesser of 0.0003 Bitcoin or 12.5\% of the more expensive option price.
+All fees are converted into USD based on the BTC/USDT exchange rate around settlement time.
+
+\section{Data}
+
+We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
+The exchange started operations in July 2017. 
+Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates for the perpetual future of Bitcoin and Ether since (approx.) July 2019.
+
+Two conditions are imposed on the option data:
+1) The maximum IV is 2.5 and the minimum IV is 0.1.
+2) In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
+3) Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
+4) We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
+
+The purpose of the first restriction is to impose a fair bound to the options that is independent of liquidity levels.
+For illiquid options, occurrences of bid prices at 0\% IV and ask prices of 500\% may occur.
+The purpose the second restriction of unique usage is to prevent a bias due to the possible more frequent trading of certain options.
+Generally, we observe that instruments with short maturity are traded more frequently.
+Yet, this could also be understood as cheaper instruments trading more frequently since (Black-Scholes) option prices increase with time-to-maturity.
+
+Bitcoin only:
+We drop 0.9\% of observations due to restriction 1)
+We drop 17\% of observations due to restriction 3)
+Overall, we have 5,028,945 observations. Post filtering, 4,150,778 observations remain in the set.
+
+Ethereum: 
+Amount of Observations outside of allowed IV range:  0.017042133327261764
+Amount of Observations outside of allowed Tau range:  0.20172172747210984
+Overall Observations: 2283869
+Amount of Observations in our set post filtering:  1809762
+
+Regarding data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
+Indeed, using actual transaction data instead of orderbook data removes the threat of wash trading (etc) to our data.
+The most likely negative factor that could affect our data quality is wash trading.
+We assess the risk of wash trading as follows:
+
+"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." (from: https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf)
+
+We asses the risk of wash trading contaminating our data set as low.
+The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
+At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot 12 USD.
+Such fees, even without consideration of spreads, make wash trading from a trader's perspective entirely infeasible.
+
+- table of amount of transactions per group
+- plot: amount of transactions over time per group (crypto)
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized.png}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized.png}
     \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_annualized_zoom.png}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized_zoom.png}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth.png}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth.png}
     \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/funding_btc_vs_eth_zoom.png}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_zoom.png}
     \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{Performance - Vanilla - No Fees}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{Performance - Vanilla - Fees}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Performance - Vanilla - Fees}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{Performance - Crash Resistant - No Fees}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{Performance - Crash Resistant - Fees}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Performance - Vanilla - Fees}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
 

### 2024-02-13 written/paper.tex
cleanup

@@
 
-\pagebreak
-\newpage
-
-NOTE: 
-USE THE TRADED VOLUME * INSTRUMENT PRICE TO FIND THE AMOUNT OF VALUE LOST DUE TO THE VOLA PREMIUM
-
-\section{Deribit}
-
-Deribit, a margin-trading platform for futures and options, has been
-launched in June 2016 in the Netherlands and is currently incorporated
-in Panama. As of time of the writing, Deribit is the largest BTC option
-exchange (Skew.com 2022). For both types of derivatives, BTC and ETH are
-the underlying as well as the currency in which settlement is conducted.
-This allows to view them as inverse options.
-
-\begin{center}
-\begin{figure}
-\includegraphics[width=0.9\textwidth]{/Users/julian/src/up/spd/plot/Skew_BTC_Open_Interest_cut.pdf}
-\caption[Open Interest in BTC Options per Exchange.]%
-{Open Interest in BTC Options per Exchange.
-Snapshot from \href{https://analytics.skew.com/dashboard/bitcoin-options}{skew.com} on 2022-01-16.
-\color{bittersweet}{Deribit}, \color{ao}{LedgerX}, \color{bananamania}{CME}, \color{bluegray}{bit.com}.
-}
-\label{fig: ivtest}
-\end{figure}
-\end{center}
-
-\subsection{Bitcoin Option Contract Specifications}
-
-Deribit offers cash-settled European-style options. The underlying is a
-synthetic index, whose exact composition is described in the data
-section. Settlement is first calculated in USD and then conducted in
-kind of the underlying. E.g. a BTC call with a strike of \(10000\) and a
-settlement value of \(12000\) at maturity will result in a cashflow of
-\(2000\) USD, which is equivalent to \(\frac{1}{6}\) BTC (excluding
-transaction cost). The settlement value is defined as the average of the
-underlying BTC index for the last 30 minutes before settlement. Each
-contract has a lot size of 1 BTC and is settled at 8am UTC on the
-respective maturity date. Maturity dates have a daily, monthly,
-quarterly and annual frequency. Deribit is the only derivatives exchange
-to offer daily options. Instruments are trading 24/7 with a tick size of
-0.0005 BTC. Due to the automatic usage of margin-trading, margin-based
-liquidation of positions is possible. Initial margin and maintenance
-margins are both zero for long positions. For short positions, initial
-margin is required (Deribit 2022b). In case of liquidation, a penalty is
-applied to the defaulting party, whose proceeds are paid into the
-Deribit Insurance Fund (Deribit 2020a).
-
-Trading and deliveries on Deribit are subject to fees (Deribit 2022c).
-The applied fees generally vary depending on whether the order was a
-liquidity maker or taker. However, for Bitcoin options they are equal.
-Trading fees are 0.03\% of the underlying or 0.0003 BTC per options
-contract. The fees constitute a maximum of 12.5\% of the contract's
-value.
-
-\section{Data}
-
-\subsection{Data Structure}
-
-The dataset consists of 8,444,664 order book snapshots, which have been
-collected from Deribit in the time from 2021-04-01 until 2022-04-01. The
-snapshots were captured via the Deribit API V2. The data base is
-available on the
-\href{https://blockchain-research-center.com}{Blockchain Research Center (BRC)}.
-The full data set includes all parameters that the
-\href{https://docs.deribit.com/#deribit-api-v2-1-1}{Deribit API V2}
-returns at the time of collection under the methods
-
-\begin{itemize}
-\tightlist
-\item
-  \{\it public/get\_last\_trades\_by\_instrument\_and\_time\}
-\item
-  \{\it public/get\_order\_book\}
-\end{itemize}
-
-Most importantly the results include
-
-\begin{itemize}
-\tightlist
-\item
-  Timestamps
-\item
-  Greeks
-\item
-  Implied Volatility
-\item
-  Tick Direction
-\item
-  Order Type
-\item
-  Volume
-\item
-  Instrument Price
-\item
-  Strike
-\item
-  Spot
-\end{itemize}
-
-High-frequent order book changes and executed trades are captured for
-options and futures whose underlying is BTC. Values of the underlying
-synthetic BTC USD Index are also saved. The underlying is calculated as
-an equally-weighted BTC/USD price of eleven major crypto exchanges,
-namely Binance, Bitfinex, Bitstamp, Bittrex, Coinbase Pro, FTX, Gemini,
-Huobi, Itbit, Kraken, LMAX Digital, OKEx. Individual feeds can be
-excluded due to administrative decisions or in case if invalid data.
-Remaining feeds are sorted, truncated around the median price and
-weighted (Deribit 2020b).
-
-\subsection{Data Integrity}
-
-Data integrity plays a crucial role in crypto markets. Mark Carney, the
-chair of the Financial Stability Board and head of the Bank of England,
-warned that wash trading, pump and dumps and spoofing, known as outlawed
-manipulation techniques in equity markets, are also present in crypto
-and pose a risk to financial stability (Rodgers 2019). Wash trading is
-used to increase trading volume and thus artificially increase demand. A
-spoofer submits market non-bona fide price quotes in order to cause
-artificial price volatility (Sar 2017). Pump \& Dump is a form of
-securities fraud in which a group of traders rapidly and artificially
-inflate a price in order to offload their previously acquired inventory.
-Since Pump \& Dump schemes require low liquidity (in the underlying), we
-can exclude this possibility for Bitcoin (La Morgia et al. 2020).
-
-Aloosh and Li (2019) find evidence for exchange-driven inflated volume,
-generated by wash trades, to market themselves under the guise of
-liquidity. Cong et al. (2019) report that on average 70\% of volume on
-decentralized exchanges is fake due to the use of wash trading.
-According to Bitmex (2019), up to 95\% of trading volume on unregulated
-exchanges is generated by wash trading. In order to ensure data
-integrity, we exclusively use orderbooks instead of executed trades in
-order to filter possible cases of wash trading.
-
-To address the potential issue of spoofing, we adopt an approach related
-to Tuccella et al. (2021). They attempt to identify spoofing on
-cryptocurrency exchanges using a GRU model. Their predictors are a
-function of the amount of cancelled orders relative to the cumulative
-order size on each side of the order book. Since Bitcoin derivatives
-order books do not have the same amount of depth as spot or futures
-markets, we employ a stricter method and exclude all orders whose
-lifetime does not exceed two seconds. We find that less than 5\% of
-orders are filtered due to short order lifetime. We figure that
-traditional spoofing techniques, based on the rapid submission and
-cancellation of orders, are difficult to implement due to Deribit's rate
-limits (Deribit 2023). Users with less than 1 million USD in
-7-day-turnover can only post five matching engine requests. These
-include request for a buy or sell order or a corresponding cancellation.
-Although the limits for a market maker (who could be allowed to post 30
-requests per second given a turnover of 25 million USD in 7 days) are
-considerably higher, the market maker must still meet the quoting
-requirements for a large range of instruments. This effectively
-restricts the influence that single entities can have on certain
-instruments via the rapid submission and cancellation of orders and
-explains the rarity of such events in our dataset.
-
-\subsection{Preprocessing}
-
-Although market makers are obliged to quote most instruments for the
-majority of the time, some may not be quoted at all or only be quoted at
-the cost of a large spread (Deribit 2020c). For Far-Out-of-Money (FOTM)
-contracts, when the minimum tick size exceeds the market IV, one can
-observe bids for 0\% IV. Cases of quotes for 0\% IV and all duplicates
-are excluded from the data set. Since the majority of option trading
-volume concentrates on instruments with short or medium time-to-maturity
-\(\tau\), we restrict \(\tau\) to be smaller or equal than one quarter
-of a year. \(\tau\) is normalized on the span of a year. Instruments are
-grouped according to their time-to-maturity, over a range of 0, 1, 2, 4,
-8 weeks. We restrict moneyness \(M = \frac{K}{S}\) to the interval
-\([0.7, 1.3]\) in order to exclude the influence of high-volatility
-observations which could be unreliable (Grith et al. 2009).
-
-Call options are exclusively used in order to estimate the IV surface in
-Rookley's method. Put-Call-Parity ensures arbitrage-free call option
-prices. However, we do not use Put-Call-Parity to increase our data
-sample. Conversion of option prices via Put-Call-Parity could introduce
-errors into our dataset due to market microstructure (MMN) noise. Our
-high-frequent order book data is extracted via an API. Due to rate
-limitations and a diverse amount of instruments, order book snapshots
-cannot be taken simultaneously for all instruments. The data scraping
-application successively iterates over all instruments and captures
-changes in order books. While the resulting data base provides a clear
-picture of order book data, it does not allow for a complete
-reconstruction of all order books at all times. Without simultaneity,
-volatility of the underlying and order competition within the spread
-could change the prices of the corresponding instruments (required for
-Put-Call-Parity) between the individual snapshots. A range of futures
-may be available on Deribit, but only the perpetual futures contract is
-actually liquid. The classic (non-perpetual) futures also price in the
-settlement cost, which often causes them to trade in backwardation close
-to maturity. But in spite of this, BTC options tend to be traded more
-frequently when they are close to maturity. The combination of these
-real-world limitations challenges the simple conversion via
-Put-Call-Parity and could introduce errors into our dataset.
-Furthermore, we do not see the necessity to use such a method as we have
-sufficient call option data to compute the IV surface from which we
-sample option prices.
-
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Preprocessing}
-
 %Deribit perpetual contracts are a derivative product similar to a future, however, they do not have an expiry date.

### 2024-02-13 written/paper.tex
writing until risk free rate section

@@
   \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
-\date{7 January 2024}
+\date{12 February 2024}
 
@@
 We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s.
-The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway and Bakshi et al in XZY year.
-
-We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. We use it as a benchmark that beta-neutral portfolios should yield. 
-We construct and evaluate the performance of beta-neutral portfolios and find that they do not generate their theoretical returns for at-the-money instruments.
-We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., high premia.of at-the-money options.
-The effect holds after compensating for market crash insurance and transaction cost.
-We assess the deadweight loss due to observed risk premia and propose a simple trading strategy that exploits this particular inefficiency.
-
-We constructs and evaluate the empirical performance of option portfolios, written on crypto assets such as Bitcoin and Ether, to allow model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
-
-Another, so far rarely used pathway is the assessment of the risk-return characteristics of Bitcoin through the lens of the options written on it, which allow new model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
-
-This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option portfolios in the early 2000s.
-
-Bakshi and Shumway both found that expected call returns exceed those of the underlying and that expected put returns underperform the underlying.
+The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway and Bakshi et al in (@quote).
+
+We discuss the existence of a risk-free rate in crypto asset markets and derive a proxy. The proxy serves as a benchmark that beta-neutral portfolios should yield. 
+Subsequently, we construct and evaluate the performance of beta-neutral option portfolios using a unique data set of executed transactions from Derbit, the largest Crypto Options Exchange.
+We find that the beta-neutral option portfolios, written on Bitcoin and Ether, are fairly priced for most levels of moneyness.
+However, the portfolios do not generate the appropriate theoretical returns for at-the-money instruments.
+We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., the existence of high premia.for at-the-money options.
+The effect holds after compensating for tail risk (market crash insurance) and transaction cost.
+
+%
+%We construct and evaluate the empirical performance of option portfolios, written on crypto assets such as Bitcoin and Ether, to allow model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
+%
+%Another, so far rarely used pathway is the assessment of the risk-return characteristics of Bitcoin through the lens of the options written on it, which allow new model-free insights into the existence and degree of a leverage effect, the existence and size of risk premia, resulting market inefficiencies (measurable in economic loss / money lost) and to explore the option (pun intended)/possibility of curing named inefficiencies under transaction cost and liquidity constraints.
+%
+%This reasoning follows the insights of Shumway and Bakshi, who separately evaluated option returns in equity markets by means of delta-neutral option portfolios in the early 2000s. 
+%
+%Bakshi and Shumway both found that expected call returns exceed those of the underlying and that expected put returns underperform the underlying.
 Both also found that the effect increases (decreases) with the strike.
-Bakshi found that zero-beta, at-the-money straddle positions produce average losses of approximately three percent per week and suggests that the reason may be a systematic volatility premium being priced in options.
-
-Following Shumway, the risk-return characteristics of options can be separated in two elements, a leverage effect and a curvature effect due to the sensitivity of option payoffs to higher moments of the underlying.
-First, the holder (buyer) of an option is subject to a leverage effect since exposure to the underlying can be obtained through the payment of a premium, which is small compared to the price of the underlying.
-If there is a leverage effect, then (long) call options should outperform their underlying and (long) put options should underperform their underlying.
+%Bakshi found that zero-beta, at-the-money straddle positions produce average losses of approximately three percent per week and suggests that the reason may be a systematic volatility premium being priced in options.
+%
+%Following Shumway, the risk-return characteristics of options can be separated in two elements, a leverage effect and a curvature effect due to the sensitivity of option payoffs to higher moments of the underlying.
+%First, the holder (buyer) of an option is subject to a leverage effect since exposure to the underlying can be obtained through the payment of a premium, which is small compared to the price of the underlying.
+%If there is a leverage effect, then (long) call options should outperform their underlying and (long) put options should underperform their underlying.
 Furthermore, the effect should increase (decrease) with the strike price for calls (puts).
-This reasoning allows a simple test of existence and size of the leverage effect and thus conclusions about the level of speculation associated to Bitcoin valuation.
-
-(The second component, related to the sensitivity of options towards higher moments, implies that options are redundant assets...)
-
-If options were redundant assets, then apart of the leverage effect, delta-neutral option portfolios should earn the risk-free rate (no premium) on average.
-Until now, there is no risk-free rate available in the space of crypto assets.
+%This reasoning allows a simple test of existence and size of the leverage effect and thus conclusions about the level of speculation associated to Bitcoin valuation. 
+%
+%(The second component, related to the sensitivity of options towards higher moments, implies that options are redundant assets...)
+%
+%If options were redundant assets, then apart of the leverage effect, delta-neutral option portfolios should earn the risk-free rate (no premium) on average.
+%Until now, there is no risk-free rate available in the space of crypto assets.
 We establish a proxy or reference rate for a possible risk-free rate, which results from the perpetual futures written on Bitcoin and Ether.
-
-Use Deribit and Binance perpetual futures for this, equally weighted.
-
-(This proxy is clearly not risk-free due to counterparty risk, but we argue that a carry trade involving a short position on perpetual futures on multiple platforms in conjunction with a secured, on-chain underlying position reduces the platform-induced counterparty risk (which is the residual risk in the carry trade) as far as possible.) (This also leaves liquidity risk though!!)
-
-All underlying code is available on \href{quantlet.com}{quantlet.com}
-and a corresponding courselet is available on
-\href{quantinar.com}{quantinar.com}.
+%
+%Use Deribit and Binance perpetual futures for this, equally weighted. 
+%
+%(This proxy is clearly not risk-free due to counterparty risk, but we argue that a carry trade involving a short position on perpetual futures on multiple platforms in conjunction with a secured, on-chain underlying position reduces the platform-induced counterparty risk (which is the residual risk in the carry trade) as far as possible.) (This also leaves liquidity risk though!!)
+%
+%All underlying code is available on \href{quantlet.com}{quantlet.com}
+%and a corresponding courselet is available on
+%\href{quantinar.com}{quantinar.com}.
+%
 
@@
 
-Another possibility: Staking
-
-Evidently, there is no established risk-free rate in crypto (or digital asset) markets.
-In the absence of riskless bond, we construct as a proxy for the risk free rate, which is the replication of the market-implied yield through a position which only has liquidity risk and counterparty risk.
+One of the most fundamental concepts in mathematical finance is the existence of a risk-free rate and a risky asset. 
+While crypto assets are well-known for their riskiness, the existence of a risk-free rate has not been established in this new market. 
+The risk-free rate in established markets derives from the practice of lending out money to low-risk, typically government institutions which owe an interest rate on top of the principal to the lender.
+Despite the naming convention, government issued bonds are not entirely risk-free due to the possibility of default.
+Although default risk is commonly mitigated by a government's possibility to create money, the chance of a sovereign debt default is non-zero and hence not entirely risk-free.
+
+In order to apply concepts of mathematical finance onto crypto assets, it is paramount to develop a risk-free rate - or at least a low-risk rate whose residual risk may converge to zero in time. 
+An interesting candidate for a low-risk bond in the crypto asset space would be staking, which is the validation of transactions under the risk of losing a principal (the stake).
+Evidently, only crypto assets which follow a Proof-of-Stake (PoS) consensus mechanism instead of a Proof-of-Work (PoW) consensus mechanism can be used for staking.
+At the time, this is still a minor amount of cryptocurrencies.
+We include one of those, Ether, in our experiment.
+However, we figure that a multitude of risks is still present in staking, such as the risk of hacks, software bugs, slashing or blockchain congestions and subsequent reduction of stakes.
+Another approach to develop a risk-free rate would be lending in the DeFi space. Yet, this space may be vulnerable to similar risks as staking through hacks or software bugs in smart contracts.
+
+In the absence of riskless bond, we construct as a proxy for the risk free rate via the replication of the market-implied yield through a position in futures contracts, whose risks mainly arise due to liquidity risk and counterparty risk.
 A large share of the trading volume in digital asset markets falls on the futures market.
@@
 short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration.
+
+Solve for interest rates from Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:
+
+\begin{equation}
+F_t = e^{r \tau} S_t
+\end{equation}
+
+Crypto exchanges often provide a so-called perpetual future, which is a synthetic (typically cash-settled instrument) whose return is tied to the underlying via a funding rate.
+Most exchanges (quote here) provide perpetual futures for Bitcoin and Ether.
+The price of each perpetual future is linked to the underlying by adjusting a variable interest rate, called the funding rate, that fluctuates depending on the deviation between the price of the perpetual future and the underlying.
+The funding rate increases the cost of holding positions against the deviation, meaning that if the price of the perpetual future is higher than the underlying, the funding rate is positive which causes the market participants who are long to pay the short side in a predefined frequency.
+Broadly said, the more extreme the deviation, the higher the funding rate and thus the higher the incentive to trade against the deviation and thus converge the price of the perpetual future towards its underlying.
+The risk-free rate is approximated using the simplest and most liquid way of realising the funding rate, a carry trade.
+In such a trade, the trader shorts (longs) the perpetual future if the funding rate is positive (negative) and simulateously buys (sells) the underlying such that the market delta of the combined position is zero.
+
+The funding rate on \href{https://www.deribit.com/kb/deribit-linear-perpetual}{Deribit} is calculated as follows:
+
+Instruments, such as inverse options, futures and perpetual futures, have a Mark Price $M$.
+The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth (quote:
+Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system.
+Usually, this is the average of the best bid and best ask price.
+However, for risk management purposes, there is price bandwidth in place.
+).
+The Deribit Index $D$, which is an equally weighted Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.
+
+\begin{equation}
+P = \frac{M - D}{D}
+\end{equation}
+
+The Funding Rate results as an 8-hour interest rate from the interval in which the Premium Rate falls.
+
+\begin{equation}
+F = \max{0.025\%, P} + \min{-0.025\%, P}
+\end{equation}
+
+The actual funding payment results $f$ from the product of the Funding Rate, Position Size and Holding Time. It is continuously added to the PnL account and settled daily at 8:00 UTC.
+
+%@Todo: Summarize!
+%Mark Price
+%It is essential to understand how the mark price is calculated. We start by determining the "Fair Price". The fair price is calculated as the average of the fair impact bid and the fair impact ask.
+%Fair Impact Bid Price is an average price at which 100,000 USDC worth of contracts can be bought.=
+%Fair Impact Ask Price is an average price at which 100,000 USDC worth of contracts can be sold.
+%Fair Price can never be higher than 0.1\% of best ask or lower than best bid
+%Fair Price = (Fair Impact Bid + Fair Impact Ask) / 2
+%The mark price is derived using both the Deribit Index and the fair price, by adding to the Deribit Index the 30 second exponential moving average (EMA) of the Fair Price - Deribit Index.
+%
+%Mark Price = Deribit Index + 30 second EMA (Fair Price - Deribit Index)
+%We implement a safety setting on our mark price to not deviate by more than a certain percentage of Index.
+This is to prevent manipulation or to curb the impact of panic trading.
+When a deviation from index is genuine, then we would increase the possible deviation.
+
+The actual annualized returns of such a carry trade are summarized in the table below.
+
+Table:
+
+Year, Currency, Exchange, Annual Return
+
+funding_btc_vs_eth_annualized_zoom.png
+funding_btc_vs_eth_zoom.png
+funding_btc_vs_eth_annualized.png
+funding_btc_vs_eth.png
 
@@
 
-Crypto exchanges often provide a so-called perpetual future, which is a synthetic (typically cash-settled instrument) whose return is tied to the underlying via a funding rate.
-Most exchanges (quote here) provide perpetual futures for Bitcoin and Ether.
-The price of each perpetual future is linked to the underlying by adjusting a variable interest rate, called the funding rate, that fluctuates depending on the deviation between the price of the perpetual future and the underlying.
-The funding rate increases the cost of holding positions against the deviation, meaning that if the price of the perpetual future is higher than the underlying, the funding rate is positive which causes the market participants who are long to pay the short side in a predefined frequency.
-Broadly said, the more extreme the deviation, the higher the funding rate and thus the higher the incentive to trade against the deviation and thus converge the price of the perpetual future towards its underlying.
-The risk-free rate is approximated using the simplest and most liquid way of realising the funding rate, a carry trade.
-In such a trade, the trader shorts (longs) the perpetual future if the funding rate is positive (negative) and simulateously buys (sells) the underlying such that the market delta of the combined position is zero.
-
-The funding rate on \href{https://www.deribit.com/kb/deribit-linear-perpetual}{Deribit} is calculated as follows:
-
-Instruments, such as inverse options, futures and perpetual futures, have a Mark Price $M$.
-The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth (quote:
-Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system.
-Usually, this is the average of the best bid and best ask price.
-However, for risk management purposes, there is price bandwidth in place.
-).
-The Deribit Index $D$, which is an equally weighted Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.
-
-\begin{equation}
-P = \frac{M - D}{D}
-\end{equation}
-
-The Funding Rate results as an 8-hour interest rate from the interval in which the Premium Rate falls.
-
-\begin{equation}
-F = \max{0.025\%, P} + \min{-0.025\%, P}
-\end{equation}
-
-The actual funding payment results $f$ from the product of the Funding Rate, Position Size and Holding Time. It is continuously added to the PnL account and settled daily at 8:00 UTC.
-
-@Todo: Summarize!
-Mark Price
-It is essential to understand how the mark price is calculated. We start by determining the "Fair Price". The fair price is calculated as the average of the fair impact bid and the fair impact ask.
-Fair Impact Bid Price is an average price at which 100,000 USDC worth of contracts can be bought.=
-Fair Impact Ask Price is an average price at which 100,000 USDC worth of contracts can be sold.
-Fair Price can never be higher than 0.1\% of best ask or lower than best bid
-Fair Price = (Fair Impact Bid + Fair Impact Ask) / 2
-The mark price is derived using both the Deribit Index and the fair price, by adding to the Deribit Index the 30 second exponential moving average (EMA) of the Fair Price - Deribit Index.
-
-Mark Price = Deribit Index + 30 second EMA (Fair Price - Deribit Index)
-We implement a safety setting on our mark price to not deviate by more than a certain percentage of Index.
-This is to prevent manipulation or to curb the impact of panic trading.
-When a deviation from index is genuine, then we would increase the possible deviation.
-
-Solve for interest rates from Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$.
-
-\begin{equation}
-F_t = e^{r \tau} S_t
-\end{equation}
-
-The actual annualized returns of such a carry trade are summarized in the table below.
-
-Table:
-
-Year, Currency, Exchange, Annual Return
-
-funding_btc_vs_eth_annualized_zoom.png
-funding_btc_vs_eth_zoom.png
-funding_btc_vs_eth_annualized.png
-funding_btc_vs_eth.png
-
 \section{Methodology}

### 2024-02-14 written/paper.tex
table labels and captions
table formatting looks good

@@
 
+Source for liquidity: 
+https://www.coingecko.com/en/derivatives
+https://www.coingecko.com/en/derivatives/futures
+
+% Source: https://www.tablesgenerator.com/#
+% Please add the following required packages to your document preamble:
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+
+As of 2024-01-07
+
+Bitcoin Perpetuals with 
+Total Open Interest \$19,343,021,437
+Total 24h Trade Volume \$50,339,886,015
+
+Ether Perpetuals
+
+Total Open Interest \$14,945,055,482
+Total 24h Trade Volume \$18,097,004,167
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% \usepackage[table,xcdraw]{xcolor}
+% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+
+BTC Futures
+
+with
+
+Total Open Interest $1,405,918,350
+Total 24h Trade Volume $324,820,482
+
+ETH Futures
+
+with 
+Total Open Interest $466,932,584
+Total 24h Trade Volume $98,238,298
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+
+\section{Methodology}
+
+We follow the argument that any beta-neutral portfolio should yield the risk-free rate.
+We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
+The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
+The weight $\theta$ is found by solving Equation 2 through Equation 3.
+The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4.
+The underlying data are executed transactions.
+All option greeks remain constant except time-to-maturity.
+Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time.
+All options are bought and held until settlement at 10am UTC.
+We match our universe of straddles as follows:
+Per definition, a straddle exists of a call and a put with similar strike and maturity.
+We construct the set of empirical straddles by iterating over our list of executed calls and puts.
+For each call (put), we use Put-Call-Parity to complete the straddle.
+The empirical performance of the resulting zero-beta straddles is assessed on a daily base.
+We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
+For each level of moneyness m, we construct an interval $[m, m + 0.05]$.
+We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
+We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
+
+Straddle Return $r_v$￼, Share of Straddle’s value in Call Options ￼$\theta$, Call and Put market Beta ￼$\beta_c$, $\beta_p$.
+
+\begin{equation}
+r_v = \theta r_c + (1-\theta)r_p
+\end{equation}
+
+\begin{equation}
+\theta \beta_c + (1-\theta)\beta_p = 0\\
+\end{equation}
+
+\begin{equation}
+\theta = \frac{-\beta_p}{\beta_c - \beta_p}\\
+\end{equation}
+
+\begin{equation}
+\beta_c = \frac{s}{C} \Delta \beta_s\\
+\end{equation}
+
+We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events.
+Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
+Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
+Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
+Maybe make a summary of the relationship between ATM and 20\% OTM premium.
+
+The performance of the vanilla and crash-resistant straddles is evaluated with and without fees.
+Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs.
+The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
+Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
+Consequently, the trading fee for one option spread would be the lesser of 0.0003 Bitcoin or 12.5\% of the more expensive option price.
+All fees are converted into USD based on the BTC/USDT exchange rate around settlement time.
+
+\section{Data}
+
+We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
+The exchange started operations in July 2017. 
+Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates for the perpetual future of Bitcoin and Ether since (approx.) July 2019.
+
+Two conditions are imposed on the option data:
+1) The maximum IV is 2.5 and the minimum IV is 0.1.
+2) In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
+3) Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
+4) We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
+
+The purpose of the first restriction is to impose a fair bound to the options that is independent of liquidity levels.
+For illiquid options, occurrences of bid prices at 0\% IV and ask prices of 500\% may occur.
+The purpose the second restriction of unique usage is to prevent a bias due to the possible more frequent trading of certain options.
+Generally, we observe that instruments with short maturity are traded more frequently.
+Yet, this could also be understood as cheaper instruments trading more frequently since (Black-Scholes) option prices increase with time-to-maturity.
+
+Bitcoin only:
+We drop 0.9\% of observations due to restriction 1)
+We drop 17\% of observations due to restriction 3)
+Overall, we have 5,028,945 observations. Post filtering, 4,150,778 observations remain in the set.
+
+Ethereum: 
+Amount of Observations outside of allowed IV range:  0.017042133327261764
+Amount of Observations outside of allowed Tau range:  0.20172172747210984
+Overall Observations: 2283869
+Amount of Observations in our set post filtering:  1809762
+
+Regarding data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
+Indeed, using actual transaction data instead of orderbook data removes the threat of wash trading (etc) to our data.
+The most likely negative factor that could affect our data quality is wash trading.
+We assess the risk of wash trading as follows:
+
+"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." (from: https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf)
+
+We asses the risk of wash trading contaminating our data set as low.
+The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
+At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot 12 USD.
+Such fees, even without consideration of spreads, make wash trading from a trader's perspective entirely infeasible.
+
+- table of amount of transactions per group
+- plot: amount of transactions over time per group (crypto)
+
+\section{Results}
+
+We find the returns of the zero-beta-straddles to be t-distributed and conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
+The null hypothesis is not rejected for all models, vanilla and crash-resistant, for ITM and OTM options.
+Conversely, the null hypothesis is firmly rejected on a high significance level for ATM options.
+Therefore, we accept the alternative hypothesis of an underperformance for ATM options.
+Consequently, we find a similar result to Shumway and Bakshi - that is the existence of a premium for ATM contracts.
+We figure the premium to be a volatility premium since a straddle's payoff depends on the relationship of Implied Volatility to Realized Volatility. 
+Unsurprisingly, the size of the premium in crypto markets is higher than the counterpart in equity markets - we figure that the reason is the higher risk in crypto markets, particularly via volatility and counterparty risk.
+Furthermore, there are mostly retailers present in the crypto option market.
+Some professional liquidity providers exist, but they remain few and therefore another reason for the premium's size could be illiquidity.
+
+- the premium is larger when tau is small.
+
+- report average returns for options grouped per strike (and overall)
+
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized.png}
+    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized_zoom.png}
+
+     \captionof{figure}{(Zoomed) Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth.png}
+    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_zoom.png}
+    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\pagebreak
+\newpage
+
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Performance - Vanilla - Fees}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Performance - Vanilla - Fees}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+We conduct a left-sided t-test to test for a population mean of zero. Values are rounded to 4 digits.
+
+Compare to weekly 0.5\% loss observed in equity options.
+
+\section{Conclusion}
+
+Further research: 
+- Evidence for leverage effect
+
+%\begin{minipage}{\textwidth}
+%    \centering
+  %  \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
+    %\captionof{figure}{Performance - Vanilla - No Fees}
+    %\centering
+    %\includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
+     %\captionof{figure}{Performance - Vanilla - Fees}
+
+%\end{minipage}
+%\begin{minipage}{\textwidth}
+%    \centering
+%    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
+%    \captionof{figure}{Performance - Crash Resistant - No Fees}
+ %   \centering
+ %   \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
+ %    \captionof{figure}{Performance - Crash Resistant - Fees}
+
+%\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+%\label{ATM Term Structure}
+%\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+%Deribit perpetual contracts are a derivative product similar to a future, however, they do not have an expiry date.
+The perpetual contract features funding payments.
+These payments have been introduced to keep the perpetual contract price as close as possible to the underlying crypto price - the relevant Deribit Index.
+If the perpetual contract trades at a higher price than the index, traders that have long positions need to make funding payments to the traders that have short positions.
+This will make the product less attractive to the long position holders and more attractive to the short position holders.
+This subsequently will cause a perpetual price to trade in line with the price of the index.
+If the perpetual trades at a price lower than the index, the short position holders will have to pay the long position holders instead.
+%
+%The Deribit perpetual contract features a continuous measurement of the difference between the mark price of the contract and the relevant Deribit Index.
+The percentage difference between these two price levels is the basis for the 8-hourly funding rate that is applied to all outstanding perpetual contracts.
+%
+%Funding payments are calculated every millisecond.
+The funding payments will be added to or subtracted from the realized PNL, which is also part of the available trading balance.
+At each daily settlement, the realized PNL will be moved to or from the cash balance, from which withdrawals can be made.
+%
+%The total funding paid will show up in the transaction log in the "funding" column.
+This column shows the funding amount that is applied to the trader's entire net position in the period between the relevant trade and the trade before that.
+Put differently: the trader can see the funding paid or received on the position between position changes.
+%
+%Funding Rate
+%When the funding rate is positive, long position holders pay funding to the short position holders; when the funding rate is negative, short position holders pay funding to the long position holders.
+The funding rate is expressed as an 8-hour interest rate, and is calculated at any given time as follows:
+%
+%Premium Rate
+%Premium Rate = ((Mark Price - Deribit Index) / Deribit Index) * 100%
+%
+%Funding Rate
+%Sequentially, the funding rate is derived from the premium rate by applying a damper.
+%
+%If the premium rate is within -0.025\% and 0.025\% range, the actual funding rate will be reduced to 0.00\%.
+%If the premium rate is lower than -0.025\%, then the actual funding rate will be the premium rate + 0.025\%.
+%If the premium rate is higher than 0.025\%, then the actual funding rate will be the premium rate - 0.025\%.
+%Additionally, the funding rate is capped at +/ - 5\% for all linear USDC perpetuals.
+%Funding Rate = Maximum (0.025\%, Premium Rate) + Minimum (-0.025\%, Premium Rate)
+%
+%Time Fraction
+%Time Fraction = Funding Rate Time Period / 8 hours
+%
+%The actual funding payment is calculated by multiplying the funding rate by the position size and the time fraction.
+%
+%Funding Payment = Funding Rate * Position Size * Time Fraction
+%
+%In reality, the spread of the Deribit Index and the mark price changes continuously, and all changes are taken into account.
+Therefore, the examples above are extreme simplifications of the actual calculations.
+The funding paid or received is continuously added to the realized PNL and is moved to or from the cash balance at the daily settlement, at 08:00 UTC.
+
+\section{References}
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{ref-aitsahalia01optionprice}{}%
+Aı̈t-Sahalia, Y., Wang, Y., \& Yared, F. (2001). Do option markets
+correctly price the probabilities of movement of the underlying asset?
+\emph{Journal of Econometrics}, \emph{102}(1), 67--110.
+\url{https://doi.org/https://doi.org/10.1016/S0304-4076(00)00091-9}
+
+\leavevmode\hypertarget{ref-ait_sahalia_wang1998}{}%
+Aït-Sahalia, Y., \& Lo, A. W. (1998). Nonparametric estimation of
+state-price densities implicit in financial asset prices. \emph{The
+Journal of Finance}, \emph{53}(2), 499--547.
+\url{https://doi.org/https://doi.org/10.1111/0022-1082.215228}
+
+\leavevmode\hypertarget{ref-alexander2022net}{}%
+Alexander, C., Deng, J., Feng, J., \& Wan, H. (2022). Net buying
+pressure and the information in bitcoin option trades. \emph{Journal of
+Financial Markets}, 100764.
+
+\leavevmode\hypertarget{ref-inverse_options}{}%
+Alexander, C., \& Imeraj, A. (2021, July). Inverse options in a
+black-scholes world.
+\url{https://doi.org/https://doi.org/10.48550/arXiv.2107.12041}
+
+\leavevmode\hypertarget{ref-aloosh}{}%
+Aloosh, A., \& Li, J. (2019). Direct evidence of bitcoin wash trading.
+\emph{Theory of Probability \& Its Applications, 5, 285-301}.
+\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3362153}
+
+\leavevmode\hypertarget{ref-bitmex}{}%
+Bitmex. (2019). Presentation to the u.s. Securities and exchange
+commission on wash trading.
+\url{https://www.sec.gov/comments/sr-nysearca-2019-01/srnysearca201901-5164833-183434.pdf}.
+Accessed 18 January 2022
+
+\leavevmode\hypertarget{ref-blase}{}%
+Blaskowitz, O., Härdle, W. K., \& Schmidt, P. (2004). Skewness and
+kurtosis trades. In (pp. 1--14).
+\url{https://doi.org/10.1007/978-0-8176-8180-7_1}
+
+\leavevmode\hypertarget{ref-speculation}{}%
+Blau, B. M. (2017). Price dynamics and speculative trading in bitcoin.
+\emph{Research in International Business and Finance}, \emph{41},
+493--499.
+\url{https://doi.org/https://doi.org/10.1016/j.ribaf.2017.05.010}
+
+\leavevmode\hypertarget{ref-bloomberg-retail-share}{}%
+Bloomberg. (2021, November 17). Retail traders slide back below 20\% of
+market's total volume.
+\url{https://www.bloomberg.com/news/articles/2021-11-17/retail-traders-retreat-as-choppy-markets-challenge-easy-profits}.
+Accessed 24 August 2021
+
+\leavevmode\hypertarget{ref-breeden_litzenberger78}{}%
+Breeden, D. T., \& Litzenberger, R. H. (1978). Prices of
+state-contingent claims implicit in option prices. \emph{The Journal of
+Business}, \emph{51}(4), 621--651.
+\url{http://www.jstor.org/stable/2352653}
+
+\leavevmode\hypertarget{ref-coins_with_benefits}{}%
+Chen, C. Y., \& Vinogradov, D. (2021). Coins with benefits: On
+existence, pricing kernel and risk premium of cryptocurrencies.
+\emph{Available at SSRN 3959984}.
+\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3864578}
+
+\leavevmode\hypertarget{ref-choi}{}%
+Choi, S., \& Shin, J. (2022). Bitcoin: An inflation hedge but not a safe
+haven. \emph{Finance Research Letters}, \emph{46}, 102379.
+\url{https://doi.org/https://doi.org/10.1016/j.frl.2021.102379}
+
+\leavevmode\hypertarget{ref-oil_spd}{}%
+Christoffersen, P., Jacobs, K., \& Pan, X. (. (2021). The State Price
+Density Implied by Crude Oil Futures and Option Prices. \emph{The Review
+of Financial Studies}, \emph{35}(2), 1064--1103.
+\url{https://doi.org/10.1093/rfs/hhab011}
+
+\leavevmode\hypertarget{ref-cryptonews_bitcoin_retail_share}{}%
+Coinbase, S., Cryptonews. (2022). Institutions \& retail compete for
+bitcoin - whose hands are stronger?
+\url{https://cryptonews.com/exclusives/institutions-retail-compete-for-bitcoin-which-is-the-biggest-9695.htm}.
+Accessed 22 March 2022
+
+\leavevmode\hypertarget{ref-decentralized_wash_trading}{}%
+Cong, L., Li, X., Tang, K., \& Yang, Y. (2019). Crypto wash trading.
+\emph{SSRN Electronic Journal}.
+\url{https://doi.org/10.2139/ssrn.3530220}
+
+\leavevmode\hypertarget{ref-jackwerth_pk}{}%
+Cuesdeanu, H., \& Jackwerth, J. C. (2018). The pricing kernel puzzle:
+survey and outlook. \emph{Annals of Finance}, \emph{14}(3), 289--329.
+\url{https://doi.org/10.1007/s10436-017-0317-9}
+
+\leavevmode\hypertarget{ref-cross_border_payments}{}%
+Deng, Q. (2020). Application analysis on blockchain technology in
+cross-border payment. In.
+\url{https://doi.org/10.2991/aebmr.k.200306.050}
+
+\leavevmode\hypertarget{ref-deribit-insurance-fund}{}%
+Deribit. (2020a). Deribit insurance fund.
+\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021
+
+\leavevmode\hypertarget{ref-synthetic-btc-index}{}%
+Deribit. (2020b). Deribit btc-usd index.
+\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021
+
+\leavevmode\hypertarget{ref-market-maker-obligations}{}%
+Deribit. (2020c). Deribit market maker obligations.
+\url{https://www.deribit.com/pages/docs/options}. Accessed 2 January
+2021
+
+\leavevmode\hypertarget{ref-deribit_retail_piechart}{}%
+Deribit. (2022a). Deribit volume share.
+\url{https://www.deribit.com/statistics/BTC/market-data}. Accessed 25
+July 2022
+
+\leavevmode\hypertarget{ref-deribit_margin}{}%
+Deribit. (2022b). Deribit margin requirements.
+\url{https://legacy.deribit.com/pages/docs/options}. Accessed 2 May 2022
+
+\leavevmode\hypertarget{ref-deribit_fees}{}%
+Deribit. (2022c). Deribit margin requirements.
+\url{https://www.deribit.com/kb/fees}. Accessed 2 May 2022
+
+\leavevmode\hypertarget{ref-deribit-rate-limit}{}%
+Deribit. (2023). Deribit rate limits.
+\url{https://www.deribit.com/kb/deribit-rate-limits}. Accessed 16 April
+2021
+
+\leavevmode\hypertarget{ref-vola_premium}{}%
+Eraker, B. (2021). The volatility premium. \emph{Quarterly Journal of
+Finance (QJF)}, \emph{11}(03), 1--35.
+\url{https://EconPapers.repec.org/RePEc:wsi:qjfxxx:v:11:y:2021:i:03:n:s2010139221500142}
+
+\leavevmode\hypertarget{ref-networkeffect}{}%
+Gandal, N., \& Halaburda, H. (2016). Can we predict the winner in a
+market with network effects? Competition in cryptocurrency market.
+\emph{Games}, \emph{7}(3). \url{https://doi.org/10.3390/g7030016}
+
+\leavevmode\hypertarget{ref-Grith09sim}{}%
+Grith, M., Härdle, W. K., \& Park, J. (2009). Shape invariant modelling
+pricing kernels and risk aversion.
+\url{https://doi.org/10.2139/ssrn.2894289}
+
+\leavevmode\hypertarget{ref-hall_1991}{}%
+Hall, P. (1991). Edgeworth expansions for nonparametric density
+estimators, with applications. \emph{Statistics}, \emph{22}(2),
+215--232. \url{https://doi.org/10.1080/02331889108802305}
+
+\leavevmode\hypertarget{ref-hayes}{}%
+Hayes, A. S. (2019). Bitcoin price and its marginal cost of production:
+Support for a fundamental value. \emph{Applied Economics Letters},
+\emph{26}(7), 554--560.
+\url{https://doi.org/10.1080/13504851.2018.1488040}
+
+\leavevmode\hypertarget{ref-w2yo}{}%
+Härdle, W. K., Okhrin, Y., \& Wang, W. (2014). Uniform Confidence Bands
+for Pricing Kernels. \emph{Journal of Financial Econometrics},
+\emph{13}(2), 376--413. \url{https://doi.org/10.1093/jjfinec/nbu002}
+
+\leavevmode\hypertarget{ref-pricing_cryptocurrency_options}{}%
+Hou, A. J., Wang, W., Chen, C. Y. H., \& Härdle, W. K. (2020). Pricing
+Cryptocurrency Options*. \emph{Journal of Financial Econometrics},
+\emph{18}(2), 250--279. \url{https://doi.org/10.1093/jjfinec/nbaa006}
+
+\leavevmode\hypertarget{ref-xfg_spd}{}%
+Huynh, K., Kervella, P., \& Zheng, J. (2002). \emph{Estimating
+state-price densities with nonparametric regression} (SFB 373 Discussion
+Papers No. 2002,40). Humboldt University of Berlin, Interdisciplinary
+Research Project 373: Quantification; Simulation of Economic Processes.
+\url{https://EconPapers.repec.org/RePEc:zbw:sfb373:200240}
+
+\leavevmode\hypertarget{ref-pumpndump}{}%
+La Morgia, M., Mei, A., Sassi, F., \& Stefa, J. (2020). Pump and dumps
+in the bitcoin era: Real time detection of cryptocurrency market
+manipulations. In \emph{2020 29th international conference on computer
+communications and networks (icccn)} (pp. 1--9).
+\url{https://doi.org/10.1109/ICCCN49398.2020.9209660}
+
+\leavevmode\hypertarget{ref-vola_stylized_facts}{}%
+Masset, P. (2011). Volatility stylized facts. \emph{SSRN Electronic
+Journal}. \url{https://doi.org/10.2139/ssrn.1804070}
+
+\leavevmode\hypertarget{ref-satoshi2009}{}%
+Nakamoto, S. (2009). Bitcoin: A peer-to-peer electronic cash system.
+\url{http://www.bitcoin.org/bitcoin.pdf}
+
+\leavevmode\hypertarget{ref-fundamental-theorem-of-asset-pricing}{}%
+Pascucci, A., \& Agliardi, R. (2011). PDE and martingale methods in
+option pricing. In (pp. 429--495).
+
+\leavevmode\hypertarget{ref-rodgers2019}{}%
+Rodgers, T. (2019, April 4). 95 percent of volume could be wash trading
+as bitcoin price surges.
+\url{https://www.forbes.com/sites/tomrodgers1/2019/04/04/99-of-volume-could-be-wash-trading-as-bitcoin-takes-back-5000/?sh=4640bcbc23d5}.
+Accessed 15 April 2023
+
+\leavevmode\hypertarget{ref-Rookley97}{}%
+Rookley, C. (1997). Fully exploiting the information content of intra
+day option quotes: Applications in option pricing and risk management.
+
+\leavevmode\hypertarget{ref-sar2017}{}%
+Sar, M. (2017). Dodd-frank and the spoofing prohibition in commodities
+markets.
+
+\leavevmode\hypertarget{ref-deriv_volume}{}%
+Skew.com. (2022). Open interest for bitcoin options over time. Skew is a
+leading crypto data analytics platform for institutional clients.
+\url{https://analytics.skew.com/dashboard/bitcoin-options}. Accessed 25
+July 2022
+
+\leavevmode\hypertarget{ref-brazilian_speculation}{}%
+Smaniotto, E. N., \& Neto, G. B. (2022). Speculative trading in bitcoin:
+A brazilian market evidence. \emph{The Quarterly Review of Economics and
+Finance}, \emph{85}, 47--54.
+\url{https://doi.org/https://doi.org/10.1016/j.qref.2020.10.024}
+
+\leavevmode\hypertarget{ref-cross_border_stellar}{}%
+Stellar Development Foundation. (2022). 2022 research reveals high
+awareness and growing cross-border use of cryptocurrency in four key
+markets.
+\url{https://www.prnewswire.com/news-releases/2022-research-reveals-high-awareness-and-growing-cross-border-use-of-cryptocurrency-in-four-key-markets-301512401.html}.
+Accessed 22 July 2022
+
+\leavevmode\hypertarget{ref-nickszabo}{}%
+Szabo, N. (2008). Bit gold.
+\url{https://unenumerated.blogspot.com/2005/12/bit-gold.html}. Accessed
+28 July 2022
+
+\leavevmode\hypertarget{ref-tuccella2021}{}%
+Tuccella, J.-N., Nadler, P., \& Șerban, O. (2021). Protecting retail
+investors from order book spoofing using a gru-based detection model.
+
+\clearpage
+
+\section{Appendix}
+
 \begin{table}[]
@@
 \end{tabular}
+\caption{Relevance of Perpetual Futures to Futures as measured by Open Interest and Trading Volume}
+\label{table:stats}
 \end{table}
-
-Source for liquidity: 
-https://www.coingecko.com/en/derivatives
-https://www.coingecko.com/en/derivatives/futures
-
-% Source: https://www.tablesgenerator.com/#
-% Please add the following required packages to your document preamble:
-% \usepackage[table,xcdraw]{xcolor}
-% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \usepackage[table,xcdraw]{xcolor}
-% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-
-As of 2024-01-07
-
-Bitcoin Perpetuals with 
-Total Open Interest \$19,343,021,437
-Total 24h Trade Volume \$50,339,886,015
 
@@
 \end{tabular}}
+\caption{Bitcoin Perpetual Futures}
+\label{table:btc_perpetuals}
 \end{table}
-
-Ether Perpetuals
-
-Total Open Interest \$14,945,055,482
-Total 24h Trade Volume \$18,097,004,167
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \usepackage[table,xcdraw]{xcolor}
-% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-% \usepackage[table,xcdraw]{xcolor}
-% Beamer presentation requires \usepackage{colortbl} instead of \usepackage[table,xcdraw]{xcolor}
-
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
 
@@
 \end{tabular}}
+\caption{Ether Perpetual Futures}
+\label{eth_perpetual_futures}
 \end{table}
-
-BTC Futures
-
-with
-
-Total Open Interest $1,405,918,350
-Total 24h Trade Volume $324,820,482
 
@@
 \end{tabular}}
+\caption{BTC Futures}
+\label{table:btc_futures}
 \end{table}
-
-ETH Futures
-
-with 
-Total Open Interest $466,932,584
-Total 24h Trade Volume $98,238,298
 
@@
 \end{tabular}}
+\caption{ETH Futures}
+\label{table:eth_futures}
 \end{table}
 
-% Please add the following required packages to your document preamble:
-% \usepackage{booktabs}
-
-\section{Methodology}
-
-We follow the argument that any beta-neutral portfolio should yield the risk-free rate.
-We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
-The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
-The weight $\theta$ is found by solving Equation 2 through Equation 3.
-The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4.
-The underlying data are executed transactions.
-All option greeks remain constant except time-to-maturity.
-Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time.
-All options are bought and held until settlement at 10am UTC.
-We match our universe of straddles as follows:
-Per definition, a straddle exists of a call and a put with similar strike and maturity.
-We construct the set of empirical straddles by iterating over our list of executed calls and puts.
-For each call (put), we use Put-Call-Parity to complete the straddle.
-The empirical performance of the resulting zero-beta straddles is assessed on a daily base.
-We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
-For each level of moneyness m, we construct an interval $[m, m + 0.05]$.
-We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
-We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
-
-Straddle Return $r_v$￼, Share of Straddle’s value in Call Options ￼$\theta$, Call and Put market Beta ￼$\beta_c$, $\beta_p$.
-
-\begin{equation}
-r_v = \theta r_c + (1-\theta)r_p
-\end{equation}
-
-\begin{equation}
-\theta \beta_c + (1-\theta)\beta_p = 0\\
-\end{equation}
-
-\begin{equation}
-\theta = \frac{-\beta_p}{\beta_c - \beta_p}\\
-\end{equation}
-
-\begin{equation}
-\beta_c = \frac{s}{C} \Delta \beta_s\\
-\end{equation}
-
-We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events.
-Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
-Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
-Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
-Maybe make a summary of the relationship between ATM and 20\% OTM premium.
-
-The performance of the vanilla and crash-resistant straddles is evaluated with and without fees.
-Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs.
-The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
-Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
-Consequently, the trading fee for one option spread would be the lesser of 0.0003 Bitcoin or 12.5\% of the more expensive option price.
-All fees are converted into USD based on the BTC/USDT exchange rate around settlement time.
-
-\section{Data}
-
-We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
-The exchange started operations in July 2017. 
-Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates for the perpetual future of Bitcoin and Ether since (approx.) July 2019.
-
-Two conditions are imposed on the option data:
-1) The maximum IV is 2.5 and the minimum IV is 0.1.
-2) In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
-3) Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
-4) We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
-
-The purpose of the first restriction is to impose a fair bound to the options that is independent of liquidity levels.
-For illiquid options, occurrences of bid prices at 0\% IV and ask prices of 500\% may occur.
-The purpose the second restriction of unique usage is to prevent a bias due to the possible more frequent trading of certain options.
-Generally, we observe that instruments with short maturity are traded more frequently.
-Yet, this could also be understood as cheaper instruments trading more frequently since (Black-Scholes) option prices increase with time-to-maturity.
-
-Bitcoin only:
-We drop 0.9\% of observations due to restriction 1)
-We drop 17\% of observations due to restriction 3)
-Overall, we have 5,028,945 observations. Post filtering, 4,150,778 observations remain in the set.
-
-Ethereum: 
-Amount of Observations outside of allowed IV range:  0.017042133327261764
-Amount of Observations outside of allowed Tau range:  0.20172172747210984
-Overall Observations: 2283869
-Amount of Observations in our set post filtering:  1809762
-
-Regarding data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
-Indeed, using actual transaction data instead of orderbook data removes the threat of wash trading (etc) to our data.
-The most likely negative factor that could affect our data quality is wash trading.
-We assess the risk of wash trading as follows:
-
-"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." (from: https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf)
-
-We asses the risk of wash trading contaminating our data set as low.
-The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
-At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot 12 USD.
-Such fees, even without consideration of spreads, make wash trading from a trader's perspective entirely infeasible.
-
-- table of amount of transactions per group
-- plot: amount of transactions over time per group (crypto)
-
-\section{Results}
-
-We find the returns of the zero-beta-straddles to be t-distributed and conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
-The null hypothesis is not rejected for all models, vanilla and crash-resistant, for ITM and OTM options.
-Conversely, the null hypothesis is firmly rejected on a high significance level for ATM options.
-Therefore, we accept the alternative hypothesis of an underperformance for ATM options.
-Consequently, we find a similar result to Shumway and Bakshi - that is the existence of a premium for ATM contracts.
-We figure the premium to be a volatility premium since a straddle's payoff depends on the relationship of Implied Volatility to Realized Volatility. 
-Unsurprisingly, the size of the premium in crypto markets is higher than the counterpart in equity markets - we figure that the reason is the higher risk in crypto markets, particularly via volatility and counterparty risk.
-Furthermore, there are mostly retailers present in the crypto option market.
-Some professional liquidity providers exist, but they remain few and therefore another reason for the premium's size could be illiquidity.
-
-- the premium is larger when tau is small.
-
-- report average returns for options grouped per strike (and overall)
-
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized.png}
-    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized_zoom.png}
-
-     \captionof{figure}{(Zoomed) Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
-
-\end{minipage}
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth.png}
-    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_zoom.png}
-    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
-
-\end{minipage}
-   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
-
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-
-\pagebreak
-\newpage
-
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{BTC - Performance - Vanilla - Fees}
-
-\end{minipage}
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}
-
-\end{minipage}
-   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
-
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{ETH - Performance - Vanilla - Fees}
-
-\end{minipage}
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
-
-\end{minipage}
-   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
-
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-
-We conduct a left-sided t-test to test for a population mean of zero. Values are rounded to 4 digits.
-
-Compare to weekly 0.5\% loss observed in equity options.
-
-\section{Conclusion}
-
-Further research: 
-- Evidence for leverage effect
-
-%\begin{minipage}{\textwidth}
-%    \centering
-  %  \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
-    %\captionof{figure}{Performance - Vanilla - No Fees}
-    %\centering
-    %\includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/vanilla/no_fees/density/moneyness_between_95_and_105.png}
-     %\captionof{figure}{Performance - Vanilla - Fees}
-
-%\end{minipage}
-%\begin{minipage}{\textwidth}
-%    \centering
-%    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
-%    \captionof{figure}{Performance - Crash Resistant - No Fees}
- %   \centering
- %   \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/out/crash_resistant/no_fees/moneyness_between_95_and_105.png}
- %    \captionof{figure}{Performance - Crash Resistant - Fees}
-
-%\end{minipage}
-   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
-
-%\label{ATM Term Structure}
-%\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-
 \begin{table}[ht]
 \hline
-\resizebox{\textwidth}{!}{\begin{tabular}{lllll}
-  Moneyness    & Vanilla ex Fee & Vanilla cum Fee & Crash Resistant ex Fee & Crash Resistant cum Fee \\
+\resizebox{\textwidth}{!}{\begin{tabular}{lrrrr}
+  \textbf{Moneyness}   & \multicolumn{1}{l}{\textbf{Vanilla ex Fee}}  & \multicolumn{1}{l}{\textbf{Vanilla cum Fee}} & \multicolumn{1}{l}{\textbf{Crash Resistant ex Fee}}&\multicolumn{1}{l}{\textbf{Crash Resistant cum Fee}} \\
 \hline
@@
 \end{tabular}}
+\caption{t-Statistics of beta-neutral BTC Option portfolios}
+\label{table:btc_t_stats}
 \end{table}
 
-%Deribit perpetual contracts are a derivative product similar to a future, however, they do not have an expiry date.
-The perpetual contract features funding payments.
-These payments have been introduced to keep the perpetual contract price as close as possible to the underlying crypto price - the relevant Deribit Index.
-If the perpetual contract trades at a higher price than the index, traders that have long positions need to make funding payments to the traders that have short positions.
-This will make the product less attractive to the long position holders and more attractive to the short position holders.
-This subsequently will cause a perpetual price to trade in line with the price of the index.
-If the perpetual trades at a price lower than the index, the short position holders will have to pay the long position holders instead.
-%
-%The Deribit perpetual contract features a continuous measurement of the difference between the mark price of the contract and the relevant Deribit Index.
-The percentage difference between these two price levels is the basis for the 8-hourly funding rate that is applied to all outstanding perpetual contracts.
-%
-%Funding payments are calculated every millisecond.
-The funding payments will be added to or subtracted from the realized PNL, which is also part of the available trading balance.
-At each daily settlement, the realized PNL will be moved to or from the cash balance, from which withdrawals can be made.
-%
-%The total funding paid will show up in the transaction log in the "funding" column.
-This column shows the funding amount that is applied to the trader's entire net position in the period between the relevant trade and the trade before that.
-Put differently: the trader can see the funding paid or received on the position between position changes.
-%
-%Funding Rate
-%When the funding rate is positive, long position holders pay funding to the short position holders; when the funding rate is negative, short position holders pay funding to the long position holders.
-The funding rate is expressed as an 8-hour interest rate, and is calculated at any given time as follows:
-%
-%Premium Rate
-%Premium Rate = ((Mark Price - Deribit Index) / Deribit Index) * 100%
-%
-%Funding Rate
-%Sequentially, the funding rate is derived from the premium rate by applying a damper.
-%
-%If the premium rate is within -0.025\% and 0.025\% range, the actual funding rate will be reduced to 0.00\%.
-%If the premium rate is lower than -0.025\%, then the actual funding rate will be the premium rate + 0.025\%.
-%If the premium rate is higher than 0.025\%, then the actual funding rate will be the premium rate - 0.025\%.
-%Additionally, the funding rate is capped at +/ - 5\% for all linear USDC perpetuals.
-%Funding Rate = Maximum (0.025\%, Premium Rate) + Minimum (-0.025\%, Premium Rate)
-%
-%Time Fraction
-%Time Fraction = Funding Rate Time Period / 8 hours
-%
-%The actual funding payment is calculated by multiplying the funding rate by the position size and the time fraction.
-%
-%Funding Payment = Funding Rate * Position Size * Time Fraction
-%
-%In reality, the spread of the Deribit Index and the mark price changes continuously, and all changes are taken into account.
-Therefore, the examples above are extreme simplifications of the actual calculations.
-The funding paid or received is continuously added to the realized PNL and is moved to or from the cash balance at the daily settlement, at 08:00 UTC.
-
-\section{References}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-aitsahalia01optionprice}{}%
-Aı̈t-Sahalia, Y., Wang, Y., \& Yared, F. (2001). Do option markets
-correctly price the probabilities of movement of the underlying asset?
-\emph{Journal of Econometrics}, \emph{102}(1), 67--110.
-\url{https://doi.org/https://doi.org/10.1016/S0304-4076(00)00091-9}
-
-\leavevmode\hypertarget{ref-ait_sahalia_wang1998}{}%
-Aït-Sahalia, Y., \& Lo, A. W. (1998). Nonparametric estimation of
-state-price densities implicit in financial asset prices. \emph{The
-Journal of Finance}, \emph{53}(2), 499--547.
-\url{https://doi.org/https://doi.org/10.1111/0022-1082.215228}
-
-\leavevmode\hypertarget{ref-alexander2022net}{}%
-Alexander, C., Deng, J., Feng, J., \& Wan, H. (2022). Net buying
-pressure and the information in bitcoin option trades. \emph{Journal of
-Financial Markets}, 100764.
-
-\leavevmode\hypertarget{ref-inverse_options}{}%
-Alexander, C., \& Imeraj, A. (2021, July). Inverse options in a
-black-scholes world.
-\url{https://doi.org/https://doi.org/10.48550/arXiv.2107.12041}
-
-\leavevmode\hypertarget{ref-aloosh}{}%
-Aloosh, A., \& Li, J. (2019). Direct evidence of bitcoin wash trading.
-\emph{Theory of Probability \& Its Applications, 5, 285-301}.
-\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3362153}
-
-\leavevmode\hypertarget{ref-bitmex}{}%
-Bitmex. (2019). Presentation to the u.s. Securities and exchange
-commission on wash trading.
-\url{https://www.sec.gov/comments/sr-nysearca-2019-01/srnysearca201901-5164833-183434.pdf}.
-Accessed 18 January 2022
-
-\leavevmode\hypertarget{ref-blase}{}%
-Blaskowitz, O., Härdle, W. K., \& Schmidt, P. (2004). Skewness and
-kurtosis trades. In (pp. 1--14).
-\url{https://doi.org/10.1007/978-0-8176-8180-7_1}
-
-\leavevmode\hypertarget{ref-speculation}{}%
-Blau, B. M. (2017). Price dynamics and speculative trading in bitcoin.
-\emph{Research in International Business and Finance}, \emph{41},
-493--499.
-\url{https://doi.org/https://doi.org/10.1016/j.ribaf.2017.05.010}
-
-\leavevmode\hypertarget{ref-bloomberg-retail-share}{}%
-Bloomberg. (2021, November 17). Retail traders slide back below 20\% of
-market's total volume.
-\url{https://www.bloomberg.com/news/articles/2021-11-17/retail-traders-retreat-as-choppy-markets-challenge-easy-profits}.
-Accessed 24 August 2021
-
-\leavevmode\hypertarget{ref-breeden_litzenberger78}{}%
-Breeden, D. T., \& Litzenberger, R. H. (1978). Prices of
-state-contingent claims implicit in option prices. \emph{The Journal of
-Business}, \emph{51}(4), 621--651.
-\url{http://www.jstor.org/stable/2352653}
-
-\leavevmode\hypertarget{ref-coins_with_benefits}{}%
-Chen, C. Y., \& Vinogradov, D. (2021). Coins with benefits: On
-existence, pricing kernel and risk premium of cryptocurrencies.
-\emph{Available at SSRN 3959984}.
-\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3864578}
-
-\leavevmode\hypertarget{ref-choi}{}%
-Choi, S., \& Shin, J. (2022). Bitcoin: An inflation hedge but not a safe
-haven. \emph{Finance Research Letters}, \emph{46}, 102379.
-\url{https://doi.org/https://doi.org/10.1016/j.frl.2021.102379}
-
-\leavevmode\hypertarget{ref-oil_spd}{}%
-Christoffersen, P., Jacobs, K., \& Pan, X. (. (2021). The State Price
-Density Implied by Crude Oil Futures and Option Prices. \emph{The Review
-of Financial Studies}, \emph{35}(2), 1064--1103.
-\url{https://doi.org/10.1093/rfs/hhab011}
-
-\leavevmode\hypertarget{ref-cryptonews_bitcoin_retail_share}{}%
-Coinbase, S., Cryptonews. (2022). Institutions \& retail compete for
-bitcoin - whose hands are stronger?
-\url{https://cryptonews.com/exclusives/institutions-retail-compete-for-bitcoin-which-is-the-biggest-9695.htm}.
-Accessed 22 March 2022
-
-\leavevmode\hypertarget{ref-decentralized_wash_trading}{}%
-Cong, L., Li, X., Tang, K., \& Yang, Y. (2019). Crypto wash trading.
-\emph{SSRN Electronic Journal}.
-\url{https://doi.org/10.2139/ssrn.3530220}
-
-\leavevmode\hypertarget{ref-jackwerth_pk}{}%
-Cuesdeanu, H., \& Jackwerth, J. C. (2018). The pricing kernel puzzle:
-survey and outlook. \emph{Annals of Finance}, \emph{14}(3), 289--329.
-\url{https://doi.org/10.1007/s10436-017-0317-9}
-
-\leavevmode\hypertarget{ref-cross_border_payments}{}%
-Deng, Q. (2020). Application analysis on blockchain technology in
-cross-border payment. In.
-\url{https://doi.org/10.2991/aebmr.k.200306.050}
-
-\leavevmode\hypertarget{ref-deribit-insurance-fund}{}%
-Deribit. (2020a). Deribit insurance fund.
-\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021
-
-\leavevmode\hypertarget{ref-synthetic-btc-index}{}%
-Deribit. (2020b). Deribit btc-usd index.
-\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021
-
-\leavevmode\hypertarget{ref-market-maker-obligations}{}%
-Deribit. (2020c). Deribit market maker obligations.
-\url{https://www.deribit.com/pages/docs/options}. Accessed 2 January
-2021
-
-\leavevmode\hypertarget{ref-deribit_retail_piechart}{}%
-Deribit. (2022a). Deribit volume share.
-\url{https://www.deribit.com/statistics/BTC/market-data}. Accessed 25
-July 2022
-
-\leavevmode\hypertarget{ref-deribit_margin}{}%
-Deribit. (2022b). Deribit margin requirements.
-\url{https://legacy.deribit.com/pages/docs/options}. Accessed 2 May 2022
-
-\leavevmode\hypertarget{ref-deribit_fees}{}%
-Deribit. (2022c). Deribit margin requirements.
-\url{https://www.deribit.com/kb/fees}. Accessed 2 May 2022
-
-\leavevmode\hypertarget{ref-deribit-rate-limit}{}%
-Deribit. (2023). Deribit rate limits.
-\url{https://www.deribit.com/kb/deribit-rate-limits}. Accessed 16 April
-2021
-
-\leavevmode\hypertarget{ref-vola_premium}{}%
-Eraker, B. (2021). The volatility premium. \emph{Quarterly Journal of
-Finance (QJF)}, \emph{11}(03), 1--35.
-\url{https://EconPapers.repec.org/RePEc:wsi:qjfxxx:v:11:y:2021:i:03:n:s2010139221500142}
-
-\leavevmode\hypertarget{ref-networkeffect}{}%
-Gandal, N., \& Halaburda, H. (2016). Can we predict the winner in a
-market with network effects? Competition in cryptocurrency market.
-\emph{Games}, \emph{7}(3). \url{https://doi.org/10.3390/g7030016}
-
-\leavevmode\hypertarget{ref-Grith09sim}{}%
-Grith, M., Härdle, W. K., \& Park, J. (2009). Shape invariant modelling
-pricing kernels and risk aversion.
-\url{https://doi.org/10.2139/ssrn.2894289}
-
-\leavevmode\hypertarget{ref-hall_1991}{}%
-Hall, P. (1991). Edgeworth expansions for nonparametric density
-estimators, with applications. \emph{Statistics}, \emph{22}(2),
-215--232. \url{https://doi.org/10.1080/02331889108802305}
-
-\leavevmode\hypertarget{ref-hayes}{}%
-Hayes, A. S. (2019). Bitcoin price and its marginal cost of production:
-Support for a fundamental value. \emph{Applied Economics Letters},
-\emph{26}(7), 554--560.
-\url{https://doi.org/10.1080/13504851.2018.1488040}
-
-\leavevmode\hypertarget{ref-w2yo}{}%
-Härdle, W. K., Okhrin, Y., \& Wang, W. (2014). Uniform Confidence Bands
-for Pricing Kernels. \emph{Journal of Financial Econometrics},
-\emph{13}(2), 376--413. \url{https://doi.org/10.1093/jjfinec/nbu002}
-
-\leavevmode\hypertarget{ref-pricing_cryptocurrency_options}{}%
-Hou, A. J., Wang, W., Chen, C. Y. H., \& Härdle, W. K. (2020). Pricing
-Cryptocurrency Options*. \emph{Journal of Financial Econometrics},
-\emph{18}(2), 250--279. \url{https://doi.org/10.1093/jjfinec/nbaa006}
-
-\leavevmode\hypertarget{ref-xfg_spd}{}%
-Huynh, K., Kervella, P., \& Zheng, J. (2002). \emph{Estimating
-state-price densities with nonparametric regression} (SFB 373 Discussion
-Papers No. 2002,40). Humboldt University of Berlin, Interdisciplinary
-Research Project 373: Quantification; Simulation of Economic Processes.
-\url{https://EconPapers.repec.org/RePEc:zbw:sfb373:200240}
-
-\leavevmode\hypertarget{ref-pumpndump}{}%
-La Morgia, M., Mei, A., Sassi, F., \& Stefa, J. (2020). Pump and dumps
-in the bitcoin era: Real time detection of cryptocurrency market
-manipulations. In \emph{2020 29th international conference on computer
-communications and networks (icccn)} (pp. 1--9).
-\url{https://doi.org/10.1109/ICCCN49398.2020.9209660}
-
-\leavevmode\hypertarget{ref-vola_stylized_facts}{}%
-Masset, P. (2011). Volatility stylized facts. \emph{SSRN Electronic
-Journal}. \url{https://doi.org/10.2139/ssrn.1804070}
-
-\leavevmode\hypertarget{ref-satoshi2009}{}%
-Nakamoto, S. (2009). Bitcoin: A peer-to-peer electronic cash system.
-\url{http://www.bitcoin.org/bitcoin.pdf}
-
-\leavevmode\hypertarget{ref-fundamental-theorem-of-asset-pricing}{}%
-Pascucci, A., \& Agliardi, R. (2011). PDE and martingale methods in
-option pricing. In (pp. 429--495).
-
-\leavevmode\hypertarget{ref-rodgers2019}{}%
-Rodgers, T. (2019, April 4). 95 percent of volume could be wash trading
-as bitcoin price surges.
-\url{https://www.forbes.com/sites/tomrodgers1/2019/04/04/99-of-volume-could-be-wash-trading-as-bitcoin-takes-back-5000/?sh=4640bcbc23d5}.
-Accessed 15 April 2023
-
-\leavevmode\hypertarget{ref-Rookley97}{}%
-Rookley, C. (1997). Fully exploiting the information content of intra
-day option quotes: Applications in option pricing and risk management.
-
-\leavevmode\hypertarget{ref-sar2017}{}%
-Sar, M. (2017). Dodd-frank and the spoofing prohibition in commodities
-markets.
-
-\leavevmode\hypertarget{ref-deriv_volume}{}%
-Skew.com. (2022). Open interest for bitcoin options over time. Skew is a
-leading crypto data analytics platform for institutional clients.
-\url{https://analytics.skew.com/dashboard/bitcoin-options}. Accessed 25
-July 2022
-
-\leavevmode\hypertarget{ref-brazilian_speculation}{}%
-Smaniotto, E. N., \& Neto, G. B. (2022). Speculative trading in bitcoin:
-A brazilian market evidence. \emph{The Quarterly Review of Economics and
-Finance}, \emph{85}, 47--54.
-\url{https://doi.org/https://doi.org/10.1016/j.qref.2020.10.024}
-
-\leavevmode\hypertarget{ref-cross_border_stellar}{}%
-Stellar Development Foundation. (2022). 2022 research reveals high
-awareness and growing cross-border use of cryptocurrency in four key
-markets.
-\url{https://www.prnewswire.com/news-releases/2022-research-reveals-high-awareness-and-growing-cross-border-use-of-cryptocurrency-in-four-key-markets-301512401.html}.
-Accessed 22 July 2022
-
-\leavevmode\hypertarget{ref-nickszabo}{}%
-Szabo, N. (2008). Bit gold.
-\url{https://unenumerated.blogspot.com/2005/12/bit-gold.html}. Accessed
-28 July 2022
-
-\leavevmode\hypertarget{ref-tuccella2021}{}%
-Tuccella, J.-N., Nadler, P., \& Șerban, O. (2021). Protecting retail
-investors from order book spoofing using a gru-based detection model.
-
 \end{document}

### 2024-02-17 plot_funding_rates.py
table for annual funding rates

@@ -1,0 +1,59 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.dates as mdates
+import pdb
+
+def plot_funding(funding, xvar, yvar1, yvar2, label1, label2, fname, ylim):
+    """
+
+    """
+    fig = plt.figure(figsize = (12,8))        
+    #plt.gca().xaxis.set_major_formatter(mdates.DateFormatter('%d/%m/%Y'))
+    #plt.gca().xaxis.set_major_locator(mdates.DayLocator())
+    #plt.gcf().autofmt_xdate()
+    plt.plot(funding[xvar], funding[yvar1], label = label1, color = 'blue') # blue #1fzzb4
+    plt.plot(funding[xvar], funding[yvar2], label = label2, color = 'orange') # #ff7f02
+    #plt.legend()
+    if ylim:
+        plt.ylim(ylim)
+    plt.savefig(fname, transparent = True)
+
+def annual_interest(full_day_funding_rate):
+    """
+    funding: pd.DataFrame
+    The rate is already a daily average, so 24h instead of 8h based
+    """
+    interest_path =  np.cumprod(1 + full_day_funding_rate) - 1
+    return interest_path.iloc[-1]
+
+
+funding = pd.read_csv('funding.csv')
+funding['date'] = pd.to_datetime(funding['date'])
+
+
+
+# Start of Funding Rates in the data. 
+funding = funding.loc[funding['date'] >= '2019-05-01']
+
+# Create a table that summarizes the annual funding rates
+# Since the perpetual future data exists from the start date in 2019, 
+# 2019 only offers the returns for half a year! So we have to adjust for a full year
+funding['year'] = funding['date'].apply(lambda x: x.year)
+btc_funding_rate_per_year = funding.groupby('year').apply(lambda x: annual_interest(x['funding_btc']))
+eth_funding_rate_per_year = funding.groupby('year').apply(lambda x: annual_interest(x['funding_eth']))
+df_funding_rate_per_year = pd.DataFrame({'btc': btc_funding_rate_per_year, 'eth': eth_funding_rate_per_year})
+
+annualization_factor = 12/4
[…]

### 2024-02-18 written/paper.tex
tables

@@
 Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments.
+As depicted in Table \ref{table:stats}, measured by the aggregate open interest and aggregate trading volume the market share of Perpetual Futures dwarfs the market share of (classic) Futures for both, Bitcoin and Ether.
 While it would be possible to use a yield from a long-short futures position (e.g.
@@
 
-Solve for interest rates from Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:
+Solve for interest rates from (classic) Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:
 
@@
 The actual annualized returns of such a carry trade are summarized in the table below.
-
-Table:
-
-Year, Currency, Exchange, Annual Return
-
-funding_btc_vs_eth_annualized_zoom.png
-funding_btc_vs_eth_zoom.png
-funding_btc_vs_eth_annualized.png
-funding_btc_vs_eth.png
-
-As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
-Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
-
-BTC Futures
-
-Total Open Interest $1,405,918,350
-Total 24h Trade Volume $324,820,482
-
-ETH Futures
-Total Open Interest $466,932,584
-Total 24h Trade Volume $98,238,298
-
-Source for liquidity: 
-https://www.coingecko.com/en/derivatives
-https://www.coingecko.com/en/derivatives/futures
+2019 returns are annualized due to the start on 1st of May 2019 of perpetual futures on Deribit.
+
+%Table: btc/out/funding_rate_per_year.csv
+\begin{table}[ht]
+\centering
+{\begin{tabular}{lll}
+\hline
+\textbf{Year} & \textbf{BTC} & \textbf{ETH} \\
+\hline
+\hline
+2019 &  0.337660 &  0.211480                    \\
+2020 &  0.092658 &  0.060110                    \\
+2022 & -0.022659 & -0.059537                   \\
+2023 &  0.057251 &  0.065914            
+\end{tabular}}
+\caption{Annual Interest Rate as implied through the Funding Rate of Perpetual Futures}
+\label{table:annual_interest_rates}
+\end{table}
+
+%
+%As of 2024-01-07, the total Open Interest for Bitcoin Perpetual Futures contracts is \$19,343,021,437 with a total 24h Trade Volume of \$50,339,886,015.
+%Open Interest for Ether Perpetual Futures contracts is Total Open Interest \$14,945,055,482 and total 24h Trade Volume is \$18,097,004,167.
+%
+%BTC Futures
+%
+%Total Open Interest $1,405,918,350
+%Total 24h Trade Volume $324,820,482
+%
+%ETH Futures
+%Total Open Interest $466,932,584
+%Total 24h Trade Volume $98,238,298
+%
+%As of 2024-01-07
+%
+%Bitcoin Perpetuals with 
+%Total Open Interest \$19,343,021,437
+%Total 24h Trade Volume \$50,339,886,015
+%
+%
+%
+%Ether Perpetuals 
+%
+%Total Open Interest \$14,945,055,482
+%Total 24h Trade Volume \$18,097,004,167
+%
+%
+%
+%BTC Futures
+%
+%with 
+%
+%Total Open Interest $1,405,918,350
+%Total 24h Trade Volume $324,820,482
+%
+%
+%
+%ETH Futures
+%
+%with 
+%Total Open Interest $466,932,584
+%Total 24h Trade Volume $98,238,298
+%
+%
+%
+%
+%Source for liquidity: 
+%https://www.coingecko.com/en/derivatives
+%https://www.coingecko.com/en/derivatives/futures
 
@@
 
-As of 2024-01-07
-
-Bitcoin Perpetuals with 
-Total Open Interest \$19,343,021,437
-Total 24h Trade Volume \$50,339,886,015
-
-Ether Perpetuals
-
-Total Open Interest \$14,945,055,482
-Total 24h Trade Volume \$18,097,004,167
-
 % Please add the following required packages to your document preamble:
@@
 % \usepackage{booktabs}
-
-BTC Futures
-
-with
-
-Total Open Interest $1,405,918,350
-Total 24h Trade Volume $324,820,482
-
-ETH Futures
-
-with 
-Total Open Interest $466,932,584
-Total 24h Trade Volume $98,238,298
 
@@
 
-\begin{table}[]
+\begin{table}[ht]
+\centering
 \begin{tabular}{lll}
+\hline
 \textbf{Instrument}            & \textbf{Aggregate Open Interest (USD)} & \textbf{24 Hour Aggregate Trade Volume (USD)} \\
+\hline
+\hline
 BTC Perpetual Futures & 19,343,021,437                & 50,339,886,015                       \\
@@
 \end{tabular}
-\caption{Relevance of Perpetual Futures to Futures as measured by Open Interest and Trading Volume}
+\caption{Relevance of Perpetual Futures to Futures as measured by Open Interest and Trading Volume as of 2024-01-07. Source: Coingecko.}
 \label{table:stats}
@@
 \end{tabular}}
-\caption{Bitcoin Perpetual Futures}
+\caption{Bitcoin Perpetual Futures. Source: Coingecko.}
 \label{table:btc_perpetuals}
@@
 \end{tabular}}
-\caption{Ether Perpetual Futures}
+\caption{Ether Perpetual Futures. Source: Coingecko.}
 \label{eth_perpetual_futures}
@@
 \end{tabular}}
-\caption{BTC Futures}
+\caption{BTC Futures. Source: Coingecko.}
 \label{table:btc_futures}
@@
 \end{tabular}}
-\caption{ETH Futures}
+\caption{ETH Futures. Source: Coingecko.}
 \label{table:eth_futures}
@@
 \end{tabular}}
-\caption{t-Statistics of beta-neutral BTC Option portfolios}
+\caption{t-Statistics of beta-neutral BTC Option portfolios. }
 \label{table:btc_t_stats}

### 2024-02-18 compare.py
compare.py adjusted for eth, btc pair

@@ -11,32 +11,32 @@ from scipy import stats
 from scipy.stats import ttest_1samp
 from pathlib import Path
 
-def ttest(dat, out_path):
+def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     """
     Groups returns by levels of moneyness (in steps of 0.05)
     performs kernel density estimation
     performs a left-sided t-test on a population mean of 0
     """
-
     Path(out_path).mkdir(parents=True, exist_ok=True)
     pdct = {}
     df = dat.copy(deep = True)
     for mn in df['moneyness'].sort_values().unique():
+        if mn >= min_moneyness and mn <= max_moneyness:
 
-        fig = plt.figure(figsize = (20, 14))
-        higher = round(mn + 0.05, 2)
-        sub = df.loc[(df['moneyness'] <= higher) & (df['moneyness'] >= mn)]
-        sub['combined_ret_daily'].plot.kde()
-        plt.title('n = ' + str(sub.shape[0]))
-        plt.xlim((-1, 1))
-        plt.savefig(out_path + '/moneyness>=' + str(mn) + '&moneyness<=' + str(higher) + '.png')
-        t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
-        print(sub.describe())
-        print('Moneyness Level: ', mn)
-        print("T-statistic value: ", t_stat)
-        print("P-Value: ", p_value)
-        pdct[mn] = p_value
-        #time.sleep(3)
+            fig = plt.figure(figsize = (20, 14))
+            higher = round(mn + 0.05, 2)
+            sub = df.loc[(df['moneyness'] <= higher) & (df['moneyness'] >= mn)]
+            sub['combined_ret_daily'].plot.kde()
+            plt.title('n = ' + str(sub.shape[0]))
+            plt.xlim((-1, 1))
+            plt.savefig(out_path + '/moneyness>=' + str(mn) + '&moneyness<=' + str(higher) + '.png')
+            t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
+            print(sub.describe())
[…]

### 2024-02-18 written/paper.tex
eth t statistics table
writing results

@@
   \href{mailto:haerdle@hu-berlin.de}{\nolinkurl{haerdle@hu-berlin.de}}}}
-\date{12 February 2024}
+\date{18 February 2024}
 
@@
 
+% Futures Plot
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized.png}
+    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized_zoom.png}
+
+     \captionof{figure}{(Zoomed) Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+
+\end{minipage}
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth.png}
+    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_zoom.png}
+    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+
+\end{minipage}
+   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
+
+\label{ATM Term Structure}
+\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+
+\pagebreak
+\newpage
+
 %
@@
 All option greeks remain constant except time-to-maturity.
-Any transaction has a time-to-maturity (tau) "reset"/synced to settlement time.
+Any transaction has a time-to-maturity $\tau$ adjusted so that it would coincide with settlement time.
 All options are bought and held until settlement at 10am UTC.
@@
 We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
-For each level of moneyness m, we construct an interval $[m, m + 0.05]$.
-We condition daily returns on over levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
+For each level of moneyness $m$, we construct an interval $[m, m + 0.05]$.
+We condition daily returns on levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
 We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
@@
 Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
-Close Call (Put) leg 20\% away from Strike. We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility (which is more than empirically justified.)
-Maybe make a summary of the relationship between ATM and 20\% OTM premium.
+Close Call (Put) leg 20\% away from Strike.
+We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility.
+This premium more than empirically justified, but we choose the size due to the possibility of illiquidity for OTM contracts and the intention to enter both legs of the straddle simultaneously.
+%Maybe make a summary of the relationship between ATM and 20\% OTM premium.
 
@@
 Clearly, application of the fees constitutes simply a linear shift, which is well-visible in the graphs.
-The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval [0.7, 1.3]. 
+The return of the straddles until settlement is re-scaled on a daily level. It is plotted as a boxplot of daily returns for each level of moneyness in the interval $[0.7, 1.3]$. 
 Fees are standard option fees on Deribit. We assume using an option combo fee, which makes the a spread's cheaper leg free of charge. 
@@
 We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
-The exchange started operations in July 2017. 
-Furthermore, we use Deribits API V2 to retrieve a complete set of funding rates for the perpetual future of Bitcoin and Ether since (approx.) July 2019.
-
-Two conditions are imposed on the option data:
-1) The maximum IV is 2.5 and the minimum IV is 0.1.
-2) In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
-3) Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
-4) We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
-
-The purpose of the first restriction is to impose a fair bound to the options that is independent of liquidity levels.
+In addition to the option data set, we are provided with a complete set of funding rates for the perpetual future of Bitcoin and Ether since 1 June 2019.
+
+We impose the following restrictions on the option data:
+\begin{itemize}
+\item In case of multiple occurrences of an instrument per day, we exclusively use the first one. 
+\item The maximum IV is 2.5 and the minimum IV is 0.1.
+\item Furthermore, we restrict our analysis to the interval of Moneyness in [0.7, 1.3]
+\item We use data exlusively past 2019-05-01, the date of first observations for the Bitcoin Perpetual Future
+\end{itemize}
+
+The purpose of the first restriction on uniqueness of observations, is to prevent a bias due to the possible more frequent trading of certain options.
+Generally, we observe that instruments with short maturity are traded more frequently.
+Yet, this could also be understood as cheaper instruments trading more frequently due to the montonous relationship between (Black-Scholes) option prices and time-to-maturity.
+The purpose the second restriction and third restriction is to impose a fair bound to the options that is independent of liquidity levels.
 For illiquid options, occurrences of bid prices at 0\% IV and ask prices of 500\% may occur.
-The purpose the second restriction of unique usage is to prevent a bias due to the possible more frequent trading of certain options.
-Generally, we observe that instruments with short maturity are traded more frequently.
-Yet, this could also be understood as cheaper instruments trading more frequently since (Black-Scholes) option prices increase with time-to-maturity.
-
-Bitcoin only:
-We drop 0.9\% of observations due to restriction 1)
-We drop 17\% of observations due to restriction 3)
-Overall, we have 5,028,945 observations. Post filtering, 4,150,778 observations remain in the set.
-
-Ethereum: 
-Amount of Observations outside of allowed IV range:  0.017042133327261764
-Amount of Observations outside of allowed Tau range:  0.20172172747210984
-Overall Observations: 2283869
-Amount of Observations in our set post filtering:  1809762
-
-Regarding data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
-Indeed, using actual transaction data instead of orderbook data removes the threat of wash trading (etc) to our data.
+Therefore, we exclude these "unfair" prices.
+
+Regarding the Bitcoin (Ether) data, we drop 0.9\% (1.7\%) of observations due to the IV restriction
+We drop 17\% (20.1\%) of observations due to the moneyness restriction
+Overall, we have 5,028,945 (2,283,869) observations. Post filtering, 4,150,778 (1,809,762) observations remain in the set.
+
+Considering data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
 The most likely negative factor that could affect our data quality is wash trading. 
-We assess the risk of wash trading as follows:
-
-"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." (from: https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf)
-
-We asses the risk of wash trading contaminating our data set as low.
+We follow the definition of XPYZ on wash trading (from: ):
+"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." ()
+
+We asses the overall risk of wash trading contaminating our data set as low.
 The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
-At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot 12 USD.
-Such fees, even without consideration of spreads, make wash trading from a trader's perspective entirely infeasible.
-
-- table of amount of transactions per group
-- plot: amount of transactions over time per group (crypto)
+At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot of 51,765 USD results in a fee of 15.5 USD.
+Such fees, even without consideration of spreads, make wash trading from a trader's perspective prohibitively expensive.
 
@@
 We find the returns of the zero-beta-straddles to be t-distributed and conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
-The null hypothesis is not rejected for all models, vanilla and crash-resistant, for ITM and OTM options.
-Conversely, the null hypothesis is firmly rejected on a high significance level for ATM options.
-Therefore, we accept the alternative hypothesis of an underperformance for ATM options.
-Consequently, we find a similar result to Shumway and Bakshi - that is the existence of a premium for ATM contracts.
-We figure the premium to be a volatility premium since a straddle's payoff depends on the relationship of Implied Volatility to Realized Volatility. 
-Unsurprisingly, the size of the premium in crypto markets is higher than the counterpart in equity markets - we figure that the reason is the higher risk in crypto markets, particularly via volatility and counterparty risk.
-Furthermore, there are mostly retailers present in the crypto option market.
+The null hypothesis is rejected on a high significance level for ATM and slightly ITM options. 
+In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level.
+The results hold across model variations, vanilla and crash resistant, with or without fees.
+
+Consequently, we find a similar result to Shumway and Bakshi, namely is the existence of a premium for ATM contracts. Additionally, we find a similar premium for slightly ITM contracts.
+Shumway et. al reported an average return of around -3.15 percent per week, whereas XYZ \% is attributable to the volatility premium.
+
+We report an average daily return of the zero-beta straddles of -1.0302\% for the vanilla Bitcoin model and -1.0322\% for the crash resistant model. 
+The vanilla Ether model has a daily return of -0.5078\% and the crash resistant model delivers -0.5098\%. 
+All results consider transaction cost as described.
+
+We define at-the-money options as those options whose moneyness falls into the interval $[0.95, 1.05]$.
+For the ATM options, we report an average daily return of the zero-beta straddles of -2.3576\% for the vanilla Bitcoin model and -2.3584\% for the crash resistant model. 
+The vanilla Ether model has a daily return of -0.9554\% and the crash resistant model delivers -0.9610\%.
+
+%We figure the premium to be a volatility premium since a straddle's payoff depends on the relationship of Implied Volatility to Realized Volatility. 
+Unsurprisingly, the size of the premium in crypto markets is higher than the counterpart in equity markets.
+We figure that the reason is the higher risk in crypto markets, particularly via volatility and counterparty risk.
+We suspect liquidity and risk averseness of liquidity providers to play a key role. 
+%Furthermore, there are mostly retailers present in the crypto option market.
 Some professional liquidity providers exist, but they remain few and therefore another reason for the premium's size could be illiquidity.
-
-- the premium is larger when tau is small.
-
-- report average returns for options grouped per strike (and overall)
+% - mention KDE and conclusion that we have a t-distribution.
+
+%Fee & ETH:
+%Crash Resistant:  -0.005098
+%Vanilla: -0.005078
+%
+%Fee & BTC:
+%Crash Resistant: -0.010322
+%Vanilla: -0.010302
+
+%NOW DO ATM-Straddles!
+%Bitcoin Vanilla: -0.023576
+%Crash Resistant;  -0.023584
+%
+%ETH: 
+%vanilla: -0.009554
+%crash resistant: -0.009610
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized.png}
-    \captionof{figure}{Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_annualized_zoom.png}
-
-     \captionof{figure}{(Zoomed) Annualized Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Performance - Vanilla - Fees}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth.png}
-    \captionof{figure}{Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/funding_btc_vs_eth_zoom.png}
-    \captionof{figure}{(Zoomed) Funding Rate \color{blue}{BTC} vs. \color{orange}{ETH}}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}
 
@@
 
-\pagebreak
-\newpage
-
 \begin{minipage}{\textwidth}
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{BTC - Performance - Vanilla - Fees}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Performance - Vanilla - Fees}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
 
@@
 
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{ETH - Performance - Vanilla - Fees}
-
-\end{minipage}
-\begin{minipage}{\textwidth}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
-
-\end{minipage}
-   % \captionof{figure}{ATM Term Structure from 2022-01-01 until 2022-01-08. Moneyness $M \in [0.9, 1.1]$}
-
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
-
-We conduct a left-sided t-test to test for a population mean of zero. Values are rounded to 4 digits.
-
-Compare to weekly 0.5\% loss observed in equity options.
-
 \section{Conclusion}
@@
 - Evidence for leverage effect
+
+Make bridge to interest rates
 
@@
 \section{References}
+
+% New
+\leavevmode\hypertarget{ref-washtrading}{}%
+Intercontinental Exchange, Inc. Wash Trade FAQ
+\url{https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf}. Accessed
+18 February 2023.
+
+% Old
 
@@
 
+\begin{table}[ht]
+\hline
+\resizebox{\textwidth}{!}{\begin{tabular}{lrrrr}
+  \textbf{Moneyness}   & \multicolumn{1}{l}{\textbf{Vanilla ex Fee}}  & \multicolumn{1}{l}{\textbf{Vanilla cum Fee}} & \multicolumn{1}{l}{\textbf{Crash Resistant ex Fee}}&\multicolumn{1}{l}{\textbf{Crash Resistant cum Fee}} \\
+     \hline
+     \hline
+0.7  & 0.9989         & 0.9984          & 0.9985                 & 0.9989                  \\
+0.71 & 0.9552         & 0.9442          & 0.9444                 & 0.9554                  \\
+0.72 & 0.9957         & 0.9938          & 0.9938                 & 0.9957                  \\
+0.73 & 0.9928         & 0.9895          & 0.9896                 & 0.9928                  \\
+0.74 & 0.9999         & 0.9999          & 0.9999                 & 0.9999                  \\
+0.75 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.76 & 0.9999         & 0.9998          & 0.9998                 & 0.9999                  \\
+0.77 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.78 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.79 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.8  & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.81 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.82 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.83 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.84 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.85 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.86 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.87 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.88 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.89 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.9  & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.91 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.92 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.93 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.94 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.95 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+0.96 & 1.0            & 0.9953          & 0.9953                 & 1.0                     \\
+0.97 & 0.9253         & 0.5154          & 0.5152                 & 0.9252                  \\
+0.98 & 0.1714         & 0.0099          & 0.0098                 & 0.1713                  \\
+0.99 & 0.0106         & 0.0001          & 0.0001                 & 0.0106                  \\
+1.0  & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.01 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.02 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.03 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.04 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.05 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.06 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.07 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.08 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.09 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.1  & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.11 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.12 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.13 & 0.0            & 0.0             & 0.0                    & 0.0                     \\
+1.14 & 0.0001         & 0.0001          & 0.0001                 & 0.0001                  \\
+1.15 & 0.0006         & 0.0003          & 0.0003                 & 0.0005                  \\
+1.16 & 0.0025         & 0.0013          & 0.0013                 & 0.0025                  \\
+1.17 & 0.0304         & 0.0203          & 0.0201                 & 0.0302                  \\
+1.18 & 0.276            & 0.2243          & 0.2231                 & 0.2746                  \\
+1.19 & 0.0465         & 0.0345          & 0.0341                 & 0.0459                  \\
+1.2  & 0.0662         & 52              & 0.0513                 & 0.0653                  \\
+1.21 & 0.1876         & 0.1587          & 156                    & 0.1845                  \\
+1.22 & 0.5361         & 0.4981          & 0.4945                 & 0.5324                  \\
+1.23 & 0.5376         & 0.5007          & 0.4964                 & 0.5332                  \\
+1.24 & 0.9978         & 0.9969          & 0.9967                 & 0.9977                  \\
+1.25 & 0.9999         & 0.9998          & 0.9998                 & 0.9999                  \\
+1.26 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+1.27 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+1.28 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+1.29 & 1.0            & 1.0             & 1.0                    & 1.0                     \\
+1.3  & 1.0            & 1.0             & 1.0                    & 1.0                    
+\end{tabular}}
+\caption{t-Statistics of beta-neutral ETH Option portfolios. }
+\label{table:eth_t_stats}
+\end{table}
+
 \end{document}

### 2024-02-18 compare.py
more stats in compare.py

@@ -7,9 +7,43 @@ import matplotlib.pyplot as plt
 import pdb
 import time
 import csv
+import statsmodels.api as sm
+import pylab
 from scipy import stats 
 from scipy.stats import ttest_1samp
 from pathlib import Path
+
+def QQ_plot(data, nn, fname):
+    # Source: https://stackoverflow.com/questions/13865596/quantile-quantile-plot-using-scipy
+    fig = plt.figure(figsize = (10,7))
+
+    # Sort as increasing
+    y = np.sort(data)
+    
+    # Compute sample mean and std
+    mean, std = np.mean(y), np.std(y)
+    
+    # Compute set of Normal quantiles
+    ppf = stats.t(df = nn, loc = mean, scale = std).ppf
+    #ppf = stats.norm(loc=mean, scale=std).ppf # Inverse CDF
+    N = len(y)
+    x = [ppf( i/(N+2) ) for i in range(1,N+1)]
+
+    # Make the QQ scatter plot
+    plt.scatter(x, y)
+    
+    # Plot diagonal line
+    dmin, dmax = np.min([x,y]), np.max([x,y])
+    diag = np.linspace(dmin, dmax, 1000)
+    plt.plot(diag, diag, color='red', linestyle='--')
+    plt.gca().set_aspect('equal')
+    
+    # Add labels
+    plt.xlabel('Normal quantiles')
+    plt.ylabel('Sample quantiles')
+    plt.show()
+    #plt.savefig(fname)
+
 
 def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     """
@@ -20,6 +54,11 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     Path(out_path).mkdir(parents=True, exist_ok=True)
     pdct = {}
     df = dat.copy(deep = True)
+
+    # Make up some dummy data and test
+    #xx = np.random.normal(loc=5.0, scale=0.5, size=1000)
+    #QQ_plot(xx)
+
     for mn in df['moneyness'].sort_values().unique():
         if mn >= min_moneyness and mn <= max_moneyness:
 
@@ -37,6 +76,13 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
             print("P-Value: ", p_value)
             pdct[mn] = p_value
             #time.sleep(3)
+            
[…]

### 2024-02-18 written/paper.tex
citations

@@
 
+\bibliography{research.bib}
 \begin{document}
@@
 \section{Introduction}
-Despite the ongoing integration into established markets (whereas the last example would be the SEC's approval of a range of Bitcoin Spot ETFs), fundamental questions about crypto asset markets remain unclear:
+On 10 January 2024, the United States Securities and Exchange Commission approved the listing and trading of a range of spot bitcoin exchange-traded product (ETP) shares (Gensler, 2024).
+In other markets, structured products in Bitcoin (and other crypto assets) have been available for years and retailers have been able to mine or buy it since its inception following Nakamoto, 2009.
+Yet, despite the ongoing integration into established markets, fundamental questions about crypto asset markets remain unclear:
 How efficient are crypto asset markets relative to established, traditional markets such as equities? 
@@
 We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s.
-The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway and Bakshi et al in (@quote).
+The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway et al.
+(2000) and Kapadia et al.
+(2001).
 
@@
 However, the portfolios do not generate the appropriate theoretical returns for at-the-money instruments.
-We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Bakshi et al and Shumway et al., the existence of high premia.for at-the-money options.
+We compare the risk-return characteristics to the late 90s equity markets and find, in a similar fashion as the results reported by Kapadia et al.
+(2001) and Shumway et al.
+(2000), the existence of high premia.for at-the-money options.
 The effect holds after compensating for tail risk (market crash insurance) and transaction cost.
@@
 
-Consequently, we find a similar result to Shumway and Bakshi, namely is the existence of a premium for ATM contracts. Additionally, we find a similar premium for slightly ITM contracts.
+Consequently, we find a similar result to Shumway et al.
+(2000) and Bakshi et al.
+(2001), namely is the existence of a premium for ATM contracts.
+Additionally, we find a similar premium for slightly ITM contracts.
 Shumway et. al reported an average return of around -3.15 percent per week, whereas XYZ \% is attributable to the volatility premium.
@@
 % New
+\leavevmode\hypertarget{ref-deribit_fees}{}%
+Deribit margin requirements (2022).
+\url{https://www.deribit.com/kb/fees}. Accessed 28 February 2024.
+
+\leavevmode\hypertarget{sec-approval}{}%
+Gary Gensler, Chair of the United States Securities and Exchange Commission. Statement on the Approval of Spot Bitcoin Exchange-Traded Products (10 January 2024).
+Available at \url{https://www.sec.gov/news/statement/gensler-statement-spot-bitcoin-011023}. Accessed 18 February 2023.
+
 \leavevmode\hypertarget{ref-washtrading}{}%
-Intercontinental Exchange, Inc. Wash Trade FAQ
-\url{https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf}. Accessed
-18 February 2023.
-
-% Old
+Intercontinental Exchange, Inc. Wash Trade FAQ.
+\url{https://www.ice.com/publicdocs/futures_us/Wash_Sale_FAQ.pdf}. Accessed 18 February 2023.
 
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-aitsahalia01optionprice}{}%
-Aı̈t-Sahalia, Y., Wang, Y., \& Yared, F. (2001). Do option markets
-correctly price the probabilities of movement of the underlying asset?
-\emph{Journal of Econometrics}, \emph{102}(1), 67--110.
-\url{https://doi.org/https://doi.org/10.1016/S0304-4076(00)00091-9}
-
-\leavevmode\hypertarget{ref-ait_sahalia_wang1998}{}%
-Aït-Sahalia, Y., \& Lo, A. W. (1998). Nonparametric estimation of
-state-price densities implicit in financial asset prices. \emph{The
-Journal of Finance}, \emph{53}(2), 499--547.
-\url{https://doi.org/https://doi.org/10.1111/0022-1082.215228}
-
-\leavevmode\hypertarget{ref-alexander2022net}{}%
-Alexander, C., Deng, J., Feng, J., \& Wan, H. (2022). Net buying
-pressure and the information in bitcoin option trades. \emph{Journal of
-Financial Markets}, 100764.
-
-\leavevmode\hypertarget{ref-inverse_options}{}%
-Alexander, C., \& Imeraj, A. (2021, July). Inverse options in a
-black-scholes world.
-\url{https://doi.org/https://doi.org/10.48550/arXiv.2107.12041}
-
-\leavevmode\hypertarget{ref-aloosh}{}%
-Aloosh, A., \& Li, J. (2019). Direct evidence of bitcoin wash trading.
-\emph{Theory of Probability \& Its Applications, 5, 285-301}.
-\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3362153}
-
-\leavevmode\hypertarget{ref-bitmex}{}%
-Bitmex. (2019). Presentation to the u.s. Securities and exchange
-commission on wash trading.
-\url{https://www.sec.gov/comments/sr-nysearca-2019-01/srnysearca201901-5164833-183434.pdf}.
-Accessed 18 January 2022
-
-\leavevmode\hypertarget{ref-blase}{}%
-Blaskowitz, O., Härdle, W. K., \& Schmidt, P. (2004). Skewness and
-kurtosis trades. In (pp. 1--14).
-\url{https://doi.org/10.1007/978-0-8176-8180-7_1}
-
-\leavevmode\hypertarget{ref-speculation}{}%
-Blau, B. M. (2017). Price dynamics and speculative trading in bitcoin.
-\emph{Research in International Business and Finance}, \emph{41},
-493--499.
-\url{https://doi.org/https://doi.org/10.1016/j.ribaf.2017.05.010}
-
-\leavevmode\hypertarget{ref-bloomberg-retail-share}{}%
-Bloomberg. (2021, November 17). Retail traders slide back below 20\% of
-market's total volume.
-\url{https://www.bloomberg.com/news/articles/2021-11-17/retail-traders-retreat-as-choppy-markets-challenge-easy-profits}.
-Accessed 24 August 2021
-
-\leavevmode\hypertarget{ref-breeden_litzenberger78}{}%
-Breeden, D. T., \& Litzenberger, R. H. (1978). Prices of
-state-contingent claims implicit in option prices. \emph{The Journal of
-Business}, \emph{51}(4), 621--651.
-\url{http://www.jstor.org/stable/2352653}
-
-\leavevmode\hypertarget{ref-coins_with_benefits}{}%
-Chen, C. Y., \& Vinogradov, D. (2021). Coins with benefits: On
-existence, pricing kernel and risk premium of cryptocurrencies.
-\emph{Available at SSRN 3959984}.
-\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3864578}
-
-\leavevmode\hypertarget{ref-choi}{}%
-Choi, S., \& Shin, J. (2022). Bitcoin: An inflation hedge but not a safe
-haven. \emph{Finance Research Letters}, \emph{46}, 102379.
-\url{https://doi.org/https://doi.org/10.1016/j.frl.2021.102379}
-
-\leavevmode\hypertarget{ref-oil_spd}{}%
-Christoffersen, P., Jacobs, K., \& Pan, X. (. (2021). The State Price
-Density Implied by Crude Oil Futures and Option Prices. \emph{The Review
-of Financial Studies}, \emph{35}(2), 1064--1103.
-\url{https://doi.org/10.1093/rfs/hhab011}
-
-\leavevmode\hypertarget{ref-cryptonews_bitcoin_retail_share}{}%
-Coinbase, S., Cryptonews. (2022). Institutions \& retail compete for
-bitcoin - whose hands are stronger?
-\url{https://cryptonews.com/exclusives/institutions-retail-compete-for-bitcoin-which-is-the-biggest-9695.htm}.
-Accessed 22 March 2022
-
-\leavevmode\hypertarget{ref-decentralized_wash_trading}{}%
-Cong, L., Li, X., Tang, K., \& Yang, Y. (2019). Crypto wash trading.
-\emph{SSRN Electronic Journal}.
-\url{https://doi.org/10.2139/ssrn.3530220}
-
-\leavevmode\hypertarget{ref-jackwerth_pk}{}%
-Cuesdeanu, H., \& Jackwerth, J. C. (2018). The pricing kernel puzzle:
-survey and outlook. \emph{Annals of Finance}, \emph{14}(3), 289--329.
-\url{https://doi.org/10.1007/s10436-017-0317-9}
-
-\leavevmode\hypertarget{ref-cross_border_payments}{}%
-Deng, Q. (2020). Application analysis on blockchain technology in
-cross-border payment. In.
-\url{https://doi.org/10.2991/aebmr.k.200306.050}
-
-\leavevmode\hypertarget{ref-deribit-insurance-fund}{}%
-Deribit. (2020a). Deribit insurance fund.
-\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021
-
-\leavevmode\hypertarget{ref-synthetic-btc-index}{}%
-Deribit. (2020b). Deribit btc-usd index.
-\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021
-
-\leavevmode\hypertarget{ref-market-maker-obligations}{}%
-Deribit. (2020c). Deribit market maker obligations.
-\url{https://www.deribit.com/pages/docs/options}. Accessed 2 January
-2021
-
-\leavevmode\hypertarget{ref-deribit_retail_piechart}{}%
-Deribit. (2022a). Deribit volume share.
-\url{https://www.deribit.com/statistics/BTC/market-data}. Accessed 25
-July 2022
-
-\leavevmode\hypertarget{ref-deribit_margin}{}%
-Deribit. (2022b). Deribit margin requirements.
-\url{https://legacy.deribit.com/pages/docs/options}. Accessed 2 May 2022
-
-\leavevmode\hypertarget{ref-deribit_fees}{}%
-Deribit. (2022c). Deribit margin requirements.
-\url{https://www.deribit.com/kb/fees}. Accessed 2 May 2022
-
-\leavevmode\hypertarget{ref-deribit-rate-limit}{}%
-Deribit. (2023). Deribit rate limits.
-\url{https://www.deribit.com/kb/deribit-rate-limits}. Accessed 16 April
-2021
-
-\leavevmode\hypertarget{ref-vola_premium}{}%
-Eraker, B. (2021). The volatility premium. \emph{Quarterly Journal of
-Finance (QJF)}, \emph{11}(03), 1--35.
-\url{https://EconPapers.repec.org/RePEc:wsi:qjfxxx:v:11:y:2021:i:03:n:s2010139221500142}
-
-\leavevmode\hypertarget{ref-networkeffect}{}%
-Gandal, N., \& Halaburda, H. (2016). Can we predict the winner in a
-market with network effects? Competition in cryptocurrency market.
-\emph{Games}, \emph{7}(3). \url{https://doi.org/10.3390/g7030016}
-
-\leavevmode\hypertarget{ref-Grith09sim}{}%
-Grith, M., Härdle, W. K., \& Park, J. (2009). Shape invariant modelling
-pricing kernels and risk aversion.
-\url{https://doi.org/10.2139/ssrn.2894289}
-
-\leavevmode\hypertarget{ref-hall_1991}{}%
-Hall, P. (1991). Edgeworth expansions for nonparametric density
-estimators, with applications. \emph{Statistics}, \emph{22}(2),
-215--232. \url{https://doi.org/10.1080/02331889108802305}
-
-\leavevmode\hypertarget{ref-hayes}{}%
-Hayes, A. S. (2019). Bitcoin price and its marginal cost of production:
-Support for a fundamental value. \emph{Applied Economics Letters},
-\emph{26}(7), 554--560.
-\url{https://doi.org/10.1080/13504851.2018.1488040}
-
-\leavevmode\hypertarget{ref-w2yo}{}%
-Härdle, W. K., Okhrin, Y., \& Wang, W. (2014). Uniform Confidence Bands
-for Pricing Kernels. \emph{Journal of Financial Econometrics},
-\emph{13}(2), 376--413. \url{https://doi.org/10.1093/jjfinec/nbu002}
-
-\leavevmode\hypertarget{ref-pricing_cryptocurrency_options}{}%
-Hou, A. J., Wang, W., Chen, C. Y. H., \& Härdle, W. K. (2020). Pricing
-Cryptocurrency Options*. \emph{Journal of Financial Econometrics},
-\emph{18}(2), 250--279. \url{https://doi.org/10.1093/jjfinec/nbaa006}
-
-\leavevmode\hypertarget{ref-xfg_spd}{}%
-Huynh, K., Kervella, P., \& Zheng, J. (2002). \emph{Estimating
-state-price densities with nonparametric regression} (SFB 373 Discussion
-Papers No. 2002,40). Humboldt University of Berlin, Interdisciplinary
-Research Project 373: Quantification; Simulation of Economic Processes.
-\url{https://EconPapers.repec.org/RePEc:zbw:sfb373:200240}
-
-\leavevmode\hypertarget{ref-pumpndump}{}%
-La Morgia, M., Mei, A., Sassi, F., \& Stefa, J. (2020). Pump and dumps
-in the bitcoin era: Real time detection of cryptocurrency market
-manipulations. In \emph{2020 29th international conference on computer
-communications and networks (icccn)} (pp. 1--9).
-\url{https://doi.org/10.1109/ICCCN49398.2020.9209660}
-
-\leavevmode\hypertarget{ref-vola_stylized_facts}{}%
-Masset, P. (2011). Volatility stylized facts. \emph{SSRN Electronic
-Journal}. \url{https://doi.org/10.2139/ssrn.1804070}
+\leavevmode\hypertarget{bakshi}{}%
+Kapadia, Nikunj and Bakshi, Gurdip S.
+and Bakshi, Gurdip S., Delta-Hedged Gains and the Negative Market Volatility Risk Premium (April 9, 2001).
+Available at SSRN: \url{https://ssrn.com/abstract=267106} or \url{http://dx.doi.org/10.2139/ssrn.267106}.
 
@@
 
-\leavevmode\hypertarget{ref-fundamental-theorem-of-asset-pricing}{}%
-Pascucci, A., \& Agliardi, R. (2011). PDE and martingale methods in
-option pricing. In (pp. 429--495).
-
-\leavevmode\hypertarget{ref-rodgers2019}{}%
-Rodgers, T. (2019, April 4). 95 percent of volume could be wash trading
-as bitcoin price surges.
-\url{https://www.forbes.com/sites/tomrodgers1/2019/04/04/99-of-volume-could-be-wash-trading-as-bitcoin-takes-back-5000/?sh=4640bcbc23d5}.
-Accessed 15 April 2023
-
-\leavevmode\hypertarget{ref-Rookley97}{}%
-Rookley, C. (1997). Fully exploiting the information content of intra
-day option quotes: Applications in option pricing and risk management.
-
-\leavevmode\hypertarget{ref-sar2017}{}%
-Sar, M. (2017). Dodd-frank and the spoofing prohibition in commodities
-markets.
-
-\leavevmode\hypertarget{ref-deriv_volume}{}%
-Skew.com. (2022). Open interest for bitcoin options over time. Skew is a
-leading crypto data analytics platform for institutional clients.
-\url{https://analytics.skew.com/dashboard/bitcoin-options}. Accessed 25
-July 2022
-
-\leavevmode\hypertarget{ref-brazilian_speculation}{}%
-Smaniotto, E. N., \& Neto, G. B. (2022). Speculative trading in bitcoin:
-A brazilian market evidence. \emph{The Quarterly Review of Economics and
-Finance}, \emph{85}, 47--54.
-\url{https://doi.org/https://doi.org/10.1016/j.qref.2020.10.024}
-
-\leavevmode\hypertarget{ref-cross_border_stellar}{}%
-Stellar Development Foundation. (2022). 2022 research reveals high
-awareness and growing cross-border use of cryptocurrency in four key
-markets.
-\url{https://www.prnewswire.com/news-releases/2022-research-reveals-high-awareness-and-growing-cross-border-use-of-cryptocurrency-in-four-key-markets-301512401.html}.
-Accessed 22 July 2022
-
-\leavevmode\hypertarget{ref-nickszabo}{}%
-Szabo, N. (2008). Bit gold.
-\url{https://unenumerated.blogspot.com/2005/12/bit-gold.html}. Accessed
-28 July 2022
-
-\leavevmode\hypertarget{ref-tuccella2021}{}%
-Tuccella, J.-N., Nadler, P., \& Șerban, O. (2021). Protecting retail
-investors from order book spoofing using a gru-based detection model.
+\hypertarget{refs}{}
+\leavevmode\hypertarget{shumway}{}%
+Shumway, Tyler and Coval, Joshua D., Expected Option Returns (June 2000). Available at SSRN: \url{https://ssrn.com/abstract=189840} or \url{http://dx.doi.org/10.2139/ssrn.189840}.
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{winkel}{}%
+Winkel, J and Härdle, WK, Pricing Kernels and Risk Premia implied in Bitcoin Options (November 21, 2022).Available at SSRN: \url{https://ssrn.com/abstract=4282905} or \url{http://dx.doi.org/10.2139/ssrn.4282905}.
+
+%
+%
+%% Old
+%
+%\hypertarget{refs}{}
+%\leavevmode\hypertarget{ref-aitsahalia01optionprice}{}%
+%Aı̈t-Sahalia, Y., Wang, Y., \& Yared, F. (2001). Do option markets
+%correctly price the probabilities of movement of the underlying asset?
+%\emph{Journal of Econometrics}, \emph{102}(1), 67--110.
+%\url{https://doi.org/https://doi.org/10.1016/S0304-4076(00)00091-9}
+%
+%\leavevmode\hypertarget{ref-ait_sahalia_wang1998}{}%
+%Aït-Sahalia, Y., \& Lo, A. W. (1998). Nonparametric estimation of
+%state-price densities implicit in financial asset prices. \emph{The
+%Journal of Finance}, \emph{53}(2), 499--547.
+%\url{https://doi.org/https://doi.org/10.1111/0022-1082.215228}
+%
+%\leavevmode\hypertarget{ref-alexander2022net}{}%
+%Alexander, C., Deng, J., Feng, J., \& Wan, H. (2022). Net buying
+%pressure and the information in bitcoin option trades. \emph{Journal of
+%Financial Markets}, 100764.
+%
+%\leavevmode\hypertarget{ref-inverse_options}{}%
+%Alexander, C., \& Imeraj, A. (2021, July). Inverse options in a
+%black-scholes world.
+%\url{https://doi.org/https://doi.org/10.48550/arXiv.2107.12041}
+%
+%\leavevmode\hypertarget{ref-aloosh}{}%
+%Aloosh, A., \& Li, J. (2019). Direct evidence of bitcoin wash trading.
+%\emph{Theory of Probability \& Its Applications, 5, 285-301}.
+%\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3362153}
+%
+%\leavevmode\hypertarget{ref-bitmex}{}%
+%Bitmex. (2019). Presentation to the u.s. Securities and exchange
+%commission on wash trading.
+%\url{https://www.sec.gov/comments/sr-nysearca-2019-01/srnysearca201901-5164833-183434.pdf}.
+%Accessed 18 January 2022
+%
+%\leavevmode\hypertarget{ref-blase}{}%
+%Blaskowitz, O., Härdle, W. K., \& Schmidt, P. (2004). Skewness and
+%kurtosis trades. In (pp. 1--14).
+%\url{https://doi.org/10.1007/978-0-8176-8180-7_1}
+%
+%\leavevmode\hypertarget{ref-speculation}{}%
+%Blau, B. M. (2017). Price dynamics and speculative trading in bitcoin.
+%\emph{Research in International Business and Finance}, \emph{41},
+%493--499.
+%\url{https://doi.org/https://doi.org/10.1016/j.ribaf.2017.05.010}
+%
+%\leavevmode\hypertarget{ref-bloomberg-retail-share}{}%
+%Bloomberg. (2021, November 17). Retail traders slide back below 20\% of
+%market's total volume.
+%\url{https://www.bloomberg.com/news/articles/2021-11-17/retail-traders-retreat-as-choppy-markets-challenge-easy-profits}.
+%Accessed 24 August 2021
+%
+%\leavevmode\hypertarget{ref-breeden_litzenberger78}{}%
+%Breeden, D. T., \& Litzenberger, R. H. (1978). Prices of
+%state-contingent claims implicit in option prices. \emph{The Journal of
+%Business}, \emph{51}(4), 621--651.
+%\url{http://www.jstor.org/stable/2352653}
+%
+%\leavevmode\hypertarget{ref-coins_with_benefits}{}%
+%Chen, C. Y., \& Vinogradov, D. (2021). Coins with benefits: On
+%existence, pricing kernel and risk premium of cryptocurrencies.
+%\emph{Available at SSRN 3959984}.
+%\url{https://doi.org/http://dx.doi.org/10.2139/ssrn.3864578}
+%
+%\leavevmode\hypertarget{ref-choi}{}%
+%Choi, S., \& Shin, J. (2022). Bitcoin: An inflation hedge but not a safe
+%haven. \emph{Finance Research Letters}, \emph{46}, 102379.
+%\url{https://doi.org/https://doi.org/10.1016/j.frl.2021.102379}
+%
+%\leavevmode\hypertarget{ref-oil_spd}{}%
+%Christoffersen, P., Jacobs, K., \& Pan, X. (. (2021). The State Price
+%Density Implied by Crude Oil Futures and Option Prices. \emph{The Review
+%of Financial Studies}, \emph{35}(2), 1064--1103.
+%\url{https://doi.org/10.1093/rfs/hhab011}
+%
+%\leavevmode\hypertarget{ref-cryptonews_bitcoin_retail_share}{}%
+%Coinbase, S., Cryptonews. (2022). Institutions \& retail compete for
+%bitcoin - whose hands are stronger?
+%\url{https://cryptonews.com/exclusives/institutions-retail-compete-for-bitcoin-which-is-the-biggest-9695.htm}.
+%Accessed 22 March 2022
+%
+%\leavevmode\hypertarget{ref-decentralized_wash_trading}{}%
+%Cong, L., Li, X., Tang, K., \& Yang, Y. (2019). Crypto wash trading.
+%\emph{SSRN Electronic Journal}.
+%\url{https://doi.org/10.2139/ssrn.3530220}
+%
+%\leavevmode\hypertarget{ref-jackwerth_pk}{}%
+%Cuesdeanu, H., \& Jackwerth, J. C. (2018). The pricing kernel puzzle:
+%survey and outlook. \emph{Annals of Finance}, \emph{14}(3), 289--329.
+%\url{https://doi.org/10.1007/s10436-017-0317-9}
+%
+%\leavevmode\hypertarget{ref-cross_border_payments}{}%
+%Deng, Q. (2020). Application analysis on blockchain technology in
+%cross-border payment. In.
+%\url{https://doi.org/10.2991/aebmr.k.200306.050}
+%
+%\leavevmode\hypertarget{ref-deribit-insurance-fund}{}%
+%Deribit. (2020a). Deribit insurance fund.
+%\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021
+%
+%\leavevmode\hypertarget{ref-synthetic-btc-index}{}%
+%Deribit. (2020b). Deribit btc-usd index.
+%\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021
+%
+%\leavevmode\hypertarget{ref-market-maker-obligations}{}%
+%Deribit. (2020c). Deribit market maker obligations.
+%\url{https://www.deribit.com/pages/docs/options}. Accessed 2 January
+%2021
+%
+%\leavevmode\hypertarget{ref-deribit_retail_piechart}{}%
+%Deribit. (2022a). Deribit volume share.
+%\url{https://www.deribit.com/statistics/BTC/market-data}. Accessed 25
+%July 2022
+%
+%\leavevmode\hypertarget{ref-deribit_margin}{}%
+%Deribit. (2022b). Deribit margin requirements.
+%\url{https://legacy.deribit.com/pages/docs/options}. Accessed 2 May 2022
+%
+%\leavevmode\hypertarget{ref-deribit_fees}{}%
+%Deribit. (2022c). Deribit margin requirements.
+%\url{https://www.deribit.com/kb/fees}. Accessed 2 May 2022
+%
+%\leavevmode\hypertarget{ref-deribit-rate-limit}{}%
+%Deribit. (2023). Deribit rate limits.
+%\url{https://www.deribit.com/kb/deribit-rate-limits}. Accessed 16 April
+%2021
+%
+%\leavevmode\hypertarget{ref-vola_premium}{}%
+%Eraker, B. (2021). The volatility premium. \emph{Quarterly Journal of
+%Finance (QJF)}, \emph{11}(03), 1--35.
+%\url{https://EconPapers.repec.org/RePEc:wsi:qjfxxx:v:11:y:2021:i:03:n:s2010139221500142}
+%
+%\leavevmode\hypertarget{ref-networkeffect}{}%
+%Gandal, N., \& Halaburda, H. (2016). Can we predict the winner in a
+%market with network effects? Competition in cryptocurrency market.
+%\emph{Games}, \emph{7}(3). \url{https://doi.org/10.3390/g7030016}
+%
+%\leavevmode\hypertarget{ref-Grith09sim}{}%
+%Grith, M., Härdle, W. K., \& Park, J. (2009). Shape invariant modelling
+%pricing kernels and risk aversion.
+%\url{https://doi.org/10.2139/ssrn.2894289}
+%
+%\leavevmode\hypertarget{ref-hall_1991}{}%
+%Hall, P. (1991). Edgeworth expansions for nonparametric density
+%estimators, with applications. \emph{Statistics}, \emph{22}(2),
+%215--232. \url{https://doi.org/10.1080/02331889108802305}
+%
+%\leavevmode\hypertarget{ref-hayes}{}%
+%Hayes, A. S. (2019). Bitcoin price and its marginal cost of production:
+%Support for a fundamental value. \emph{Applied Economics Letters},
+%\emph{26}(7), 554--560.
+%\url{https://doi.org/10.1080/13504851.2018.1488040}
+%
+%\leavevmode\hypertarget{ref-w2yo}{}%
+%Härdle, W. K., Okhrin, Y., \& Wang, W. (2014). Uniform Confidence Bands
+%for Pricing Kernels. \emph{Journal of Financial Econometrics},
+%\emph{13}(2), 376--413. \url{https://doi.org/10.1093/jjfinec/nbu002}
+%
+%\leavevmode\hypertarget{ref-pricing_cryptocurrency_options}{}%
+%Hou, A. J., Wang, W., Chen, C. Y. H., \& Härdle, W. K. (2020). Pricing
+%Cryptocurrency Options*. \emph{Journal of Financial Econometrics},
+%\emph{18}(2), 250--279. \url{https://doi.org/10.1093/jjfinec/nbaa006}
+%
+%\leavevmode\hypertarget{ref-xfg_spd}{}%
+%Huynh, K., Kervella, P., \& Zheng, J. (2002). \emph{Estimating
+%state-price densities with nonparametric regression} (SFB 373 Discussion
+%Papers No. 2002,40). Humboldt University of Berlin, Interdisciplinary
+%Research Project 373: Quantification; Simulation of Economic Processes.
+%\url{https://EconPapers.repec.org/RePEc:zbw:sfb373:200240}
+%
+%\leavevmode\hypertarget{ref-pumpndump}{}%
+%La Morgia, M., Mei, A., Sassi, F., \& Stefa, J. (2020). Pump and dumps
+%in the bitcoin era: Real time detection of cryptocurrency market
+%manipulations. In \emph{2020 29th international conference on computer
+%communications and networks (icccn)} (pp. 1--9).
+%\url{https://doi.org/10.1109/ICCCN49398.2020.9209660}
+%
+%\leavevmode\hypertarget{ref-vola_stylized_facts}{}%
+%Masset, P. (2011). Volatility stylized facts. \emph{SSRN Electronic
+%Journal}. \url{https://doi.org/10.2139/ssrn.1804070}
+%
+%
+%
+%\leavevmode\hypertarget{ref-fundamental-theorem-of-asset-pricing}{}%
+%Pascucci, A., \& Agliardi, R. (2011). PDE and martingale methods in
+%option pricing. In (pp. 429--495).
+%
+%\leavevmode\hypertarget{ref-rodgers2019}{}%
+%Rodgers, T. (2019, April 4). 95 percent of volume could be wash trading
+%as bitcoin price surges.
+%\url{https://www.forbes.com/sites/tomrodgers1/2019/04/04/99-of-volume-could-be-wash-trading-as-bitcoin-takes-back-5000/?sh=4640bcbc23d5}.
+%Accessed 15 April 2023
+%
+%\leavevmode\hypertarget{ref-Rookley97}{}%
+%Rookley, C. (1997). Fully exploiting the information content of intra
+%day option quotes: Applications in option pricing and risk management.
+%
+%\leavevmode\hypertarget{ref-sar2017}{}%
+%Sar, M. (2017). Dodd-frank and the spoofing prohibition in commodities
+%markets.
+%
+%\leavevmode\hypertarget{ref-deriv_volume}{}%
+%Skew.com. (2022). Open interest for bitcoin options over time. Skew is a
+%leading crypto data analytics platform for institutional clients.
+%\url{https://analytics.skew.com/dashboard/bitcoin-options}. Accessed 25
+%July 2022
+%
+%\leavevmode\hypertarget{ref-brazilian_speculation}{}%
+%Smaniotto, E. N., \& Neto, G. B. (2022). Speculative trading in bitcoin:
+%A brazilian market evidence. \emph{The Quarterly Review of Economics and
+%Finance}, \emph{85}, 47--54.
+%\url{https://doi.org/https://doi.org/10.1016/j.qref.2020.10.024}
+%
+%\leavevmode\hypertarget{ref-cross_border_stellar}{}%
+%Stellar Development Foundation. (2022). 2022 research reveals high
+%awareness and growing cross-border use of cryptocurrency in four key
+%markets.
+%\url{https://www.prnewswire.com/news-releases/2022-research-reveals-high-awareness-and-growing-cross-border-use-of-cryptocurrency-in-four-key-markets-301512401.html}.
+%Accessed 22 July 2022
+%
+%\leavevmode\hypertarget{ref-nickszabo}{}%
+%Szabo, N. (2008). Bit gold.
+%\url{https://unenumerated.blogspot.com/2005/12/bit-gold.html}. Accessed
+%28 July 2022
+%
+%\leavevmode\hypertarget{ref-tuccella2021}{}%
+%Tuccella, J.-N., Nadler, P., \& Șerban, O. (2021). Protecting retail
+%investors from order book spoofing using a gru-based detection model.
 

### 2024-02-18 written/paper.tex
written

@@
 On 10 January 2024, the United States Securities and Exchange Commission approved the listing and trading of a range of spot bitcoin exchange-traded product (ETP) shares (Gensler, 2024).
-In other markets, structured products in Bitcoin (and other crypto assets) have been available for years and retailers have been able to mine or buy it since its inception following Nakamoto, 2009.
+In other markets, structured Bitcoin (BTC) products have been available for years and retailers have been able to mine or buy Bitcoin since its inception following Nakamoto, 2009.
 Yet, despite the ongoing integration into established markets, fundamental questions about crypto asset markets remain unclear:
@@
 Are derivatives, written on crypto assets, fairly priced or at least fairly priced relative to other derivatives?
-We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 2000s.
+We assess these fundamental questions and find that the methods required to conduct our analysis have been readily available; in fact we are employing similar methods to those, under which the efficiency of equity option markets had been assessed in their "youth" in the early 1990s.
 The common key behind the employed methods is the precise and bespoke tailoring of risk-return characteristics through the use of options, as proposed by Shumway et al.
@@
 (2001) and Shumway et al.
-(2000), the existence of high premia.for at-the-money options.
+(2000), the existence of high premia for at-the-money options.
 The effect holds after compensating for tail risk (market crash insurance) and transaction cost.
@@
 Evidently, only crypto assets which follow a Proof-of-Stake (PoS) consensus mechanism instead of a Proof-of-Work (PoW) consensus mechanism can be used for staking.
-At the time, this is still a minor amount of cryptocurrencies.
+At the time, this is still a minor share of the crypto asset universe.
 We include one of those, Ether, in our experiment.
@@
 short a short-tenor future and long a longer-tenor future), we argue that in order to minimize liquidity risk, the most liquid instruments should be taken into consideration.
-
-Solve for interest rates from (classic) Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:
+Solve for interest rates under observale Futures price $F$ Spot price $S$ at time $t$ and time-to-maturity $\tau$:
 
@@
 We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
-The straddle's payoff $r_v$ is depicted in Equation 1, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
-The weight $\theta$ is found by solving Equation 2 through Equation 3.
-The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\delta$, the Black-Scholes option price $C$ and the market beta $\beta_m (=1)$ as depicted in Equation 4.
+The straddle's payoff $r_v$ is depicted in Equation 4, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
+The weight $\theta$ is found by solving Equation 5 through Equation 6.
+The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\Delta$, the Black-Scholes option price $C$ as depicted in Equation 7.
+% and the market beta $\beta_m (=1)$
 The underlying data are executed transactions.
@@
 We condition daily returns on levels of the interval and we conduct a left-sided t-test on the null hypothesis of a population mean greater or equal to zero.
-We define a structural (or significant?) non-zero return of the zero-beta straddle returns as (volatility risk) premium.
+We define a measurable non-zero return on a 95\% significance level of the zero-beta straddle returns as (volatility) risk premium.
 
@@
 Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
-Hedge Straddle with FOTM Option in order to exclude influence of Fat Tail Events
-Close Call (Put) leg 20\% away from Strike.
+In order to exclude influence of Fat Tail Events, we hedge the straddle with far-out-the-money (FOTM) options.
+This results in a so-called "Reverse Iron Butterfly Spread", whose risk is limited to the sum of option premia.
+We close the Call (Put) leg 20\% away from Strike.
 We suppose that a such a leg would come at a 30\% premium compared to the ATM volatility.
@@
 
-Considering data authenticity, we refer to our previous paper Risk Premia and Pricing Kernels for Bitcoin. 
+Regarding matters of data authenticity, we refer to our previous paper regarding the study of Bitcoin option data (Winkel and Härdle, 2023).
 The most likely negative factor that could affect our data quality is wash trading. 
-We follow the definition of XPYZ on wash trading (from: ):
-"A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery." ()
-
+We follow the definition of Intercontinental Exchange, Inc.
+(2001): "A wash trade occurs when there is an act of entering into, or purporting to enter into, transactions with no intent to obtain a bona fide market position or activity that gives the false appearance of an executed transaction(s), but does not subject the Principal to any market risk or change in position or aid in price discovery."
 We asses the overall risk of wash trading contaminating our data set as low.
@@
 Additionally, we find a similar premium for slightly ITM contracts.
-Shumway et. al reported an average return of around -3.15 percent per week, whereas XYZ \% is attributable to the volatility premium.
+Shumway et. al reported an average return of around -3.15\% per week.% whereas XYZ \% is attributable to the volatility premium.
 
@@
 The vanilla Ether model has a daily return of -0.9554\% and the crash resistant model delivers -0.9610\%.
+
+Evidently, these large, negative returns are neither explainable by the interest rate proxy via the perpetual futures nor government bonds.
 
@@
 - Evidence for leverage effect
-
-Make bridge to interest rates
 
@@
 Gary Gensler, Chair of the United States Securities and Exchange Commission. Statement on the Approval of Spot Bitcoin Exchange-Traded Products (10 January 2024).
-Available at \url{https://www.sec.gov/news/statement/gensler-statement-spot-bitcoin-011023}. Accessed 18 February 2023.
+\url{https://www.sec.gov/news/statement/gensler-statement-spot-bitcoin-011023}. Accessed 18 February 2023.
 
@@
 \leavevmode\hypertarget{winkel}{}%
-Winkel, J and Härdle, WK, Pricing Kernels and Risk Premia implied in Bitcoin Options (November 21, 2022).Available at SSRN: \url{https://ssrn.com/abstract=4282905} or \url{http://dx.doi.org/10.2139/ssrn.4282905}.
+Winkel, J. and Härdle, W.K. Pricing Kernels and Risk Premia implied in Bitcoin Options. Risks 2023, 11, 85. Available at \url{https://doi.org/10.3390/risks11050085}.
 
@@
 %Deribit. (2020a). Deribit insurance fund.
-%\url{https://www.deribit.com/main\#/insurance}. Accessed 4 January 2021
+%\url{https://www.deribit.com/main/insurance}. Accessed 4 January 2021
 %
@@
 %Deribit. (2020b). Deribit btc-usd index.
-%\url{https://www.deribit.com/main\#/indexes}. Accessed 2 January 2021
+%\url{https://www.deribit.com/main/indexes}. Accessed 2 January 2021
 %
@@
 \hline
-\# Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
-\# Binance (Futures) & BTCUSD\_PERP    & \$44,008.70                        & 44037.64 USD                             & +0.066\%                           & 0.01\%                              & 0.010\%                                   & \$808,036,100                              & \$973,585,131.72                        \\
-\# BingX (Futures)   & BTC-USDT        & \$44,042.40                        & 44046.6 USDT                             & +0.044\%                           & 0.01\%                              & 0.010\%                                   & \$909,897,901                              & \$1,867,895,422.35                      \\
-\# Bitget Futures    & BTCUSDT\_UMCBL  & \$44,049.08                        & 44033.85 USDT                            & +0.015\%                           & 0.01\%                              & 0.011\%                                   & \$1,790,553,246                            & \$5,701,072,691.79                      \\
-\# Bitmart Futures   & BTCUSDT         & \$44,015.47                        & 44003.79 USDT                            & +0.024\%                           & 0.01\%                              & 0.010\%                                   & \$641,006,203                              & \$2,917,088,729.74                      \\
-\# Bybit (Futures)   & BTCUSDT         & \$44,039.88                        & 44016.82 USDT                            & -0.003\%                           & 0.01\%                              & 0.010\%                                   & \$2,538,053,148                            & \$2,672,726,926.85                      \\
-\# Bybit (Futures)   & BTCUSD          & \$43,995.50                        & 44037.2 USD                              & +0.095\%                           & 0.01\%                              & 0.010\%                                   & \$652,512,486                              & \$283,394,472.00                        \\
-\# Deribit           & BTC-PERPETUAL   & \$44,020.00                        & 44028.17 USD                             & +0.019\%                           & 0.01\%                              & 0.004\%                                   & \$577,506,570                              & \$204,526,951.86                        \\
-\# OKX (Futures)     & BTC-USDT-SWAP   & \$44,014.07                        & 43989.3 USDT                             & -0.006\%                           & 0.01\%                              & -0.009\%                                  & \$984,130,801                              & \$2,648,725,568.71                      \\
-\# Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31
+ Binance (Futures) & BTCUSDT         & \$43,995.06                        & 44011.67 USDT                            & +0.087\%                           & 0.01\%                              & 0.010\%                                   & \$3,214,727,375                            & \$6,822,091,229.25                      \\
+ Binance (Futures) & BTCUSD\_PERP    & \$44,008.70                        & 44037.64 USD                             & +0.066\%                           & 0.01\%                              & 0.010\%                                   & \$808,036,100                              & \$973,585,131.72                        \\
+ BingX (Futures)   & BTC-USDT        & \$44,042.40                        & 44046.6 USDT                             & +0.044\%                           & 0.01\%                              & 0.010\%                                   & \$909,897,901                              & \$1,867,895,422.35                      \\
+ Bitget Futures    & BTCUSDT\_UMCBL  & \$44,049.08                        & 44033.85 USDT                            & +0.015\%                           & 0.01\%                              & 0.011\%                                   & \$1,790,553,246                            & \$5,701,072,691.79                      \\
+ Bitmart Futures   & BTCUSDT         & \$44,015.47                        & 44003.79 USDT                            & +0.024\%                           & 0.01\%                              & 0.010\%                                   & \$641,006,203                              & \$2,917,088,729.74                      \\
+ Bybit (Futures)   & BTCUSDT         & \$44,039.88                        & 44016.82 USDT                            & -0.003\%                           & 0.01\%                              & 0.010\%                                   & \$2,538,053,148                            & \$2,672,726,926.85                      \\
+ Bybit (Futures)   & BTCUSD          & \$43,995.50                        & 44037.2 USD                              & +0.095\%                           & 0.01\%                              & 0.010\%                                   & \$652,512,486                              & \$283,394,472.00                        \\
+ Deribit           & BTC-PERPETUAL   & \$44,020.00                        & 44028.17 USD                             & +0.019\%                           & 0.01\%                              & 0.004\%                                   & \$577,506,570                              & \$204,526,951.86                        \\
+ OKX (Futures)     & BTC-USDT-SWAP   & \$44,014.07                        & 43989.3 USDT                             & -0.006\%                           & 0.01\%                              & -0.009\%                                  & \$984,130,801                              & \$2,648,725,568.71                      \\
+ Prime XBT         & BTC/USD         & \$43,981.30                        & -                                        & -                                  & 0.02\%                              & -                                         & \$920,322,200                              & \$60,224,491.31
 \end{tabular}}
@@
 \hline
-\# Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
-\# Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
-\# Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
-\# OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
-\# Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
-\# BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
-\# Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
-\# Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
-\# Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
-\# XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30
+ Deepcoin (Derivatives) & ETHUSDT         & \$2,232.18                         & 2232.46 USDT                             & +0.047\%                           & 0.02\%                              & 0.006\%                                   & \$6,376,015,545                            & \$237,202,788.68                        \\
+ Binance (Futures)      & ETHUSDT         & \$2,227.11                         & 2227.74 USDT                             & +0.078\%                           & 0.01\%                              & 0.010\%                                   & \$1,680,165,204                            & \$2,843,630,044.97                      \\
+ Bybit (Futures)        & ETHUSDT         & \$2,228.15                         & 2228.15 USDT                             & +0.049\%                           & 0.01\%                              & 0.010\%                                   & \$1,027,647,498                            & \$540,402,664.24                        \\
+ OKX (Futures)          & ETH-USDT-SWAP   & \$2,227.96                         & 2227.07 USDT                             & +0.010\%                           & 0.01\%                              & -0.003\%                                  & \$584,652,223                              & \$1,748,266,659.63                      \\
+ Gate.io (Futures)      & ETH\_USDT       & \$2,228.62                         & 2227.03 USDT                             & -0.021\%                           & 0.01\%                              & 0.010\%                                   & \$508,608,257                              & \$189,744,908.47                        \\
+ BingX (Futures)        & ETH-USDT        & \$2,229.64                         & 2230.26 USDT                             & +0.062\%                           & 0.02\%                              & 0.010\%                                   & \$475,301,553                              & \$609,765,117.59                        \\
+ Prime XBT              & ETH/USD         & \$2,227.49                         & -                                        & -                                  & 0.04\%                              & -                                         & \$473,765,000                              & \$16,309,868.89                         \\
+ Deribit                & ETH-PERPETUAL   & \$2,228.05                         & 2228.59 USD                              & +0.024\%                           & 0.01\%                              & 0.004\%                                   & \$447,911,369                              & \$82,175,344.52                         \\
+ Binance (Futures)      & ETHUSD\_PERP    & \$2,227.69                         & 2228.74 USD                              & +0.047\%                           & 0.01\%                              & 0.010\%                                   & \$366,493,140                              & \$257,267,395.24                        \\
+ XT.COM (Derivatives)   & ETH\_USDT       & \$2,228.19                         & 2225.55 USDT                             & +0.031\%                           & 0.01\%                              & -0.010\%                                  & \$325,480,371                              & \$1,137,587,629.30
 \end{tabular}}
@@
 \hline
-\# Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
-\# Binance (Futures)             & BTCUSD\_240628     & \$46,802.20                        & 44037.64 USD                             & -5.907\%                           & 0.02\%                              & 6 months                                & \$60,673,400                               & \$11,015,730.09                         \\
-\# Binance (Futures)             & BTCUSDT\_240329    & \$45,340.32                        & 44011.62 USDT                            & -2.883\%                           & 0.04\%                              & -                                       & \$38,608,233                               & \$13,341,161.63                         \\
-\# Binance (Futures)             & BTCUSDT\_240628    & \$46,588.03                        & 44011.62 USDT                            & -5.484\%                           & 0.02\%                              & -                                       & \$7,296,676                                & \$6,727,917.37                          \\
-\# BitMEX (Derivative)           & XBTH24             & \$45,170.00                        & 44016.02 USD                             & -2.555\%                           & 0.03\%                              & 3 months                                & \$23,123,300                               & \$2,586,155.50                          \\
-\# BitMEX (Derivative)           & XBTM24             & \$46,319.00                        & 44016.02 USD                             & -4.972\%                           & 0.15\%                              & 6 months                                & \$14,701,700                               & \$899,753.13                            \\
-\# BitMEX (Derivative)           & XBTF24             & \$44,599.50                        & 44016.02 USD                             & -1.308\%                           & 0.18\%                              & 19 days                                 & \$3,686,400                                & \$42,073.68                             \\
-\# BitMEX (Derivative)           & XBTU24             & \$47,680.00                        & 44016.02 USD                             & -7.685\%                           & 0.82\%                              & 9 months                                & \$874,700                                  & \$14,332.62                             \\
-\# BitMEX (Derivative)           & XBTG24             & \$45,034.50                        & 44016.02 USD                             & -2.262\%                           & 0.2\%                               & about 2 months                          & \$149,400                                  & \$502.57                                \\
-\# BitMEX (Derivative)           & XBTUSDTH24         & \$44,913.12                        & 43991.27 USDT                            & -2.003\%                           & 22.08\%                             & 3 months                                & \$67,027                                   & \$23,309.91                             \\
-\# BTSE (Futures)                & BTC-240329         & \$45,346.20                        & 45337.26 USD                             & -0.020\%                           & 0.15\%                              & 3 months                                & \$70,779,838                               & \$70,829.75                             \\
-\# BTSE (Futures)                & BTC-240628         & \$46,578.30                        & 46774.54 USD                             & +0.421\%                           & 0.2\%                               & 6 months                                & \$68,641,915                               & \$58,755.91                             \\
-\# Bybit (Futures)               & BTCUSDH24          & \$45,515.00                        & 44050.12 USD                             & -3.218\%                           & 0.01\%                              & 3 months                                & \$31,042,370                               & \$8,992,250.00                          \\
-\# Bybit (Futures)               & BTCUSDM24          & \$46,867.50                        & 44046.87 USD                             & -6.018\%                           & 0.01\%                              & 6 months                                & \$13,200,403                               & \$932,634.00                            \\
-\# Bybit (Futures)               & BTC-29MAR24        & \$45,288.92                        & 44042.99 USDC                            & -2.786\%                           & 0.07\%                              & 3 months                                & -                                          & \$1,650,409.10                          \\
-\# Bybit (Futures)               & BTC-28JUN24        & \$46,655.43                        & 44042.83 USDC                            & -5.633\%                           & 0.07\%                              & 6 months                                & -                                          & \$636,256.66                            \\
-\# Bybit (Futures)               & BTC-12JAN24        & \$44,205.30                        & 44042.83 USDC                            & -0.403\%                           & 0.02\%                              & 5 days                                  & -                                          & \$320,758.50                            \\
-\# Bybit (Futures)               & BTC-19JAN24        & \$44,341.25                        & 44042.83 USDC                            & -0.708\%                           & 0.03\%                              & 12 days                                 & -                                          & \$117,823.82                            \\
-\# Bybit (Futures)               & BTC-27SEP24        & \$47,694.06                        & 44042.99 USDC                            & -7.688\%                           & 0.08\%                              & 9 months                                & -                                          & \$66,406.59                             \\
-\# Bybit (Futures)               & BTC-26JAN24        & \$44,370.24                        & 44042.75 USDC                            & -0.773\%                           & 0.02\%                              & 19 days                                 & -                                          & \$47,245.15                             \\
-\# Bybit (Futures)               & BTC-23FEB24        & \$44,806.59                        & 44042.99 USDC                            & -1.739\%                           & 0.03\%                              & about 2 months                          & -                                          & \$8,650.36                              \\
-\# Crypto.com Exchange (Futures) & BTCUSD-240628      & \$46,384.20                        & 44003.38 USD                             & -5.133\%                           & 0.41\%                              & -                                       & \$24,557,224                               & \$15,659.31                             \\
-\# Crypto.com Exchange (Futures) & BTCUSD-240329      & \$45,024.60                        & 44003.38 USD                             & -2.268\%                           & 0.46\%                              & -                                       & \$1,118,289                                & \$17,244.42                             \\
-\# Crypto.com Exchange (Futures) & BTCUSD-240126      & \$44,215.10                        & 44003.38 USD                             & -0.479\%                           & 0.29\%                              & -                                       & \$9,701                                    & \$18,428.85                             \\
-\# Crypto.com Exchange (Futures) & BTCUSD-240223      & \$44,624.00                        & 44003.38 USD                             & -1.391\%                           & 0.43\%                              & -                                       & \$3,539                                    & \$14,931.19                             \\
-\# Deribit                       & BTC-29MAR24        & \$45,300.00                        & 44026.9 USD                              & -2.810\%                           & 0.02\%                              & 3 months                                & \$208,084,190                              & \$15,282,281.56                         \\
-\# Deribit                       & BTC-26JAN24        & \$44,475.00                        & 44026.9 USD                              & -1.008\%                           & 0.1\%                               & 19 days                                 & \$89,621,140                               & \$3,132,087.87                          \\
-\# Deribit                       & BTC-28JUN24        & \$46,577.50                        & 44026.9 USD                              & -5.476\%                           & 0.02\%                              & 6 months                                & \$79,314,230                               & \$7,916,251.72                          \\
-\# Deribit                       & BTC-27SEP24        & \$47,715.00                        & 44026.9 USD                              & -7.729\%                           & 0.09\%                              & 9 months                                & \$32,099,570                               & \$1,034,939.35                          \\
-\# Deribit                       & BTC-12JAN24        & \$44,110.00                        & 44026.9 USD                              & -0.188\%                           & 0.03\%                              & 5 days                                  & \$25,884,930                               & \$7,230,738.10                          \\
-\# Deribit                       & BTC-23FEB24        & \$44,767.50                        & 44026.9 USD                              & -1.654\%                           & 0.03\%                              & about 2 months                          & \$22,571,940                               & \$744,850.73                            \\
-\# Deribit                       & BTC-27DEC24        & \$49,247.50                        & 44026.9 USD                              & -10.601\%                          & 0.13\%                              & 12 months                               & \$11,398,600                               & \$600,503.46                            \\
-\# Deribit                       & BTC-19JAN24        & \$44,222.50                        & 44026.9 USD                              & -0.442\%                           & 0.04\%                              & 12 days                                 & \$5,538,440                                & \$2,799,269.71                          \\
-\# HTX Futures                   & BTC\_CQ            & \$45,297.68                        & 44023.11 USD                             & -2.814\%                           & 0.38\%                              & 3 months                                & \$1,002,200                                & \$1,602,716.03                          \\
-\# HTX Futures                   & BTC\_CW            & \$44,095.65                        & 44030.71 USD                             & -0.147\%                           & 0.45\%                              & 4 days                                  & \$47,100                                   & \$1,011,419.90                          \\
-\# HTX Futures                   & BTC\_NW            & \$44,211.45                        & 44023.11 USD                             & -0.426\%                           & 0.4\%                               & 11 days                                 & \$9,000                                    & \$967,082.71                            \\
-\# Kraken (Futures)              & FI\_XBTUSD\_240329 & \$45,520.50                        & 44013.38 USD                             & -3.311\%                           & 0.08\%                              & 3 months                                & \$6,608,999                                & \$112,442.00                            \\
-\# Kraken (Futures)              & FI\_XBTUSD\_240628 & \$46,571.50                        & 44013.38 USD                             & -5.493\%                           & 0.24\%                              & 6 months                                & \$1,929,982                                & \$275,529.00                            \\
-\# Kraken (Futures)              & FI\_XBTUSD\_240126 & \$44,191.50                        & 44013.38 USD                             & -0.403\%                           & 0.4\%                               & 19 days                                 & \$300,856                                  & \$3.00                                  \\
-\# Kraken (Futures)              & FF\_XBTUSD\_240329 & \$45,284.00                        & 44013.38 USD                             & -2.806\%                           & 0.11\%                              & 3 months                                & \$87                                       & \$22.68                                 \\
-\# Kraken (Futures)              & FF\_XBTUSD\_240126 & \$44,307.00                        & 44013.38 USD                             & -0.663\%                           & 0.08\%                              & 19 days                                 & \$32                                       & \$4.61                                  \\
-\# KuCoin Futures                & XBTMH24            & \$45,444.00                        & 44072.8 USD                              & -3.017\%                           & 0.19\%                              & 3 months                                & \$11,251,580                               & \$86,193.00                             \\
-\# OKX (Futures)                 & BTC-USD-240329     & \$45,322.90                        & 44016.1 USD                              & -2.883\%                           & 0.01\%                              & 3 months                                & \$175,555,100                              & \$42,597,534.31                         \\
-\# OKX (Futures)                 & BTC-USD-240628     & \$46,744.90                        & 44016.1 USD                              & -5.838\%                           & 0.03\%                              & 6 months                                & \$67,199,400                               & \$13,281,039.45                         \\
-\# OKX (Futures)                 & BTC-USDT-240329    & \$45,345.34                        & 43989.3 USDT                             & -2.942\%                           & 0.02\%                              & 3 months                                & \$54,809,841                               & \$32,494,014.76                         \\
-\# OKX (Futures)                 & BTC-USDT-240628    & \$46,824.58                        & 43989.3 USDT                             & -6.008\%                           & 0.02\%                              & 6 months                                & \$49,096,426                               & \$8,216,309.33                          \\
-\# OKX (Futures)                 & BTC-USD-240126     & \$44,235.20                        & 44016.1 USD                              & -0.495\%                           & 0.04\%                              & 19 days                                 & \$20,945,300                               & \$1,424,116.88                          \\
-\# OKX (Futures)                 & BTC-USD-240112     & \$44,085.20                        & 44016.1 USD                              & -0.157\%                           & 0.01\%                              & 5 days                                  & \$15,394,800                               & \$11,575,786.01                         \\
-\# OKX (Futures)                 & BTC-USDT-240126    & \$44,284.50                        & 43989.3 USDT                             & -0.617\%                           & 0.06\%                              & 19 days                                 & \$8,573,427                                & \$1,552,614.65                          \\
-\# OKX (Futures)                 & BTC-USD-240223     & \$44,719.10                        & 44016.1 USD                              & -1.572\%                           & 0.04\%                              & about 2 months                          & \$8,046,700                                & \$3,603,630.54                          \\
-\# OKX (Futures)                 & BTC-USD-240119     & \$44,198.90                        & 44016.1 USD                              & -0.414\%                           & 0.01\%                              & 12 days                                 & \$4,957,200                                & \$6,247,231.64                          \\
-\# OKX (Futures)                 & BTC-USDT-240112    & \$44,080.50                        & 43989.3 USDT                             & -0.157\%                           & 0.03\%                              & 5 days                                  & \$3,560,036                                & \$12,798,332.26                         \\
-\# OKX (Futures)                 & BTC-USDT-240223    & \$44,781.65                        & 43989.3 USDT                             & -1.720\%                           & 0.08\%                              & about 2 months                          & \$2,960,896                                & \$711,132.65                            \\
-\# OKX (Futures)                 & BTC-USDT-240119    & \$44,192.36                        & 43989.3 USDT                             & -0.409\%                           & 0.04\%                              & 12 days                                 & \$975,364                                  & \$4,235,395.39                          \\
-\# OKX (Futures)                 & BTC-USDC-240628    & \$46,788.02                        & 44015.4 USDC                             & -5.958\%                           & 0.39\%                              & 6 months                                & -                                          & \$17,320.92                             \\
-\# OKX (Futures)                 & BTC-USDC-240119    & \$44,137.13                        & 44020.7 USDC                             & -0.298\%                           & 0.1\%                               & 12 days                                 & -                                          & \$6,285.13                              \\
-\# OKX (Futures)                 & BTC-USDC-240329    & \$45,832.15                        & 44020.7 USDC                             & -3.985\%                           & 0.31\%                              & 3 months                                & -                                          & \$1,874.53                              \\
-\# OKX (Futures)                 & BTC-USDC-240112    & \$44,107.04                        & 44015.4 USDC                             & -0.242\%                           & 0.13\%                              & 5 days                                  & -                                          & \$9,765.30                              \\
-\# XT.COM (Derivatives)          & BTC\_USD\_240329   & \$45,380.70                        & -                                        & -3.586\%                           & 0.01\%                              & 3 months                                & -                                          & \$33,113,000.00                         \\
-\# XT.COM (Derivatives)          & BTC\_USD\_240628   & \$46,797.20                        & -                                        & -                                  & 0.01\%                              & 6 months                                & -                                          & \$31,000,200.00                         \\
-\# XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & -                                  & 0.06\%                              & 3 months                                & -                                          & \$20,870,477.00
+ Binance (Futures)             & BTCUSD\_240329     & \$45,372.20                        & 44041.17 USD                             & -2.934\%                           & 0.01\%                              & 3 months                                & \$136,765,200                              & \$19,534,741.00                         \\
+ Binance (Futures)             & BTCUSD\_240628     & \$46,802.20                        & 44037.64 USD                             & -5.907\%                           & 0.02\%                              & 6 months                                & \$60,673,400                               & \$11,015,730.09                         \\
+ Binance (Futures)             & BTCUSDT\_240329    & \$45,340.32                        & 44011.62 USDT                            & -2.883\%                           & 0.04\%                              & -                                       & \$38,608,233                               & \$13,341,161.63                         \\
+ Binance (Futures)             & BTCUSDT\_240628    & \$46,588.03                        & 44011.62 USDT                            & -5.484\%                           & 0.02\%                              & -                                       & \$7,296,676                                & \$6,727,917.37                          \\
+ BitMEX (Derivative)           & XBTH24             & \$45,170.00                        & 44016.02 USD                             & -2.555\%                           & 0.03\%                              & 3 months                                & \$23,123,300                               & \$2,586,155.50                          \\
+ BitMEX (Derivative)           & XBTM24             & \$46,319.00                        & 44016.02 USD                             & -4.972\%                           & 0.15\%                              & 6 months                                & \$14,701,700                               & \$899,753.13                            \\
+ BitMEX (Derivative)           & XBTF24             & \$44,599.50                        & 44016.02 USD                             & -1.308\%                           & 0.18\%                              & 19 days                                 & \$3,686,400                                & \$42,073.68                             \\
+ BitMEX (Derivative)           & XBTU24             & \$47,680.00                        & 44016.02 USD                             & -7.685\%                           & 0.82\%                              & 9 months                                & \$874,700                                  & \$14,332.62                             \\
+ BitMEX (Derivative)           & XBTG24             & \$45,034.50                        & 44016.02 USD                             & -2.262\%                           & 0.2\%                               & about 2 months                          & \$149,400                                  & \$502.57                                \\
+ BitMEX (Derivative)           & XBTUSDTH24         & \$44,913.12                        & 43991.27 USDT                            & -2.003\%                           & 22.08\%                             & 3 months                                & \$67,027                                   & \$23,309.91                             \\
+ BTSE (Futures)                & BTC-240329         & \$45,346.20                        & 45337.26 USD                             & -0.020\%                           & 0.15\%                              & 3 months                                & \$70,779,838                               & \$70,829.75                             \\
+ BTSE (Futures)                & BTC-240628         & \$46,578.30                        & 46774.54 USD                             & +0.421\%                           & 0.2\%                               & 6 months                                & \$68,641,915                               & \$58,755.91                             \\
+ Bybit (Futures)               & BTCUSDH24          & \$45,515.00                        & 44050.12 USD                             & -3.218\%                           & 0.01\%                              & 3 months                                & \$31,042,370                               & \$8,992,250.00                          \\
+ Bybit (Futures)               & BTCUSDM24          & \$46,867.50                        & 44046.87 USD                             & -6.018\%                           & 0.01\%                              & 6 months                                & \$13,200,403                               & \$932,634.00                            \\
+ Bybit (Futures)               & BTC-29MAR24        & \$45,288.92                        & 44042.99 USDC                            & -2.786\%                           & 0.07\%                              & 3 months                                & -                                          & \$1,650,409.10                          \\
+ Bybit (Futures)               & BTC-28JUN24        & \$46,655.43                        & 44042.83 USDC                            & -5.633\%                           & 0.07\%                              & 6 months                                & -                                          & \$636,256.66                            \\
+ Bybit (Futures)               & BTC-12JAN24        & \$44,205.30                        & 44042.83 USDC                            & -0.403\%                           & 0.02\%                              & 5 days                                  & -                                          & \$320,758.50                            \\
+ Bybit (Futures)               & BTC-19JAN24        & \$44,341.25                        & 44042.83 USDC                            & -0.708\%                           & 0.03\%                              & 12 days                                 & -                                          & \$117,823.82                            \\
+ Bybit (Futures)               & BTC-27SEP24        & \$47,694.06                        & 44042.99 USDC                            & -7.688\%                           & 0.08\%                              & 9 months                                & -                                          & \$66,406.59                             \\
+ Bybit (Futures)               & BTC-26JAN24        & \$44,370.24                        & 44042.75 USDC                            & -0.773\%                           & 0.02\%                              & 19 days                                 & -                                          & \$47,245.15                             \\
+ Bybit (Futures)               & BTC-23FEB24        & \$44,806.59                        & 44042.99 USDC                            & -1.739\%                           & 0.03\%                              & about 2 months                          & -                                          & \$8,650.36                              \\
+ Crypto.com Exchange (Futures) & BTCUSD-240628      & \$46,384.20                        & 44003.38 USD                             & -5.133\%                           & 0.41\%                              & -                                       & \$24,557,224                               & \$15,659.31                             \\
+ Crypto.com Exchange (Futures) & BTCUSD-240329      & \$45,024.60                        & 44003.38 USD                             & -2.268\%                           & 0.46\%                              & -                                       & \$1,118,289                                & \$17,244.42                             \\
+ Crypto.com Exchange (Futures) & BTCUSD-240126      & \$44,215.10                        & 44003.38 USD                             & -0.479\%                           & 0.29\%                              & -                                       & \$9,701                                    & \$18,428.85                             \\
+ Crypto.com Exchange (Futures) & BTCUSD-240223      & \$44,624.00                        & 44003.38 USD                             & -1.391\%                           & 0.43\%                              & -                                       & \$3,539                                    & \$14,931.19                             \\
+ Deribit                       & BTC-29MAR24        & \$45,300.00                        & 44026.9 USD                              & -2.810\%                           & 0.02\%                              & 3 months                                & \$208,084,190                              & \$15,282,281.56                         \\
+ Deribit                       & BTC-26JAN24        & \$44,475.00                        & 44026.9 USD                              & -1.008\%                           & 0.1\%                               & 19 days                                 & \$89,621,140                               & \$3,132,087.87                          \\
+ Deribit                       & BTC-28JUN24        & \$46,577.50                        & 44026.9 USD                              & -5.476\%                           & 0.02\%                              & 6 months                                & \$79,314,230                               & \$7,916,251.72                          \\
+ Deribit                       & BTC-27SEP24        & \$47,715.00                        & 44026.9 USD                              & -7.729\%                           & 0.09\%                              & 9 months                                & \$32,099,570                               & \$1,034,939.35                          \\
+ Deribit                       & BTC-12JAN24        & \$44,110.00                        & 44026.9 USD                              & -0.188\%                           & 0.03\%                              & 5 days                                  & \$25,884,930                               & \$7,230,738.10                          \\
+ Deribit                       & BTC-23FEB24        & \$44,767.50                        & 44026.9 USD                              & -1.654\%                           & 0.03\%                              & about 2 months                          & \$22,571,940                               & \$744,850.73                            \\
+ Deribit                       & BTC-27DEC24        & \$49,247.50                        & 44026.9 USD                              & -10.601\%                          & 0.13\%                              & 12 months                               & \$11,398,600                               & \$600,503.46                            \\
+ Deribit                       & BTC-19JAN24        & \$44,222.50                        & 44026.9 USD                              & -0.442\%                           & 0.04\%                              & 12 days                                 & \$5,538,440                                & \$2,799,269.71                          \\
+ HTX Futures                   & BTC\_CQ            & \$45,297.68                        & 44023.11 USD                             & -2.814\%                           & 0.38\%                              & 3 months                                & \$1,002,200                                & \$1,602,716.03                          \\
+ HTX Futures                   & BTC\_CW            & \$44,095.65                        & 44030.71 USD                             & -0.147\%                           & 0.45\%                              & 4 days                                  & \$47,100                                   & \$1,011,419.90                          \\
+ HTX Futures                   & BTC\_NW            & \$44,211.45                        & 44023.11 USD                             & -0.426\%                           & 0.4\%                               & 11 days                                 & \$9,000                                    & \$967,082.71                            \\
+ Kraken (Futures)              & FI\_XBTUSD\_240329 & \$45,520.50                        & 44013.38 USD                             & -3.311\%                           & 0.08\%                              & 3 months                                & \$6,608,999                                & \$112,442.00                            \\
+ Kraken (Futures)              & FI\_XBTUSD\_240628 & \$46,571.50                        & 44013.38 USD                             & -5.493\%                           & 0.24\%                              & 6 months                                & \$1,929,982                                & \$275,529.00                            \\
+ Kraken (Futures)              & FI\_XBTUSD\_240126 & \$44,191.50                        & 44013.38 USD                             & -0.403\%                           & 0.4\%                               & 19 days                                 & \$300,856                                  & \$3.00                                  \\
+ Kraken (Futures)              & FF\_XBTUSD\_240329 & \$45,284.00                        & 44013.38 USD                             & -2.806\%                           & 0.11\%                              & 3 months                                & \$87                                       & \$22.68                                 \\
+ Kraken (Futures)              & FF\_XBTUSD\_240126 & \$44,307.00                        & 44013.38 USD                             & -0.663\%                           & 0.08\%                              & 19 days                                 & \$32                                       & \$4.61                                  \\
+ KuCoin Futures                & XBTMH24            & \$45,444.00                        & 44072.8 USD                              & -3.017\%                           & 0.19\%                              & 3 months                                & \$11,251,580                               & \$86,193.00                             \\
+ OKX (Futures)                 & BTC-USD-240329     & \$45,322.90                        & 44016.1 USD                              & -2.883\%                           & 0.01\%                              & 3 months                                & \$175,555,100                              & \$42,597,534.31                         \\
+ OKX (Futures)                 & BTC-USD-240628     & \$46,744.90                        & 44016.1 USD                              & -5.838\%                           & 0.03\%                              & 6 months                                & \$67,199,400                               & \$13,281,039.45                         \\
+ OKX (Futures)                 & BTC-USDT-240329    & \$45,345.34                        & 43989.3 USDT                             & -2.942\%                           & 0.02\%                              & 3 months                                & \$54,809,841                               & \$32,494,014.76                         \\
+ OKX (Futures)                 & BTC-USDT-240628    & \$46,824.58                        & 43989.3 USDT                             & -6.008\%                           & 0.02\%                              & 6 months                                & \$49,096,426                               & \$8,216,309.33                          \\
+ OKX (Futures)                 & BTC-USD-240126     & \$44,235.20                        & 44016.1 USD                              & -0.495\%                           & 0.04\%                              & 19 days                                 & \$20,945,300                               & \$1,424,116.88                          \\
+ OKX (Futures)                 & BTC-USD-240112     & \$44,085.20                        & 44016.1 USD                              & -0.157\%                           & 0.01\%                              & 5 days                                  & \$15,394,800                               & \$11,575,786.01                         \\
+ OKX (Futures)                 & BTC-USDT-240126    & \$44,284.50                        & 43989.3 USDT                             & -0.617\%                           & 0.06\%                              & 19 days                                 & \$8,573,427                                & \$1,552,614.65                          \\
+ OKX (Futures)                 & BTC-USD-240223     & \$44,719.10                        & 44016.1 USD                              & -1.572\%                           & 0.04\%                              & about 2 months                          & \$8,046,700                                & \$3,603,630.54                          \\
+ OKX (Futures)                 & BTC-USD-240119     & \$44,198.90                        & 44016.1 USD                              & -0.414\%                           & 0.01\%                              & 12 days                                 & \$4,957,200                                & \$6,247,231.64                          \\
+ OKX (Futures)                 & BTC-USDT-240112    & \$44,080.50                        & 43989.3 USDT                             & -0.157\%                           & 0.03\%                              & 5 days                                  & \$3,560,036                                & \$12,798,332.26                         \\
+ OKX (Futures)                 & BTC-USDT-240223    & \$44,781.65                        & 43989.3 USDT                             & -1.720\%                           & 0.08\%                              & about 2 months                          & \$2,960,896                                & \$711,132.65                            \\
+ OKX (Futures)                 & BTC-USDT-240119    & \$44,192.36                        & 43989.3 USDT                             & -0.409\%                           & 0.04\%                              & 12 days                                 & \$975,364                                  & \$4,235,395.39                          \\
+ OKX (Futures)                 & BTC-USDC-240628    & \$46,788.02                        & 44015.4 USDC                             & -5.958\%                           & 0.39\%                              & 6 months                                & -                                          & \$17,320.92                             \\
+ OKX (Futures)                 & BTC-USDC-240119    & \$44,137.13                        & 44020.7 USDC                             & -0.298\%                           & 0.1\%                               & 12 days                                 & -                                          & \$6,285.13                              \\
+ OKX (Futures)                 & BTC-USDC-240329    & \$45,832.15                        & 44020.7 USDC                             & -3.985\%                           & 0.31\%                              & 3 months                                & -                                          & \$1,874.53                              \\
+ OKX (Futures)                 & BTC-USDC-240112    & \$44,107.04                        & 44015.4 USDC                             & -0.242\%                           & 0.13\%                              & 5 days                                  & -                                          & \$9,765.30                              \\
+ XT.COM (Derivatives)          & BTC\_USD\_240329   & \$45,380.70                        & -                                        & -3.586\%                           & 0.01\%                              & 3 months                                & -                                          & \$33,113,000.00                         \\
+ XT.COM (Derivatives)          & BTC\_USD\_240628   & \$46,797.20                        & -                                        & -                                  & 0.01\%                              & 6 months                                & -                                          & \$31,000,200.00                         \\
+ XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & -                                  & 0.06\%                              & 3 months                                & -                                          & \$20,870,477.00
 \end{tabular}}
@@
 \hline
-\# Binance (Futures)             & ETHUSD\_240329     & \$2,300.60                         & 2228.81 USD                              & -3.121\%                           & 0.01\%                              & 3 months                                & \$72,215,240                               & \$16,326,927.83                         \\
-\# Binance (Futures)             & ETHUSD\_240628     & \$2,368.79                         & 2229.03 USD                              & -5.900\%                           & 0.02\%                              & 6 months                                & \$11,183,360                               & \$4,224,925.26                          \\
-\# Binance (Futures)             & ETHUSDT\_240329    & \$2,300.46                         & 2227.81 USDT                             & -3.110\%                           & 0.02\%                              & -                                       & \$35,040                                   & \$6,902,127.72                          \\
-\# Binance (Futures)             & ETHUSDT\_240628    & \$2,360.43                         & 2227.81 USDT                             & -5.572\%                           & 0.03\%                              & -                                       & \$4,604                                    & \$4,303,853.27                          \\
-\# BitMEX (Derivative)           & ETHUSDH24          & \$2,452.60                         & 2228.01 USD                              & -9.157\%                           & 0.02\%                              & 3 months                                & \$4,341,286                                & \$537,210.05                            \\
-\# BitMEX (Derivative)           & ETHH24             & \$2,217.23                         & 0.05 XBT                                 & +0.457\%                           & 0.37\%                              & 3 months                                & \$1,575,478                                & \$69,244.08                             \\
-\# BTSE (Futures)                & ETH-240628         & \$2,350.05                         & 2367.26 USD                              & +0.732\%                           & 0.75\%                              & 6 months                                & \$2,517,764                                & \$49,845.75                             \\
-\# BTSE (Futures)                & ETH-240329         & \$2,297.48                         & 2298.78 USD                              & +0.057\%                           & 0.23\%                              & 3 months                                & \$2,081,180                                & \$49,130.96                             \\
-\# Bybit (Futures)               & ETHUSDM24          & \$2,357.45                         & 2229.63 USD                              & -5.422\%                           & 0.05\%                              & 6 months                                & -                                          & \$448,716.00                            \\
-\# Bybit (Futures)               & ETHUSDH24          & \$2,287.90                         & 2229.53 USD                              & -2.551\%                           & 0.06\%                              & 3 months                                & -                                          & \$294,007.00                            \\
-\# Bybit (Futures)               & ETH-26JAN24        & \$2,243.65                         & 2229.46 USDC                             & -0.668\%                           & 0.05\%                              & 19 days                                 & -                                          & \$286,245.77                            \\
-\# Bybit (Futures)               & ETH-12JAN24        & \$2,231.66                         & 2229.51 USDC                             & -0.132\%                           & 0.03\%                              & 5 days                                  & -                                          & \$99,683.25                             \\
-\# Bybit (Futures)               & ETH-28JUN24        & \$2,368.66                         & 2229.46 USDC                             & -5.910\%                           & 0.1\%                               & 6 months                                & -                                          & \$97,357.35                             \\
-\# Bybit (Futures)               & ETH-19JAN24        & \$2,238.21                         & 2229.51 USDC                             & -0.424\%                           & 0.06\%                              & 12 days                                 & -                                          & \$92,957.40                             \\
-\# Bybit (Futures)               & ETH-23FEB24        & \$2,274.64                         & 2229.51 USDC                             & -2.019\%                           & 0.03\%                              & about 2 months                          & -                                          & \$68,610.65                             \\
-\# Bybit (Futures)               & ETH-29MAR24        & \$2,297.48                         & 2229.51 USDC                             & -2.993\%                           & 0.03\%                              & 3 months                                & -                                          & \$36,926.81                             \\
-\# Bybit (Futures)               & ETH-27SEP24        & \$2,420.24                         & 2229.46 USDC                             & -7.915\%                           & 0.12\%                              & 9 months                                & -                                          & \$30,008.99                             \\
-\# Crypto.com Exchange (Futures) & ETHUSD-240628      & \$2,347.68                         & 2224.96 USD                              & -5.227\%                           & 0.24\%                              & -                                       & \$24,573,170                               & \$822.63                                \\
-\# Crypto.com Exchange (Futures) & ETHUSD-240126      & \$2,234.13                         & 2224.96 USD                              & -0.410\%                           & 0.14\%                              & -                                       & \$79,732                                   & \$742.18                                \\
-\# Crypto.com Exchange (Futures) & ETHUSD-240329      & \$2,286.18                         & 2224.96 USD                              & -2.678\%                           & 0.29\%                              & -                                       & \$58,845                                   & \$895.27                                \\
-\# Crypto.com Exchange (Futures) & ETHUSD-240223      & \$2,249.95                         & 2224.92 USD                              & -1.112\%                           & 0.17\%                              & -                                       & \$27,557                                   & \$1,247.37                              \\
-\# Deribit                       & ETH-29MAR24        & \$2,296.00                         & 2228.59 USD                              & -2.936\%                           & 0.02\%                              & 3 months                                & \$88,364,731                               & \$2,438,537.07                          \\
-\# Deribit                       & ETH-28JUN24        & \$2,363.75                         & 2228.59 USD                              & -5.718\%                           & 0.01\%                              & 6 months                                & \$35,776,949                               & \$1,152,627.40                          \\
-\# Deribit                       & ETH-26JAN24        & \$2,247.75                         & 2228.59 USD                              & -0.852\%                           & 0.02\%                              & 19 days                                 & \$34,172,788                               & \$2,694,255.34                          \\
-\# Deribit                       & ETH-27SEP24        & \$2,414.50                         & 2228.59 USD                              & -7.700\%                           & 0.02\%                              & 9 months                                & \$22,332,082                               & \$781,745.26                            \\
-\# Deribit                       & ETH-12JAN24        & \$2,232.25                         & 2228.59 USD                              & -0.164\%                           & 0.01\%                              & 5 days                                  & \$10,281,174                               & \$1,626,945.44                          \\
-\# Deribit                       & ETH-23FEB24        & \$2,273.25                         & 2228.59 USD                              & -1.965\%                           & 0.08\%                              & about 2 months                          & \$10,187,446                               & \$484,690.68                            \\
-\# Deribit                       & ETH-27DEC24        & \$2,463.00                         & 2228.59 USD                              & -9.517\%                           & 0.21\%                              & 12 months                               & \$6,513,788                                & \$630,519.38                            \\
-\# Deribit                       & ETH-19JAN24        & \$2,235.50                         & 2228.59 USD                              & -0.309\%                           & 0.03\%                              & 12 days                                 & \$1,564,812                                & \$1,319,273.13                          \\
-\# HTX Futures                   & ETH\_CQ            & \$2,298.00                         & 2228.66 USD                              & -3.018\%                           & 0.01\%                              & 3 months                                & \$1,130,370                                & \$562,732.95                            \\
-\# HTX Futures                   & ETH\_CW            & \$2,233.11                         & 2228.54 USD                              & -0.205\%                           & 0.01\%                              & 4 days                                  & \$49,870                                   & \$481,669.51                            \\
-\# HTX Futures                   & ETH\_NW            & \$2,242.45                         & 2228.66 USD                              & -0.615\%                           & 0.35\%                              & 11 days                                 & \$31,200                                   & \$302,572.28                            \\
-\# Kraken (Futures)              & FI\_ETHUSD\_240329 & \$2,300.00                         & 2228 USD                                 & -3.130\%                           & 0.11\%                              & 3 months                                & \$4,415,821                                & \$29,062.00                             \\
-\# Kraken (Futures)              & FI\_ETHUSD\_240628 & \$2,366.30                         & 2228 USD                                 & -5.845\%                           & 0.25\%                              & 6 months                                & \$3,541,749                                & \$40,752.00                             \\
-\# Kraken (Futures)              & FF\_ETHUSD\_240329 & \$2,314.00                         & 2228 USD                                 & -3.717\%                           & 0.13\%                              & 3 months                                & \$1,584                                    & \$0.45                                  \\
-\# Kraken (Futures)              & FF\_ETHUSD\_240126 & \$2,254.90                         & 2228 USD                                 & -1.193\%                           & 0.09\%                              & 19 days                                 & \$299                                      & \$36.69                                 \\
-\# Kraken (Futures)              & FI\_ETHUSD\_240126 & \$2,254.15                         & 2228 USD                                 & -1.160\%                           & 0.24\%                              & 19 days                                 & \$48,594                                   & \$10,184.00                             \\
-\# OKX (Futures)                 & ETH-USD-240329     & \$2,296.78                         & 2228.71 USD                              & -2.964\%                           & 0.01\%                              & 3 months                                & \$61,638,000                               & \$13,362,284.32                         \\
-\# OKX (Futures)                 & ETH-USD-240628     & \$2,370.47                         & 2228.67 USD                              & -5.982\%                           & 0.03\%                              & 6 months                                & \$29,831,250                               & \$8,793,848.00                          \\
-\# OKX (Futures)                 & ETH-USDT-240329    & \$2,296.43                         & 2226.75 USDT                             & -2.985\%                           & 0.02\%                              & 3 months                                & \$20,412,503                               & \$5,701,567.75                          \\
-\# OKX (Futures)                 & ETH-USD-240112     & \$2,231.34                         & 2228.71 USD                              & -0.118\%                           & 0.01\%                              & 5 days                                  & \$7,456,500                                & \$8,340,344.15                          \\
-\# OKX (Futures)                 & ETH-USDT-240628    & \$2,366.59                         & 2227.15 USDT                             & -5.845\%                           & 0.02\%                              & 6 months                                & \$3,885,976                                & \$3,157,980.17                          \\
-\# OKX (Futures)                 & ETH-USD-240119     & \$2,233.42                         & 2228.71 USD                              & -0.211\%                           & 0.03\%                              & 12 days                                 & \$3,212,320                                & \$3,467,988.47                          \\
-\# OKX (Futures)                 & ETH-USDT-240112    & \$2,229.86                         & 2226.75 USDT                             & -0.089\%                           & 0.01\%                              & 5 days                                  & \$2,298,019                                & \$3,571,348.57                          \\
-\# OKX (Futures)                 & ETH-USDT-240119    & \$2,235.50                         & 2226.75 USDT                             & -0.341\%                           & 0.01\%                              & 12 days                                 & \$690,474                                  & \$2,364,707.49                          \\
-\# OKX (Futures)                 & ETH-USDC-240329    & \$2,296.52                         & 2227.93 USDC                             & -3.020\%                           & 0.38\%                              & 3 months                                & -                                          & \$55,373.71                             \\
-\# OKX (Futures)                 & ETH-USDC-240112    & \$2,251.63                         & 2227.89 USDC                             & -1.088\%                           & 0.09\%                              & 5 days                                  & -                                          & \$5,770.92                              \\
-\# OKX (Futures)                 & ETH-USDC-240119    & \$2,251.87                         & 2227.93 USDC                             & -1.037\%                           & 0.14\%                              & 12 days                                 & -                                          & \$9.01                                  \\
-\# XT.COM (Derivatives)          & ETH\_USD\_240628   & \$2,368.07                         & -                                        & -                                  & 0.04\%                              & 6 months                                & -                                          & \$2,929,170.00                          \\
-\# XT.COM (Derivatives)          & ETH\_USD\_240329   & \$2,299.63                         & -                                        & -2.350\%                           & 0.01\%                              & 3 months                                & -                                          & \$2,698,030.00                          \\
-\# XT.COM (Derivatives)          & ETH\_USDT\_240329  & \$2,301.93                         & -                                        & -                                  & 0.03\%                              & 3 months                                & -                                          & \$124,645.12                            \\
-\# OKX (Futures)                 & BTC-USDT-240112    & \$44,080.50                        & -0.157\%                                 & 0.03\%                             & 5 days                              & \$3,560,036                             & \$12,798,332.26                            & \multicolumn{1}{l}{}                    \\
-\# OKX (Futures)                 & BTC-USDT-240223    & \$44,781.65                        & -1.720\%                                 & 0.08\%                             & about 2 months                      & \$2,960,896                             & \$711,132.65                               & \multicolumn{1}{l}{}                    \\
-\# OKX (Futures)                 & BTC-USDT-240119    & \$44,192.36                        & -0.409\%                                 & 0.04\%                             & 12 days                             & \$975,364                               & \$4,235,395.39                             & \multicolumn{1}{l}{}                    \\
-\# OKX (Futures)                 & BTC-USDC-240628    & \$46,788.02                        & -5.958\%                                 & 0.39\%                             & 6 months                            & -                                       & \$17,320.92                                & \multicolumn{1}{l}{}                    \\
-\# OKX (Futures)                 & BTC-USDC-240119    & \$44,137.13                        & -0.298\%                                 & 0.1\%                              & 12 days                             & -                                       & \$6,285.13                                 & \multicolumn{1}{l}{}                    \\
-\# OKX (Futures)                 & BTC-USDC-240329    & \$45,832.15                        & -3.985\%                                 & 0.31\%                             & 3 months                            & -                                       & \$1,874.53                                 & \multicolumn{1}{l}{}                    \\
-\# OKX (Futures)                 & BTC-USDC-240112    & \$44,107.04                        & -0.242\%                                 & 0.13\%                             & 5 days                              & -                                       & \$9,765.30                                 & \multicolumn{1}{l}{}                    \\
-\# XT.COM (Derivatives)          & BTC\_USD\_240329   & \$45,380.70                        & -3.586\%                                 & 0.01\%                             & 3 months                            & -                                       & \$33,113,000.00                            & \multicolumn{1}{l}{}                    \\
-\# XT.COM (Derivatives)          & BTC\_USD\_240628   & \$46,797.20                        & -                                        & 0.01\%                             & 6 months                            & -                                       & \$31,000,200.00                            & \multicolumn{1}{l}{}                    \\
-\# XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & 0.06\%                             & 3 months                            & -                                       & \$20,870,477.00                            & \multicolumn{1}{l}{}
+ Binance (Futures)             & ETHUSD\_240329     & \$2,300.60                         & 2228.81 USD                              & -3.121\%                           & 0.01\%                              & 3 months                                & \$72,215,240                               & \$16,326,927.83                         \\
+ Binance (Futures)             & ETHUSD\_240628     & \$2,368.79                         & 2229.03 USD                              & -5.900\%                           & 0.02\%                              & 6 months                                & \$11,183,360                               & \$4,224,925.26                          \\
+ Binance (Futures)             & ETHUSDT\_240329    & \$2,300.46                         & 2227.81 USDT                             & -3.110\%                           & 0.02\%                              & -                                       & \$35,040                                   & \$6,902,127.72                          \\
+ Binance (Futures)             & ETHUSDT\_240628    & \$2,360.43                         & 2227.81 USDT                             & -5.572\%                           & 0.03\%                              & -                                       & \$4,604                                    & \$4,303,853.27                          \\
+ BitMEX (Derivative)           & ETHUSDH24          & \$2,452.60                         & 2228.01 USD                              & -9.157\%                           & 0.02\%                              & 3 months                                & \$4,341,286                                & \$537,210.05                            \\
+ BitMEX (Derivative)           & ETHH24             & \$2,217.23                         & 0.05 XBT                                 & +0.457\%                           & 0.37\%                              & 3 months                                & \$1,575,478                                & \$69,244.08                             \\
+ BTSE (Futures)                & ETH-240628         & \$2,350.05                         & 2367.26 USD                              & +0.732\%                           & 0.75\%                              & 6 months                                & \$2,517,764                                & \$49,845.75                             \\
+ BTSE (Futures)                & ETH-240329         & \$2,297.48                         & 2298.78 USD                              & +0.057\%                           & 0.23\%                              & 3 months                                & \$2,081,180                                & \$49,130.96                             \\
+ Bybit (Futures)               & ETHUSDM24          & \$2,357.45                         & 2229.63 USD                              & -5.422\%                           & 0.05\%                              & 6 months                                & -                                          & \$448,716.00                            \\
+ Bybit (Futures)               & ETHUSDH24          & \$2,287.90                         & 2229.53 USD                              & -2.551\%                           & 0.06\%                              & 3 months                                & -                                          & \$294,007.00                            \\
+ Bybit (Futures)               & ETH-26JAN24        & \$2,243.65                         & 2229.46 USDC                             & -0.668\%                           & 0.05\%                              & 19 days                                 & -                                          & \$286,245.77                            \\
+ Bybit (Futures)               & ETH-12JAN24        & \$2,231.66                         & 2229.51 USDC                             & -0.132\%                           & 0.03\%                              & 5 days                                  & -                                          & \$99,683.25                             \\
+ Bybit (Futures)               & ETH-28JUN24        & \$2,368.66                         & 2229.46 USDC                             & -5.910\%                           & 0.1\%                               & 6 months                                & -                                          & \$97,357.35                             \\
+ Bybit (Futures)               & ETH-19JAN24        & \$2,238.21                         & 2229.51 USDC                             & -0.424\%                           & 0.06\%                              & 12 days                                 & -                                          & \$92,957.40                             \\
+ Bybit (Futures)               & ETH-23FEB24        & \$2,274.64                         & 2229.51 USDC                             & -2.019\%                           & 0.03\%                              & about 2 months                          & -                                          & \$68,610.65                             \\
+ Bybit (Futures)               & ETH-29MAR24        & \$2,297.48                         & 2229.51 USDC                             & -2.993\%                           & 0.03\%                              & 3 months                                & -                                          & \$36,926.81                             \\
+ Bybit (Futures)               & ETH-27SEP24        & \$2,420.24                         & 2229.46 USDC                             & -7.915\%                           & 0.12\%                              & 9 months                                & -                                          & \$30,008.99                             \\
+ Crypto.com Exchange (Futures) & ETHUSD-240628      & \$2,347.68                         & 2224.96 USD                              & -5.227\%                           & 0.24\%                              & -                                       & \$24,573,170                               & \$822.63                                \\
+ Crypto.com Exchange (Futures) & ETHUSD-240126      & \$2,234.13                         & 2224.96 USD                              & -0.410\%                           & 0.14\%                              & -                                       & \$79,732                                   & \$742.18                                \\
+ Crypto.com Exchange (Futures) & ETHUSD-240329      & \$2,286.18                         & 2224.96 USD                              & -2.678\%                           & 0.29\%                              & -                                       & \$58,845                                   & \$895.27                                \\
+ Crypto.com Exchange (Futures) & ETHUSD-240223      & \$2,249.95                         & 2224.92 USD                              & -1.112\%                           & 0.17\%                              & -                                       & \$27,557                                   & \$1,247.37                              \\
+ Deribit                       & ETH-29MAR24        & \$2,296.00                         & 2228.59 USD                              & -2.936\%                           & 0.02\%                              & 3 months                                & \$88,364,731                               & \$2,438,537.07                          \\
+ Deribit                       & ETH-28JUN24        & \$2,363.75                         & 2228.59 USD                              & -5.718\%                           & 0.01\%                              & 6 months                                & \$35,776,949                               & \$1,152,627.40                          \\
+ Deribit                       & ETH-26JAN24        & \$2,247.75                         & 2228.59 USD                              & -0.852\%                           & 0.02\%                              & 19 days                                 & \$34,172,788                               & \$2,694,255.34                          \\
+ Deribit                       & ETH-27SEP24        & \$2,414.50                         & 2228.59 USD                              & -7.700\%                           & 0.02\%                              & 9 months                                & \$22,332,082                               & \$781,745.26                            \\
+ Deribit                       & ETH-12JAN24        & \$2,232.25                         & 2228.59 USD                              & -0.164\%                           & 0.01\%                              & 5 days                                  & \$10,281,174                               & \$1,626,945.44                          \\
+ Deribit                       & ETH-23FEB24        & \$2,273.25                         & 2228.59 USD                              & -1.965\%                           & 0.08\%                              & about 2 months                          & \$10,187,446                               & \$484,690.68                            \\
+ Deribit                       & ETH-27DEC24        & \$2,463.00                         & 2228.59 USD                              & -9.517\%                           & 0.21\%                              & 12 months                               & \$6,513,788                                & \$630,519.38                            \\
+ Deribit                       & ETH-19JAN24        & \$2,235.50                         & 2228.59 USD                              & -0.309\%                           & 0.03\%                              & 12 days                                 & \$1,564,812                                & \$1,319,273.13                          \\
+ HTX Futures                   & ETH\_CQ            & \$2,298.00                         & 2228.66 USD                              & -3.018\%                           & 0.01\%                              & 3 months                                & \$1,130,370                                & \$562,732.95                            \\
+ HTX Futures                   & ETH\_CW            & \$2,233.11                         & 2228.54 USD                              & -0.205\%                           & 0.01\%                              & 4 days                                  & \$49,870                                   & \$481,669.51                            \\
+ HTX Futures                   & ETH\_NW            & \$2,242.45                         & 2228.66 USD                              & -0.615\%                           & 0.35\%                              & 11 days                                 & \$31,200                                   & \$302,572.28                            \\
+ Kraken (Futures)              & FI\_ETHUSD\_240329 & \$2,300.00                         & 2228 USD                                 & -3.130\%                           & 0.11\%                              & 3 months                                & \$4,415,821                                & \$29,062.00                             \\
+ Kraken (Futures)              & FI\_ETHUSD\_240628 & \$2,366.30                         & 2228 USD                                 & -5.845\%                           & 0.25\%                              & 6 months                                & \$3,541,749                                & \$40,752.00                             \\
+ Kraken (Futures)              & FF\_ETHUSD\_240329 & \$2,314.00                         & 2228 USD                                 & -3.717\%                           & 0.13\%                              & 3 months                                & \$1,584                                    & \$0.45                                  \\
+ Kraken (Futures)              & FF\_ETHUSD\_240126 & \$2,254.90                         & 2228 USD                                 & -1.193\%                           & 0.09\%                              & 19 days                                 & \$299                                      & \$36.69                                 \\
+ Kraken (Futures)              & FI\_ETHUSD\_240126 & \$2,254.15                         & 2228 USD                                 & -1.160\%                           & 0.24\%                              & 19 days                                 & \$48,594                                   & \$10,184.00                             \\
+ OKX (Futures)                 & ETH-USD-240329     & \$2,296.78                         & 2228.71 USD                              & -2.964\%                           & 0.01\%                              & 3 months                                & \$61,638,000                               & \$13,362,284.32                         \\
+ OKX (Futures)                 & ETH-USD-240628     & \$2,370.47                         & 2228.67 USD                              & -5.982\%                           & 0.03\%                              & 6 months                                & \$29,831,250                               & \$8,793,848.00                          \\
+ OKX (Futures)                 & ETH-USDT-240329    & \$2,296.43                         & 2226.75 USDT                             & -2.985\%                           & 0.02\%                              & 3 months                                & \$20,412,503                               & \$5,701,567.75                          \\
+ OKX (Futures)                 & ETH-USD-240112     & \$2,231.34                         & 2228.71 USD                              & -0.118\%                           & 0.01\%                              & 5 days                                  & \$7,456,500                                & \$8,340,344.15                          \\
+ OKX (Futures)                 & ETH-USDT-240628    & \$2,366.59                         & 2227.15 USDT                             & -5.845\%                           & 0.02\%                              & 6 months                                & \$3,885,976                                & \$3,157,980.17                          \\
+ OKX (Futures)                 & ETH-USD-240119     & \$2,233.42                         & 2228.71 USD                              & -0.211\%                           & 0.03\%                              & 12 days                                 & \$3,212,320                                & \$3,467,988.47                          \\
+ OKX (Futures)                 & ETH-USDT-240112    & \$2,229.86                         & 2226.75 USDT                             & -0.089\%                           & 0.01\%                              & 5 days                                  & \$2,298,019                                & \$3,571,348.57                          \\
+ OKX (Futures)                 & ETH-USDT-240119    & \$2,235.50                         & 2226.75 USDT                             & -0.341\%                           & 0.01\%                              & 12 days                                 & \$690,474                                  & \$2,364,707.49                          \\
+ OKX (Futures)                 & ETH-USDC-240329    & \$2,296.52                         & 2227.93 USDC                             & -3.020\%                           & 0.38\%                              & 3 months                                & -                                          & \$55,373.71                             \\
+ OKX (Futures)                 & ETH-USDC-240112    & \$2,251.63                         & 2227.89 USDC                             & -1.088\%                           & 0.09\%                              & 5 days                                  & -                                          & \$5,770.92                              \\
+ OKX (Futures)                 & ETH-USDC-240119    & \$2,251.87                         & 2227.93 USDC                             & -1.037\%                           & 0.14\%                              & 12 days                                 & -                                          & \$9.01                                  \\
+ XT.COM (Derivatives)          & ETH\_USD\_240628   & \$2,368.07                         & -                                        & -                                  & 0.04\%                              & 6 months                                & -                                          & \$2,929,170.00                          \\
+ XT.COM (Derivatives)          & ETH\_USD\_240329   & \$2,299.63                         & -                                        & -2.350\%                           & 0.01\%                              & 3 months                                & -                                          & \$2,698,030.00                          \\
+ XT.COM (Derivatives)          & ETH\_USDT\_240329  & \$2,301.93                         & -                                        & -                                  & 0.03\%                              & 3 months                                & -                                          & \$124,645.12                            \\
+ OKX (Futures)                 & BTC-USDT-240112    & \$44,080.50                        & -0.157\%                                 & 0.03\%                             & 5 days                              & \$3,560,036                             & \$12,798,332.26                            & \multicolumn{1}{l}{}                    \\
+ OKX (Futures)                 & BTC-USDT-240223    & \$44,781.65                        & -1.720\%                                 & 0.08\%                             & about 2 months                      & \$2,960,896                             & \$711,132.65                               & \multicolumn{1}{l}{}                    \\
+ OKX (Futures)                 & BTC-USDT-240119    & \$44,192.36                        & -0.409\%                                 & 0.04\%                             & 12 days                             & \$975,364                               & \$4,235,395.39                             & \multicolumn{1}{l}{}                    \\
+ OKX (Futures)                 & BTC-USDC-240628    & \$46,788.02                        & -5.958\%                                 & 0.39\%                             & 6 months                            & -                                       & \$17,320.92                                & \multicolumn{1}{l}{}                    \\
+ OKX (Futures)                 & BTC-USDC-240119    & \$44,137.13                        & -0.298\%                                 & 0.1\%                              & 12 days                             & -                                       & \$6,285.13                                 & \multicolumn{1}{l}{}                    \\
+ OKX (Futures)                 & BTC-USDC-240329    & \$45,832.15                        & -3.985\%                                 & 0.31\%                             & 3 months                            & -                                       & \$1,874.53                                 & \multicolumn{1}{l}{}                    \\
+ OKX (Futures)                 & BTC-USDC-240112    & \$44,107.04                        & -0.242\%                                 & 0.13\%                             & 5 days                              & -                                       & \$9,765.30                                 & \multicolumn{1}{l}{}                    \\
+ XT.COM (Derivatives)          & BTC\_USD\_240329   & \$45,380.70                        & -3.586\%                                 & 0.01\%                             & 3 months                            & -                                       & \$33,113,000.00                            & \multicolumn{1}{l}{}                    \\
+ XT.COM (Derivatives)          & BTC\_USD\_240628   & \$46,797.20                        & -                                        & 0.01\%                             & 6 months                            & -                                       & \$31,000,200.00                            & \multicolumn{1}{l}{}                    \\
+ XT.COM (Derivatives)          & BTC\_USDT\_240329  & \$45,369.50                        & -                                        & 0.06\%                             & 3 months                            & -                                       & \$20,870,477.00                            & \multicolumn{1}{l}{}
 \end{tabular}}

### 2024-02-18 analyzeZeroBetaStraddles.py
init

@@ -1,0 +1,509 @@
+"""
+Construct Portfolio of a Long Call and a Delta Hedge
+Rebalanced Daily
+Analyze PnL 
+
+Then go for Put, Call Spread, Put Spread, Straddle
+
+So for each instrument, observe over time and adjust Portfolio
+
+Use associated Future for risk-free rate
+Get risk-free rate for the time of the instrument!
+"""
+
+from numpy.core.defchararray import center
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import math
+import pdb
+from datetime import timedelta
+from pathlib import Path
+from math import ceil
+from src.plots import simple_3d_plot, plot_performance, grouped_boxplot
+from src.blackscholes import Call, Put
+from src.helpers import assign_groups, load_expiration_price_history, compute_vola
+from src.zero_beta_straddles import get_call_beta, get_combined_beta, get_put_beta, get_straddle_weights, get_beta
+
+def greeks(options, iv_var_name):
+    """
+
+    """
+    #First, use BS Call value function to get Dollar Value for Call Parameters
+    options['instrument_price_on_expiration'] = options.apply(lambda x: Call.Price(x['expiration_price'], x['strike'], 0, x[iv_var_name], 0) if x['is_call'] == 1 else Put.Price(x['expiration_price'], x['strike'], 0, x[iv_var_name], 0), axis = 1)
+    options['instrument_price'] = options.apply(lambda x: Call.Price(x['spot'], x['strike'], 0, x[iv_var_name], x['tau']) if x['is_call'] == 1 else Put.Price(x['spot'], x['strike'], 0, x[iv_var_name], x['tau']), axis = 1)
+    options['delta'] = options.apply(lambda x: Call.Delta(x['spot'], x['strike'], 0, x[iv_var_name], x['tau']) if x['is_call'] == 1 else Put.Delta(x['spot'], x['strike'], 0, x[iv_var_name], x['tau']), axis = 1)
+    
+    # Calculate Call Beta, Put Beta for every day. Both calculations work
+    options['old_beta'] = options.apply(lambda x: get_call_beta(x['spot'], x['strike'], 0, x[iv_var_name], x['tau']) if x['is_call'] == 1 else np.nan, axis = 1)
+    options['beta'] = options.apply(lambda x: get_beta(x['spot'], x['strike'], 0, x[iv_var_name], x['tau'], x['is_call']), axis = 1)
[…]

### 2024-02-18 compare.py

@@ -1,0 +1,175 @@
+# Compare Performance of analyzeZeroBetaStraddles
+
+import pandas as pd
+import numpy as np
+
+import matplotlib.pyplot as plt
+import pdb
+import time
+import csv
+import statsmodels.api as sm
+import pylab
+from scipy import stats 
+from scipy.stats import ttest_1samp
+from pathlib import Path
+
+def QQ_plot(data, nn, fname):
+    # Source: https://stackoverflow.com/questions/13865596/quantile-quantile-plot-using-scipy
+    fig = plt.figure(figsize = (10,7))
+
+    # Sort as increasing
+    y = np.sort(data)
+    
+    # Compute sample mean and std
+    mean, std = np.mean(y), np.std(y)
+    
+    # Compute set of Normal quantiles
+    ppf = stats.t(df = nn, loc = mean, scale = std).ppf
+    #ppf = stats.norm(loc=mean, scale=std).ppf # Inverse CDF
+    N = len(y)
+    x = [ppf( i/(N+2) ) for i in range(1,N+1)]
+
+    # Make the QQ scatter plot
+    plt.scatter(x, y)
+    
+    # Plot diagonal line
+    dmin, dmax = np.min([x,y]), np.max([x,y])
+    diag = np.linspace(dmin, dmax, 1000)
+    plt.plot(diag, diag, color='red', linestyle='--')
+    plt.gca().set_aspect('equal')
+    
+    # Add labels
+    plt.xlabel('Normal quantiles')
+    plt.ylabel('Sample quantiles')
+    plt.show()
+    #plt.savefig(fname)
+
+
+def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
+    """
+    Groups returns by levels of moneyness (in steps of 0.05)
+    performs kernel density estimation
+    performs a left-sided t-test on a population mean of 0
+    """
+    Path(out_path).mkdir(parents=True, exist_ok=True)
+    pdct = {}
+    df = dat.copy(deep = True)
+
+    # Make up some dummy data and test
+    #xx = np.random.normal(loc=5.0, scale=0.5, size=1000)
+    #QQ_plot(xx)
+
+    for mn in df['moneyness'].sort_values().unique():
+        if mn >= min_moneyness and mn <= max_moneyness:
+
+            fig = plt.figure(figsize = (20, 14))
[…]

### 2024-02-18 src/brc.py

@@ -1,0 +1,571 @@
+import sshtunnel
+import pymongo
+import datetime
+import pandas as pd
+import numpy as np
+import websockets
+import asyncio
+import pdb
+import matplotlib.pyplot as plt
+from helpers import decompose_future_name # src.
+from plots import group_plot # src.
+import json
+from bson.json_util import dumps # dump Output
+#from src.vola_plots import trisurf, vola_surface_interpolated
+#from src.helpers import decompose_instrument_name
+
+# Todo: connection doesnt stop atm
+class BRC:
+    def __init__(self, collection_name):
+        
+        self.MONGO_HOST = '35.205.115.90'
+        self.MONGO_DB   = 'cryptocurrency'
+        self.MONGO_USER = 'winjules2'
+        self.MONGO_PASS = ''
+        self.PORT = 27017
+        print('\nGoing Local')
+        self.client = pymongo.MongoClient('localhost', 27017) 
+        self.db = self.client[self.MONGO_DB]
+        self.collection_name = collection_name #'deribit_transactions'
+        self.collection = self.db[self.collection_name]
+        print('using collection: ', self.collection_name)
+        self._generate_stats()
+        
+
+    def _server(self):
+        self.server = sshtunnel.SSHTunnelForwarder(
+            self.MONGO_HOST,
+            ssh_username=self.MONGO_USER,
+            ssh_password=self.MONGO_PASS,
+            remote_bind_address=('127.0.0.1', self.PORT)
+            )
+        return self.server
+
+    def _start(self):
+        #self.server = self._server()
+        #self.server.start()
+        return True
+
+    def _stop(self):
+        #self.server.stop()
+        return True
+
+    def _filter_by_timestamp(self, starttime, endtime):        
+        """
+        Example:
+        starttime = datetime.datetime(2020, 4, 19, 0, 0, 0)
+        endtime = datetime.datetime(2020, 4, 20, 0, 0, 0)
+        """
+        ts_high     = round(endtime.timestamp() * 1000)
+        ts_low      = round(starttime.timestamp() * 1000)
+        return ts_high, ts_low
+
+    def _generate_stats(self):
+        print('\n Established Server Connection')
+        print('\n Size in GB: ', self.db.command('dbstats')['dataSize'] * 0.000000001) 
+        
+        # Get first and last element:
+        last_ele = self.collection.find_one(
+        sort=[( '_id', pymongo.DESCENDING )]
+        )
+
+        first_ele = self.collection.find_one(
[…]

### 2024-02-18 src/bs_vola.py

@@ -1,0 +1,25 @@
+import numpy as np
+from scipy.stats import norm
+N = norm.cdf
+
+def bs_call(S, K, T, r, vol):
+    d1 = (np.log(S/K) + (r + 0.5*vol**2)*T) / (vol*np.sqrt(T))
+    d2 = d1 - vol * np.sqrt(T)
+    return S * norm.cdf(d1) - np.exp(-r * T) * K * norm.cdf(d2)
+
+def bs_vega(S, K, T, r, sigma):
+    d1 = (np.log(S / K) + (r + 0.5 * sigma ** 2) * T) / (sigma * np.sqrt(T))
+    return S * norm.pdf(d1) * np.sqrt(T)
+
+def find_vol(target_value, S, K, T, r, *args):
+    MAX_ITERATIONS = 200
+    PRECISION = 1.0e-5
+    sigma = 0.5
+    for i in range(0, MAX_ITERATIONS):
+        price = bs_call(S, K, T, r, sigma)
+        vega = bs_vega(S, K, T, r, sigma)
+        diff = target_value - price  # our root
+        if (abs(diff) < PRECISION):
+            return sigma
+        sigma = sigma + diff/vega # f(x) / f'(x)
+    return sigma # value wasn't found, return best guess so far

### 2024-02-18 src/helpers.py

@@ -1,0 +1,155 @@
+import datetime
+import math
+import pandas as pd
+import numpy as np
+import matplotlib.pyplot as plt
+import pdb
+
+def decompose_instrument_name(_instrument_names, tradedate, round_tau_digits = 4):
+    """
+    Input:
+        instrument names, as e.g. pandas column / series
+        in this format: 'BTC-6MAR20-8750-C'
+    Output:
+        Pandas df consisting of:
+            Decomposes name of an instrument into
+            Strike K
+            Maturity Date T
+            Type (Call | Put)
+    """
+    try:
+        _split = _instrument_names.str.split('-', expand = True)
+        _split.columns = ['base', 'maturity', 'strike', 'is_call'] 
+        
+        # call == 1, put == 0 in is_call
+        _split['is_call'] = _split['is_call'].replace('C', 1)
+        _split['is_call'] = _split['is_call'].replace('P', 0)
+
+        # Calculate Tau; being time to maturity
+        #Error here: time data '27MAR20' does not match format '%d%b%y'
+        _split['maturitystr'] = _split['maturity'].astype(str)
+        # Funny Error: datetime does recognize MAR with German AE instead of A
+        maturitydate        = list(map(lambda x: datetime.datetime.strptime(x, '%d%b%y') + datetime.timedelta(hours = 8), _split['maturitystr'])) # always 8 o clock
+        reference_date      = tradedate.dt.date #list(map(lambda x: x.dt.date, tradedate))#tradedate.dt.date # Round to date, else the taus are all unique and the rounding creates different looking maturities
+        Tdiff               = pd.Series(maturitydate).dt.date - reference_date #list(map(lambda x: x - reference_date, maturitydate))
+        Tdiff               = Tdiff[:len(maturitydate)]
+        sec_to_date_factor   = 60*60*24
+        _Tau                = list(map(lambda x: (x.days + (x.seconds/sec_to_date_factor)) / 365, Tdiff))#Tdiff/365 #list(map(lambda x: x.days/365, Tdiff)) # else: Tdiff/365
+        _split['tau']       = _Tau
+        _split['tau']       = round(_split['tau'], round_tau_digits)
+
+        # Strike must be float
+        _split['strike'] =    _split['strike'].astype(float)
+
+        # Add maturitydate for trading simulation
[…]

### 2024-02-18 src/plots.py

@@ -1,0 +1,89 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+import matplotlib.dates as mdates
+
+def simple_3d_plot(x,y,z, save_path, xlabel = 'Tau', ylabel = 'Moneyness', zlabel = 'Fitted IV', zlim_min = 0, zlim_max = 4):
+
+    fig = plt.figure()
+    ax = fig.add_subplot(111, projection='3d')
+    ax.scatter(x,y,z)
+    ax.set_xlabel(xlabel)
+    ax.set_ylabel(ylabel)
+    ax.set_zlabel(zlabel)
+    plt.xlim(0, 1)
+    plt.ylim(0, 2)
+    ax.set_zlim(zlim_min, zlim_max)
+    plt.show()
+    #plt.savefig(save_path, transparent = True)
+
+def plot_performance(performance_overview, time_var_name, crash_resistant, _dir):
+    """
+    time_var_name = 'rounded_tau' or 'nweeks'
+    plot_fname = 'plots/' + 'zero_beta_straddle_tau=' + tau_label + '.png'
+    """
+    performance_overview['day'] = pd.to_datetime(performance_overview['day'])
+    for tau in performance_overview[time_var_name].unique():
+
+        tau_sub = performance_overview.loc[performance_overview[time_var_name] == tau]
+        tau_sub.sort_values('day', inplace = True)
+        tau_label = str(tau)
+
+        # Group per Week
+        # @Todo: Now relate this plot to the IV over Realized Vola premium!!
+        fig = plt.figure(figsize = (20,14))
+        plt.gca().xaxis.set_major_formatter(mdates.DateFormatter('%m/%d/%Y'))
+        plt.gca().xaxis.set_major_locator(mdates.DayLocator())
+            
+        plt.subplot(2, 1, 1)
+        plt.plot(tau_sub['day'], tau_sub['combined_payoff'], label = tau_label)
+        plt.ylim(-5000, 5000)
+        
+        plt.subplot(2,1,2)
+        plt.plot(tau_sub['day'], tau_sub['combined_ret'], label = tau_label)
+        plt.ylim(-2, 2)
+
+        plt.gcf().autofmt_xdate()
+        plt.legend()
+        if crash_resistant:
+            fname = _dir + 'zero_beta_straddle_' + time_var_name + '=' + tau_label + '.png'
+        else:
[…]

### 2024-02-18 src/vola_plots.py

@@ -1,0 +1,154 @@
+import datetime
+import pandas as pd
+import numpy as np
+import scipy.interpolate as interp
+import matplotlib.pyplot as plt
+
+def trisurf(x, y, z, xlab, ylab, zlab, filename, blockplots):
+    # This is the data we have: vola ~ tau + moneyness
+    # https://stackoverflow.com/questions/9170838/surface-plots-in-matplotlib
+    fig = plt.figure()
+    ax = fig.gca(projection='3d')
+    ax.set_xlabel('Moneyness')
+    ax.set_ylabel('Tau')
+    ax.set_zlabel('IV')
+    #x, y = np.meshgrid(x, y)
+
+    df = pd.DataFrame({'x': x, 'y': y, 'z': z})
+    surf = ax.plot_trisurf(df.x, df.y, df.z, cmap=plt.cm.jet, linewidth=0.1)
+    fig.colorbar(surf, shrink=0.5, aspect=5)   
+    plt.title('Empirical Vola Smile') 
+    plt.savefig(filename)
+    plt.draw()
+    #plt.show(block = blockplots)
+
+def vola_surface_interpolated(df, out_path = 'out/volasurface/', moneyness_min = 0.7, moneyness_max = 1.3):
+
+
+    # Adjust date
+    df['date_short'] = df['date'].apply(lambda x: datetime.datetime.strftime(x, '%Y-%m-%d'))
+    
+    # Adjust mark iv
+    df['mark_iv'] = df['mark_iv']/100
+
+    print('Using Calls only for Vola Surface. Restricting Moneyness to ', moneyness_min, ' - ',moneyness_max)
+    for d in df['date_short'].unique():
+        
+        sub = df.loc[df['date_short'] == d]
+
+        fig = plt.figure(figsize=(12, 7)) 
+        ax = fig.gca(projection='3d')   # set up canvas for 3D plotting
+
+        sub = sub.loc[(sub['mark_iv'] >= 0) & (sub['mark_iv'] <= 3) & (sub['is_call'] == 1) & (sub['moneyness'] >= moneyness_min) & (sub['moneyness'] <= moneyness_max)]
+
+        X = sub['moneyness'].tolist()
+        Y = sub['tau'].tolist()
+        Z = sub['mark_iv'].tolist()
+        
+        plotx,ploty, = np.meshgrid(np.linspace(np.min(X),np.max(X),50),\
+                            np.linspace(np.min(Y),np.max(Y),50))
+        
[…]

### 2024-02-18 src/zero_beta_straddles.py

@@ -1,0 +1,162 @@
+from matplotlib.pyplot import thetagrids
+import numpy as np
+from scipy.stats import norm
+
+from src.blackscholes import Call, Put, d1
+import pdb
+
+# Easier Version for both, Call and Put Betas together
+def get_beta(s, k, r, vol, tau, is_call, _lambda = 0, beta_s = 1):
+    """
+    Calculate Black Scholes Beta for Put OR Call
+    as Equation (11) in Shumway: Expected Option Returns
+
+    s: spot
+    k: strike
+    r: interest rate
+    vol: IV
+    tau: time-to-maturity
+    is_call: boolean. 1 for call, 0 for put
+    _lambda: dividend yield is always 0 for BTC, ETH
+    beta_s: always equals1, following page 14 Shumway
+    """
+
+    N = norm.cdf
+    if is_call == 1:
+        price = Call.Price(s, k, r, vol, tau)
+        delta = Call.Delta(s, k, r, vol, tau)
+    elif is_call == 0:
+        price = Put.Price(s, k, r, vol, tau)
+        delta = Put.Delta(s, k, r, vol, tau)
+    else:
+        raise NotImplementedError('Neither Put nor Call')
+
+    beta = (s/price) * delta * beta_s
+    return beta
+
+# Easier Version for both, Call and Put Betas together
+def get_combined_beta(p1, p2, delta1, delta2, spot ,_lambda = 0, beta_s = 1):
+    """
+    Calculate Black Scholes Beta for Put OR Call
+    as Equation (11) in Shumway: Expected Option Returns
+
+    s: spot
+    k: strike
+    r: interest rate
+    vol: IV
+    tau: time-to-maturity
+    is_call: boolean. 1 for call, 0 for put
+    _lambda: dividend yield is always 0 for BTC, ETH
+    beta_s: always equals1, following page 14 Shumway
+    """
+
+    beta = (spot/(p1 - p2)) * (delta1 - delta2) * beta_s
+    return beta
+
+def get_call_beta(s, k, r, vol, tau, _lambda = 0, beta_s = 1):
+    """
+    Calculate Black Scholes Call Beta
+    as Equation (11) in Shumway: Expected Option Returns
+
+    s: spot
+    k: strike
+    r: interest rate
+    vol: IV
+    tau: time-to-maturity
+    _lambda: dividend yield is always 0 for BTC, ETH
+    beta_s: always equals1, following page 14 Shumway
+    """
+
+    N = norm.cdf
[…]

### 2024-02-20 written/paper.tex
QQ plots and table links

@@
 \singlespacing 
-abstract
+We provide insight into fundamental components of the crypto asset markets via derivatives written on Bitcoin and Ether.
+We use perpetual swap contracts to derive a proxy for the risk free rate in crypto asset markets.
+The interest rate serves as a benchmark for the performance of a range of beta-neutral option portfolios.
+The empirical option performance confirms the existence of large (volatility) risk premia for at-the-money and in-the-money options.
+We cannot confirm similar risk premia for other levels of moneyness.
+We compare the observed risk premia to those of equity options and find our results to be related but larger in size.
 
  \medskip
- \textbf{Keywords:} Bitcoin, Ether, Deribit, risk, risk premium, volatility premium, option, hedging  \\
+ \textbf{Keywords:} Bitcoin, Ether, Deribit, risk, risk premium, volatility premium, option  \\
  \indent \textbf{JEL Classification:} C14, C50, G10  \\
@@
 Among the futures trading, perpetual instruments have historically been and currently are the most liquid instruments.
-As depicted in Table \ref{table:stats}, measured by the aggregate open interest and aggregate trading volume the market share of Perpetual Futures dwarfs the market share of (classic) Futures for both, Bitcoin and Ether.
+As depicted in Table~\ref{table:stats}, measured by the aggregate open interest and aggregate trading volume the market share of Perpetual Futures dwarfs the market share of (classic) Futures for both, Bitcoin and Ether.
 While it would be possible to use a yield from a long-short futures position (e.g.
@@
 Crypto exchanges often provide a so-called perpetual future, which is a synthetic (typically cash-settled instrument) whose return is tied to the underlying via a funding rate.
-Most exchanges (quote here) provide perpetual futures for Bitcoin and Ether.
+Most exchanges provide perpetual futures for Bitcoin and Ether (Table~\ref{table:btc_futures} and~\ref{table:eth_futures}).
 The price of each perpetual future is linked to the underlying by adjusting a variable interest rate, called the funding rate, that fluctuates depending on the deviation between the price of the perpetual future and the underlying.
@@
 In such a trade, the trader shorts (longs) the perpetual future if the funding rate is positive (negative) and simulateously buys (sells) the underlying such that the market delta of the combined position is zero.
+In order calculate the proxy interest rate, we hold the short perpetual futures position and the long underlying constant.
+This also has the advantage of minimizing transaction cost and market impact, since the position can be entered slowly.
 
@@
 
-The actual annualized returns of such a carry trade are summarized in the table below.
+The actual annualized returns of such a carry trade are summarized in Table~\ref{table:annual_interest_rates}.
 2019 returns are annualized due to the start on 1st of May 2019 of perpetual futures on Deribit.
@@
 
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+\label{Interest Rates inferred from Perpetual Futures}
+\href{https://github.com/QuantLet/Option-Risk-Premia/blob/master/plot_funding_rates.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Funding Rates}
 
@@
 
-Regarding matters of data authenticity, we refer to our previous paper regarding the study of Bitcoin option data (Winkel and Härdle, 2023).
+Regarding matters of data authenticity, we refer to our previous paper regarding the study of option data (Winkel and Härdle, 2023).
 The most likely negative factor that could affect our data quality is wash trading. 
@@
 
-We find the returns of the zero-beta-straddles to be t-distributed and conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero. 
+We refer to the QQ plots of the daily returns of the zero-beta portfolios versus the t-distribution to conclude that the returns are in fact t-distributed (Figure 5 and Figure 6).
+We conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero.
 The null hypothesis is rejected on a high significance level for ATM and slightly ITM options. 
-In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level.
-The results hold across model variations, vanilla and crash resistant, with or without fees.
+In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table 7 and Table 8).
+The results hold across model variations, vanilla and crash resistant, with or without fees (Figure 7-14).
 
@@
 Additionally, we find a similar premium for slightly ITM contracts.
-Shumway et. al reported an average return of around -3.15\% per week.% whereas XYZ \% is attributable to the volatility premium.
+Shumway et. al reported an average return of around -3.15 percent per week.
 
@@
     \centering
+    \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/btc/out/qq.png}
+    \captionof{figure}{BTC Portfolio}
+    \centering
+    \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/eth/out/qq.png}
+     \captionof{figure}{ETH Portfolio}
+
+\end{minipage}
+
+\label{QQ Plot of beta-neutral daily Returns vs. t-Distribution}
+\href{https://github.com/QuantLet/Option-Risk-Premia/blob/master/compare.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,QQ}
+
+\begin{minipage}{\textwidth}
+    \centering
     \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
@@
 
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+\label{Boxplots of Daily Returns (BTC)}
+\href{https://github.com/QuantLet/Option-Risk-Premia/blob/master/analyzeZeroBetaStraddles.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,analyzeZeroBetaStraddles}
 
@@
 
-\label{ATM Term Structure}
-\href{https://github.com/QuantLet/BitcoinOptions/blob/master/main.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,Main}
+\label{Boxplots of Daily Returns (ETH)}
+\href{https://github.com/QuantLet/Option-Risk-Premia/blob/master/analyzeZeroBetaStraddles.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,analyzeZeroBetaStraddles}
 
@@
 Further research: 
-- Evidence for leverage effect
+- We could use a similar procedure to search for evidence for leverage effect
 

### 2024-02-20 compare.py
qq plots

@@ -54,11 +54,17 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     Path(out_path).mkdir(parents=True, exist_ok=True)
     pdct = {}
     df = dat.copy(deep = True)
+    
+    
+    vec = df['combined_ret_daily'].loc[(df['moneyness'] >= min_moneyness) & (df['moneyness'] <= max_moneyness)]
+    wins = stats.mstats.winsorize((1+vec)**2 - 1, limits=[0.01, 0.01]) # 0.025 is pretty good
+    sm.qqplot(wins, stats.t, distargs=(len(wins),), loc = wins.mean(), scale = wins.std())
+    plt.ylim(-1,1)
+    plt.xlim(-1,1)
+    plt.savefig(out_path + '/qq.png', transparent = True)
+    #stats.probplot(wins, dist="norm", plot=pylab)
 
-    # Make up some dummy data and test
-    #xx = np.random.normal(loc=5.0, scale=0.5, size=1000)
-    #QQ_plot(xx)
-
+    pdb.set_trace()
     for mn in df['moneyness'].sort_values().unique():
         if mn >= min_moneyness and mn <= max_moneyness:
 
@@ -110,7 +116,11 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     pylab.show()
     
     # Working test for T-distribution
-    #sm.qqplot(vec_standardized, stats.t, distargs=(vec.shape[0],), loc = vec.mean(), scale = vec.std())
+    vec = df['combined_ret_daily']
+    wins = stats.mstats.winsorize(vec, limits=[0.05, 0.05])
+    sm.qqplot(wins, stats.t, distargs=(vec.shape[0],), loc = wins.mean(), scale = wins.std())
+
+    stats.probplot(wins, dist="norm", plot=pylab)
     """
 
 
@@ -123,7 +133,7 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
 
 # Config
 # Choose BTC or ETH
-base = 'eth/'
+base = 'btc/'#'eth/'
 
 
 pf = 'performance_overview.csv'
@@ -155,7 +165,6 @@ for df in [vanilla_fee, vanilla_no_fee, crash_resistant_fee, crash_resistant_no_
[…]

### 2024-02-20 written/paper.tex
more table links

@@
 The null hypothesis is rejected on a high significance level for ATM and slightly ITM options. 
-In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table 7 and Table 8).
+In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table~\ref{table:btc_t_stats} and ~\ref{table:eth_t_stats}).
 The results hold across model variations, vanilla and crash resistant, with or without fees (Figure 7-14).

### 2024-03-11 compare.py
kde plot adjustment

@@ -64,7 +64,7 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     plt.savefig(out_path + '/qq.png', transparent = True)
     #stats.probplot(wins, dist="norm", plot=pylab)
 
-    pdb.set_trace()
+    #pdb.set_trace()
     for mn in df['moneyness'].sort_values().unique():
         if mn >= min_moneyness and mn <= max_moneyness:
 
@@ -72,9 +72,10 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
             higher = round(mn + 0.05, 2)
             sub = df.loc[(df['moneyness'] <= higher) & (df['moneyness'] >= mn)]
             sub['combined_ret_daily'].plot.kde()
-            plt.title('n = ' + str(sub.shape[0]))
+            # Title deactivated for paper plots
+            #plt.title('n = ' + str(sub.shape[0]))
             plt.xlim((-1, 1))
-            plt.savefig(out_path + '/moneyness>=' + str(mn) + '&moneyness<=' + str(higher) + '.png')
+            plt.savefig(out_path + '/moneyness>=' + str(mn) + '&moneyness<=' + str(higher) + '.png', transparent = True)
             t_stat, p_value = ttest_1samp(sub['combined_ret_daily'], popmean=0, alternative = 'less', nan_policy = 'omit') #, alternative = 'less'
             print(sub.describe())
             print('Moneyness Level: ', mn)
@@ -99,7 +100,7 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
     sub['combined_ret_daily'].plot.kde()
     plt.title('n = ' + str(sub.shape[0]))
     plt.xlim((-1, 1))
-    plt.savefig(out_path + '/moneyness_between_95_and_105' + '.png')
+    plt.savefig(out_path + '/moneyness_between_95_and_105' + '.png', transparent = True)
 
     """
     pdb.set_trace()
@@ -133,7 +134,7 @@ def ttest(dat, out_path, min_moneyness = 0.7, max_moneyness = 1.3):
 
 # Config
 # Choose BTC or ETH
-base = 'btc/'#'eth/'
+base = 'eth/' # 'btc/'
 
 
 pf = 'performance_overview.csv'
[…]

### 2024-03-11 analyzeZeroBetaStraddles.py
pre and post filtering distributions displayed

@@ -141,8 +141,8 @@ def analyze_portfolio(dat, week, iv_var_name, center_on_expiration_price, first_
     # (main.py uses dat['index_price'] for moneyness )
     sub['moneyness'] = round(sub['strike'] / sub['spot'], 2)
 
-    # Restrict Moneyness
-    sub = sub.loc[(sub['moneyness'] <= 1.3) & (sub['moneyness'] >= 0.7) & (sub['tau'] <= 0.3)]
+    # Restrict Moneyness / already happening in parent function
+    #sub = sub.loc[(sub['moneyness'] <= 1.3) & (sub['moneyness'] >= 0.7) & (sub['tau'] <= 0.3)]
     
     # Min 4 days to maturity
     existing_options = sub.copy(deep = True)
@@ -178,7 +178,7 @@ def analyze_portfolio(dat, week, iv_var_name, center_on_expiration_price, first_
     
     for i in range(len(exist)): #.loc[options['is_call'] == 1]
         try:
-
+            
             #@Hint: We can also match by index here as each index in existing_options correspoinds to missing_options!
             # Why does call_df have less columns than exist?!
             #print('Why does call_df have less columns than exist?!')
@@ -225,7 +225,6 @@ def analyze_portfolio(dat, week, iv_var_name, center_on_expiration_price, first_
 
             #print('need to adjust straddle weights for FOTM Options too!!')
             call_weight, put_weight = get_straddle_weights(call_df['beta'], put_df['beta'])
-
 
             # Test implementing the adjusted beta calculation for crash-resistant Straddles
             if crash_resistant:
@@ -322,7 +321,7 @@ def analyze_portfolio(dat, week, iv_var_name, center_on_expiration_price, first_
         except Exception as e:
             print(e)
             print('Error!')
-            pdb.set_trace()
+            #pdb.set_trace()
     print('done')
     return out_dct
 
@@ -371,12 +370,24 @@ if __name__ == '__main__':
             out_dir = out_dir_start + 'no_fees/'
             plot_dir = plot_dir_start + 'no_fees/'
 
+        # config
+        base_currency = 'btc'
+        print("###")
+        print(base_currency)
+        print("###")
+        if base_currency == 'eth':
+            f = 'eth/out/raw_deribit_transactions_eth.csv'
+        elif base_currency == 'btc':
+            f = 'btc/out/raw_deribit_transactions.csv'
+        else: 
[…]

### 2024-03-11 written/paper.tex
green ink correction in progress

--- 2024-02-20 written/paper.tex
@@
 
-\title{Empirical Option Returns and the risk-free Rate in Crypto Asset Markets}
+\title{Option Returns and the risk-free Rate in Crypto Asset Markets}
 \author{Julian Winkel\footnote{International Research Training Group 1792;
@@
 \singlespacing 
-We provide insight into fundamental components of the crypto asset markets via derivatives written on Bitcoin and Ether.
+We examine the empirical returns of options written on Bitcoin and Ether in the light of fundamental asset pricing mechanics. In principle, beta-neutral portfolios should yield the risk-free rate.
 We use perpetual swap contracts to derive a proxy for the risk free rate in crypto asset markets.
-The interest rate serves as a benchmark for the performance of a range of beta-neutral option portfolios.
+The risk free rate serves as a benchmark for the performance of a range of beta-neutral option portfolios.
 The empirical option performance confirms the existence of large (volatility) risk premia for at-the-money and in-the-money options.
@@
 On 10 January 2024, the United States Securities and Exchange Commission approved the listing and trading of a range of spot bitcoin exchange-traded product (ETP) shares (Gensler, 2024).
-In other markets, structured Bitcoin (BTC) products have been available for years and retailers have been able to mine or buy Bitcoin since its inception following Nakamoto, 2009.
+In other markets, structured Bitcoin (BTC) products have been available for years and retailers have been able to mine or buy Bitcoin since its inception following Nakamoto (2009).
 Yet, despite the ongoing integration into established markets, fundamental questions about crypto asset markets remain unclear:
@@
 
-Crypto exchanges often provide a so-called perpetual future, which is a synthetic (typically cash-settled instrument) whose return is tied to the underlying via a funding rate.
-Most exchanges provide perpetual futures for Bitcoin and Ether (Table~\ref{table:btc_futures} and~\ref{table:eth_futures}).
+Almost all large crypto exchanges provide a so-called perpetual future, which is a synthetic instrument whose return is tied to the underlying via a funding rate.
+An overview of perpetual futures for Bitcoin and Ether on relevant exchanges is provided in Table~\ref{table:btc_futures} and~\ref{table:eth_futures}.
 The price of each perpetual future is linked to the underlying by adjusting a variable interest rate, called the funding rate, that fluctuates depending on the deviation between the price of the perpetual future and the underlying.
@@
 
-The funding rate on \href{https://www.deribit.com/kb/deribit-linear-perpetual}{Deribit} is calculated as follows:
-
-Instruments, such as inverse options, futures and perpetual futures, have a Mark Price $M$.
-The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth (quote:
-Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system.
+Deribit refers to their perpetual futures written on BTC and ETH as inverse perpetual futures, because they are settled in terms of the underlying.
+The funding rate on \href{https://www.deribit.com/kb/deribit-inverse-perpetual}{Deribit} is calculated as follows (Deribit Inverse Perpetual, 2024):
+
+%(quote Deribit: Mark price of an options contract is the current value of the option as calculated by the Deribit risk management system.
 Usually, this is the average of the best bid and best ask price.
-However, for risk management purposes, there is price bandwidth in place.
-).
+However, for risk management purposes, there is price bandwidth in place.).
+Instruments, such as (inverse) options, futures and (inverse) perpetual futures, have a Mark Price $M$.
+The Mark Price at a time is defined as the average of the highest bid and lowest ask price within an unspecified bandwidth.
 The Deribit Index $D$, which is an equally weighted Index of BTC/USD pairs across different exchanges, is used in conjunction with the Mark Price to calculate the Premium Rate $P$ of the Perpetual Future $F$ over the Deribit Index.
@@
 \centering
-{\begin{tabular}{lll}
+{\begin{tabular}{rrr}
 \hline
@@
 We construct zero-beta portfolios by pairing a call option and a put option to a straddle and adjusting the weights so that the sum of option betas yields zero.
-The straddle's payoff $r_v$ is depicted in Equation 4, consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
-The weight $\theta$ is found by solving Equation 5 through Equation 6.
-The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\Delta$, the Black-Scholes option price $C$ as depicted in Equation 7.
+The straddle's payoff $r_v$ is depicted in (4), consisting of the payoff of the call $r_c$ and the payoff of the put $r_p$.
+The weight $\theta$ is found by solving (5) through (6).
+The (market) beta of a call (put) can be calculated through knowledge of the spot price $s$, the option delta $\Delta$, the Black-Scholes option price $C$ as depicted in (7).
 % and the market beta $\beta_m (=1)$
 The underlying data are executed transactions.
-All option greeks remain constant except time-to-maturity.
-Any transaction has a time-to-maturity $\tau$ adjusted so that it would coincide with settlement time.
+All option greeks remain constant except time-to-maturity $\tau$.
+Any transaction has $\tau$ adjusted so that it would coincide with settlement time.
 All options are bought and held until settlement at 10am UTC.
@@
 We inspect the densities (via Kernel Density Estimation) of the daily returns and argue that they are t-distributed.
+Alternatively, \href{https://quantinar.com/course/144/tukeys-g-and-h-transformations}{Tukey's g- and h-transformations} could be used.
 For each level of moneyness $m$, we construct an interval $[m, m + 0.05]$.
@@
 
-We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events.
+We consider the possibility that if a volatility premium is found in the vanilla Zero-Beta-Straddles, then it may attributed to the risk of Black Swan events (Taleb, 2007).
 Therefore we repeat the analysis for a set of "crash-resistant" zero-beta straddles.
@@
 
-We use the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
+We collect data from the \href{blockchain-research-center.de}{Blockchain Research Center} to retrieve a complete set of all transactions conducted on Deribit's options written on Bitcoin and Ether. 
 In addition to the option data set, we are provided with a complete set of funding rates for the perpetual future of Bitcoin and Ether since 1 June 2019.
@@
 Regarding the Bitcoin (Ether) data, we drop 0.9\% (1.7\%) of observations due to the IV restriction
-We drop 17\% (20.1\%) of observations due to the moneyness restriction
+We drop 17\% (20.1\%) of observations due to the moneyness restriction.
 Overall, we have 5,028,945 (2,283,869) observations. Post filtering, 4,150,778 (1,809,762) observations remain in the set.
+
+BTC Distribution pre filtering:
+\begin{tabular}{lr}
+\toprule
+{} &          iv \\
+\midrule
+count &  5028945.00 \\
+mean  &        0.90 \\
+std   &        0.35 \\
+min   &        0.00 \\
+25\%   &        0.69 \\
+50\%   &        0.83 \\
+75\%   &        1.03 \\
+max   &        5.00 \\
+\bottomrule
+\end{tabular}
+
+BTC Distribution post filtering:
+\begin{tabular}{lr}
+\toprule
+{} &          iv \\
+\midrule
+count &  4150778.00 \\
+mean  &        0.86 \\
+std   &        0.29 \\
+min   &        0.10 \\
+25\%   &        0.67 \\
+50\%   &        0.80 \\
+75\%   &        0.98 \\
+max   &        2.50 \\
+\bottomrule
+\end{tabular}
+
+ETH Distribution pre filtering:
+\begin{tabular}{lr}
+\toprule
+{} &          iv \\
+\midrule
+count &  2275011.00 \\
+mean  &        1.12 \\
+std   &        0.42 \\
+min   &        0.00 \\
+25\%   &        0.87 \\
+50\%   &        1.02 \\
+75\%   &        1.27 \\
+max   &        5.00 \\
+\bottomrule
+\end{tabular}
+
+ETH post filtering:
+\begin{tabular}{lr}
+\toprule
+{} &          iv \\
+\midrule
+count &  1802556.00 \\
+mean  &        1.06 \\
+std   &        0.34 \\
+min   &        0.11 \\
+25\%   &        0.84 \\
+50\%   &        0.98 \\
+75\%   &        1.18 \\
+max   &        2.50 \\
+\bottomrule
+\end{tabular}
 
@@
 The reasoning behind the low risk assessment is that we are solely dealing with actual transactions associated with transaction cost.
-At the time of the writing, the transaction cost is 0.0003 BTC which is per current spot of 51,765 USD results in a fee of 15.5 USD.
+At 18 February 2024, the transaction cost is 0.0003 BTC which is per current spot of 51,765 USD results in a fee of 15.5 USD.
 Such fees, even without consideration of spreads, make wash trading from a trader's perspective prohibitively expensive.
@@
 
-We refer to the QQ plots of the daily returns of the zero-beta portfolios versus the t-distribution to conclude that the returns are in fact t-distributed (Figure 5 and Figure 6).
-We conduct a left-sided t-test under the null hypothesis of a population mean greater or equal to zero.
+We refer to the QQ plots of the daily returns of the zero-beta portfolios versus the $t$-distribution to conclude that the returns are in fact $t$-distributed (Figure 5 and Figure 6).
+We conduct a left-sided $t$-test under the null hypothesis of a population mean greater or equal to zero.
 The null hypothesis is rejected on a high significance level for ATM and slightly ITM options. 
-In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table 7 and Table 8).
+In the BTC (ETH) case, the hypotheses tests are rejected for the levels of moneyness in the interval $[0.98, 1.15]$ ($[0.99, 1.17]$) on a 95\% significance level (Table~\ref{table:btc_t_stats} and~\ref{table:eth_t_stats}).
 The results hold across model variations, vanilla and crash resistant, with or without fees (Figure 7-14).
+The amount of observations per batch of moneyness range between a minimum of 47 (OTM) and a maximum of 3498 (ATM) in the BTC case and between 205 and 3085 in the ETH case.
 
@@
 (2000) and Bakshi et al.
-(2001), namely is the existence of a premium for ATM contracts.
+(2001), namely the existence of a premium for ATM contracts.
 Additionally, we find a similar premium for slightly ITM contracts.
-Shumway et. al reported an average return of around -3.15 percent per week.
+Shumway et. al (2000) reported an average return of around -3.15 percent per week.
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{BTC - Performance - Vanilla - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{BTC - Performance - Vanilla - Fees}
+    \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/btc/out/vanilla/no_fees/density/moneyness>=1.05&moneyness<=1.1.png}
+    \captionof{figure}{BTC KDE. 2908 Observations fall in the Interval.}
+    \centering
+    \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/eth/out/vanilla/no_fees/density/moneyness>=1.05&moneyness<=1.1.png}
+     \captionof{figure}{ETH KDE. 2545 Observations fall in the Interval.}
+
+\end{minipage}
+
+\label{Kernel Density Estimator of the Batch in 1.05 and 1.1}
+\href{https://github.com/QuantLet/Option-Risk-Premia/blob/master/compare.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,KDE}
+
+\begin{minipage}{\textwidth}
+    \centering
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Daily Returns grouped by Moneyness -  Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Daily Returns grouped by Moneyness -  Vanilla - Fees}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{BTC - Performance - Crash Resistant - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{BTC - Performance - Crash Resistant - Fees}
+    \includegraphics[width=5.in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{BTC - Daily Returns grouped by Moneyness -  Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5.in]{/Users/julian/src/bitcoin-vola-premium/btc/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{BTC - Daily Returns grouped by Moneyness -  Crash Resistant - Fees}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{ETH - Performance - Vanilla - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{ETH - Performance - Vanilla - Fees}
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Daily Returns grouped by Moneyness -  Vanilla - No Fees}
+    \centering
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/vanilla/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Daily Returns grouped by Moneyness -  Vanilla - Fees}
 
@@
     \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
-    \captionof{figure}{ETH - Performance - Crash Resistant - No Fees}
-    \centering
-    \includegraphics[width=5.6in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
-     \captionof{figure}{ETH - Performance - Crash Resistant - Fees}
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/no_fees/boxplot_combined_ret_daily_over_moneyness_.png}
+    \captionof{figure}{ETH - Daily Returns grouped by Moneyness -  Crash Resistant - No Fees}
+    \centering
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/eth/plots/crash_resistant/fees/boxplot_combined_ret_daily_over_moneyness_.png}
+     \captionof{figure}{ETH - Daily Returns grouped by Moneyness -  Crash Resistant - Fees}
 
@@
 \section{Conclusion}
+
+Difference between ETH and BTC annualized Funding Rate due to Liquidity.
 
@@
 
+\leavevmode\hypertarget{ref-deribit_perpetuals}{}%
+Deribit Inverse Perpetual (2024).
+\url{https://www.deribit.com/kb/deribit-inverse-perpetual}. Accessed 28 February 2024.
+
 \leavevmode\hypertarget{sec-approval}{}%
@@
 Shumway, Tyler and Coval, Joshua D., Expected Option Returns (June 2000). Available at SSRN: \url{https://ssrn.com/abstract=189840} or \url{http://dx.doi.org/10.2139/ssrn.189840}.
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{taleb}{}%
+Taleb, Nassim Nicholas. The Black Swan: the Impact of the Highly Improbable. New York: Random House, 2007.
 

### 2024-03-11 written/paper.tex
progress correcting green ink

@@
   Institute for Studies in Economics, Xiamen University, Xiamen, China;
-  Dept. Information Management and Finance, National Chiao Tung
+  Dept. Information Management and Finance, National Yang Ming Chiao Tung
   University, Hsinchu, Taiwan, ROC; Dept. Mathematics and Physics,
-  Charles University, Prague, Czech Republic, Grants -- DFG IRTG 1792
+  Charles University, Prague, Czech Republic; Institute for Digital Assets, Romania; Grants -- DFG IRTG 1792
   and the Czech Science Foundation's grant no. 19-28231X / CAS XDA
@@
 
-One of the most fundamental concepts in mathematical finance is the existence of a risk-free rate and a risky asset. 
+One of the most fundamental assumptions in asset pricing and indeed a conceptional pillar of mathematical finance is the existence of a risk-free rate and a risky underlying. 
 While crypto assets are well-known for their riskiness, the existence of a risk-free rate has not been established in this new market. 
@@
 
-In order to apply concepts of mathematical finance onto crypto assets, it is paramount to develop a risk-free rate - or at least a low-risk rate whose residual risk may converge to zero in time. 
+In order to apply pricing concepts of theoretical finance onto crypto assets, it is paramount to develop a risk-free rate - or at least a low-risk rate whose residual risk may converge to zero in time.
 An interesting candidate for a low-risk bond in the crypto asset space would be staking, which is the validation of transactions under the risk of losing a principal (the stake).
 Evidently, only crypto assets which follow a Proof-of-Stake (PoS) consensus mechanism instead of a Proof-of-Work (PoW) consensus mechanism can be used for staking.
-At the time, this is still a minor share of the crypto asset universe.
+At the time, PoS-based assets represent a minor share of the crypto asset universe.
 We include one of those, Ether, in our experiment.
 However, we figure that a multitude of risks is still present in staking, such as the risk of hacks, software bugs, slashing or blockchain congestions and subsequent reduction of stakes.
-Another approach to develop a risk-free rate would be lending in the DeFi space. Yet, this space may be vulnerable to similar risks as staking through hacks or software bugs in smart contracts.
+Another approach to develop a risk-free rate would be lending in the DeFi space (Liu et al., 2024).
+Yet, this space may be vulnerable to similar risks as staking through hacks or software bugs in smart contracts.
 
@@
 
-BTC Distribution pre filtering:
-\begin{tabular}{lr}
-\toprule
-{} &          iv \\
-\midrule
-count &  5028945.00 \\
-mean  &        0.90 \\
-std   &        0.35 \\
-min   &        0.00 \\
-25\%   &        0.69 \\
-50\%   &        0.83 \\
-75\%   &        1.03 \\
-max   &        5.00 \\
-\bottomrule
-\end{tabular}
-
-BTC Distribution post filtering:
-\begin{tabular}{lr}
-\toprule
-{} &          iv \\
-\midrule
-count &  4150778.00 \\
-mean  &        0.86 \\
-std   &        0.29 \\
-min   &        0.10 \\
-25\%   &        0.67 \\
-50\%   &        0.80 \\
-75\%   &        0.98 \\
-max   &        2.50 \\
-\bottomrule
-\end{tabular}
-
-ETH Distribution pre filtering:
-\begin{tabular}{lr}
-\toprule
-{} &          iv \\
-\midrule
-count &  2275011.00 \\
-mean  &        1.12 \\
-std   &        0.42 \\
-min   &        0.00 \\
-25\%   &        0.87 \\
-50\%   &        1.02 \\
-75\%   &        1.27 \\
-max   &        5.00 \\
-\bottomrule
-\end{tabular}
-
-ETH post filtering:
-\begin{tabular}{lr}
-\toprule
-{} &          iv \\
-\midrule
-count &  1802556.00 \\
-mean  &        1.06 \\
-std   &        0.34 \\
-min   &        0.11 \\
-25\%   &        0.84 \\
-50\%   &        0.98 \\
-75\%   &        1.18 \\
-max   &        2.50 \\
-\bottomrule
-\end{tabular}
+\begin{table}[ht]
+\resizebox{\textwidth}{!}{\begin{tabular}{lrrrrr}
+\hline
+\textbf{}         & \multicolumn{1}{l}{\textbf{BTC Pre-Filtering}} & \multicolumn{1}{l}{\textbf{BTC Post-Filtering}} & \multicolumn{1}{l}{\textbf{ETH Pre-Filtering}} & \multicolumn{1}{l}{\textbf{ETH Post-Filtering}} \\
+\hline
+\hline
+% Count             	  & 5028945    	& 4150778                         & 2275011                      & 1802556                       \\
+ Mean               	& 0.90                  & 0.86                            & 1.12                           & 1.06                                              \\
+ Std                   & 0.35                         & 0.29                           & 0.42                           & 0.34                                  \\
+ Min                  & 0                            & 0.10                             & 0                           & 0.11                                    \\
+ 25\%               & 0.69                         & 0.67                            & 0.87                           & 0.84                                                 \\
+ 50\%                & 0.83                         & 0.80                             & 1.02                           & 0.98                                          \\
+ 75\%               & 1.03                         & 0.98                            & 1.27                         & 1.18                                             \\
+ Max                 & 5.00                              & 2.50                             & 5.00                           & 2.50                               
+\end{tabular}}
+\caption{IV Summary Statistics Pre and Post Filtering}
+\label{btc_eth_iv_summary}
+\end{table}
+
+%
+%
+%ETH Distribution pre filtering:
+%\begin{tabular}{lr}
+%\toprule
+%{} &          iv \\
+%\midrule
+%count &  2275011.00 \\
+%mean  &        1.12 \\
+%std   &        0.42 \\
+%min   &        0.00 \\
+%25\%   &        0.87 \\
+%50\%   &        1.02 \\
+%75\%   &        1.27 \\
+%max   &        5.00 \\
+%\bottomrule
+%\end{tabular}
+%
+%ETH post filtering:
+%\begin{tabular}{lr}
+%\toprule
+%{} &          iv \\
+%\midrule
+%count &  1802556.00 \\
+%mean  &        1.06 \\
+%std   &        0.34 \\
+%min   &        0.11 \\
+%25\%   &        0.84 \\
+%50\%   &        0.98 \\
+%75\%   &        1.18 \\
+%max   &        2.50 \\
+%\bottomrule
+%\end{tabular}
+%
+%BTC Distribution pre filtering:
+%\begin{tabular}{lr}
+%\toprule
+%{} &          iv \\
+%\midrule
+%count &  5028945.00 \\
+%mean  &        0.90 \\
+%std   &        0.35 \\
+%min   &        0.00 \\
+%25\%   &        0.69 \\
+%50\%   &        0.83 \\
+%75\%   &        1.03 \\
+%max   &        5.00 \\
+%\bottomrule
+%\end{tabular}
+%
+%BTC Distribution post filtering:
+%\begin{tabular}{lr}
+%\toprule
+%{} &          iv \\
+%\midrule
+%count &  4150778.00 \\
+%mean  &        0.86 \\
+%std   &        0.29 \\
+%min   &        0.10 \\
+%25\%   &        0.67 \\
+%50\%   &        0.80 \\
+%75\%   &        0.98 \\
+%max   &        2.50 \\
+%\bottomrule
+%\end{tabular}
 
@@
     \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/btc/out/qq.png}
-    \captionof{figure}{BTC Portfolio}
+    \captionof{figure}{QQ Plot of beta-neutral daily \textbf{BTC} Returns vs. $t$-Distribution}
     \centering
     \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/eth/out/qq.png}
-     \captionof{figure}{ETH Portfolio}
+     \captionof{figure}{QQ Plot of beta-neutral daily \textbf{ETH} Returns vs. $t$-Distribution}
 
@@
     \centering
-    \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/btc/out/vanilla/no_fees/density/moneyness>=1.05&moneyness<=1.1.png}
-    \captionof{figure}{BTC KDE. 2908 Observations fall in the Interval.}
-    \centering
-    \includegraphics[width=3.5in]{/Users/julian/src/bitcoin-vola-premium/eth/out/vanilla/no_fees/density/moneyness>=1.05&moneyness<=1.1.png}
-     \captionof{figure}{ETH KDE. 2545 Observations fall in the Interval.}
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/btc/out/vanilla/no_fees/density/moneyness>=1.05&moneyness<=1.1.png}
+    \captionof{figure}{Kernel Density Estimation over 2908 BTC Portfolio Returns for Moneyness in $[1.05, 1.1]$. }
+    \centering
+    \includegraphics[width=5in]{/Users/julian/src/bitcoin-vola-premium/eth/out/vanilla/no_fees/density/moneyness>=1.05&moneyness<=1.1.png}
+     \captionof{figure}{Kernel Density Estimation over 2545 ETH Portfolio Returns for Moneyness in $[1.05, 1.1]$}
 
@@
 
-\label{Kernel Density Estimator of the Batch in 1.05 and 1.1}
 \href{https://github.com/QuantLet/Option-Risk-Premia/blob/master/compare.py}{\hspace*{\fill} \raisebox{-1pt}{\includegraphics[scale=0.05]{/Users/julian/src/up/spd/written/logos/qletlogo_tr.png}}\,KDE}
@@
 Available at SSRN: \url{https://ssrn.com/abstract=267106} or \url{http://dx.doi.org/10.2139/ssrn.267106}.
+
+\hypertarget{refs}{}
+\leavevmode\hypertarget{liu}{}%
+Liu, F., Packham, N., Sepp, A. and Härdle WK (2024). Jump risk premia in the presence of clustered jumps. Available at SSRN 4735365.
 
